### 2024-10-27 Notes/Notes.tex
Creating the notes file

\documentclass[12pt,letterpaper]{article}
\usepackage{fullpage}
\usepackage[top=1.5cm, bottom=3.5cm, left=2.2cm, right=2.2cm]{geometry}
\usepackage{amsmath,amsthm,amsfonts,amssymb,amscd, esint}
\usepackage{lastpage}
\usepackage{enumerate}
\usepackage{fancyhdr}
\usepackage{mathrsfs}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{hyperref}
\usepackage[english]{babel}
\usepackage{lipsum}
\usepackage[table,xcdraw]{xcolor}
\usepackage{enumitem}
\usepackage{float}
\usepackage{chemfig}
\usepackage{yfonts}
\usepackage{tikz}
\usepackage{wrapfig}
\usepackage{url}
\usepackage{natbib}
\usepackage[normalem]{ulem}
\usepackage{multicol}
\useunder{\uline}{\ul}{}

%%%%%%%%%%%%%%% CODELISTINGS %%%%%%%%%%%%%%%%
\usepackage{listings}
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=t,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}

\lstset{style=mystyle}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newtheorem{definition}{Definition}
\newtheorem{observation}{Observation}
\newtheorem{reflection}{Reflection}
\newtheorem{PyPackage}{Package}
\newtheorem{book}{Book}

\newcommand{\HRule}[1]{\rule{\linewidth}{#1}}
\setcounter{tocdepth}{5}
\setcounter{secnumdepth}{5}

\setlength{\parindent}{0.0in}
\setlength{\parskip}{0.05in}

% Edit these as appropriate
\newcommand\course{}
\newcommand\subject{Final Degree Project}
\newcommand\degree{Bachelor's Degree in Physics}
\newcommand\documenttitle{Notes: Quantum State Exclusion - Temporal Name -}
\newcommand\NetIDb{Universitat Autònoma de Barcelona}

\begin{document}
\title{\vspace{4cm} \normalsize 
		\includegraphics[width = 0.25\textwidth]{GeneralSources/UABLogo.png}\\ [0.5cm]
		\textsc{\NetIDb}\\ [2.0cm]
		\HRule{0.5pt} \\
		\LARGE \textbf{\uppercase{\documenttitle}}
		\HRule{2pt} \\ [1.5cm]
		\normalsize \begin{tabular}{rcl}  % Create a right-left column alignment
        \textsc{Author} & : & \textsc{Sergio Castañeiras Morales} \\
        \textsc{Supervisor} & : & \textsc{Ramón Muñoz Tapia} \\
        \textsc{Co-Supervisor} & : & \textsc{Santiago Llorens Fernández}
    \end{tabular}
    \normalsize \vspace*{5\baselineskip}
		}

\date{2024-2025}

\author{\large \textsc{\subject} \\ \textsc{\degree}}

\begin{titlepage}
\clearpage\maketitle
\thispagestyle{empty}
\end{titlepage}

\newpage
\pagestyle{fancyplain}
\headheight 35pt
\lhead{\NetIDb}    
\rhead{\subject}
\cfoot{}
\rfoot{\small\thepage}
\headsep 1.5em

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%% DEFINITIONS %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{multicols}{2}
[
\section{Definitions}
]
\begin{definition}Yey\cite{Bandyopadhyay2014}
\end{definition}

\end{multicols}
\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%% BIBLIOGRAPHY %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliographystyle{plain}
\bibliography{references} 
%%%%%%%%

\end{document}

### 2025-01-02 Notes/Notes.tex
experimenting with picos

@@
 ]
-\begin{definition}Yey\cite{Bandyopadhyay2014}
+\begin{definition}
+\textbf{Completely positive map}: "Let $ A $ and $ B $ be C*-algebras. A linear map $ \phi: A \to B $ is called a \textit{positive map} if $ \phi $ maps positive elements to positive elements:
+\begin{align}
+a \geq 0 \implies \phi(a) \geq 0.
+\end{align}
+
+Any linear map $ \phi: A \to B $ induces another map
+\begin{align}
+\mathrm{id} \otimes \phi : \mathbb{C}^{k \times k} \otimes A \to \mathbb{C}^{k \times k} \otimes B
+\end{align}
+in a natural way.
+If $ \mathbb{C}^{k \times k} \otimes A $ is identified with the C*-algebra $ A^{k \times k} $ of $ k \times k $-matrices with entries in $ A $, then $ \mathrm{id} \otimes \phi $ acts as
+\begin{align}
+\begin{pmatrix}
+a_{11} & \cdots & a_{1k} \\
+\vdots & \ddots & \vdots \\
+a_{k1} & \cdots & a_{kk}
+\end{pmatrix}
+\mapsto
+\begin{pmatrix}
+\phi(a_{11}) & \cdots & \phi(a_{1k}) \\
+\vdots & \ddots & \vdots \\
+\phi(a_{k1}) & \cdots & \phi(a_{kk})
+\end{pmatrix}.
+\end{align}
+
+The map $ \phi $ is called \textit{k-positive} if $ \mathrm{id}_{\mathbb{C}^{k \times k}} \otimes \phi $ is a positive map, and \textit{completely positive} if $ \phi $ is $ k $-positive for all $ k $."\cite{completely_positive_map_Wikipedia}
+\end{definition}
+\begin{definition}\textbf{Kraus operator: } 
+\end{definition}
+
+\begin{definition}\label{innerProductDefinition}
+\textbf{Inner product}: Given a vector space $A$ and a field $F$ we define the an inner product $\langle \cdot , \cdot \rangle$ as $\langle \cdot , \cdot \rangle:A\times A\rightarrow F$ that satisfies the following properties.
+Given $x,y,z\in A$ and $\lambda,\mu\in F$:
+\begin{enumerate}
+\item Conjugate symmetry: $\langle x,y\rangle=(\langle y,x\rangle)^*$.
+\item Linearity: $\langle \lambda x+\mu y, z\rangle=\lambda\langle  x, z\rangle+\mu\langle  y, z\rangle$
+\item Positive-definiteness: $\langle x,x\rangle>0$ if $x\neq0$
+\end{enumerate}
+\end{definition}
+
+\begin{definition}
+\textbf{Inner product space}: Given a vector space $A$ and a field $F$ we define the  inner product space as the duple $(A,\langle \cdot , \cdot \rangle)$ such that  $\langle \cdot , \cdot \rangle:A\times A\rightarrow F$ is an inner product.
+\end{definition}
+
+\begin{definition}
+\textbf{Gram matrix}: Given a vector space $A$, a field $F$ , a set of vectors $\{v_i\}_{i=0}^n\subset A$ and an inner product space such that  $\langle \cdot , \cdot \rangle:A\times A\rightarrow F$  the Gram matrix $G$ is defined as the matrix $G\in F^{n\times n}$ whose entries are $g_{i,j}=\langle v_i,v_j\rangle$ i.e,
+\begin{align}
+G=\begin{pmatrix}
+\langle v_1,v_1\rangle & \hdots & \langle v_1,v_n\rangle\\
+\vdots & \ddots & \vdots\\
+\langle v_n,v_1\rangle & \hdots & \langle v_n,v_n\rangle
+\end{pmatrix}.
+\end{align}
+Due to the first property of the inner product definition \ref{innerProductDefinition} it is immediate that $G^\dagger =G$ in other word G is hemitian (trivial proof).
 \end{definition}

### 2025-01-02 Scripts/SquareRootMeasurement.py

@@ -1,0 +1,74 @@
+########################################################################################################
+#                                                                                                      #
+#  Project:  Physics TFG                                                                               #
+#  Author:   Sergio Castañeiras Morales                                                                #
+#  Date:     02/01/2025                                                                                #
+#  Purpose:  Testing the Square Root Measurement                                                       #
+#                                                                                                      #
+########################################################################################################
+import numpy
+import picos
+
+# defining sigma_y
+sigma_y=picos.Constant([[0, -1j],[1j,0]])
+
+# Show sigma_y
+print("Sigma_y = ",sigma_y)
+
+# print sigma_y dagger,
+print("Sigma_y dagger = ",sigma_y.H)
+
+#Creating a function that tells us weather a matrix is hermitian or not 
+def Hermitian(matrix):
+    return numpy.allclose(matrix.value, matrix.H.value)
+
+# Is 'sigma_y' hermitian
+print("Is sigma_y hermitian? ", Hermitian(sigma_y))
+
+# Lets create an hermitian we start by defining a non hermitian matrix '_P'
+_P = picos.Constant([
+[ 1 -1j, 2 +2j, 1 ],
+[ 3j, -2j, -1 -1j],
+[ 1 +2j, -0.5+1j, 1.5 ]])
+
+print("Is '_P' hermitian? ", Hermitian(_P))
+
+# now we construct P as _P*_P^dagger which ensures that P is hermitian
+
+P = (_P*_P.H).renamed("P")
+
+print("Is 'P' hermitian? ", Hermitian(P))
+
+# We do the same procedure with a Q matrix
+
+_Q = picos.Constant([
+[-1 -2j, 2j, 1.5 ],
+[ 1 +2j, -2j, 2.0-3j],
+[ 1 +2j, -1 +1j, 1 +4j]])
+Q = (_Q*_Q.H).renamed("Q")
+
+print("Is '_Q' hermitian? ", Hermitian(_P))
+
+print("Is 'Q' hermitian? ", Hermitian(P))
+
+"""
+# Define the problem.
+F = picos.Problem()
+Z = picos.ComplexVariable("Z", P.shape)
+F.set_objective("max", 0.5*picos.trace(Z + Z.H))
[…]

### 2025-01-03 Scripts/DensityMatricesAndPriorsClass.py
Implementing POVMs how cool is this

@@ -1,0 +1,49 @@
+########################################################################################################
+#                                                                                                      #
+#  Project:  Physics TFG                                                                               #
+#  Author:   Sergio Castañeiras Morales                                                                #
+#  Date:     03/01/2025                                                                                #
+#  Purpose:  Defining the DensityMaticesAndPriors class                                                #
+#                                                                                                      #
+########################################################################################################
+
+import UsefullFunctions
+import numpy as np 
+import picos
+
+class DensityMaticesAndPriors:
+    def __init__(self, NumberOfMatrices, MatrixDimension):
+        if not isinstance(MatrixDimension,int):
+            raise TypeError("The given MatrixDimension must be an Integer")
+        if not isinstance(NumberOfMatrices,int):
+            raise TypeError("The given NumberOfMatrices must be an Integer")
+        self.NumberOfMatrices   = NumberOfMatrices
+        self.MatrixDimension    = MatrixDimension
+    def to_dict(self):
+        return {
+            'NumberOfMatrices'   : self.NumberOfMatrices,
+            'MatrixDimension'    : self.MatrixDimension,
+            'PriorProbabilities' : UsefullFunctions.RandomSetOfProbabilities(self.NumberOfMatrices),
+            'DensityMatrices'    : UsefullFunctions.RandomSetOfDensityMatrices(self.NumberOfMatrices,self.MatrixDimension)
+        }
+    def __getitem__(self, key):
+        return self.to_dict()[key]
+
+    def getDesityMatrices(self):
+        return self.to_dict()['DensityMatrices']
+
+    def getPriorProbabilities(self):
+        return self.to_dict()['PriorProbabilities']
+
+    def getNumberOfMatrices(self):
+        return self.to_dict()['NumberOfMatrices']   
+
+    def getMatrixDimension(self):
+        return self.to_dict()['MatrixDimension']   
+
+    def __repr__(self):
+        PrintingText = "The working paramaters are:\n"
+        for iVariable in self.to_dict():
+            PrintingText+= f'{iVariable :<30}:{self.to_dict()[iVariable] }\n'
+        return PrintingText
+

### 2025-01-03 Scripts/Main.py

@@ -1,27 +1,0 @@
-########################################################################################################
-#                                                                                                      #
-#  Project:  AI Application for Azophotoswitches Optimization with Pharmacological Interest            #
-#  Author:   Sergio Castañeiras Morales                                                                #
-#  Date:     12/10/2024                                                                                #
-#  Purpose:  Link all the files and store the hole Machine Learning Process                            #
-#                                                                                                      #
-########################################################################################################
-
-
-import requests     # Package used for generating the database requests
-import pandas as pd # Importing pandas in order to use DataFrames
-
-import ChEMBLDataExtractorMacro # Importing the macro called "ChEMBLDataExtractorMacro.py"
-import DataFilterAndPlotsMacro  # Importing the macro called "DataFilterAndPlotsMacro.py"
-
-targetIDChEMBL       = "CHEMBL372" # Defining ChEMBL ID for COX-2, our target. 
-targetProperty       = "IC50"      # Defining our target poperty
-lowerTargetProperty  = -1          # Defining the lowest 'standard_value' (= targetProperty) we want to take into acount
-higherTargetProperty = 200         # Defining the highest 'standard_value' (= targetProperty) we want to take into acount
-percentageEresed	 = 0.2	       # Defining the percentage of the data we want to erase (number between 0 and 1)
-testSizeProportion	 = 0.2         # Defining the percentage of the data we want to keep for our training set (number between 0 and 1)
-randomSplitState     = 42	       # Defining the randomness for the Train/test splitting (Typically will be around 42)
-
-ChEMBLDataExtractorMacro.ChEMBLExtractData(targetIDChEMBL, targetProperty)
-DataFilterAndPlotsMacro.ChEMBLDataProcessingMacro(targetIDChEMBL, targetProperty,lowerTargetProperty,higherTargetProperty,
-												  percentageEresed,testSizeProportion,randomSplitState)

### 2025-01-03 Scripts/QSExSetUp.py

@@ -1,0 +1,12 @@
+########################################################################################################
+#                                                                                                      #
+#  Project:  Physics TFG                                                                               #
+#  Author:   Sergio Castañeiras Morales                                                                #
+#  Date:     03/01/2025                                                                                #
+#  Purpose:  Store all the dependencies of the Project: class definitions, functions etc...            #
+#                                                                                                      #
+########################################################################################################
+
+import DensityMatricesAndPriorsClass
+import UsefullFunctions
+import SDPSolver

### 2025-01-03 Scripts/SDPSolver.py

@@ -1,0 +1,44 @@
+########################################################################################################
+#                                                                                                      #
+#  Project:  Physics TFG                                                                               #
+#  Author:   Sergio Castañeiras Morales                                                                #
+#  Date:     03/01/2025                                                                                #
+#  Purpose:  Store the SDP solver function                                                             #
+#                                                                                                      #
+########################################################################################################
+
+import picos
+import numpy as np
+import DensityMatricesAndPriorsClass
+
+def SolveSDP(Conditions):
+    if not isinstance(Conditions,DensityMatricesAndPriorsClass.DensityMaticesAndPriors):
+        raise TypeError("The given conditions must be a DensityMatricesAndPriorsClass.DensityMaticesAndPriors")
+    MyDenisityMatrices     = Conditions.getDesityMatrices()
+    MyPriorsPropbabilities = Conditions.getPriorProbabilities()
+    NumberOfMatrices       = Conditions.getNumberOfMatrices()
+    NumberOfDimensions     = Conditions.getMatrixDimension()
+
+    MySDP = picos.Problem()
+
+    POVMlist = []
+    for iPOVM in range(NumberOfMatrices):
+        POVM = picos.HermitianVariable(f"POVM_{iPOVM}", MyDenisityMatrices[iPOVM].shape)
+        POVMlist.append(POVM)
+
+    SuccessProbability = 0
+
+    for iPOVM in range(NumberOfMatrices):
+        SuccessProbability += MyPriorsPropbabilities[iPOVM]*picos.trace(POVMlist[iPOVM]*MyPriorsPropbabilities[iPOVM])
+
+    MySDP.set_objective("max", SuccessProbability)
+
+    for iPOVM in range(NumberOfMatrices):
+        MySDP.add_constraint(POVMlist[iPOVM]>>0)
+
+    I = np.eye(NumberOfDimensions) 
+    MySDP.add_constraint(sum(POVMlist) == picos.Constant(I))
+
+    MySDP.solve(solver="cvxopt")
+
+    return {'SDPSolution' : MySDP, 'POVMs' : POVMlist}

### 2025-01-03 Scripts/SquareRootMeasurement.py

@@ -9,35 +9,15 @@
 import numpy
 import picos
 
-# defining sigma_y
-sigma_y=picos.Constant([[0, -1j],[1j,0]])
-
-# Show sigma_y
-print("Sigma_y = ",sigma_y)
-
-# print sigma_y dagger,
-print("Sigma_y dagger = ",sigma_y.H)
-
-#Creating a function that tells us weather a matrix is hermitian or not 
-def Hermitian(matrix):
-    return numpy.allclose(matrix.value, matrix.H.value)
-
-# Is 'sigma_y' hermitian
-print("Is sigma_y hermitian? ", Hermitian(sigma_y))
-
 # Lets create an hermitian we start by defining a non hermitian matrix '_P'
 _P = picos.Constant([
 [ 1 -1j, 2 +2j, 1 ],
 [ 3j, -2j, -1 -1j],
 [ 1 +2j, -0.5+1j, 1.5 ]])
 
-print("Is '_P' hermitian? ", Hermitian(_P))
-
 # now we construct P as _P*_P^dagger which ensures that P is hermitian
 
 P = (_P*_P.H).renamed("P")
-
-print("Is 'P' hermitian? ", Hermitian(P))
 
 # We do the same procedure with a Q matrix
 
@@ -47,11 +27,6 @@ _Q = picos.Constant([
 [ 1 +2j, -1 +1j, 1 +4j]])
 Q = (_Q*_Q.H).renamed("Q")
 
-print("Is '_Q' hermitian? ", Hermitian(_P))
-
-print("Is 'Q' hermitian? ", Hermitian(P))
-
-"""
 # Define the problem.
 F = picos.Problem()
 Z = picos.ComplexVariable("Z", P.shape)
@@ -71,4 +46,3 @@ S,U = numpy.linalg.eig(QQ)
 sqQ = U * numpy.diag([s**0.5 for s in S]) * U.H # Square root of Q.
 Fnp = sum(numpy.linalg.svd(sqP * sqQ)[1]) # Trace-norm of sqrt(P)·sqrt(Q).
 print("Fidelity F(P,Q) computed by NumPy:", round(Fnp, 4))
-"""

### 2025-01-03 Scripts/Testing1.py

@@ -1,0 +1,27 @@
+########################################################################################################
+#                                                                                                      #
+#  Project:  Physics TFG                                                                               #
+#  Author:   Sergio Castañeiras Morales                                                                #
+#  Date:     03/01/2025                                                                                #
+#  Purpose:  Testing                                                                                   #
+#                                                                                                      #
+########################################################################################################
+
+import QSExSetUp
+import picos
+import numpy as np
+
+NumberOfMatrices       = 10
+MatrixDimension        = 3
+RandomConditions       = QSExSetUp.DensityMatricesAndPriorsClass.DensityMaticesAndPriors(NumberOfMatrices,MatrixDimension)
+
+print(RandomConditions)
+
+Solution = QSExSetUp.SDPSolver.SolveSDP(RandomConditions)
+
+print("The given problem has been", Solution['SDPSolution'])
+
+print("The POVMs found are:\n")
+
+for iPOVM in range(len(Solution['POVMs'])):
+    print(f"POVM_{iPOVM}:\n",Solution['POVMs'][iPOVM])

### 2025-01-03 Scripts/Testing2.py

@@ -1,0 +1,35 @@
+import QSExSetUp
+import picos as pc
+import numpy as np
+
+NumberOfMatrices       = 10
+MatrixDimension        = 5
+RandomConditions       = QSExSetUp.DensityMatricesAndPriorsClass.DensityMaticesAndPriors(NumberOfMatrices,MatrixDimension)
+MyDenisityMatrices     = RandomConditions.getDesityMatrices()
+MyPriorsPropbabilities = RandomConditions.getPriorProbabilities()
+# Assuming RandomConditions is a class you have already defined, which provides the matrices
+# Replace this with your actual data:
+MyDenisityMatrices = RandomConditions.getDesityMatrices()  # Replace with actual method to get matrices
+MyPriorsProbabilities = RandomConditions.getPriorProbabilities()  # Replace with actual method to get priors
+
+# Define the problem
+F = pc.Problem()
+
+# Define Z as a complex decision variable (Hermitian matrix)
+Z = F.add_variable("Z", MyDenisityMatrices[0].shape, "hermitian")
+
+# Set the objective: maximize trace(Z * MyDenisityMatrices[0])
+F.set_objective("max", pc.trace(Z * MyDenisityMatrices[0]))
+
+# Add constraint: trace(Z) == 1
+F.add_constraint(pc.trace(Z) == 1)
+
+# Add positive semidefinite constraint: Z must be positive semidefinite (Z >> 0)
+F.add_constraint(Z >> 0)
+
+# Solve the problem using cvxopt solver
+F.solve(solver="cvxopt")
+
+# Output the results
+print("\nOptimal value:", round(F.value, 4))
+print("Optimal Z:", Z.value, sep="\n")

### 2025-01-03 Scripts/UsefullFunctions.py

@@ -1,0 +1,42 @@
+########################################################################################################
+#                                                                                                      #
+#  Project:  Physics TFG                                                                               #
+#  Author:   Sergio Castañeiras Morales                                                                #
+#  Date:     03/01/2025                                                                                #
+#  Purpose:  Store rellevant functions and utilities                                                   #
+#                                                                                                      #
+########################################################################################################
+
+import numpy as np 
+import picos
+
+def Hermitian(matrix, SilentMode = True):
+    if not isinstance(matrix,(picos.expressions.exp_affine.AffineExpression,
+                              picos.expressions.exp_affine.ComplexAffineExpression)):
+        raise TypeError(f"The given matrix is not valid for computing the hermicity")
+    if np.allclose(matrix.value, matrix.H.value):
+        if not SilentMode : print("The matrix is Hermitian")
+        return True
+    if not SilentMode : print("The matrix is NOT hermitian")
+    return False
+
+def RandomSetOfDensityMatrices (NumberOfMatrices, MatrixDimension):
+    if not isinstance(MatrixDimension,int):
+        raise TypeError("The given MatrixDimension must be an Integer")
+    if not isinstance(NumberOfMatrices,int):
+        raise TypeError("The given NumberOfMatices must be an Integer")
+    def RandomDensityMatrix(Dimension):
+        NonHemitianMatix = picos.Constant([[np.random.rand()+1j*np.random.rand() for jDimension in range(Dimension)] 
+                                            for iDimension in range(Dimension)])
+        HermitianMatix   = NonHemitianMatix.H*NonHemitianMatix
+        return HermitianMatix/picos.trace(HermitianMatix)
+    return [RandomDensityMatrix(MatrixDimension) for iDensityMatrix in range(NumberOfMatrices)]
+
+def RandomSetOfProbabilities (NumberOfMatrices):
+    if not isinstance(NumberOfMatrices,int):
+        raise TypeError("The given NumberOfMatices must be an Integer")
+    priorProbabilities = np.random.rand(NumberOfMatrices)
+    priorProbabilities /= sum(priorProbabilities)
+    return priorProbabilities
+
+

### 2025-01-03 Scripts/DensityMatricesAndPriorsClass.py
Implementing Group Generated States

@@ -12,20 +12,42 @@ import numpy as np
 import picos
 
 class DensityMaticesAndPriors:
-    def __init__(self, NumberOfMatrices, MatrixDimension):
+    def __init__(self, NumberOfMatrices, MatrixDimension, ConstructionMethod, Overlap = None):
         if not isinstance(MatrixDimension,int):
             raise TypeError("The given MatrixDimension must be an Integer")
         if not isinstance(NumberOfMatrices,int):
             raise TypeError("The given NumberOfMatrices must be an Integer")
+        if not isinstance(ConstructionMethod,str):
+            raise TypeError("The given ConstructionMethod is not a String")
+        if not (ConstructionMethod in ['Random', 'GroupGenerated']):
+            raise ValueError("The given ConstructionMethod must be either: ", ['Random','GroupGenerated'])
+        if (ConstructionMethod != 'Random') and (Overlap == None):
+            raise ValueError("A Overlap value must be given.")
+            if (not isinstance(Overlap,complex)) or (not abs(Overlap)<1):
+                raise ValueError("The given Overlap be a complex number with modulus less than 1.")
         self.NumberOfMatrices   = NumberOfMatrices
         self.MatrixDimension    = MatrixDimension
+        self.ConstructionMethod = ConstructionMethod
+        self.Overlap            = Overlap
     def to_dict(self):
-        return {
-            'NumberOfMatrices'   : self.NumberOfMatrices,
-            'MatrixDimension'    : self.MatrixDimension,
-            'PriorProbabilities' : UsefullFunctions.RandomSetOfProbabilities(self.NumberOfMatrices),
-            'DensityMatrices'    : UsefullFunctions.RandomSetOfDensityMatrices(self.NumberOfMatrices,self.MatrixDimension)
-        }
+        if self.ConstructionMethod == "Random":
+            return {
+                'NumberOfMatrices'   : self.NumberOfMatrices,
+                'MatrixDimension'    : self.MatrixDimension,
+                'PriorProbabilities' : UsefullFunctions.RandomSetOfProbabilities(self.NumberOfMatrices),
+                'DensityMatrices'    : UsefullFunctions.RandomSetOfDensityMatrices(self.NumberOfMatrices,self.MatrixDimension),
+                'Overlap'            : None,
+                'ConstructionMethod' : "Random"
+            }
+        if self.ConstructionMethod == "GroupGenerated":
+            return {
[…]

### 2025-01-03 Scripts/Testing1.py

@@ -11,17 +11,27 @@ import QSExSetUp
 import picos
 import numpy as np
 
-NumberOfMatrices       = 10
-MatrixDimension        = 3
-RandomConditions       = QSExSetUp.DensityMatricesAndPriorsClass.DensityMaticesAndPriors(NumberOfMatrices,MatrixDimension)
+NumberOfMatrices = 4 
+MatrixDimension  = 3
+GenerationMethod = 'Random'
+Overlap          = 0
 
-print(RandomConditions)
+Conditions = QSExSetUp.DensityMatricesAndPriorsClass.DensityMaticesAndPriors(NumberOfMatrices,MatrixDimension,GenerationMethod, Overlap = Overlap)
 
-Solution = QSExSetUp.SDPSolver.SolveSDP(RandomConditions)
+print(Conditions)
 
-print("The given problem has been", Solution['SDPSolution'])
+DensityMatrices = Conditions.getDesityMatrices()
 
-print("The POVMs found are:\n")
+for iMatix in range(len(DensityMatrices)):
+    print(f"Matrix number {iMatix}:\n",DensityMatrices[iMatix])
+
+Solution = QSExSetUp.SDPSolver.SolveSDP(Conditions)
+
+print("The given problem has been:\n", Solution['SDPSolution'])
+
+print("The success probability is: ", round(Solution['SDPSolution'],4))
+
+print("The found POVMs are:\n")
 
 for iPOVM in range(len(Solution['POVMs'])):
     print(f"POVM_{iPOVM}:\n",Solution['POVMs'][iPOVM])

### 2025-01-03 Scripts/Testing2.py

@@ -1,35 +1,0 @@
-import QSExSetUp
-import picos as pc
-import numpy as np
-
-NumberOfMatrices       = 10
-MatrixDimension        = 5
-RandomConditions       = QSExSetUp.DensityMatricesAndPriorsClass.DensityMaticesAndPriors(NumberOfMatrices,MatrixDimension)
-MyDenisityMatrices     = RandomConditions.getDesityMatrices()
-MyPriorsPropbabilities = RandomConditions.getPriorProbabilities()
-# Assuming RandomConditions is a class you have already defined, which provides the matrices
-# Replace this with your actual data:
-MyDenisityMatrices = RandomConditions.getDesityMatrices()  # Replace with actual method to get matrices
-MyPriorsProbabilities = RandomConditions.getPriorProbabilities()  # Replace with actual method to get priors
-
-# Define the problem
-F = pc.Problem()
-
-# Define Z as a complex decision variable (Hermitian matrix)
-Z = F.add_variable("Z", MyDenisityMatrices[0].shape, "hermitian")
-
-# Set the objective: maximize trace(Z * MyDenisityMatrices[0])
-F.set_objective("max", pc.trace(Z * MyDenisityMatrices[0]))
-
-# Add constraint: trace(Z) == 1
-F.add_constraint(pc.trace(Z) == 1)
-
-# Add positive semidefinite constraint: Z must be positive semidefinite (Z >> 0)
-F.add_constraint(Z >> 0)
-
-# Solve the problem using cvxopt solver
-F.solve(solver="cvxopt")
-
-# Output the results
-print("\nOptimal value:", round(F.value, 4))
-print("Optimal Z:", Z.value, sep="\n")

### 2025-01-03 Scripts/UsefullFunctions.py

@@ -39,4 +39,16 @@ def RandomSetOfProbabilities (NumberOfMatrices):
     priorProbabilities /= sum(priorProbabilities)
     return priorProbabilities
 
+def GrupGeneratedDensityMatrices (NumberOfMatrices, MatrixDimension, Overlap):
+    if not isinstance(MatrixDimension,int):
+        raise TypeError("The given MatrixDimension must be an Integer")
+    if not isinstance(NumberOfMatrices,int):
+        raise TypeError("The given NumberOfMatices must be an Integer")
+    def GroupGenerateDensityMatrix(Dimension, Overlap):
+        return picos.Constant([[1 if iDimension == jDimension else (Overlap if iDimension < jDimension else Overlap.conjugate()) for jDimension in range(MatrixDimension)]for iDimension in range(MatrixDimension)])
+    return [GroupGenerateDensityMatrix(MatrixDimension, Overlap) for iDensityMatrix in range(NumberOfMatrices)]
 
+def SetOfEqualProbabilities (NumberOfMatrices):
+    if not isinstance(NumberOfMatrices,int):
+        raise TypeError("The given NumberOfMatices must be an Integer")
+    return np.array([1/NumberOfMatrices for iMatrix in range (NumberOfMatrices)])

### 2025-02-03 Scripts/Testing1.py
Adding the Pipfile

@@ -77,3 +77,8 @@ print("The given problem has been  :\n", Solution['SDPSolution'])
 print("The POVMs are               :\n", Solution['POVMs'])
 
 print("Uncertainity probability is :\n", round(Solution['SDPSolution'],4))
+
+for iElement, iPOVM in enumerate(Solution['POVMs']):
+    print(f"POVM {iElement}:")
+    print(iPOVM)
+

### 2025-02-03 Scripts/UsefullFunctions.py

@@ -70,9 +70,9 @@ def setOfGropGeneratedDensityMatrices(seedState, groupSize, involutionalMatrix):
         raise ValueError(f"The given seed state mus be normalized.")
     def groupGenerateStateDensityMatrix(seedState, groupSize, elementNumber, involutionalMatrix):
         if not isinstance(elementNumber, int): raise TyperError("The given value of the elementNumber must be an integer.")
-        if elementNumber%groupSize == 0: return seedState*seedState.H
+        if elementNumber%groupSize == 0: return picos.Constant(seedState*seedState.H)
         state = picos.Constant(expm(1j*involutionalMatrix*np.pi*(elementNumber%groupSize)/groupSize))*seedState
-        if not np.allclose(state.value, seedState.value): return state*state.H
+        if not np.allclose(state.value, seedState.value): return picos.Constant(state*state.H)
         raise ValueError(f"The given seed state is an eigen state of the given matrix.")
     return [groupGenerateStateDensityMatrix(seedState,groupSize,iElement, involutionalMatrix) for iElement in range(groupSize)]
 

### 2025-02-04 Scripts/DensityMatricesAndPriorsClass.py
adding Gram Generated States

@@ -12,7 +12,7 @@ import numpy as np
 import picos
 
 class DensityMaticesAndPriors:
-    def __init__(self, NumberOfMatrices, MatrixDimension, MatrixConstructionMethod, ProbabilitiesContructionMethod = "Equal", seedState = None, involutionalMatrix = None):
+    def __init__(self, NumberOfMatrices, MatrixDimension, MatrixConstructionMethod, ProbabilitiesContructionMethod = "Equal", seedState = None, involutoryMatrix = None):
         if not isinstance(MatrixDimension,int):
             raise TypeError("The given MatrixDimension must be an Integer")
         if not isinstance(NumberOfMatrices,int):
@@ -21,12 +21,27 @@ class DensityMaticesAndPriors:
             raise TypeError("The given MatrixConstructionMethod is not a String")
         if not isinstance(ProbabilitiesContructionMethod,str):
             raise TypeError("The given ProbabilitiesContructionMethod is not a String")
+        if MatrixConstructionMethod == "GroupGeneratedStates":
+            if not isinstance(seedState,(picos.expressions.exp_affine.AffineExpression,
+                              picos.expressions.exp_affine.ComplexAffineExpression)):
+                raise TypeError("The given seed state is not valid.")
+            if not isinstance(involutoryMatrix,(picos.expressions.exp_affine.AffineExpression,
+                              picos.expressions.exp_affine.ComplexAffineExpression)):
+                raise TypeError("The given involutory matrix is not valid.")
+            if not seedState.shape[1] == 1:
+                raise ValueError("The given seed state must be a vector")
+            if not seedState.shape[0] == MatrixDimension:
+                raise ValueError("The given seed state dimention does not coincide with the MatrixDimension")
+            if not (len(involutoryMatrix.shape) == 2 and (involutoryMatrix.shape[0] == involutoryMatrix.shape[1])):
+                raise TypeError("The given involutory matrix must be a square matrix.")
+            if not involutoryMatrix.shape[0] == MatrixDimension:
+                raise ValueError("The given involutory matrix dimension does not coincide with the MatrixDimension")
         self.NumberOfMatrices               = NumberOfMatrices
         self.MatrixDimension                = MatrixDimension
         self.MatrixConstructionMethod       = MatrixConstructionMethod
[…]

### 2025-02-04 Scripts/GramGeneratedFunctions.py

@@ -1,0 +1,116 @@
+########################################################################################################
+#                                                                                                      #
+#  Project:  Physics TFG                                                                               #
+#  Author:   Sergio Castañeiras Morales                                                                #
+#  Date:     04/02/2025                                                                                #
+#  Purpose:  Store functions used in the Gram Generated States Class                                   #
+#                                                                                                      #
+########################################################################################################
+
+import numpy as np
+import picos
+from scipy.linalg import sqrtm
+
+def Hermitian(matrix, SilentMode = True):
+    if not isinstance(matrix,(picos.expressions.exp_affine.AffineExpression,
+                              picos.expressions.exp_affine.ComplexAffineExpression)):
+        raise TypeError(f"The given matrix is not valid for computing the hermicity")
+    if np.allclose(matrix.value, matrix.H.value):
+        if not SilentMode : print("The matrix is Hermitian")
+        return True
+    if not SilentMode : print("The matrix is NOT hermitian")
+    return False
+
+def SetOfRandomProbabilities (NumberOfMatrices):
+    if not isinstance(NumberOfMatrices,int):
+        raise TypeError("The given NumberOfMatices must be an Integer")
+    priorProbabilities = np.random.rand(NumberOfMatrices)
+    priorProbabilities /= sum(priorProbabilities)
+    return priorProbabilities
+
+def SetOfEqualProbabilities (NumberOfMatrices):
+    if not isinstance(NumberOfMatrices,int):
+        raise TypeError("The given NumberOfMatices must be an Integer")
+    return np.array([1/NumberOfMatrices for iMatrix in range (NumberOfMatrices)])
+
+def SetOfMatrices (MatrixMethod, NumberOfMatrices, MatrixDimension, seedState, involutionalMatrix):
+    if not isinstance(MatrixDimension,int):
+        raise TypeError("The given MatrixDimension must be an Integer")
+    if not isinstance(NumberOfMatrices,int):
+        raise TypeError("The given NumberOfMatices must be an Integer")
+    if not isinstance(MatrixMethod, str):
[…]

### 2025-02-04 Scripts/GramGeneratedStates.py

@@ -1,0 +1,71 @@
+########################################################################################################
+#                                                                                                      #
+#  Project:  Physics TFG                                                                               #
+#  Author:   Sergio Castañeiras Morales                                                                #
+#  Date:     04/02/2025                                                                                #
+#  Purpose:  Defining the GramGeneratedStatesClass                                                     #
+#                                                                                                      #
+########################################################################################################
+
+import GramGeneratedFunctions
+from scipy.linalg import sqrtm
+import picos
+
+class GramGeneratedStatesClass:
+    def __init__(self, NumberOfMatrices, MatrixDimension, MatrixConstructionMethod, ProbabilitiesContructionMethod = "Equal", Overlap = 0):
+        if not isinstance(MatrixDimension,int):
+            raise TypeError("The given MatrixDimension must be an Integer")
+        if not isinstance(NumberOfMatrices,int):
+            raise TypeError("The given NumberOfMatrices must be an Integer")
+        if not isinstance(MatrixConstructionMethod,str):
+            raise TypeError("The given MatrixConstructionMethod is not a String")
+        if not isinstance(ProbabilitiesContructionMethod,str):
+            raise TypeError("The given ProbabilitiesContructionMethod is not a String")
+        self.NumberOfMatrices               = NumberOfMatrices
+        self.MatrixDimension                = MatrixDimension
+        self.MatrixConstructionMethod       = MatrixConstructionMethod
+        self.ProbabilitiesContructionMethod = ProbabilitiesContructionMethod
+        self.PriorProbabilities             = GramGeneratedFunctions.SetOfProbabilities(ProbabilitiesContructionMethod,NumberOfMatrices)
+        self.GramMatrix                     = GramGeneratedFunctions.GenerateGramMatrix(NumberOfMatrices,MatrixConstructionMethod, Overlap)
+        self.SquareRoot                     = picos.Constant(sqrtm(self.GramMatrix))
+        self.GramMatrixWithPriors           = GramGeneratedFunctions.GenerateGramMatrixWithPriors(self.GramMatrix, self.PriorProbabilities,self.NumberOfMatrices)
+        self.SquareRootWithPriors           =picos.Constant(sqrtm(self.GramMatrixWithPriors))
[…]

### 2025-02-04 Scripts/QSExSetUp.py

@@ -10,3 +10,5 @@
 import DensityMatricesAndPriorsClass
 import UsefullFunctions
 import SDPSolver
+import GramGeneratedStates
+import GramGeneratedFunctions

### 2025-02-04 Scripts/SDPSolver.py

@@ -10,14 +10,17 @@
 import picos
 import numpy as np
 import DensityMatricesAndPriorsClass
+import GramGeneratedStates
 
 def SolveSDPMinimumError(Conditions):
-    if not isinstance(Conditions,DensityMatricesAndPriorsClass.DensityMaticesAndPriors):
-        raise TypeError("The given conditions must be a DensityMatricesAndPriorsClass.DensityMaticesAndPriors")
+    if not isinstance(Conditions,(DensityMatricesAndPriorsClass.DensityMaticesAndPriors,GramGeneratedStates.GramGeneratedStatesClass)):
+        raise TypeError("The given conditions must be a DensityMatricesAndPriorsClass.DensityMaticesAndPriors or GramGeneratedStates.GramGeneratedStatesClass")
     MyDensityMatrices      = Conditions.getDensityMatrices()
     MyPriorsPropbabilities = Conditions.getPriorProbabilities()
     NumberOfMatrices       = Conditions.getNumberOfMatrices()
     NumberOfDimensions     = Conditions.getMatrixDimension()
+    
+    print(Conditions)
 
     MySDP = picos.Problem()
 
@@ -38,14 +41,16 @@ def SolveSDPMinimumError(Conditions):
 
     I = np.eye(NumberOfDimensions) 
     MySDP.add_constraint(sum(POVMlist) == picos.Constant(I))
+    
+    print(MySDP)
 
     MySDP.solve(solver="cvxopt")
 
     return {'SDPSolution' : MySDP, 'POVMs' : POVMlist}
 
 def SolveSDPDualMinimumError(Conditions):
-    if not isinstance(Conditions,DensityMatricesAndPriorsClass.DensityMaticesAndPriors):
-        raise TypeError("The given conditions must be a DensityMatricesAndPriorsClass.DensityMaticesAndPriors")
+    if not isinstance(Conditions,(DensityMatricesAndPriorsClass.DensityMaticesAndPriors,GramGeneratedStates.GramGeneratedStatesClass)):
+        raise TypeError("The given conditions must be a DensityMatricesAndPriorsClass.DensityMaticesAndPriors or GramGeneratedStates.GramGeneratedStatesClass")
     MyDensityMatrices      = Conditions.getDensityMatrices()
     MyPriorsPropbabilities = Conditions.getPriorProbabilities()
     NumberOfMatrices       = Conditions.getNumberOfMatrices()
[…]

### 2025-02-04 Scripts/Testing1.py

@@ -12,13 +12,14 @@ import picos
 import numpy as np
 from scipy.linalg import sqrtm
 
-NumberOfMatrices              = 5
-MatrixDimension               = 2
+NumberOfMatrices              = 4
+MatrixDimension               = 3
 MatrixGenerationMethod        = "GroupGeneratedStates"
 ProbabliltiesGenerationMethod = "Equal"
-initialState                  = picos.Constant([1/np.sqrt(2),1j/np.sqrt(2)])
-sigmaX                        = picos.Constant([[0,1],[1,0]])
-Conditions                    = QSExSetUp.DensityMatricesAndPriorsClass.DensityMaticesAndPriors(NumberOfMatrices,MatrixDimension,MatrixGenerationMethod, ProbabliltiesGenerationMethod, seedState = initialState, involutionalMatrix = sigmaX)
+initialState                  = picos.Constant([1,0,0])
+sigmaX                        = picos.Constant([[0,1,0],[1,0,0],[0,0,1]])
+print(len(sigmaX.shape))
+Conditions                    = QSExSetUp.DensityMatricesAndPriorsClass.DensityMaticesAndPriors(NumberOfMatrices,MatrixDimension,MatrixGenerationMethod, ProbabliltiesGenerationMethod, seedState = initialState, involutoryMatrix = sigmaX)
 DensityMatrices               = Conditions.getDensityMatrices()
 
 print(Conditions)
@@ -78,7 +79,18 @@ print("The POVMs are               :\n", Solution['POVMs'])
 
 print("Uncertainity probability is :\n", round(Solution['SDPSolution'],4))
 
+print("The probability of perfect exclussion is:\n", round(1-float(Solution['SDPSolution']),4))
+
+
+UnknownPOVM = Solution["UncertainPOVM"]
+
+print("We do not now what is going on if the POVM is:\n",UnknownPOVM)
+
 for iElement, iPOVM in enumerate(Solution['POVMs']):
     print(f"POVM {iElement}:")
     print(iPOVM)
+    UnknownPOVM += iPOVM
+    print(f"DensityMatrices{iElement}:\n",picos.trace(DensityMatrices[iElement]*iPOVM))
+
+print("Does the sum equal the identity?\n",UnknownPOVM)
 

### 2025-02-04 Scripts/Testing2.py

@@ -1,0 +1,48 @@
+########################################################################################################
+#                                                                                                      #
+#  Project:  Physics TFG                                                                               #
+#  Author:   Sergio Castañeiras Morales                                                                #
+#  Date:     24/01/2025                                                                                #
+#  Purpose:  Testing                                                                                   #
+#                                                                                                      #
+########################################################################################################
+
+import QSExSetUp
+import picos
+import numpy as np
+from scipy.linalg import sqrtm
+import matplotlib.pyplot as plt
+
+NumberOfMatrices              = 10
+MatrixDimension               = 10
+MatrixGenerationMethod        = "Zn"
+ProbabliltiesGenerationMethod = "Equal"
+Overlap                       = 0
+Acuracy                       = 100
+SuccesProbabilityList         = []
+OverlapsList                  = []
+
+for i in range (1,Acuracy):
+    Overlap += 1/Acuracy
+    Conditions = QSExSetUp.GramGeneratedStates.GramGeneratedStatesClass(NumberOfMatrices,MatrixDimension,MatrixGenerationMethod, ProbabilitiesContructionMethod = ProbabliltiesGenerationMethod, Overlap = Overlap)
+    SuccesProbabilityList.append(Conditions.getSRMSuccessProbability())
+    OverlapsList.append(Overlap)
+
+plt.scatter(OverlapsList, SuccesProbabilityList)
+plt.xlabel("Overlap")
+plt.ylabel("Success Probability")
+plt.title(f"Group generated Z{NumberOfMatrices}")
+plt.savefig(f"../Plots/OverlapVSSucessProbabilityZ{NumberOfMatrices}.pdf")
+
+
+"""
+print("------------------------\n\
+Computing the primal SDP\n\
+------------------------")
+
+Solution = QSExSetUp.SDPSolver.SolveSDPMinimumError(Conditions)
+
+print("The given problem has been:\n", Solution['SDPSolution'])
+
+print("The success probability is: ", round(Solution['SDPSolution'],4))
+"""

### 2025-02-04 Scripts/UsefullFunctions.py

@@ -11,6 +11,7 @@ import numpy as np
 import picos
 import qiskit
 from scipy.linalg import expm
+from scipy.linalg import sqrtm
 
 def Hermitian(matrix, SilentMode = True):
     if not isinstance(matrix,(picos.expressions.exp_affine.AffineExpression,
@@ -38,7 +39,7 @@ def SetOfRandomDensityMatricesMixed(NumberOfMatrices, MatrixDimension):
     if not isinstance(MatrixDimension,int):
         raise TypeError("The given MatrixDimension must be an Integer")
     if not isinstance(NumberOfMatrices,int):
-        raise TypeError("The given NumberOfMatices must be an Integer")
+        raise TypeError("The given NumberOfMatrices must be an Integer")
     def RandomDensityMatrixMixed(Dimension):
         return picos.Constant(qiskit.quantum_info.random_density_matrix(Dimension).data)
     return [RandomDensityMatrixMixed(MatrixDimension) for iDensityMatrix in range(NumberOfMatrices)]
@@ -47,7 +48,7 @@ def SetOfRandomDensityMatricesPure (NumberOfMatrices, MatrixDimension):
     if not isinstance(MatrixDimension,int):
         raise TypeError("The given MatrixDimension must be an Integer")
     if not isinstance(NumberOfMatrices,int):
-        raise TypeError("The given NumberOfMatices must be an Integer")
+        raise TypeError("The given NumberOfMatrices must be an Integer")
     def RandomDensityMatrixPure(Dimension):
         randomState         = qiskit.quantum_info.random_statevector(Dimension)
         randomDensityMatrix = np.outer(randomState.data, np.conj(randomState.data))
@@ -78,21 +79,21 @@ def setOfGropGeneratedDensityMatrices(seedState, groupSize, involutionalMatrix):
 
 def SetOfRandomProbabilities (NumberOfMatrices):
     if not isinstance(NumberOfMatrices,int):
-        raise TypeError("The given NumberOfMatices must be an Integer")
+        raise TypeError("The given NumberOfMatrices must be an Integer")
     priorProbabilities = np.random.rand(NumberOfMatrices)
     priorProbabilities /= sum(priorProbabilities)
     return priorProbabilities
 
 def SetOfEqualProbabilities (NumberOfMatrices):
     if not isinstance(NumberOfMatrices,int):
[…]

### 2025-02-05 Notes/Notes.tex
Day of work

@@
 \usepackage[english]{babel}
+\usepackage{emoji}
 \usepackage{lipsum}
+\usepackage{braket}
 \usepackage[table,xcdraw]{xcolor}
@@
 \newpage
+\thispagestyle{empty}
+\vspace*{\fill} % Push content to vertical center
+\begin{flushright}
+    \emph{“The dumbest people I know are those who know it all.”}\\[1em]
+    \textbf{Malcolm S. Forbes}
+\end{flushright}
+\vspace*{\fill} % Balance vertical spacing
+
+\newpage
 \pagestyle{fancyplain}
@@
 
-\begin{definition}
+\begin{definition}\label{defGramMatrix}
 \textbf{Gram matrix}: Given a vector space $A$, a field $F$ , a set of vectors $\{v_i\}_{i=0}^n\subset A$ and an inner product space such that  $\langle \cdot , \cdot \rangle:A\times A\rightarrow F$  the Gram matrix $G$ is defined as the matrix $G\in F^{n\times n}$ whose entries are $g_{i,j}=\langle v_i,v_j\rangle$ i.e,
@@
 
+\begin{multicols}{2}
+\begin{observation}
+Let $\mathcal{U}$ be a unitary matrix such that $\mathcal{U}^n=\mathbb{I}_d$ and $\mathcal{U}^i\neq\mathbb{I}_d\;\;\forall i\in\{0,...,n-1\}$, let $\ket{\psi}$ also be a normalised state.
+We might define the set of quantum states $\Omega=\{\ket{\psi_i}=\mathcal{U}^i\ket{\psi}\}_{i=0}^{n-1}$ a group generated ensamble of states, since the set  $\{\mathcal{U}^i\}_{i=0}^{n-1}$ is obviously a group with the usual product.
+From the group structure of $\{\mathcal{U}^i\}_{i=0}^{n-1}$ it is natural to define $\star$ operation such that,
+\begin{align}
+\star:\Omega\times\Omega\rightarrow&\Omega\\
+(\ket{\psi_i},\ket{\psi_j})\mapsto&\ket{\psi_{i+j}}.
+\end{align}
+Hence we observe the ensamble of states inherites the group structure from the generator $\mathcal{U}$ nature.
+More particularly, $\Omega$ is isomorphic to $\mathbb{Z}/n\mathbb{Z}$.
+Hence we want to compute the gram matrix of $\Omega$, applying the Definition (\ref{defGramMatrix}) we obtain,
+\begin{align}
+G_{i,j} =& \braket{\psi_{i}|\psi_{j}} \\
+=& \bra{\psi} \left(\mathcal{U}^i\right)^\dagger U^j\ket{\psi}\\
+=& \bra{\psi} \left(\mathcal{U}^\dagger\right)^i U^j\ket{\psi}\\
+=& \bra{\psi} \left(\mathcal{U}^{-1}\right)^i U^j\ket{\psi}\\
+=& \bra{\psi} \mathcal{U}^{-i} U^j\ket{\psi}\\
+=& \braket{\mathcal{U}^{-i+j}}_\psi.
+\end{align}
+The gram matrix must have the shape
+\begin{align}
+G=\begin{pmatrix}
+ 1 & \braket{\mathcal{U}^{1}}_{\psi} & \hdots &  \braket{\mathcal{U}^{n-1}}_{\psi} \\
+  \braket{\mathcal{U}^{-1}}_{\psi} & 1 & \hdots &  \braket{\mathcal{U}^{n-2}}_{\psi} \\
+   \vdots & \vdots & \ddots & \vdots \\
+  \braket{\mathcal{U}^{-n+1}}_{\psi} & \braket{\mathcal{U}^{-n+2}}_{\psi}  & \hdots &  1
+\end{pmatrix}.
+\end{align}
+Since $\braket{\mathcal{U}^{-j}}_{\psi}=\braket{\mathcal{U}^{j}}_{\psi}^*$ the hermicity is preserved (as it should). Also we note that,
+\begin{align}
+\braket{\mathcal{U}^{-n+i}}_{\psi}=\braket{\mathcal{U}^{-n+i}\mathbb{I}_d}_{\psi}=\braket{\mathcal{U}^{-n+i}\mathcal{U}^{n}}_{\psi}=\braket{\mathcal{U}^{i}}_{\psi}
+\end{align}
+hence,
+\begin{align}
+G=\begin{pmatrix}
+ 1 & \braket{\mathcal{U}}_{\psi} & \braket{\mathcal{U}^{2}}_{\psi} & \hdots &  \braket{\mathcal{U}}_{\psi}^* \\
+  \braket{\mathcal{U}}_{\psi}^* & 1 & \braket{\mathcal{U}}_{\psi} & \hdots &  \braket{\mathcal{U}^{2}}_{\psi}^* \\
+    \braket{\mathcal{U}^{2}}_{\psi}^* &  \braket{\mathcal{U}}_{\psi}^*  & 1 & \hdots &  \braket{\mathcal{U}^{3}}_{\psi}^* \\
+   \vdots & \vdots & \vdots & \ddots & \vdots \\
+  \braket{\mathcal{U}}_{\psi} & \braket{\mathcal{U}^{2}}_{\psi}  & \braket{\mathcal{U}^{3}}_{\psi}  & \hdots &  1 
+\end{pmatrix}.
+\end{align}
+\textbf{Question} how does $\braket{\mathcal{U}^{j}}_{\psi}$ depend on $\braket{\mathcal{U}}_{\psi}$.
+I know we have said $\braket{\mathcal{U}^{j}}_{\psi} =\braket{\mathcal{U}}_{\psi}$ but I cannot see why \emoji{sad-but-relieved-face}\par
+As a matter of fact by computing some matrices I can get situations such that $\braket{\mathcal{U}^{i}}_{\psi}=0$ for instance by performing a rotation of $\pi/4$ in the $x$ axis of the state pointing in the $z$ direction I can get a group generated ensamble of $\mathbb{Z}/4\mathbb{Z}$.
+But the second state (rotation of $\pi/2$) is orthogonal to the first state and $\braket{\mathcal{U}^2}_{\psi}=0\neq \frac{1}{\sqrt{2}}\braket{\mathcal{U}}_{\psi}$.
+\par
+\textbf{Stuff I know},\par 
+Since $\mathcal{U}$ is an unitary matrix such that $\mathcal{U}^n=\mathbb{I}_d$ I know that in the basis of eigenvalues of $\mathcal{U}$ denoted as $\{\ket{u_i}\}_{i=0}^{n-1}$
+\begin{align}
+\mathcal{U}=\sum_{k=0}^{n-1}e^{i2\pi k/n}\ket{u_k}\bra{u_k}
+\end{align}
+Let $\ket{\psi}=\sum_{i=0}^{n-1}c_i\ket{u_i}$ be the expression of $\ket{\psi}$ in the $\{\ket{u_i}\}_{i=0}^{n-1}$ basis.
+Notice from the unicity of $\mathcal{U}$ can be expressed as $\mathcal{U}=e^{iA}$ for a hermitian matrix $A$, which decomposes in the basis orthonormal basis as $A=\sum_{i=0}^{n-1}\alpha_i\ket{a_i}\bra{a_i}$.
+Therefore,
+\begin{align}
+\mathcal{U}=&e^{iA}\\
+=&\sum_{j=0}^{\infty}\frac{i^j}{j!}A^j\\
+=&\sum_{j=0}^{\infty}\frac{i^j}{j!}\left(\sum_{k=0}^{n-1}\alpha_k\ket{a_k}\bra{a_k}\right)^j\\
+=&\sum_{j=0}^{\infty}\frac{i^j}{j!}\sum_{k=0}^{n-1}\alpha_k^j\ket{a_k}\bra{a_k}\\
+=&\sum_{k=0}^{n-1}\left(\sum_{j=0}^{\infty}\frac{i^j}{j!}\alpha_k^j\right)\ket{a_k}\bra{a_k}\\
+=&\sum_{k=0}^{n-1}e^{i\alpha_k}\ket{a_k}\bra{a_k}
+\end{align}
+here we deduce 
+\begin{align}
+\ket{u_k}=&\ket{a_k}\\
+2\pi k/n =& \alpha_k\\
+A=&\frac{2\pi}{n}\sum_{i=0}^{n-1}i \ket{a_i}\bra{a_i}\\
+\ket{\psi}=&\sum_{i=0}^{n-1}c_i\ket{a_i}.
+\end{align}
+Then we might compute $\braket{\mathcal{U}}_\psi$ as,
+\begin{align}
+\braket{\mathcal{U}}_\psi= \sum_{k=0}^{n-1}|c_i|^2e^{i2\pi k/n}
+\end{align}
+which is not necessarily a real quantity, then we compute $\braket{\mathcal{U}^j}_\psi$ as
+\begin{align}
+\braket{\mathcal{U}^j}_\psi= \sum_{k=0}^{n-1}|c_k|^2e^{i2\pi kj/n}
+\end{align}
+The basis we knew the gram matrix decompose in \emoji{star-struck} (the Fourier's basis), it is a genuine surprise I did not expect this result. Then the Gram matrix can be written as,
+\end{observation}
+\end{multicols}
+\begin{align}
+G=\begin{pmatrix}
+ 1 & \sum_{k=0}^{n-1}|c_k|^2e^{i2\pi k/n} & \sum_{k=0}^{n-1}|c_k|^2e^{i4\pi k/n}  & \hdots &  \sum_{k=0}^{n-1}|c_k|^2e^{-i2\pi k/n} \\
+  \sum_{k=0}^{n-1}|c_k|^2e^{-i2\pi k/n} & 1 & \sum_{k=0}^{n-1}|c_k|^2e^{-i2\pi k/n} & \hdots & \sum_{k=0}^{n-1}|c_k|^2e^{-i4\pi k/n} \\
+   \sum_{k=0}^{n-1}|c_k|^2e^{-i4\pi k/n} &  \sum_{k=0}^{n-1}|c_k|^2e^{-i2\pi k/n}  & 1 & \hdots & \sum_{k=0}^{n-1}|c_k|^2e^{-i6\pi k/n} \\
+   \vdots & \vdots & \vdots & \ddots & \vdots \\
+  \sum_{k=0}^{n-1}|c_k|^2e^{i2\pi k/n} &\sum_{k=0}^{n-1}|c_k|^2e^{i4\pi k/n}  & \sum_{k=0}^{n-1}|c_k|^2e^{i6\pi k/n}  & \hdots &  1 
+\end{pmatrix}.
+\end{align}
+\begin{multicols}{2}
+\begin{observation}
+We can immediately see the gram matrix is completely determined by the decomposition of $\ket{\psi}$ in the basis of eigenvectors of $A$ i.e.
+$\mathcal{U}$ but the statement $\braket{\mathcal{U}^{j}}_{\psi} =\braket{\mathcal{U}}_{\psi}$ still remains untrue in general.
+\par
+An interesting case can be $\ket{\psi}=\ket{a_t}$ for a given $t\in\{0,..,n-1\}$. In this case we can see that 
+\begin{align}
+U^j\ket{\psi}&=U^j\ket{a_t}\\&=e^{i2\pi t/n}\ket{a_t}\\&=e^{i2\pi t/n}\ket{\psi}
+\end{align}
+In this case the gram matrix is
+\end{observation}
+\end{multicols}
+\begin{align}\label{eqGramMatrixZn}
+G=\begin{pmatrix}
+ 1 & |c_t|^2e^{i2\pi t/n} & |c_t|^2e^{i4\pi t/n} & \hdots &  |c_t|^2e^{-i2\pi t/n} \\
+  |c_t|^2e^{-i2\pi t/n} & 1 & |c_t|^2e^{i2\pi t/n} & \hdots & |c_t|^2e^{-i4\pi t/n} \\
+  |c_t|^2e^{i4\pi t/n} &  |c_t|^2e^{-i2\pi t/n}  & 1 & \hdots & |c_t|^2e^{-i6\pi t/n}  \\
+   \vdots & \vdots & \vdots & \ddots & \vdots \\
+  |c_t|^2e^{i2\pi t/n} &|c_t|^2e^{i4\pi t/n}  & |c_t|^2e^{i6\pi t/n}  & \hdots &  1 
+\end{pmatrix}
+\end{align}
+
+\begin{multicols}{2}
+\begin{observation}
+Still we need to get rid off the global phase in each entry to get the result explain in the meetings... \par
+\textbf{Question} Which is the criteria to do this?
+Why can we choose $\ket{\psi}$ to be an eigenket of $A$ arbitrarily?
+Regarding the previous example we had our state pointing in the $z$ direction (i.e.
+not an eigenket of $\sigma_x$) which would explain the inconsistency.
+\end{observation}
+\begin{observation}
+Let us analyse the case of the group generated ensemble of $\mathbb{Z}/2\mathbb{Z}\times\mathbb{Z}/2\mathbb{Z}$. We will denote 
+\end{observation}
+\begin{observation}\label{ObsZnZm}
+Let us analyse the case the case $\mathbb{Z}/n\mathbb{Z}\times\mathbb{Z}/m\mathbb{Z}$ in order to do so let $\mathcal{U}_n$ and $\mathcal{U}_m$ two unitary operators such that $\mathcal{U}_n^n=\mathbb{I}_d$, $\mathcal{U}_m^m=\mathbb{I}_d$ respectively, and $[U_n,U_m]=0$.
+Here we distinguish two cases $n=m$ and $n\neq m$.
+Since $[U_n,U_m]=0$ we know there exists a basis $\{\ket{u}_i\}_{i=0}^{nm-1}$ where both unitary operators are diagonal.
+Taking into account the group representations are equivalent up to isomorphism we can consider one representation and extend it to any other representation.
+Here we might consider,
+\begin{align}
+U_n=&\sum_{i=0}^{nm-1}e^{i2\pi i/n}\ket{u_i}\bra{u_i}\\
+U_m=&\sum_{i=0}^{nm-1}e^{i2\pi i/m}\ket{u_i}\bra{u_i}
+\end{align}
+Notice the rellevance $n\neq m\Rightarrow U_n\neq U_m$ otherwise the states generated by $U_n$ and $U_m$ will be the same ones and we would go back to the case $\mathbb{Z}/n\mathbb{Z}$.
+\emoji{thinking-face}\par
+Now our set of states is $\Omega=\{U_{n}^iU_{m}^j\ket{\psi}\}_{0\leq i\leq n-1; 0\leq j\leq m-1}$ without loss of generality and for notation purposes we will choose $n>m$ and denote $U_{n}^iU_{m}^j\ket{\psi}=\ket{\psi_{(i,j)}}$ and we will define the oder relation \footnote{We need to order our ensemble for generating the gram matrix.},
+\begin{align}
+\ket{\psi_{(i,j)}}=&\ket{\psi_{(k,l)}}\Leftrightarrow i=k\;\&\;j=k\\
+\ket{\psi_{(i,j)}}>&\ket{\psi_{(k,l)}}\Leftrightarrow\begin{cases}i>k\\i=k\;\&\;j>k\end{cases}\\
+\ket{\psi_{(i,j)}}<&\ket{\psi_{(k,l)}}\Leftrightarrow\begin{cases}i<k\\i=k\;\&\;j<k\end{cases}
+\end{align}
+now we have $\Omega$ ready to compute the gram matrix. Let $G_m$ be the gram matrix of the $\mathbb{Z}/m\mathbb{Z}$ group generated from Eq.(\ref{eqGramMatrixZn}), then the gram matrix is nothing but,
+\end{observation}
+\end{multicols}
+\begin{align}\label{EqGramZnZm}
+G_{nm}=\begin{pmatrix}
+ G_m & G_me^{i2\pi t/n} & G_me^{i4\pi t/n} & \hdots &  G_me^{-i2\pi t/n} \\
+  G_me^{-i2\pi t/n} & G_m & G_me^{i2\pi t/n} & \hdots & G_me^{-i4\pi t/n} \\
+  G_me^{i4\pi t/n} &  G_me^{-i2\pi t/n}  & G_m & \hdots & G_me^{-i6\pi t/n}  \\
+   \vdots & \vdots & \vdots & \ddots & \vdots \\
+  G_me^{i2\pi t/n} &G_me^{i4\pi t/n}  & G_me^{i6\pi t/n}  & \hdots &  G_m 
+\end{pmatrix}
+\end{align}
+
+\begin{multicols}{2}
+\begin{observation}
+Notice by changing the ordering definition we can easily see $G_{nm}$ is totally equivalent to $G_{mn}$ since $\mathbb{Z}/n\mathbb{Z}\times\mathbb{Z}/m\mathbb{Z}\equiv \mathbb{Z}/m\mathbb{Z}\times\mathbb{Z}/n\mathbb{Z}$ naturally.
+From Observation (\ref{ObsZnZm}) and Eq.
+(\ref{EqGramZnZm}) one can deduce, for the case $\mathbb{Z}/n_1\mathbb{Z}\times\mathbb{Z}/n_2\mathbb{Z}\times\dots\times \mathbb{Z}/n_k\mathbb{Z}$, the gram matrix in nothing but,
+\end{observation}
+\end{multicols}
+\begin{align}
+G_{n_1,n_2,...,n_k}=\begin{pmatrix}
+ G_{n_1,n_2,...,n_{k-1}} & G_{n_1,n_2,...,n_{k-1}}e^{i2\pi t/n_k} & \hdots &  G_{n_1,n_2,...,n_{k-1}}e^{-i2\pi t/n_k} \\
+  G_{n_1,n_2,...,n_{k-1}}e^{-i2\pi t/n_k} & G_{n_1,n_2,...,n_{k-1}} & \hdots & G_{n_1,n_2,...,n_{k-1}}e^{-i4\pi t/n_k} \\
+   \vdots & \vdots  & \ddots & \vdots \\
+  G_{n_1,n_2,...,n_{k-1}}e^{i2\pi t/n_k} & G_{n_1,n_2,...,n_{k-1}}e^{i4\pi t/n_k}  & \hdots &  G_{n_1,n_2,...,n_{k-1}} 
+\end{pmatrix}.
+\end{align}
+
+\newpage
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2025-02-05 Scripts/PlotOverlapVSSuccessProbability.py

@@ -1,0 +1,40 @@
+########################################################################################################
+#                                                                                                      #
+#  Project:  Physics TFG                                                                               #
+#  Author:   Sergio Castañeiras Morales                                                                #
+#  Date:     24/01/2025                                                                                #
+#  Purpose:  Plot Overlap VS Succes Probability for group generated states                             #
+#                                                                                                      #
+########################################################################################################
+
+import QSExSetUp
+import matplotlib.pyplot as plt
+
+FirstGroup                    = 2
+LastGroup                     = 10
+MatrixGenerationMethod        = "Zn"
+ProbabliltiesGenerationMethod = "Equal"
+Acuracy                       = 100
+
+colors = [plt.cm.rainbow(i / (LastGroup-FirstGroup)) for i in range(LastGroup+1-FirstGroup)]
+
+for i,iGroup in enumerate(range(FirstGroup,LastGroup+1)):
+    NumberOfMatrices              = iGroup
+    MatrixDimension               = iGroup
+    Overlap                       = 0
+    SuccesProbabilityList         = []
+    OverlapsList                  = []
+
+    for iPoint in range (1,Acuracy):
+        Overlap += 1/Acuracy
+        Conditions = QSExSetUp.GramGeneratedStates.GramGeneratedStatesClass(NumberOfMatrices,MatrixDimension,MatrixGenerationMethod, ProbabilitiesContructionMethod = ProbabliltiesGenerationMethod, Overlap = Overlap)
+        SuccesProbabilityList.append(Conditions.getSRMSuccessProbability())
+        OverlapsList.append(Overlap)
+    plt.plot(OverlapsList, SuccesProbabilityList, label = f'{MatrixGenerationMethod[0]}{iGroup}', color = colors[i])
+
+plt.xlabel("Overlap")
+plt.ylabel("Success Probability")
+plt.title(f"Group generated {MatrixGenerationMethod}")
+plt.legend()
+plt.savefig(f"../Plots/OverlapVSSucessProbability{MatrixGenerationMethod}from{FirstGroup}to{LastGroup}.pdf")
+

### 2025-02-05 Scripts/Testing1.py

@@ -12,12 +12,12 @@ import picos
 import numpy as np
 from scipy.linalg import sqrtm
 
-NumberOfMatrices              = 4
+NumberOfMatrices              = 3
 MatrixDimension               = 3
 MatrixGenerationMethod        = "GroupGeneratedStates"
 ProbabliltiesGenerationMethod = "Equal"
-initialState                  = picos.Constant([1,0,0])
-sigmaX                        = picos.Constant([[0,1,0],[1,0,0],[0,0,1]])
+initialState                  = picos.Constant([1,0])
+sigmaX                        = picos.Constant([[0,1],[1,0]])
 print(len(sigmaX.shape))
 Conditions                    = QSExSetUp.DensityMatricesAndPriorsClass.DensityMaticesAndPriors(NumberOfMatrices,MatrixDimension,MatrixGenerationMethod, ProbabliltiesGenerationMethod, seedState = initialState, involutoryMatrix = sigmaX)
 DensityMatrices               = Conditions.getDensityMatrices()

### 2025-02-05 Scripts/Testing2.py

@@ -18,24 +18,10 @@ MatrixDimension               = 10
 MatrixGenerationMethod        = "Zn"
 ProbabliltiesGenerationMethod = "Equal"
 Overlap                       = 0
-Acuracy                       = 100
-SuccesProbabilityList         = []
-OverlapsList                  = []
+Conditions = QSExSetUp.GramGeneratedStates.GramGeneratedStatesClass(NumberOfMatrices,MatrixDimension,MatrixGenerationMethod, ProbabilitiesContructionMethod = ProbabliltiesGenerationMethod, Overlap = Overlap)
 
-for i in range (1,Acuracy):
-    Overlap += 1/Acuracy
-    Conditions = QSExSetUp.GramGeneratedStates.GramGeneratedStatesClass(NumberOfMatrices,MatrixDimension,MatrixGenerationMethod, ProbabilitiesContructionMethod = ProbabliltiesGenerationMethod, Overlap = Overlap)
-    SuccesProbabilityList.append(Conditions.getSRMSuccessProbability())
-    OverlapsList.append(Overlap)
+print(Conditions)
 
-plt.scatter(OverlapsList, SuccesProbabilityList)
-plt.xlabel("Overlap")
-plt.ylabel("Success Probability")
-plt.title(f"Group generated Z{NumberOfMatrices}")
-plt.savefig(f"../Plots/OverlapVSSucessProbabilityZ{NumberOfMatrices}.pdf")
-
-
-"""
 print("------------------------\n\
 Computing the primal SDP\n\
 ------------------------")
@@ -45,4 +31,3 @@ Solution = QSExSetUp.SDPSolver.SolveSDPMinimumError(Conditions)
 print("The given problem has been:\n", Solution['SDPSolution'])
 
 print("The success probability is: ", round(Solution['SDPSolution'],4))
-"""

### 2025-02-05 Scripts/UsefullFunctions.py

@@ -72,7 +72,7 @@ def setOfGropGeneratedDensityMatrices(seedState, groupSize, involutionalMatrix):
     def groupGenerateStateDensityMatrix(seedState, groupSize, elementNumber, involutionalMatrix):
         if not isinstance(elementNumber, int): raise TyperError("The given value of the elementNumber must be an integer.")
         if elementNumber%groupSize == 0: return picos.Constant(seedState*seedState.H)
-        state = picos.Constant(expm(1j*involutionalMatrix*np.pi*(elementNumber%groupSize)/groupSize))*seedState
+        state = picos.Constant(expm(1j*involutionalMatrix*2*np.pi*(elementNumber%groupSize)/groupSize))*seedState
         if not np.allclose(state.value, seedState.value): return picos.Constant(state*state.H)
         raise ValueError(f"The given seed state is an eigen state of the given matrix.")
     return [groupGenerateStateDensityMatrix(seedState,groupSize,iElement, involutionalMatrix) for iElement in range(groupSize)]

### 2025-02-06 Notes/Notes.tex
Day of work again

@@
  1 & \sum_{k=0}^{n-1}|c_k|^2e^{i2\pi k/n} & \sum_{k=0}^{n-1}|c_k|^2e^{i4\pi k/n}  & \hdots &  \sum_{k=0}^{n-1}|c_k|^2e^{-i2\pi k/n} \\
-  \sum_{k=0}^{n-1}|c_k|^2e^{-i2\pi k/n} & 1 & \sum_{k=0}^{n-1}|c_k|^2e^{-i2\pi k/n} & \hdots & \sum_{k=0}^{n-1}|c_k|^2e^{-i4\pi k/n} \\
+  \sum_{k=0}^{n-1}|c_k|^2e^{-i2\pi k/n} & 1 & \sum_{k=0}^{n-1}|c_k|^2e^{i2\pi k/n} & \hdots & \sum_{k=0}^{n-1}|c_k|^2e^{-i4\pi k/n} \\
    \sum_{k=0}^{n-1}|c_k|^2e^{-i4\pi k/n} &  \sum_{k=0}^{n-1}|c_k|^2e^{-i2\pi k/n}  & 1 & \hdots & \sum_{k=0}^{n-1}|c_k|^2e^{-i6\pi k/n} \\
@@
 $\mathcal{U}$ but the statement $\braket{\mathcal{U}^{j}}_{\psi} =\braket{\mathcal{U}}_{\psi}$ still remains untrue in general.
+Regarding that $G_{i,j} =  \braket{\mathcal{U}^{-i+j}}_\psi $ one may find,
+\begin{align}
+G_{j,k}=\braket{\mathcal{U}^{-j+k}}_\psi= \sum_{\ell=0}^{n-1}|c_\ell|^2e^{i2\pi \ell(k-j)/n}\\
+G=\sum_{j,k,\ell=0}^{n-1}|c_\ell|^2e^{i2\pi \ell(k-j)/n}\ket{a_k}\bra{a_j}
+\end{align}
+
 \par 
@@
 \begin{observation}
-Let us analyse the case of the group generated ensemble of $\mathbb{Z}/2\mathbb{Z}\times\mathbb{Z}/2\mathbb{Z}$. We will denote 
+Let us analyse the case of the group generated ensemble of $\mathbb{Z}/2\mathbb{Z}\times\mathbb{Z}/2\mathbb{Z}$.
+We will denote $\mathcal{U},\tilde{\mathcal{U}}\in\mathcal{H}^4$ our generators that fulfil $\mathcal{U}^2=\tilde{\mathcal{U}}^2=\mathbb{I}_d$; $[\mathcal{U},\tilde{\mathcal{U}}]=0$ and $\mathcal{U}\neq\tilde{\mathcal{U}}$.
+From a given seed state $\ket{\psi}$ one gets the following group generated set $\{\ket{\psi},\mathcal{U}\ket{\psi},\tilde{\mathcal{U}}\ket{\psi},\mathcal{U}\tilde{\mathcal{U}}\ket{\psi}\}$.
+Hence the gram matrix is,
+\begin{align}
+G=\begin{pmatrix}
+1 & \braket{\mathcal{U}}_\psi & \braket{\tilde{\mathcal{U}}}_\psi &  \braket{\mathcal{U}\tilde{\mathcal{U}}}_\psi \\
+\braket{\mathcal{U}^\dagger}_\psi & 1 &  \braket{\mathcal{U}^\dagger\tilde{\mathcal{U}}}_\psi & \braket{\tilde{\mathcal{U}}}_\psi \\
+ \braket{\tilde{\mathcal{U}}^\dagger}_\psi &  \braket{\mathcal{U}\tilde{\mathcal{U}}^\dagger}_\psi & 1 & \braket{\mathcal{U}^\dagger}_\psi \\
+\braket{\mathcal{U}^\dagger\tilde{\mathcal{U}}^\dagger}_\psi & \braket{\tilde{\mathcal{U}}^\dagger}_\psi & \braket{\mathcal{U}}_\psi &  1
+\end{pmatrix}
+\end{align}
+since,
+\begin{align}
+\mathcal{U}^\dagger=\mathcal{U}^{-1}=\mathcal{U}\hspace{0.5cm}\tilde{\mathcal{U}}^\dagger=\tilde{\mathcal{U}}^{-1}=\tilde{\mathcal{U}}
+\end{align}
+we can write,
+\begin{align}
+G=\begin{pmatrix}
+1 & \braket{\mathcal{U}}_\psi & \braket{\tilde{\mathcal{U}}}_\psi &  \braket{\mathcal{U}\tilde{\mathcal{U}}}_\psi \\
+\braket{\mathcal{U}}_\psi & 1 &  \braket{\mathcal{U}\tilde{\mathcal{U}}}_\psi & \braket{\tilde{\mathcal{U}}}_\psi \\
+ \braket{\tilde{\mathcal{U}}}_\psi &  \braket{\mathcal{U}\tilde{\mathcal{U}}}_\psi & 1 & \braket{\mathcal{U}}_\psi \\
+\braket{\mathcal{U}\tilde{\mathcal{U}}}_\psi & \braket{\tilde{\mathcal{U}}}_\psi & \braket{\mathcal{U}}_\psi &  1
+\end{pmatrix}
+\end{align}
+The expected result \emoji{smiling-face-with-smiling-eyes}.
 \end{observation}
+
+\begin{observation}
+\textbf{It is a rearrangement of the clay table!!!!!!}
+\end{observation}
+
 \begin{observation}\label{ObsZnZm}

### 2025-02-06 Scripts/GramGeneratedFunctions.py

@@ -108,7 +108,7 @@ def GetGramDensityMatrices(GramMatrix, NumberOfStates):
     return States
 
 def SquareRootMeasurementSuccessPorbability(SquareRoot):
-    SquareRootDiagonal = np.diagonal(SquareRoot.value)
+    SquareRootDiagonal = np.diagonal(SquareRoot)
     sumSquare          = 0
     for iElement in SquareRootDiagonal: sumSquare += abs(iElement)**2
     return float(sumSquare)

### 2025-02-06 Scripts/GramGeneratedStates.py

@@ -62,6 +62,9 @@ class GramGeneratedStatesClass:
 
     def getSRMSuccessProbability(self):
         return self.to_dict()['SquareRootSuccessProbability']
+
+    def getGramMatrix(self):
+        return self.to_dict()['GramMatrix']
     
     def __repr__(self):
         PrintingText = "The working paramaters are:\n"

### 2025-02-06 Scripts/PlotOverlapVSSuccessProbability.py

@@ -9,7 +9,9 @@
 
 import QSExSetUp
 import matplotlib.pyplot as plt
+from tqdm import tqdm
 
+############################## Zn Plot ##############################
 FirstGroup                    = 2
 LastGroup                     = 10
 MatrixGenerationMethod        = "Zn"
@@ -18,19 +20,28 @@ Acuracy                       = 100
 
 colors = [plt.cm.rainbow(i / (LastGroup-FirstGroup)) for i in range(LastGroup+1-FirstGroup)]
 
-for i,iGroup in enumerate(range(FirstGroup,LastGroup+1)):
+for i, iGroup in enumerate(tqdm(range(FirstGroup, LastGroup + 1), desc="Calculating...")):
     NumberOfMatrices              = iGroup
     MatrixDimension               = iGroup
     Overlap                       = 0
-    SuccesProbabilityList         = []
+    SuccesProbabilitySRM          = []
+    SuccesProbabilitySDP          = []
     OverlapsList                  = []
 
     for iPoint in range (1,Acuracy):
-        Overlap += 1/Acuracy
-        Conditions = QSExSetUp.GramGeneratedStates.GramGeneratedStatesClass(NumberOfMatrices,MatrixDimension,MatrixGenerationMethod, ProbabilitiesContructionMethod = ProbabliltiesGenerationMethod, Overlap = Overlap)
-        SuccesProbabilityList.append(Conditions.getSRMSuccessProbability())
+        Overlap     += 1/Acuracy
+        Conditions  = QSExSetUp.GramGeneratedStates.GramGeneratedStatesClass(NumberOfMatrices,
+                                                                             MatrixDimension,
+                                                                             MatrixGenerationMethod, 
+                                                                             ProbabilitiesContructionMethod = ProbabliltiesGenerationMethod, 
+                                                                             Overlap = Overlap)
+        Solution    = QSExSetUp.SDPSolver.SolveSDPDualMinimumError(Conditions)
+        SuccesProbabilitySRM.append(Conditions.getSRMSuccessProbability())
+        SuccesProbabilitySDP.append(round(Solution['SDPSolution'],8))
         OverlapsList.append(Overlap)
-    plt.plot(OverlapsList, SuccesProbabilityList, label = f'{MatrixGenerationMethod[0]}{iGroup}', color = colors[i])
[…]

### 2025-02-06 Scripts/SDPSolver.py

@@ -71,22 +71,77 @@ def SolveSDPDualMinimumError(Conditions):
 def SolveSDPZeroError(Conditions):
     if not isinstance(Conditions,(DensityMatricesAndPriorsClass.DensityMaticesAndPriors,GramGeneratedStates.GramGeneratedStatesClass)):
         raise TypeError("The given conditions must be a DensityMatricesAndPriorsClass.DensityMaticesAndPriors or GramGeneratedStates.GramGeneratedStatesClass")
+
     MyDensityMatrices      = Conditions.getDensityMatrices()
     MyPriorsPropbabilities = Conditions.getPriorProbabilities()
     NumberOfMatrices       = Conditions.getNumberOfMatrices()
     NumberOfDimensions     = Conditions.getMatrixDimension()
     MySDP                  = picos.Problem()
-    POVMlist               = MyDensityMatrices
-    UncertainPOVM          = picos.HermitianVariable(f"UncertainPOVM", MyDensityMatrices[0].shape)
+
+    POVMlist = []
+    for iPOVM in range(NumberOfMatrices):
+        POVM = picos.HermitianVariable(f"POVM_{iPOVM}", MyDensityMatrices[iPOVM].shape)
+        POVMlist.append(POVM)
+
     UncertainProbability   = 0
 
-    for iElement in range(NumberOfMatrices):
-        UncertainProbability += MyPriorsPropbabilities[iElement]*picos.trace(UncertainPOVM*MyDensityMatrices[iElement])
+    for iPOVM in range(NumberOfMatrices):
+        UncertainProbability += MyPriorsPropbabilities[iPOVM]*picos.trace(MyDensityMatrices[iPOVM]*POVMlist[iPOVM])
 
-    MySDP.set_objective("min", UncertainProbability)
+    MySDP.set_objective("max", UncertainProbability)
 
-    MySDP.add_constraint(UncertainPOVM >> 0)
-    
+    for iPOVM in range(NumberOfMatrices):
+        MySDP.add_constraint(POVMlist[iPOVM]>>0)
+
+    I = np.eye(NumberOfDimensions) 
+    MySDP.add_constraint(sum(POVMlist) << picos.Constant(I))
+
+    for iPOVM in range(NumberOfMatrices):
+        for jPOVM in range(NumberOfMatrices):
+            if not iPOVM == jPOVM:
[…]

### 2025-02-06 Scripts/Testing1.py

@@ -12,8 +12,8 @@ import picos
 import numpy as np
 from scipy.linalg import sqrtm
 
-NumberOfMatrices              = 3
-MatrixDimension               = 3
+NumberOfMatrices              = 2
+MatrixDimension               = 2
 MatrixGenerationMethod        = "GroupGeneratedStates"
 ProbabliltiesGenerationMethod = "Equal"
 initialState                  = picos.Constant([1,0])
@@ -78,19 +78,4 @@ print("The given problem has been  :\n", Solution['SDPSolution'])
 print("The POVMs are               :\n", Solution['POVMs'])
 
 print("Uncertainity probability is :\n", round(Solution['SDPSolution'],4))
-
-print("The probability of perfect exclussion is:\n", round(1-float(Solution['SDPSolution']),4))
-
-
-UnknownPOVM = Solution["UncertainPOVM"]
-
-print("We do not now what is going on if the POVM is:\n",UnknownPOVM)
-
-for iElement, iPOVM in enumerate(Solution['POVMs']):
-    print(f"POVM {iElement}:")
-    print(iPOVM)
-    UnknownPOVM += iPOVM
-    print(f"DensityMatrices{iElement}:\n",picos.trace(DensityMatrices[iElement]*iPOVM))
-
-print("Does the sum equal the identity?\n",UnknownPOVM)
 

### 2025-02-06 Scripts/Testing2.py

@@ -13,21 +13,43 @@ import numpy as np
 from scipy.linalg import sqrtm
 import matplotlib.pyplot as plt
 
-NumberOfMatrices              = 10
-MatrixDimension               = 10
+NumberOfMatrices              = 4
+MatrixDimension               = 4
 MatrixGenerationMethod        = "Zn"
 ProbabliltiesGenerationMethod = "Equal"
-Overlap                       = 0
+Overlap                       = 0.5
 Conditions = QSExSetUp.GramGeneratedStates.GramGeneratedStatesClass(NumberOfMatrices,MatrixDimension,MatrixGenerationMethod, ProbabilitiesContructionMethod = ProbabliltiesGenerationMethod, Overlap = Overlap)
 
 print(Conditions)
 
+# print("------------------------\n\
+# Computing the primal SDP\n\
+# ------------------------")
+#
+# Solution = QSExSetUp.SDPSolver.SolveSDPMinimumError(Conditions)
+#
+# print("The given problem has been:\n", Solution['SDPSolution'])
+#
+# print("The success probability is: ", round(Solution['SDPSolution'],4))
+
 print("------------------------\n\
-Computing the primal SDP\n\
+Computing the Dual SDP\n\
 ------------------------")
 
-Solution = QSExSetUp.SDPSolver.SolveSDPMinimumError(Conditions)
+Solution = QSExSetUp.SDPSolver.SolveSDPDualMinimumError(Conditions)
 
 print("The given problem has been:\n", Solution['SDPSolution'])
 
 print("The success probability is: ", round(Solution['SDPSolution'],4))
+
+print("----------------------------\n\
+Computing the Zero Error SDP\n\
+----------------------------")
+
+Solution = QSExSetUp.SDPSolver.SolveSDPZeroError(Conditions)
+
+print("The given problem has been:\n", Solution['SDPSolution'])
+
+print("The success probability is: ", round(Solution['SDPSolution'],4))
+
+

### 2025-02-24 Notes/Notes.tex
Pretty plots

@@
 \useunder{\uline}{\ul}{}
+
+\DeclareMathOperator{\tr}{tr}
 
@@
 
+\begin{multicols}{2}
+\begin{observation}
+Let us write the SDP for unambiguous discrimination.
+Given a set of states $\{\rho_i=\ket{\psi_i}\bra{\psi_i}\}_{i=1}^{n}$, each of them with a prior probability of $\{\eta_i\}_{i=1}^{n}$ one may define the unambiguous SDP as,
+\begin{align}
+P_S=\max_{\{E_i\}}\sum_{i=1}^{n}&\eta_i\tr{(\rho_iE_i)}\\
+\text{s.t.}\hspace{0.5cm}E_i\geq&0\\
+\mathbb{I}_d-\sum_{i=1}^{n}E_i\geq&0\\
+\tr(\rho_iE_j)=&0\hspace{0.5cm}\forall j\neq i
+\end{align}
+\end{observation}
+However if we decompose the gram Matrix into $G=X^\dagger X$, one may find,
+\begin{align}
+X=&\sum_{i,j}\braket{\omega_i|\psi_j}\ket{\omega_i}\bra{\omega_j}\\
+X^\dagger=&\sum_{i,j}\braket{\psi_j|\omega_i}\ket{\omega_j}\bra{\omega_i}
+\end{align}
+since 
+\begin{align}
+X^\dagger X=&\left(\sum_{i,j}\braket{\psi_j|\omega_i}\ket{\omega_j}\bra{\omega_i}\right)\left(\sum_{k,l}\braket{\omega_k|\psi_l}\ket{\omega_k}\bra{\omega_l}\right)\\
+=&\sum_{i,j,k,l}\braket{\omega_k|\psi_l}\braket{\psi_j|\omega_i}\ket{\omega_j}\braket{\omega_i|\omega_k}\bra{\omega_l}\\
+=&\sum_{i,j,k,l}\braket{\omega_k|\psi_l}\braket{\psi_j|\omega_i}\ket{\omega_j}\bra{\omega_l}\delta_{ik}\\
+=&\sum_{i,j,l}\braket{\omega_i|\psi_l}\braket{\psi_j|\omega_i}\ket{\omega_j}\bra{\omega_l}\\
+=&\sum_{j,l}\left(\bra{\psi_l}\left(\sum_{i}\ket{\omega_{i}}\bra{\omega_j}\right)\ket{\psi_j}\ket{\omega_j}\bra{\omega_l}\right)\\
+=&\sum_{j,l}\braket{\psi_l|\psi_j}\ket{\omega_j}\bra{\omega_l}\\
+=&G
+\end{align}
+Since $X^{-1}X=\mathbb{I}_d$ it is immediate that the vectors formed by the rows of $X^{-1}$ denoted as $\ket{\chi_i}$ and the column vectors of $X$ (which are $\ket{\psi_i}$ expressed in the $\ket{\omega_{i}}$ base) fulfil $\braket{\chi_j|\psi_i}=\delta_{i,j}$.
+Hence, one might deduce the SDP constrain $\tr(\rho_iE_j)=0\hspace{0.5cm}\forall j\neq i$ can be eliminated by taking $E_j=\gamma_j\ket{\chi_j}\bra{\chi_j}$ for a certain values $\gamma_j\geq0$\footnote{The constrain of $\gamma_j\geq 0$ is given by the positive-definition of $E_j$ since is a POVM.} given that $\rho_i=\ket{\psi_i}\bra{\psi_i}$.
+We can also notice that,
+\begin{align}
+\sum_{i=1}^{n}E_i=&\sum_{i=1}^{n}\gamma_i\ket{\chi_i}\bra{\chi_i}\\
+=&(X^{-1})^\dagger\Gamma_DX^{-1}\implies\\
+\Gamma_D=&X^\dagger\left(\sum_{i=1}^{n}E_i\right)X
+\end{align}
+where $\Gamma_D$ is the diagonal matrix such that $\Gamma_{D_{i,j}}=\delta_{i,j}\gamma_i$. Then one might rewrite the constrain $\mathbb{I}_d-\sum_{i=1}^{n}E_i\geq0$ as 
+\begin{align}
+\mathbb{I}_d-\sum_{i=1}^{n}E_i\geq&0\implies\\
+X^\dagger X-X^\dagger\left(\sum_{i=1}^{n}E_i\right)X\geq&0\implies\\
+G-\Gamma_D\geq0
+\end{align}
+the constrain $\gamma_i\geq0$ can be written as $\gamma_D\geq0$. Then we might define a matrix
+
+\end{multicols}
+
 \newpage

### 2025-02-24 Scripts/GramGeneratedFunctions.py

@@ -10,6 +10,7 @@
 import numpy as np
 import picos
 from scipy.linalg import sqrtm
+import GramGeneratedStates
 
 def Hermitian(matrix, SilentMode = True):
     if not isinstance(matrix,(picos.expressions.exp_affine.AffineExpression,
@@ -69,18 +70,18 @@ def SetOfProbabilities (ProbabilitiesMethod, NumberOfMatrices):
 # Generating functions #
 ########################
 
-def GenerateGramMatrix(NumberOfMatrices, MatrixMethod, Overlap):
+def GenerateGramMatrix(NumberOfMatrices, MatrixMethod, GenerationConditions):
     if not isinstance(NumberOfMatrices,int):
         raise TypeError("The given NumberOfMatrices must be an Integer")
-    ValidMethods = ["Zn"]
+    ValidMethods = ["ZnOverlap", "ZnEigenValues"]
     if not MatrixMethod in ValidMethods:
         raise ValueError(f"The given MatrixMethod is not a valid method, the valid methods are: {ValidMethods}")
-    if not isinstance(Overlap, (float, int)):
-        raise TypeError("The given Overlap must be an Integer or a float")
-    if (Overlap > 1 or Overlap < 0):
-        raise ValueError("The given Overlap must be a number between 0 and 1.")
-    if MatrixMethod == "Zn":
-        return ZnGramMatrix(NumberOfMatrices, Overlap)
+    if not isinstance(GenerationConditions, (GramGeneratedStates.ZnGramMatrixConditionsOverlap,GramGeneratedStates.ZnGramMatrixConditionsEigenValues)):
+        raise TypeError("The GenerationConditions type is not valid")
+    if MatrixMethod == "ZnOverlap":
+        return ZnGramMatrixOverlap(NumberOfMatrices, GenerationConditions)
+    if MatrixMethod == "ZnEigenValues":
+        return ZnGramMatrixEigenValues(GenerationConditions)
 
 def GenerateGramMatrixWithPriors(GramMatrix, priorProbabilities, NumberOfStates):
     GramMatrixWithPriors = np.array(GramMatrix)
@@ -89,21 +90,66 @@ def GenerateGramMatrixWithPriors(GramMatrix, priorProbabilities, NumberOfStates)
             GramMatrixWithPriors[iState][jState] *= (np.sqrt(priorProbabilities[iState])*np.sqrt(priorProbabilities[jState]))
[…]

### 2025-02-24 Scripts/GramGeneratedStates.py

@@ -10,9 +10,10 @@
 import GramGeneratedFunctions
 from scipy.linalg import sqrtm
 import picos
+import numpy as np
 
 class GramGeneratedStatesClass:
-    def __init__(self, NumberOfMatrices, MatrixDimension, MatrixConstructionMethod, ProbabilitiesContructionMethod = "Equal", Overlap = 0):
+    def __init__(self, NumberOfMatrices, MatrixDimension, MatrixConstructionMethod, GenerationConditions, ProbabilitiesContructionMethod = "Equal"):
         if not isinstance(MatrixDimension,int):
             raise TypeError("The given MatrixDimension must be an Integer")
         if not isinstance(NumberOfMatrices,int):
@@ -21,15 +22,17 @@ class GramGeneratedStatesClass:
             raise TypeError("The given MatrixConstructionMethod is not a String")
         if not isinstance(ProbabilitiesContructionMethod,str):
             raise TypeError("The given ProbabilitiesContructionMethod is not a String")
+        if not isinstance(GenerationConditions, (ZnGramMatrixConditionsOverlap,ZnGramMatrixConditionsEigenValues)):
+            raise TypeError("The given GenerationConditions type in not valid.")
         self.NumberOfMatrices               = NumberOfMatrices
         self.MatrixDimension                = MatrixDimension
         self.MatrixConstructionMethod       = MatrixConstructionMethod
         self.ProbabilitiesContructionMethod = ProbabilitiesContructionMethod
         self.PriorProbabilities             = GramGeneratedFunctions.SetOfProbabilities(ProbabilitiesContructionMethod,NumberOfMatrices)
-        self.GramMatrix                     = GramGeneratedFunctions.GenerateGramMatrix(NumberOfMatrices,MatrixConstructionMethod, Overlap)
+        self.GramMatrix                     = GramGeneratedFunctions.GenerateGramMatrix(NumberOfMatrices,MatrixConstructionMethod, GenerationConditions)
         self.SquareRoot                     = picos.Constant(sqrtm(self.GramMatrix))
         self.GramMatrixWithPriors           = GramGeneratedFunctions.GenerateGramMatrixWithPriors(self.GramMatrix, self.PriorProbabilities,self.NumberOfMatrices)
-        self.SquareRootWithPriors           =picos.Constant(sqrtm(self.GramMatrixWithPriors))
+        self.SquareRootWithPriors           = picos.Constant(sqrtm(self.GramMatrixWithPriors))
[…]

### 2025-02-24 Scripts/PlotEigenValuesVSSuccessProbability.py

@@ -1,0 +1,133 @@
+########################################################################################################
+#                                                                                                      #
+#  Project:  Physics TFG                                                                               #
+#  Author:   Sergio Castañeiras Morales                                                                #
+#  Date:     22/02/2025                                                                                #
+#  Purpose:  Plot                                                                                      #
+#                                                                                                      #
+########################################################################################################
+
+import QSExSetUp
+import numpy as np
+import matplotlib.pyplot as plt
+from mpl_toolkits.mplot3d import Axes3D
+from tqdm import tqdm
+
+######################## Minimum Error Anlaysis ######################## 
+
+NumberOfMatrices              = 3
+MatrixDimension               = 3
+MatrixGenerationMethod        = "ZnEigenValues"
+ProbabliltiesGenerationMethod = "Equal"
+IterationsMinimumError        = 50000
+IterationsZeroError           = 5000
+DataMinimumError              = []
+DataZeroError                 = []
+
+for iIteration in tqdm(range(IterationsMinimumError),"Computing points for the Minimum Error plot"):
+    EigenValues                   = np.random.rand(NumberOfMatrices)
+    EigenValuesNormalized         = [iEigenValue*NumberOfMatrices/sum(EigenValues) for iEigenValue in EigenValues]
+    Conditions                    = QSExSetUp.GramGeneratedStates.GramGeneratedStatesClass(NumberOfMatrices,MatrixDimension,MatrixGenerationMethod, QSExSetUp.GramGeneratedStates.ZnGramMatrixConditionsEigenValues(EigenValuesNormalized, NumberOfMatrices), ProbabilitiesContructionMethod = ProbabliltiesGenerationMethod)
[…]

### 2025-02-24 Scripts/PlotOverlapVSSuccessProbability.py

@@ -10,76 +10,94 @@
 import QSExSetUp
 import matplotlib.pyplot as plt
 from tqdm import tqdm
+import numpy as np
+from mpl_toolkits.mplot3d import Axes3D
 
-############################## Zn Plot ##############################
-FirstGroup                    = 2
-LastGroup                     = 10
-MatrixGenerationMethod        = "Zn"
-ProbabliltiesGenerationMethod = "Equal"
-Acuracy                       = 100
-
-colors = [plt.cm.rainbow(i / (LastGroup-FirstGroup)) for i in range(LastGroup+1-FirstGroup)]
-
-for i, iGroup in enumerate(tqdm(range(FirstGroup, LastGroup + 1), desc="Calculating...")):
-    NumberOfMatrices              = iGroup
-    MatrixDimension               = iGroup
-    Overlap                       = 0
-    SuccesProbabilitySRM          = []
-    SuccesProbabilitySDP          = []
-    OverlapsList                  = []
-
-    for iPoint in range (1,Acuracy):
-        Overlap     += 1/Acuracy
-        Conditions  = QSExSetUp.GramGeneratedStates.GramGeneratedStatesClass(NumberOfMatrices,
-                                                                             MatrixDimension,
-                                                                             MatrixGenerationMethod, 
-                                                                             ProbabilitiesContructionMethod = ProbabliltiesGenerationMethod, 
-                                                                             Overlap = Overlap)
-        Solution    = QSExSetUp.SDPSolver.SolveSDPDualMinimumError(Conditions)
-        SuccesProbabilitySRM.append(Conditions.getSRMSuccessProbability())
-        SuccesProbabilitySDP.append(round(Solution['SDPSolution'],8))
-        OverlapsList.append(Overlap)
-    if i == 0: plt.scatter(OverlapsList, SuccesProbabilitySDP, label = "SDP",marker = ".", color = "grey")
-    else     : plt.scatter(OverlapsList, SuccesProbabilitySDP,marker = ".", color = "grey")
-    plt.plot(OverlapsList, SuccesProbabilitySRM, label = f'SRM{MatrixGenerationMethod[0]}{iGroup}', color = colors[i])
-
-plt.xlabel("Overlap")
-plt.ylabel("Success Probability")
[…]

### 2025-02-24 Scripts/SDPSolver.py

@@ -19,8 +19,6 @@ def SolveSDPMinimumError(Conditions):
     MyPriorsPropbabilities = Conditions.getPriorProbabilities()
     NumberOfMatrices       = Conditions.getNumberOfMatrices()
     NumberOfDimensions     = Conditions.getMatrixDimension()
-    
-    print(Conditions)
 
     MySDP = picos.Problem()
 
@@ -41,12 +39,34 @@ def SolveSDPMinimumError(Conditions):
 
     I = np.eye(NumberOfDimensions) 
     MySDP.add_constraint(sum(POVMlist) == picos.Constant(I))
-    
-    print(MySDP)
 
     MySDP.solve(solver="cvxopt")
 
     return {'SDPSolution' : MySDP, 'POVMs' : POVMlist}
+
+# def SolveSDPMinimumError(Conditions):
+#     if not isinstance(Conditions,(DensityMatricesAndPriorsClass.DensityMaticesAndPriors,GramGeneratedStates.GramGeneratedStatesClass)):
+#         raise TypeError("The given conditions must be a DensityMatricesAndPriorsClass.DensityMaticesAndPriors or GramGeneratedStates.GramGeneratedStatesClass")
+#     NumberOfMatrices     = Conditions.getNumberOfMatrices()
+#     GramMatrixWithPriors = Conditions.getGramMatrixWithPriors()
+#     MySDP                = picos.Problem()
+#     XMatrix              = picos.ComplexVariable('XMatrix', GramMatrixWithPriors.shape)
+#     SuccessProbability   = 0
+#
+#     for iElement in range(NumberOfMatrices):
+#         OrthonormalVectorList = []
+#         for jElement in range(NumberOfMatrices):
+#             if (iElement == jElement):
+#                 OrthonormalVectorList.append(1)
+#             else:
+#                 OrthonormalVectorList.append(0)
+#         OrthonormalVector = picos.Constant(OrthonormalVectorList)
+#         SuccessProbability += (OrthonormalVector.H*XMatrix*OrthonormalVector)*(OrthonormalVector.H*XMatrix.H*OrthonormalVector)
+#     MySDP.set_objective("max", SuccessProbability)
+#     MySDP.add_constraint(XMatrix.H*XMatrix == GramMatrixWithPriors)
+#     MySDP.solve(solver = 'cvxopt')
+#
+#     return {'SDPSolution' : MySDP}
 
[…]

### 2025-02-24 Scripts/Testing2.py

@@ -8,29 +8,25 @@
 ########################################################################################################
 
 import QSExSetUp
-import picos
-import numpy as np
-from scipy.linalg import sqrtm
-import matplotlib.pyplot as plt
 
 NumberOfMatrices              = 4
 MatrixDimension               = 4
-MatrixGenerationMethod        = "Zn"
+MatrixGenerationMethod        = "ZnEigenValues"
 ProbabliltiesGenerationMethod = "Equal"
-Overlap                       = 0.5
-Conditions = QSExSetUp.GramGeneratedStates.GramGeneratedStatesClass(NumberOfMatrices,MatrixDimension,MatrixGenerationMethod, ProbabilitiesContructionMethod = ProbabliltiesGenerationMethod, Overlap = Overlap)
+EigenValues                   = [1,1,1,1]
+Conditions                    = QSExSetUp.GramGeneratedStates.GramGeneratedStatesClass(NumberOfMatrices,MatrixDimension,MatrixGenerationMethod, QSExSetUp.GramGeneratedStates.ZnGramMatrixConditionsEigenValues(EigenValues, NumberOfMatrices), ProbabilitiesContructionMethod = ProbabliltiesGenerationMethod)
 
 print(Conditions)
 
-# print("------------------------\n\
-# Computing the primal SDP\n\
-# ------------------------")
-#
-# Solution = QSExSetUp.SDPSolver.SolveSDPMinimumError(Conditions)
-#
-# print("The given problem has been:\n", Solution['SDPSolution'])
-#
-# print("The success probability is: ", round(Solution['SDPSolution'],4))
+print("------------------------\n\
+Computing the primal SDP\n\
+------------------------")
+
+Solution = QSExSetUp.SDPSolver.SolveSDPMinimumError(Conditions)
+
+print("The given problem has been:\n", Solution['SDPSolution'])
+
+print("The success probability is: ", round(Solution['SDPSolution'],4))
 
 print("------------------------\n\
 Computing the Dual SDP\n\
@@ -52,4 +48,13 @@ print("The given problem has been:\n", Solution['SDPSolution'])
 
 print("The success probability is: ", round(Solution['SDPSolution'],4))
 
+print("---------------------------------\n\
+Computing the Dual SDP Zero Error\n\
+---------------------------------")
+
+Solution = QSExSetUp.SDPSolver.SolveSDPDualZeroError(Conditions)
+
+print("The given problem has been:\n", Solution['SDPSolution'])
+
[…]

### 2025-02-24 Scripts/Testing3.sage.py

@@ -1,19 +1,0 @@
-
-
-# This file was *autogenerated* from the file Testing3.sage
-from sage.all_cmdline import *   # import sage library
-
-_sage_const_4 = Integer(4)########################################################################################################
-#                                                                                                      #
-#  Project:  Physics TFG                                                                               #
-#  Author:   Sergio Castañeiras Morales                                                                #
-#  Date:     06/02/2025                                                                                #
-#  Purpose:  Testing                                                                                   #
-#                                                                                                      #
-########################################################################################################
-
-i = _sage_const_4 
-G = SymmetricGroup(i) 
-print(f"Printing S{i}:")
-show(G.cayley_table())
-

### 2025-04-07 Scripts/GramGeneratedFunctions.py
Norm plots

@@ -10,7 +10,10 @@
 import numpy as np
 import picos
 from scipy.linalg import sqrtm
+from scipy.linalg import qr
+from scipy.linalg import eig
 import GramGeneratedStates
+from scipy.stats import unitary_group
 
 def Hermitian(matrix, SilentMode = True):
     if not isinstance(matrix,(picos.expressions.exp_affine.AffineExpression,
@@ -73,7 +76,7 @@ def SetOfProbabilities (ProbabilitiesMethod, NumberOfMatrices):
 def GenerateGramMatrix(NumberOfMatrices, MatrixMethod, GenerationConditions):
     if not isinstance(NumberOfMatrices,int):
         raise TypeError("The given NumberOfMatrices must be an Integer")
-    ValidMethods = ["ZnOverlap", "ZnEigenValues"]
+    ValidMethods = ["ZnOverlap", "ZnEigenValues", "Random"]
     if not MatrixMethod in ValidMethods:
         raise ValueError(f"The given MatrixMethod is not a valid method, the valid methods are: {ValidMethods}")
     if not isinstance(GenerationConditions, (GramGeneratedStates.ZnGramMatrixConditionsOverlap,GramGeneratedStates.ZnGramMatrixConditionsEigenValues)):
@@ -82,6 +85,8 @@ def GenerateGramMatrix(NumberOfMatrices, MatrixMethod, GenerationConditions):
         return ZnGramMatrixOverlap(NumberOfMatrices, GenerationConditions)
     if MatrixMethod == "ZnEigenValues":
         return ZnGramMatrixEigenValues(GenerationConditions)
+    if MatrixMethod == "Random":
+        return RandomGramMatrixEigenValues(GenerationConditions)
 
 def GenerateGramMatrixWithPriors(GramMatrix, priorProbabilities, NumberOfStates):
     GramMatrixWithPriors = np.array(GramMatrix)
@@ -114,11 +119,11 @@ def ZnGramMatrixOverlap(NumberOfStates, GenerationConditions):
                 continue
             GramMatrixRow.append(OverlapList[ListToMatrixZn(iState,jState,n)]*np.exp(1j * PhaseList[ListToMatrixZn(iState,jState,n)]))
         GramMatrix.append(GramMatrixRow)
-    return 0.5*(picos.Constant(GramMatrix)+picos.Constant(GramMatrix).H)
+    GramMatrix = 0.5*(picos.Constant(GramMatrix)+picos.Constant(GramMatrix).H)
[…]

### 2025-04-07 Scripts/GramGeneratedStates.py

@@ -29,13 +29,15 @@ class GramGeneratedStatesClass:
         self.MatrixConstructionMethod       = MatrixConstructionMethod
         self.ProbabilitiesContructionMethod = ProbabilitiesContructionMethod
         self.PriorProbabilities             = GramGeneratedFunctions.SetOfProbabilities(ProbabilitiesContructionMethod,NumberOfMatrices)
-        self.GramMatrix                     = GramGeneratedFunctions.GenerateGramMatrix(NumberOfMatrices,MatrixConstructionMethod, GenerationConditions)
+        GramMatrixAndUnitaryMatrix          = GramGeneratedFunctions.GenerateGramMatrix(NumberOfMatrices,MatrixConstructionMethod, GenerationConditions)
+        self.GramMatrix                     = GramMatrixAndUnitaryMatrix["GramMatrix"]
         self.SquareRoot                     = picos.Constant(sqrtm(self.GramMatrix))
         self.GramMatrixWithPriors           = GramGeneratedFunctions.GenerateGramMatrixWithPriors(self.GramMatrix, self.PriorProbabilities,self.NumberOfMatrices)
         self.SquareRootWithPriors           = picos.Constant(sqrtm(self.GramMatrixWithPriors))
         self.DensityMatrices                = GramGeneratedFunctions.GetGramDensityMatrices(self.GramMatrix, self.NumberOfMatrices)
         self.SquareRootSuccessProbability   = GramGeneratedFunctions.SquareRootMeasurementSuccessPorbability(self.SquareRootWithPriors)
         self.PerfectExlusion                = GramGeneratedFunctions.PerfectExlusion(self.GramMatrixWithPriors)
+        self.UnitaryMatrix                  = GramMatrixAndUnitaryMatrix["UnitaryMatrix"]
     def to_dict(self):
         return {
             'NumberOfMatrices'               : self.NumberOfMatrices,
@@ -49,7 +51,8 @@ class GramGeneratedStatesClass:
             'SquareRootWithPriors'           : self.SquareRootWithPriors,
             'DensityMatrices'                : self.DensityMatrices,
             'SquareRootSuccessProbability'   : self.SquareRootSuccessProbability,
-            'PerfectExlusion'                : self.PerfectExlusion
+            'PerfectExlusion'                : self.PerfectExlusion,
+            'UnitaryMatrix'                  : self.UnitaryMatrix
         }
     def __getitem__(self, key):
[…]

### 2025-04-07 Scripts/NormVSExclussionProbability.py

@@ -1,0 +1,54 @@
+########################################################################################################
+#                                                                                                      #
+#  Project:  Physics TFG                                                                               #
+#  Author:   Sergio Castañeiras Morales                                                                #
+#  Date:     05/04/2025                                                                                #
+#  Purpose:  Testing                                                                                   #
+#                                                                                                      #
+########################################################################################################
+import picos
+import QSExSetUp
+import numpy as np
+import matplotlib.pyplot as plt
+from tqdm import tqdm
+
+NumberOfMatrices              = 51
+MatrixDimension               = 51
+MatrixGenerationMethod        = "Random"
+ProbabliltiesGenerationMethod = "Equal"
+EigenValues                   = [10 for i in range(NumberOfMatrices - 1)]
+EigenValues.append(100)
+EigenValuesNormalized         = [iEigenValue*NumberOfMatrices/sum(EigenValues) for iEigenValue in EigenValues]
+Iterations                    = 1000
+GroupGeneratedConditions      = QSExSetUp.GramGeneratedStates.GramGeneratedStatesClass(NumberOfMatrices,MatrixDimension, "ZnEigenValues", QSExSetUp.GramGeneratedStates.ZnGramMatrixConditionsEigenValues(EigenValuesNormalized, NumberOfMatrices), ProbabilitiesContructionMethod = ProbabliltiesGenerationMethod)
+
+
+DistanceFrobenius             = []
+Distance1                     = []
+DistanceInfinite              = []
+DistanceSpectral              = []
+DistanceNuclear               = []
+ExlusionSuccessProbability    = []
+
+for iIteration in tqdm(range(Iterations),"Computing SDP"):
+    Conditions = QSExSetUp.GramGeneratedStates.GramGeneratedStatesClass(NumberOfMatrices,MatrixDimension,MatrixGenerationMethod, QSExSetUp.GramGeneratedStates.ZnGramMatrixConditionsEigenValues(EigenValuesNormalized, NumberOfMatrices), ProbabilitiesContructionMethod = ProbabliltiesGenerationMethod)
[…]

### 2025-04-07 Scripts/PlotExclusion.py

@@ -52,7 +52,7 @@ plt.colorbar(sc, ax=ax, label="Exclusion probability")
 
 ax.set_xlabel("Overlap")
 ax.set_ylabel("Phase (radians)")
-# ax.set_title(f"Z{NumberOfMatrices} - Heat Map Overlap vs. Phase vs. Perfect Exclusion Probability")
+# plt.show()
 plt.savefig(f"../Plots/ExlusionOverlapVSPhaseVSMinimumErrorProbabilityZ{NumberOfMatrices}HeatMap.pdf")
 plt.close()
 
@@ -100,6 +100,6 @@ plt.scatter(Overlap_values1, Phase_values1, c='darkred', label = 'Perfect exclus
 plt.xlabel("Overlap")
 plt.ylabel("Phase (radians)")
 plt.legend()
-# plt.title(f"Z{NumberOfMatrices} - Representation of the perfect exclusion zone")
 plt.savefig(f"../Plots/ExlusionOverlapVSPhaseVSPerfectExclussionZoneZ{NumberOfMatrices}BinaryHeatMap.pdf")
-
+# plt.show()
+plt.close()

### 2025-04-07 Scripts/PlotExclusionRandomEigenValues.py

@@ -1,0 +1,135 @@
+########################################################################################################
+#                                                                                                      #
+#  Project:  Physics TFG                                                                               #
+#  Author:   Sergio Castañeiras Morales                                                                #
+#  Date:     05/03/2025                                                                                #
+#  Purpose:  Plot                                                                                      #
+#                                                                                                      #
+########################################################################################################
+
+import QSExSetUp
+import numpy as np
+import matplotlib.pyplot as plt
+from mpl_toolkits.mplot3d import Axes3D
+from tqdm import tqdm
+import mpltern
+
+NumberOfMatrices              = 3
+MatrixDimension               = 3
+MatrixGenerationMethod        = "Random"
+ProbabliltiesGenerationMethod = "Equal"
+IterationsRandomSets          = 50000
+DataMinimumError              = []
+EigenValue0                   = []
+EigenValue1                   = []
+SDPMinimumErrorList           = []
+LowerBound                    = []
+
+for iIteration in tqdm(range(IterationsRandomSets),"Computing points for the Minimum Error plot"):
+    EigenValues             = np.random.rand(NumberOfMatrices)
+    EigenValuesNormalized   = [iEigenValue*NumberOfMatrices/sum(EigenValues) for iEigenValue in EigenValues]
+    Conditions              = QSExSetUp.GramGeneratedStates.GramGeneratedStatesClass(NumberOfMatrices,MatrixDimension,MatrixGenerationMethod, QSExSetUp.GramGeneratedStates.ZnGramMatrixConditionsEigenValues(EigenValuesNormalized, NumberOfMatrices), ProbabilitiesContructionMethod = ProbabliltiesGenerationMethod)
+    if Conditions.getPerfectExlusion():
[…]

### 2025-04-07 Scripts/SDPSolver.py

@@ -163,11 +163,10 @@ def SolveSDPExlusionDualMinimumError(Conditions):
     MySDP                  = picos.Problem()
     LagrangeMultiplierY    = picos.HermitianVariable("LagrangeMultiplier", MyDensityMatrices[0].shape)
 
-    MySDP.set_objective("max", picos.trace(LagrangeMultiplierY))
+    MySDP.set_objective("min", 1 - picos.trace(LagrangeMultiplierY))
     
     for iContrain in range(NumberOfMatrices):
         MySDP.add_constraint(MyPriorsPropbabilities[iContrain]*MyDensityMatrices[iContrain]-LagrangeMultiplierY >> 0)
-    MySDP.add_constraint(LagrangeMultiplierY >> 0)
 
     MySDP.solve(solver="mosek")
 

### 2025-04-07 Scripts/Testing1.py

@@ -1,4 +1,4 @@
-########################################################################################################
+#######################################################################################################
 #                                                                                                      #
 #  Project:  Physics TFG                                                                               #
 #  Author:   Sergio Castañeiras Morales                                                                #
@@ -11,11 +11,10 @@ import QSExSetUp
 
 NumberOfMatrices              = 3
 MatrixDimension               = 3
-MatrixGenerationMethod        = "ZnEigenValues"
+MatrixGenerationMethod        = "Random"
 ProbabliltiesGenerationMethod = "Equal"
 EigenValues                   = [1,2,10]
 EigenValuesNormalized         = [iEigenValue*NumberOfMatrices/sum(EigenValues) for iEigenValue in EigenValues]
-print(EigenValuesNormalized)
 Conditions                    = QSExSetUp.GramGeneratedStates.GramGeneratedStatesClass(NumberOfMatrices,MatrixDimension,MatrixGenerationMethod, QSExSetUp.GramGeneratedStates.ZnGramMatrixConditionsEigenValues(EigenValuesNormalized, NumberOfMatrices), ProbabilitiesContructionMethod = ProbabliltiesGenerationMethod)
 
 print(Conditions)
@@ -86,7 +85,7 @@ Solution = QSExSetUp.SDPSolver.SolveSDPExlusionDualMinimumError(Conditions)
 
 print("The given problem has been:\n", Solution['SDPSolution'])
 
-print("The success probability is: ", 1 - round(Solution['SDPSolution'],4))
+print("The success probability is: ", round(Solution['SDPSolution'],4))
 
 print("-----------------------------------\n\
 Computing the primal SDP Zero Error\n\

### 2025-04-07 Scripts/Testing2.py

@@ -1,0 +1,55 @@
+#######################################################################################################
+#                                                                                                      #
+#  Project:  Physics TFG                                                                               #
+#  Author:   Sergio Castañeiras Morales                                                                #
+#  Date:     24/01/2025                                                                                #
+#  Purpose:  Testing                                                                                   #
+#                                                                                                      #
+########################################################################################################
+
+import picos
+import QSExSetUp
+import numpy as np
+import matplotlib.pyplot as plt
+from tqdm import tqdm
+
+NumberOfMatrices              = 5
+MatrixDimension               = 5
+MatrixGenerationMethod        = "Random"
+ProbabliltiesGenerationMethod = "Equal"
+EigenValues                   = [0.1 for i in range(NumberOfMatrices - 1)]
+EigenValues.append(100)
+EigenValuesNormalized         = [iEigenValue*NumberOfMatrices/sum(EigenValues) for iEigenValue in EigenValues]
+Iterations                    = 10000
+GroupGeneratedConditions      = QSExSetUp.GramGeneratedStates.GramGeneratedStatesClass(NumberOfMatrices,MatrixDimension, "ZnEigenValues", QSExSetUp.GramGeneratedStates.ZnGramMatrixConditionsEigenValues(EigenValuesNormalized, NumberOfMatrices), ProbabilitiesContructionMethod = ProbabliltiesGenerationMethod)
+
+
+DistanceFrobenius             = []
+Distance1                     = []
+DistanceInfinite              = []
+DistanceSpectral              = []
+DistanceNuclear               = []
+ExlusionSuccessProbability    = []
+
+for iIteration in tqdm(range(Iterations),"Computing SDP"):
+    Conditions = QSExSetUp.GramGeneratedStates.GramGeneratedStatesClass(NumberOfMatrices,MatrixDimension,MatrixGenerationMethod, QSExSetUp.GramGeneratedStates.ZnGramMatrixConditionsEigenValues(EigenValuesNormalized, NumberOfMatrices), ProbabilitiesContructionMethod = ProbabliltiesGenerationMethod)
[…]

### 2025-04-07 Scripts/Testing3.py

@@ -1,0 +1,52 @@
+import QSExSetUp
+import numpy as np
+import picos
+from tqdm import tqdm
+from scipy.stats import unitary_group
+
+NumberOfMatrices              = 5
+MatrixDimension               = 5
+MatrixGenerationMethod        = "Random"
+ProbabliltiesGenerationMethod = "Equal"
+EigenValues                   = [0.1,0.1,0.1,0.1,100]
+EigenValuesNormalized         = [iEigenValue*NumberOfMatrices/sum(EigenValues) for iEigenValue in EigenValues]
+Iterations                    = 10000
+GroupGeneratedConditions      = QSExSetUp.GramGeneratedStates.GramGeneratedStatesClass(NumberOfMatrices,MatrixDimension, "ZnEigenValues", QSExSetUp.GramGeneratedStates.ZnGramMatrixConditionsEigenValues(EigenValuesNormalized, NumberOfMatrices), ProbabilitiesContructionMethod = ProbabliltiesGenerationMethod)
+
+print(picos.Norm(GroupGeneratedConditions.getUnitaryMatrix() - GroupGeneratedConditions.getUnitaryMatrix(),1))
+
+DistanceFrobenius             = []
+Distance1                     = []
+DistanceInfinite              = []
+DistanceSpectral              = []
+DistanceNuclear               = []
+ExlusionSuccessProbability    = []
+
+def random_unitary(n):
+    # Create a random complex matrix
+    A = np.random.randn(n, n) + 1j * np.random.randn(n, n)
+    # QR decomposition
+    Q, R = np.linalg.qr(A)
+    # Normalize to make Q unitary
+    D = np.diag(R) / np.abs(np.diag(R))
+    Q = Q @ np.diag(D.conj())
+    return Q
+from scipy.linalg import expm
+
+def skew_hermitian(n):
+    A = np.random.randn(n, n) + 1j * np.random.randn(n, n)
+    return A - A.conj().T
+
+def unitary_from_exponential(n):
+    A = skew_hermitian(n)
+    return expm(A)
+
+for iIteration in tqdm(range(Iterations),"Computing SDP"):
+    DistanceFrobenius.append(picos.Norm(GroupGeneratedConditions.getUnitaryMatrix() - random_unitary(NumberOfMatrices),2))
[…]

### 2025-04-08 Manuscript/Manuscript.tex
writting

--- 2025-02-05 Notes/Notes.tex
@@
 \usepackage[english]{babel}
-\usepackage{emoji}
 \usepackage{lipsum}
-\usepackage{braket}
 \usepackage[table,xcdraw]{xcolor}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+\usepackage{titlesec}
+\usepackage{textcase} % for uppercase handling
+
+% --- Section formatting ---
+\titleformat{\section}
+  {\normalfont\normalsize\bfseries\centering} % font size, bold, centered
+  {\thesection}{1em}{\MakeTextUppercase} % uppercase text
+
+% --- Subsection formatting ---
+\titleformat{\subsection}
+  {\normalfont\large\bfseries\centering}
+  {\thesubsection}{1em}{\MakeTextUppercase}
+
+% --- Roman numerals for numbering ---
+\renewcommand{\thesection}{\Roman{section}}
+\renewcommand{\thesubsection}{\Roman{section}.\roman{subsection}}
 
@@
 \newcommand\degree{Bachelor's Degree in Physics}
-\newcommand\documenttitle{Notes: Quantum State Exclusion - Temporal Name -}
+\newcommand\documenttitle{Lower bounds of the success probability in quantum state exclusion for general ensembles}
 \newcommand\NetIDb{Universitat Autònoma de Barcelona}
+\newcommand\AuthorName{Sergio Castañeiras Morales}
+
+\hypersetup{%
+  pdftitle  = \documenttitle,
+  pdfauthor = \AuthorName,
+  pdfsubject= \degree,
+  pdfcreator= \AuthorName,
+}
 
@@
 		\normalsize \begin{tabular}{rcl}  % Create a right-left column alignment
-        \textsc{Author} & : & \textsc{Sergio Castañeiras Morales} \\
+        \textsc{Author} & : & \textsc{\AuthorName} \\
         \textsc{Supervisor} & : & \textsc{Ramón Muñoz Tapia} \\
@@
 
+\thispagestyle{empty}
+\mbox{} 
 \newpage
@@
 \begin{flushright}
-    \emph{“The dumbest people I know are those who know it all.”}\\[1em]
+    \emph{The dumbest people I know are those who know it all.}\\[1em]
     \textbf{Malcolm S. Forbes}
 \end{flushright}
-\vspace*{\fill} % Balance vertical spacing
+\vspace*{\fill} 
+\newpage
 
@@
 \lhead{\NetIDb}    
-\rhead{\subject}
+\rhead{\degree}
 \cfoot{}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%% DEFINITIONS %%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{multicols}{2}[\begin{center}
+\begin{abstract}
+Given a quantum state known to be prepared from an ensemble of two or more states, quantum state exclusion aims to rule out the possibility that it was prepared in a particular state from the ensemble.
+Using the known solution for group generated ensembles \cite{MainPaper}, we study this result as a lower bound for randomly generated ensembles via semidefinite programming.
+\end{abstract}
+\end{center}
+Keywords: \emph{SDP, Quantum state exclusion , \textcolor{blue}{Add keywords}}.
+]
+\section{Introduction}
 
-\begin{multicols}{2}
-[
-\section{Definitions}
-]
-\begin{definition}
-\textbf{Completely positive map}: "Let $ A $ and $ B $ be C*-algebras. A linear map $ \phi: A \to B $ is called a \textit{positive map} if $ \phi $ maps positive elements to positive elements:
-\begin{align}
-a \geq 0 \implies \phi(a) \geq 0.
-\end{align}
+In many real-world scenarios, excluding a certain hypothesis can be more practical than solving the problem entirely.
+For instance, in disease diagnosis, ruling out potential diseases often serves as the first step in identifying the actual condition.
+Similarly, when repairing a machine, it is sometimes more efficient to identify the components that are functioning correctly, which narrows down the search for the faulty part.
 
-Any linear map $ \phi: A \to B $ induces another map
-\begin{align}
-\mathrm{id} \otimes \phi : \mathbb{C}^{k \times k} \otimes A \to \mathbb{C}^{k \times k} \otimes B
-\end{align}
-in a natural way.
-If $ \mathbb{C}^{k \times k} \otimes A $ is identified with the C*-algebra $ A^{k \times k} $ of $ k \times k $-matrices with entries in $ A $, then $ \mathrm{id} \otimes \phi $ acts as
-\begin{align}
-\begin{pmatrix}
-a_{11} & \cdots & a_{1k} \\
-\vdots & \ddots & \vdots \\
-a_{k1} & \cdots & a_{kk}
-\end{pmatrix}
-\mapsto
-\begin{pmatrix}
-\phi(a_{11}) & \cdots & \phi(a_{1k}) \\
-\vdots & \ddots & \vdots \\
-\phi(a_{k1}) & \cdots & \phi(a_{kk})
-\end{pmatrix}.
-\end{align}
+In this project, we adapt this concept to the quantum domain, focusing on the exclusion of quantum states.
+Rather than directly determining the exact state of a quantum system, we explore the process of eliminating states from a known ensemble, which may be more suitable or efficient in certain quantum applications.
 
-The map $ \phi $ is called \textit{k-positive} if $ \mathrm{id}_{\mathbb{C}^{k \times k}} \otimes \phi $ is a positive map, and \textit{completely positive} if $ \phi $ is $ k $-positive for all $ k $."\cite{completely_positive_map_Wikipedia}
-\end{definition}
-\begin{definition}\textbf{Kraus operator: } 
-\end{definition}
-
-\begin{definition}\label{innerProductDefinition}
-\textbf{Inner product}: Given a vector space $A$ and a field $F$ we define the an inner product $\langle \cdot , \cdot \rangle$ as $\langle \cdot , \cdot \rangle:A\times A\rightarrow F$ that satisfies the following properties.
-Given $x,y,z\in A$ and $\lambda,\mu\in F$:
-\begin{enumerate}
-\item Conjugate symmetry: $\langle x,y\rangle=(\langle y,x\rangle)^*$.
-\item Linearity: $\langle \lambda x+\mu y, z\rangle=\lambda\langle  x, z\rangle+\mu\langle  y, z\rangle$
-\item Positive-definiteness: $\langle x,x\rangle>0$ if $x\neq0$
-\end{enumerate}
-\end{definition}
-
-\begin{definition}
-\textbf{Inner product space}: Given a vector space $A$ and a field $F$ we define the  inner product space as the duple $(A,\langle \cdot , \cdot \rangle)$ such that  $\langle \cdot , \cdot \rangle:A\times A\rightarrow F$ is an inner product.
-\end{definition}
-
-\begin{definition}\label{defGramMatrix}
-\textbf{Gram matrix}: Given a vector space $A$, a field $F$ , a set of vectors $\{v_i\}_{i=0}^n\subset A$ and an inner product space such that  $\langle \cdot , \cdot \rangle:A\times A\rightarrow F$  the Gram matrix $G$ is defined as the matrix $G\in F^{n\times n}$ whose entries are $g_{i,j}=\langle v_i,v_j\rangle$ i.e,
-\begin{align}
-G=\begin{pmatrix}
-\langle v_1,v_1\rangle & \hdots & \langle v_1,v_n\rangle\\
-\vdots & \ddots & \vdots\\
-\langle v_n,v_1\rangle & \hdots & \langle v_n,v_n\rangle
-\end{pmatrix}.
-\end{align}
-Due to the first property of the inner product definition \ref{innerProductDefinition} it is immediate that $G^\dagger =G$ in other word G is hemitian (trivial proof).
-\end{definition}
-
-\end{multicols}
-\newpage
-
-\begin{multicols}{2}
-\begin{observation}
-Let $\mathcal{U}$ be a unitary matrix such that $\mathcal{U}^n=\mathbb{I}_d$ and $\mathcal{U}^i\neq\mathbb{I}_d\;\;\forall i\in\{0,...,n-1\}$, let $\ket{\psi}$ also be a normalised state.
-We might define the set of quantum states $\Omega=\{\ket{\psi_i}=\mathcal{U}^i\ket{\psi}\}_{i=0}^{n-1}$ a group generated ensamble of states, since the set  $\{\mathcal{U}^i\}_{i=0}^{n-1}$ is obviously a group with the usual product.
-From the group structure of $\{\mathcal{U}^i\}_{i=0}^{n-1}$ it is natural to define $\star$ operation such that,
-\begin{align}
-\star:\Omega\times\Omega\rightarrow&\Omega\\
-(\ket{\psi_i},\ket{\psi_j})\mapsto&\ket{\psi_{i+j}}.
-\end{align}
-Hence we observe the ensamble of states inherites the group structure from the generator $\mathcal{U}$ nature.
-More particularly, $\Omega$ is isomorphic to $\mathbb{Z}/n\mathbb{Z}$.
-Hence we want to compute the gram matrix of $\Omega$, applying the Definition (\ref{defGramMatrix}) we obtain,
-\begin{align}
-G_{i,j} =& \braket{\psi_{i}|\psi_{j}} \\
-=& \bra{\psi} \left(\mathcal{U}^i\right)^\dagger U^j\ket{\psi}\\
-=& \bra{\psi} \left(\mathcal{U}^\dagger\right)^i U^j\ket{\psi}\\
-=& \bra{\psi} \left(\mathcal{U}^{-1}\right)^i U^j\ket{\psi}\\
-=& \bra{\psi} \mathcal{U}^{-i} U^j\ket{\psi}\\
-=& \braket{\mathcal{U}^{-i+j}}_\psi.
-\end{align}
-The gram matrix must have the shape
-\begin{align}
-G=\begin{pmatrix}
- 1 & \braket{\mathcal{U}^{1}}_{\psi} & \hdots &  \braket{\mathcal{U}^{n-1}}_{\psi} \\
-  \braket{\mathcal{U}^{-1}}_{\psi} & 1 & \hdots &  \braket{\mathcal{U}^{n-2}}_{\psi} \\
-   \vdots & \vdots & \ddots & \vdots \\
-  \braket{\mathcal{U}^{-n+1}}_{\psi} & \braket{\mathcal{U}^{-n+2}}_{\psi}  & \hdots &  1
-\end{pmatrix}.
-\end{align}
-Since $\braket{\mathcal{U}^{-j}}_{\psi}=\braket{\mathcal{U}^{j}}_{\psi}^*$ the hermicity is preserved (as it should). Also we note that,
-\begin{align}
-\braket{\mathcal{U}^{-n+i}}_{\psi}=\braket{\mathcal{U}^{-n+i}\mathbb{I}_d}_{\psi}=\braket{\mathcal{U}^{-n+i}\mathcal{U}^{n}}_{\psi}=\braket{\mathcal{U}^{i}}_{\psi}
-\end{align}
-hence,
-\begin{align}
-G=\begin{pmatrix}
- 1 & \braket{\mathcal{U}}_{\psi} & \braket{\mathcal{U}^{2}}_{\psi} & \hdots &  \braket{\mathcal{U}}_{\psi}^* \\
-  \braket{\mathcal{U}}_{\psi}^* & 1 & \braket{\mathcal{U}}_{\psi} & \hdots &  \braket{\mathcal{U}^{2}}_{\psi}^* \\
-    \braket{\mathcal{U}^{2}}_{\psi}^* &  \braket{\mathcal{U}}_{\psi}^*  & 1 & \hdots &  \braket{\mathcal{U}^{3}}_{\psi}^* \\
-   \vdots & \vdots & \vdots & \ddots & \vdots \\
-  \braket{\mathcal{U}}_{\psi} & \braket{\mathcal{U}^{2}}_{\psi}  & \braket{\mathcal{U}^{3}}_{\psi}  & \hdots &  1 
-\end{pmatrix}.
-\end{align}
-\textbf{Question} how does $\braket{\mathcal{U}^{j}}_{\psi}$ depend on $\braket{\mathcal{U}}_{\psi}$.
-I know we have said $\braket{\mathcal{U}^{j}}_{\psi} =\braket{\mathcal{U}}_{\psi}$ but I cannot see why \emoji{sad-but-relieved-face}\par
-As a matter of fact by computing some matrices I can get situations such that $\braket{\mathcal{U}^{i}}_{\psi}=0$ for instance by performing a rotation of $\pi/4$ in the $x$ axis of the state pointing in the $z$ direction I can get a group generated ensamble of $\mathbb{Z}/4\mathbb{Z}$.
-But the second state (rotation of $\pi/2$) is orthogonal to the first state and $\braket{\mathcal{U}^2}_{\psi}=0\neq \frac{1}{\sqrt{2}}\braket{\mathcal{U}}_{\psi}$.
-\par
-\textbf{Stuff I know},\par 
-Since $\mathcal{U}$ is an unitary matrix such that $\mathcal{U}^n=\mathbb{I}_d$ I know that in the basis of eigenvalues of $\mathcal{U}$ denoted as $\{\ket{u_i}\}_{i=0}^{n-1}$
-\begin{align}
-\mathcal{U}=\sum_{k=0}^{n-1}e^{i2\pi k/n}\ket{u_k}\bra{u_k}
-\end{align}
-Let $\ket{\psi}=\sum_{i=0}^{n-1}c_i\ket{u_i}$ be the expression of $\ket{\psi}$ in the $\{\ket{u_i}\}_{i=0}^{n-1}$ basis.
-Notice from the unicity of $\mathcal{U}$ can be expressed as $\mathcal{U}=e^{iA}$ for a hermitian matrix $A$, which decomposes in the basis orthonormal basis as $A=\sum_{i=0}^{n-1}\alpha_i\ket{a_i}\bra{a_i}$.
-Therefore,
-\begin{align}
-\mathcal{U}=&e^{iA}\\
-=&\sum_{j=0}^{\infty}\frac{i^j}{j!}A^j\\
-=&\sum_{j=0}^{\infty}\frac{i^j}{j!}\left(\sum_{k=0}^{n-1}\alpha_k\ket{a_k}\bra{a_k}\right)^j\\
-=&\sum_{j=0}^{\infty}\frac{i^j}{j!}\sum_{k=0}^{n-1}\alpha_k^j\ket{a_k}\bra{a_k}\\
-=&\sum_{k=0}^{n-1}\left(\sum_{j=0}^{\infty}\frac{i^j}{j!}\alpha_k^j\right)\ket{a_k}\bra{a_k}\\
-=&\sum_{k=0}^{n-1}e^{i\alpha_k}\ket{a_k}\bra{a_k}
-\end{align}
-here we deduce 
-\begin{align}
-\ket{u_k}=&\ket{a_k}\\
-2\pi k/n =& \alpha_k\\
-A=&\frac{2\pi}{n}\sum_{i=0}^{n-1}i \ket{a_i}\bra{a_i}\\
-\ket{\psi}=&\sum_{i=0}^{n-1}c_i\ket{a_i}.
-\end{align}
-Then we might compute $\braket{\mathcal{U}}_\psi$ as,
-\begin{align}
-\braket{\mathcal{U}}_\psi= \sum_{k=0}^{n-1}|c_i|^2e^{i2\pi k/n}
-\end{align}
-which is not necessarily a real quantity, then we compute $\braket{\mathcal{U}^j}_\psi$ as
-\begin{align}
-\braket{\mathcal{U}^j}_\psi= \sum_{k=0}^{n-1}|c_k|^2e^{i2\pi kj/n}
-\end{align}
-The basis we knew the gram matrix decompose in \emoji{star-struck} (the Fourier's basis), it is a genuine surprise I did not expect this result. Then the Gram matrix can be written as,
-\end{observation}
-\end{multicols}
-\begin{align}
-G=\begin{pmatrix}
- 1 & \sum_{k=0}^{n-1}|c_k|^2e^{i2\pi k/n} & \sum_{k=0}^{n-1}|c_k|^2e^{i4\pi k/n}  & \hdots &  \sum_{k=0}^{n-1}|c_k|^2e^{-i2\pi k/n} \\
-  \sum_{k=0}^{n-1}|c_k|^2e^{-i2\pi k/n} & 1 & \sum_{k=0}^{n-1}|c_k|^2e^{-i2\pi k/n} & \hdots & \sum_{k=0}^{n-1}|c_k|^2e^{-i4\pi k/n} \\
-   \sum_{k=0}^{n-1}|c_k|^2e^{-i4\pi k/n} &  \sum_{k=0}^{n-1}|c_k|^2e^{-i2\pi k/n}  & 1 & \hdots & \sum_{k=0}^{n-1}|c_k|^2e^{-i6\pi k/n} \\
-   \vdots & \vdots & \vdots & \ddots & \vdots \\
-  \sum_{k=0}^{n-1}|c_k|^2e^{i2\pi k/n} &\sum_{k=0}^{n-1}|c_k|^2e^{i4\pi k/n}  & \sum_{k=0}^{n-1}|c_k|^2e^{i6\pi k/n}  & \hdots &  1 
-\end{pmatrix}.
-\end{align}
-\begin{multicols}{2}
-\begin{observation}
-We can immediately see the gram matrix is completely determined by the decomposition of $\ket{\psi}$ in the basis of eigenvectors of $A$ i.e.
-$\mathcal{U}$ but the statement $\braket{\mathcal{U}^{j}}_{\psi} =\braket{\mathcal{U}}_{\psi}$ still remains untrue in general.
-\par
-An interesting case can be $\ket{\psi}=\ket{a_t}$ for a given $t\in\{0,..,n-1\}$. In this case we can see that 
-\begin{align}
-U^j\ket{\psi}&=U^j\ket{a_t}\\&=e^{i2\pi t/n}\ket{a_t}\\&=e^{i2\pi t/n}\ket{\psi}
-\end{align}
-In this case the gram matrix is
-\end{observation}
-\end{multicols}
-\begin{align}\label{eqGramMatrixZn}
-G=\begin{pmatrix}
- 1 & |c_t|^2e^{i2\pi t/n} & |c_t|^2e^{i4\pi t/n} & \hdots &  |c_t|^2e^{-i2\pi t/n} \\
-  |c_t|^2e^{-i2\pi t/n} & 1 & |c_t|^2e^{i2\pi t/n} & \hdots & |c_t|^2e^{-i4\pi t/n} \\
-  |c_t|^2e^{i4\pi t/n} &  |c_t|^2e^{-i2\pi t/n}  & 1 & \hdots & |c_t|^2e^{-i6\pi t/n}  \\
-   \vdots & \vdots & \vdots & \ddots & \vdots \\
-  |c_t|^2e^{i2\pi t/n} &|c_t|^2e^{i4\pi t/n}  & |c_t|^2e^{i6\pi t/n}  & \hdots &  1 
-\end{pmatrix}
-\end{align}
-
-\begin{multicols}{2}
-\begin{observation}
-Still we need to get rid off the global phase in each entry to get the result explain in the meetings... \par
-\textbf{Question} Which is the criteria to do this?
-Why can we choose $\ket{\psi}$ to be an eigenket of $A$ arbitrarily?
-Regarding the previous example we had our state pointing in the $z$ direction (i.e.
-not an eigenket of $\sigma_x$) which would explain the inconsistency.
-\end{observation}
-\begin{observation}
-Let us analyse the case of the group generated ensemble of $\mathbb{Z}/2\mathbb{Z}\times\mathbb{Z}/2\mathbb{Z}$. We will denote 
-\end{observation}
-\begin{observation}\label{ObsZnZm}
-Let us analyse the case the case $\mathbb{Z}/n\mathbb{Z}\times\mathbb{Z}/m\mathbb{Z}$ in order to do so let $\mathcal{U}_n$ and $\mathcal{U}_m$ two unitary operators such that $\mathcal{U}_n^n=\mathbb{I}_d$, $\mathcal{U}_m^m=\mathbb{I}_d$ respectively, and $[U_n,U_m]=0$.
-Here we distinguish two cases $n=m$ and $n\neq m$.
-Since $[U_n,U_m]=0$ we know there exists a basis $\{\ket{u}_i\}_{i=0}^{nm-1}$ where both unitary operators are diagonal.
-Taking into account the group representations are equivalent up to isomorphism we can consider one representation and extend it to any other representation.
-Here we might consider,
-\begin{align}
-U_n=&\sum_{i=0}^{nm-1}e^{i2\pi i/n}\ket{u_i}\bra{u_i}\\
-U_m=&\sum_{i=0}^{nm-1}e^{i2\pi i/m}\ket{u_i}\bra{u_i}
-\end{align}
-Notice the rellevance $n\neq m\Rightarrow U_n\neq U_m$ otherwise the states generated by $U_n$ and $U_m$ will be the same ones and we would go back to the case $\mathbb{Z}/n\mathbb{Z}$.
-\emoji{thinking-face}\par
-Now our set of states is $\Omega=\{U_{n}^iU_{m}^j\ket{\psi}\}_{0\leq i\leq n-1; 0\leq j\leq m-1}$ without loss of generality and for notation purposes we will choose $n>m$ and denote $U_{n}^iU_{m}^j\ket{\psi}=\ket{\psi_{(i,j)}}$ and we will define the oder relation \footnote{We need to order our ensemble for generating the gram matrix.},
-\begin{align}
-\ket{\psi_{(i,j)}}=&\ket{\psi_{(k,l)}}\Leftrightarrow i=k\;\&\;j=k\\
-\ket{\psi_{(i,j)}}>&\ket{\psi_{(k,l)}}\Leftrightarrow\begin{cases}i>k\\i=k\;\&\;j>k\end{cases}\\
-\ket{\psi_{(i,j)}}<&\ket{\psi_{(k,l)}}\Leftrightarrow\begin{cases}i<k\\i=k\;\&\;j<k\end{cases}
-\end{align}
-now we have $\Omega$ ready to compute the gram matrix. Let $G_m$ be the gram matrix of the $\mathbb{Z}/m\mathbb{Z}$ group generated from Eq.(\ref{eqGramMatrixZn}), then the gram matrix is nothing but,
-\end{observation}
-\end{multicols}
-\begin{align}\label{EqGramZnZm}
-G_{nm}=\begin{pmatrix}
- G_m & G_me^{i2\pi t/n} & G_me^{i4\pi t/n} & \hdots &  G_me^{-i2\pi t/n} \\
-  G_me^{-i2\pi t/n} & G_m & G_me^{i2\pi t/n} & \hdots & G_me^{-i4\pi t/n} \\
-  G_me^{i4\pi t/n} &  G_me^{-i2\pi t/n}  & G_m & \hdots & G_me^{-i6\pi t/n}  \\
-   \vdots & \vdots & \vdots & \ddots & \vdots \\
-  G_me^{i2\pi t/n} &G_me^{i4\pi t/n}  & G_me^{i6\pi t/n}  & \hdots &  G_m 
-\end{pmatrix}
-\end{align}
-
-\begin{multicols}{2}
-\begin{observation}
-Notice by changing the ordering definition we can easily see $G_{nm}$ is totally equivalent to $G_{mn}$ since $\mathbb{Z}/n\mathbb{Z}\times\mathbb{Z}/m\mathbb{Z}\equiv \mathbb{Z}/m\mathbb{Z}\times\mathbb{Z}/n\mathbb{Z}$ naturally.
-From Observation (\ref{ObsZnZm}) and Eq.
-(\ref{EqGramZnZm}) one can deduce, for the case $\mathbb{Z}/n_1\mathbb{Z}\times\mathbb{Z}/n_2\mathbb{Z}\times\dots\times \mathbb{Z}/n_k\mathbb{Z}$, the gram matrix in nothing but,
-\end{observation}
-\end{multicols}
-\begin{align}
-G_{n_1,n_2,...,n_k}=\begin{pmatrix}
- G_{n_1,n_2,...,n_{k-1}} & G_{n_1,n_2,...,n_{k-1}}e^{i2\pi t/n_k} & \hdots &  G_{n_1,n_2,...,n_{k-1}}e^{-i2\pi t/n_k} \\
-  G_{n_1,n_2,...,n_{k-1}}e^{-i2\pi t/n_k} & G_{n_1,n_2,...,n_{k-1}} & \hdots & G_{n_1,n_2,...,n_{k-1}}e^{-i4\pi t/n_k} \\
-   \vdots & \vdots  & \ddots & \vdots \\
-  G_{n_1,n_2,...,n_{k-1}}e^{i2\pi t/n_k} & G_{n_1,n_2,...,n_{k-1}}e^{i4\pi t/n_k}  & \hdots &  G_{n_1,n_2,...,n_{k-1}} 
-\end{pmatrix}.
-\end{align}
-
-\newpage
+Given a certain
 
@@
 
+\end{multicols}
 \end{document}

### 2025-04-08 Manuscript/Manuscript.tex
writting

@@
 \usepackage{yfonts}
+\usepackage{braket}
+\usepackage{dsfont}
 \usepackage{tikz}
@@
 
+\usepackage{glossaries}
+\usepackage{glossary-longragged}
+
+\makenoidxglossaries
+\newacronym{qse}{QSE}{Quantum State Exclusion}
+\newacronym{qsd}{QSD}{Quantum State Discrimination}
+\newacronym{sdp}{SDP}{Semidefinite Program}
+\newacronym{povm}{POVM}{Positive Operator-Valued Measure}
+\newacronym{me}{ME}{Minimum Error}
+\newacronym{ze}{ZE}{Zero Error}
+\glsaddall[types=\acronymtype]
+
+\DeclareMathOperator{\tr}{Tr}
+
 \begin{document}
@@
 \begin{flushright}
-    \emph{The dumbest people I know are those who know it all.}\\[1em]
-    \textbf{Malcolm S. Forbes}
+    \emph{Ab ovo usque ad mala.}\\[1em]
+    \textbf{Horace}
 \end{flushright}
@@
 \lhead{\NetIDb}    
-\rhead{\degree}
-\cfoot{}
-\rfoot{\small\thepage}
+\rhead{\subject}
+\cfoot{\small\thepage}
 \headsep 1.5em
@@
 \section{Introduction}
-
+\vspace{-0.5cm}
 In many real-world scenarios, excluding a certain hypothesis can be more practical than solving the problem entirely.
@@
 
-In this project, we adapt this concept to the quantum domain, focusing on the exclusion of quantum states.
-Rather than directly determining the exact state of a quantum system, we explore the process of eliminating states from a known ensemble, which may be more suitable or efficient in certain quantum applications.
+In this project, we project this idea into the quantum realm by focusing on \gls{qse}.
+Rather than determining the exact state of a quantum system, we aim to eliminate one or more possible candidates from a known ensemble of states.
+Notice, this approach can be more suitable or efficient in certain quantum information tasks.
 
-Given a certain
+Given a quantum state known to be prepared from a finite ensemble, \gls{qsd} seeks to identify which specific state from the ensemble corresponds to the given system.
+In contrast, \gls{qse}~\cite{PhysicsExclusionSource} adopts the opposite perspective: it aims to determine which states from the ensemble do not correspond to the prepared state.
+While \gls{qsd} has been deeply studied in recent years\cite{DiscriminationArticle}, with significant advances since its inception~\cite{helstromBook}, \gls{qse} offers a complementary framework with distinct advantages.
 
+Although the tasks of exclusion and discrimination coincide for ensembles containing only two states \footnote{Since for the two states case excluding one necessarily implies identifying the other.}, when dealing with ensembles of three or more states, the two problems diverge in both approach and complexity.
+One of the most significant features of \gls{qse} is the possibility of achieving \emph{perfect exclusion}, where certain states can be ruled out with zero probability of error in cases where perfect discrimination is impossible\cite{OptimalitySRM}.
+
+This capability opens new frontiers in quantum information theory, particularly in the context of partial information retrieval from quantum systems.
+By excluding certain states, it is possible to gain insight into the encoded information without needing to fully determine the original state.
+
+As with \gls{qsd}, obtaining a general analytical solution for \gls{qse} remains an open problem.
+However, analytical results have been found in specific cases when the ensemble of quantum states exhibits a certain degree of symmetry.
+In particular, when the ensemble is generated by the action of a finite group, the problem becomes more tractable and exact solutions have been derived.
+
+The exclusion task can be carried out under two main protocols: \emph{Minimum Error} and \emph{Zero Error}\footnote{Also known as \emph{unambiguous exclusion}.}.
+In the Minimum Error scenario, the goal is to minimize the probability of mistakenly excluding the actual prepared state.
+In contrast, the Zero Error approach seeks to exclude a state with absolute certainty, even if that means sometimes the procedure yields an inconclusive result.
+
+Building on recent results that provide exact solutions for exclusion tasks in group generated ensembles \cite{MainPaper}, this project undertakes a numerical study of such results as lower bounds for more general, randomly generated ensembles.
+To this end, we employ \gls{sdp} to explore \gls{qse} performance in arbitrary settings.
+Furthermore, we investigate improved bounds for the general case based on how closely a given ensemble resembles a group-generated one\footnote{The notion of "how close" will be formally defined in Section~\textcolor{blue}{add section}.}.
+
+\vspace{-0.5cm}
+\section{Formulation of the problem}
+\vspace{-0.5cm}
+Let $\left\{(\rho_i,\eta_i)\right\}_{i=1}^n$ be a set of $n$ states and $n$ probabilities, where $\rho_i$ dennotes the density matrix $\rho_i=\ket{\psi_i}\bra{\psi_i}$, and $\eta_i$ dennotes the prior probability in which $\rho_i$ accours.
+Additionally, let $\rho_j$ be a state belonging to the ensemble be our target state, we aim to develope a proceadure to find $\rho_k\in\left\{\rho_i\right\}_{i=1}^n$ such that $\rho_j\neq\rho_k$.
+
+The quantum mesurement is represented by a \gls{povm} set dennoted as $\left\{\Pi_j\right\}_j$ acting on quantum states' Hilbert space $\mathcal{H}$.
+
+Hence, the formulation in a \gls{sdp} problem for the \gls{me} protocol for the miminization of the probability of excluding our target state from our hypothesis in the minimum error protocol reads,
+\begin{align*}\label{EquationMinimumError}
+	P_{\text{\gls{me}}}^e=\min_{\Pi_i}&\sum_{i=1}^n\tr{(\Pi \rho_i)},\\
+	\text{subject to }&\sum_{i=1}^n \Pi_i = \mathds{1},\Pi_i\geq0 \hspace{0.5cm}\forall i\in\set{1,...,n}
+\end{align*}
+
+notice that both conditions $\sum_{i=1}^n \Pi_i = \mathds{1}$ and $\Pi_i\geq0$ stands for the \gls{povm} definition i.e.
+by demanding possible definitness and a sum equal to the identity we are demanding $\left\{\Pi_j\right\}_j$ to be a set of \gls{povm}s.
+Notice the $e$ upperindex stands for the \emph{error probability}.
+
+Similarly the problem can trivially be formulated in an equivalent way in terms of the maximization of the \emph{success probability}, defined as the probabilty of a successfull exclusion form the point of view
+
+\begin{align*}\label{EquationMinimumError}
+	P_{\text{\gls{me}}}^s=\max_{\Pi_i}1-&\sum_{i=1}^n\tr{(\Pi \rho_i)},\\
+	\text{subject to }&\sum_{i=1}^n \Pi_i = \mathds{1},\Pi_i\geq0 \hspace{0.5cm}\forall i\in\set{1,...,n}
+\end{align*}
+Since naturally, $P_{\text{\gls{me}}}^s+P_{\text{\gls{me}}}^e = 1$.
+
+Moreover we refere an ensemble as a \emph{group generated ensemble} when it is the outcome of one or more unitary transformations $U_i$ applied onto a seed state such that $U_i$ generates a finite group.
+For instance if $U_i^n=\mathds{1}$ will lead up a $\mathbb{Z}/n\mathbb{Z}$ group generated ensemble.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%
+\section*{List of abbreviations}
+\renewcommand{\glsnamefont}[1]{\textbf{#1}}
+\printnoidxglossary[type=main, title={\vspace{-1cm}}, nonumberlist, nogroupskip, style=super]
 

### 2025-04-08 Manuscript/Manuscript.tex
writting

@@
 
-\setlength{\parindent}{0.0in}
-\setlength{\parskip}{0.05in}
+%\setlength{\parindent}{0.0in}
+%\setlength{\parskip}{0.05in}
 
@@
   pdfcreator= \AuthorName,
+  hidelinks = true,
 }
@@
 \DeclareMathOperator{\tr}{Tr}
+\usetikzlibrary{arrows.meta, positioning}
 
@@
 \section{Introduction}
-\vspace{-0.5cm}
 In many real-world scenarios, excluding a certain hypothesis can be more practical than solving the problem entirely.
@@
 
-\vspace{-0.5cm}
 \section{Formulation of the problem}
-\vspace{-0.5cm}
-Let $\left\{(\rho_i,\eta_i)\right\}_{i=1}^n$ be a set of $n$ states and $n$ probabilities, where $\rho_i$ dennotes the density matrix $\rho_i=\ket{\psi_i}\bra{\psi_i}$, and $\eta_i$ dennotes the prior probability in which $\rho_i$ accours.
-Additionally, let $\rho_j$ be a state belonging to the ensemble be our target state, we aim to develope a proceadure to find $\rho_k\in\left\{\rho_i\right\}_{i=1}^n$ such that $\rho_j\neq\rho_k$.
 
-The quantum mesurement is represented by a \gls{povm} set dennoted as $\left\{\Pi_j\right\}_j$ acting on quantum states' Hilbert space $\mathcal{H}$.
+Let $\left\{(\rho_i, \eta_i)\right\}_{i=1}^n$ be an ensemble of $n$ quantum states, where each $\rho_i$ denotes a pure-state density matrix, $\rho_i = \ket{\psi_i}\bra{\psi_i}$, and $\eta_i$ represents the prior probability of occurrence of state $\rho_i$.
+Let $\rho_j$ be the target state from this ensemble.
+Our goal is to develop a procedure to find another state $\rho_k \in \left\{\rho_i\right\}_{i=1}^n$, such that $\rho_k \neq \rho_j$.
 
-Hence, the formulation in a \gls{sdp} problem for the \gls{me} protocol for the miminization of the probability of excluding our target state from our hypothesis in the minimum error protocol reads,
-\begin{align*}\label{EquationMinimumError}
-	P_{\text{\gls{me}}}^e=\min_{\Pi_i}&\sum_{i=1}^n\tr{(\Pi \rho_i)},\\
-	\text{subject to }&\sum_{i=1}^n \Pi_i = \mathds{1},\Pi_i\geq0 \hspace{0.5cm}\forall i\in\set{1,...,n}
+Quantum measurements are represented by a set of \glspl{povm}, denoted $\left\{\Pi_i\right\}_{i=1}^n$, acting on the Hilbert space $\mathcal{H}$ of the quantum system.
+
+The goal of the minimum-error (\gls{me}) protocol is miminizing the probability of excluding the target state from our hypothesis. In an \gls{sdp} formulation the problem reads,
+\begin{align*}
+	P_{\text{\gls{me}}}^e = \min_{\left\{\Pi_i\right\}} &\sum_{i=1}^n \tr(\Pi_i \rho_i),\\
+	\text{subject to} & \sum_{i=1}^n \Pi_i = \mathds{1}, \Pi_i \geq 0 \quad \forall i \in \{1, \dots, n\}.
 \end{align*}
 
-notice that both conditions $\sum_{i=1}^n \Pi_i = \mathds{1}$ and $\Pi_i\geq0$ stands for the \gls{povm} definition i.e.
-by demanding possible definitness and a sum equal to the identity we are demanding $\left\{\Pi_j\right\}_j$ to be a set of \gls{povm}s.
-Notice the $e$ upperindex stands for the \emph{error probability}.
+Note that the conditions $\sum_{i=1}^n \Pi_i = \mathds{1}$ and $\Pi_i \geq 0$ define the \gls{povm} elements, ensuring positivity and completeness.
+The superscript $e$ in $P_{\text{\gls{me}}}^e$ stands for the \emph{error probability}.
 
-Similarly the problem can trivially be formulated in an equivalent way in terms of the maximization of the \emph{success probability}, defined as the probabilty of a successfull exclusion form the point of view
+Alternatively, the problem can be formulated in terms of the \emph{success probability} $P_{\text{\gls{me}}}^s$, which represents the probability of successful exclusion.
+This is other perspective is nothing but,
 
-\begin{align*}\label{EquationMinimumError}
-	P_{\text{\gls{me}}}^s=\max_{\Pi_i}1-&\sum_{i=1}^n\tr{(\Pi \rho_i)},\\
-	\text{subject to }&\sum_{i=1}^n \Pi_i = \mathds{1},\Pi_i\geq0 \hspace{0.5cm}\forall i\in\set{1,...,n}
+\begin{align*}
+	P_{\text{\gls{me}}}^s = \max_{\left\{\Pi_i\right\}} &\left(1 - \sum_{i=1}^n \tr(\Pi_i \rho_i)\right),\\
+	\text{subject to} & \sum_{i=1}^n \Pi_i = \mathds{1}, \Pi_i \geq 0 \quad \forall i \in \{1, \dots, n\}.
 \end{align*}
-Since naturally, $P_{\text{\gls{me}}}^s+P_{\text{\gls{me}}}^e = 1$.
 
-Moreover we refere an ensemble as a \emph{group generated ensemble} when it is the outcome of one or more unitary transformations $U_i$ applied onto a seed state such that $U_i$ generates a finite group.
-For instance if $U_i^n=\mathds{1}$ will lead up a $\mathbb{Z}/n\mathbb{Z}$ group generated ensemble.
+Naturally, $P_{\text{\gls{me}}}^s + P_{\text{\gls{me}}}^e = 1$.
+
+In the case of the zero-error (\gls{ze}) protocol, the \gls{povm}s must additionally satisfy the unambiguity condition i.e.
+each measurement operator $\Pi_i$ must be orthogonal to the corresponding state $\rho_i$, in other words,
+
+\begin{equation*}
+\tr(\Pi_i \rho_i) = 0 \quad \forall i \in \{1, \dots, n\}.
+\end{equation*}
+
+An additional inconclusive outcome, denoted by a \gls{povm} element $\Pi_?$ (representing failure to exclude any state), must be introduced to ensure the completeness of the measurement,
+
+\begin{equation*}
+\Pi_? = \mathds{1} - \sum_{i=1}^n \Pi_i.
+\end{equation*}
+
+If the measurement outcome corresponds to $\Pi_?$ (i.e., "?" is observed), the result is inconclusive.
+The corresponding \gls{sdp} for minimizing the error probability (i.e., the probability of an inconclusive outcome) in the \gls{ze} protocol is:
+
+\begin{align*}
+	P_{\text{\gls{ze}}}^e = \min_{\left\{\Pi_i\right\}} &\sum_{i=1}^n \tr(\Pi_? \rho_i),\\
+	\text{subject to} \quad & \sum_{i=1}^n \Pi_i + \Pi_? = \mathds{1}, \quad \Pi_? \geq 0,\\
+	& \tr(\Pi_i \rho_i) = 0, \quad \Pi_i \geq 0 \quad \forall i \in \{1, \dots, n\}.
+\end{align*}
+
+Similarly, the corresponding success probability is:
+
+\begin{align*}
+	P_{\text{\gls{ze}}}^s = \max_{\left\{\Pi_i\right\}} &\left(1 - \sum_{i=1}^n \tr(\Pi_? \rho_i)\right),\\
+	\text{subject to} \quad & \sum_{i=1}^n \Pi_i + \Pi_? = \mathds{1}, \quad \Pi_? \geq 0,\\
+	& \tr(\Pi_i \rho_i) = 0, \quad \Pi_i \geq 0 \quad \forall i \in \{1, \dots, n\}.
+\end{align*}
+
+Note that this formulation is analogous to the \gls{me} protocol, except for the constraint $\tr(\Pi_i \rho_i) = 0$, which enforces unambiguous discrimination.
+
+Finally, we define a **group-generated ensemble** as one constructed by applying a finite group of unitary transformations to a fixed seed state.
+For example, let $U$ be a unitary operator such that $U^n = \mathds{1}$.
+Then the states of the ensemble are given by,
+
+\begin{equation*}
+\rho_i = U^i \rho (U^\dagger)^i, \quad i = 1, \dots, n,
+\end{equation*}
+
+where $\rho$ is the seed state. This forms a $\mathbb{Z}/n\mathbb{Z}$ generated ensemble.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2025-04-09 Manuscript/Manuscript.tex
writting

@@
 \headsep 1.5em
-
+\setcounter{page}{1}
 \begin{multicols}{2}[\begin{center}
@@
 Although the tasks of exclusion and discrimination coincide for ensembles containing only two states \footnote{Since for the two states case excluding one necessarily implies identifying the other.}, when dealing with ensembles of three or more states, the two problems diverge in both approach and complexity.
-One of the most significant features of \gls{qse} is the possibility of achieving \emph{perfect exclusion}, where certain states can be ruled out with zero probability of error in cases where perfect discrimination is impossible\cite{OptimalitySRM}.
+One of the most significant features of \gls{qse} is the possibility of achieving \emph{perfect exclusion}, where certain states can be ruled out with zero probability of error in cases where \emph{perfect discrimination} is impossible\cite{OptimalitySRM}.
 
@@
 
-The exclusion task can be carried out under two main protocols: \emph{Minimum Error} and \emph{Zero Error}\footnote{Also known as \emph{unambiguous exclusion}.}.
+The exclusion task can be carried out under two main protocols: \gls{me} and \gls{ze}\footnote{Also known as \emph{unambiguous exclusion}.}.
 In the Minimum Error scenario, the goal is to minimize the probability of mistakenly excluding the actual prepared state.
@@
 To this end, we employ \gls{sdp} to explore \gls{qse} performance in arbitrary settings.
-Furthermore, we investigate improved bounds for the general case based on how closely a given ensemble resembles a group-generated one\footnote{The notion of "how close" will be formally defined in Section~\textcolor{blue}{add section}.}.
+Furthermore, we investigate improved bounds for the general case based on how closely a given ensemble resembles a group generated one\footnote{The notion of "how close" will be formally defined in Section~\textcolor{blue}{add section}.}.
 
-\section{Formulation of the problem}
+\section{Formulation of the Problem}
 
-Let $\left\{(\rho_i, \eta_i)\right\}_{i=1}^n$ be an ensemble of $n$ quantum states, where each $\rho_i$ denotes a pure-state density matrix, $\rho_i = \ket{\psi_i}\bra{\psi_i}$, and $\eta_i$ represents the prior probability of occurrence of state $\rho_i$.
+Let $\left\{(\rho_i, \eta_i)\right\}_{i=1}^n$ be an ensemble of $n$ quantum states, where each $\rho_i$ denotes a pure state density matrix\footnote{This formulation hols true for mixed states but the project will only discuss the pure state scenario.}, i.e., $\rho_i = \ket{\psi_i}\bra{\psi_i}$, and $\eta_i$ represents the prior probability of occurrence of the state $\rho_i$.
 Let $\rho_j$ be the target state from this ensemble.
-Our goal is to develop a procedure to find another state $\rho_k \in \left\{\rho_i\right\}_{i=1}^n$, such that $\rho_k \neq \rho_j$.
+Our objective is to develop a procedure to identify another state $\rho_k \in \left\{\rho_i\right\}_{i=1}^n$, such that $\rho_k \neq \rho_j$.
 
-Quantum measurements are represented by a set of \glspl{povm}, denoted $\left\{\Pi_i\right\}_{i=1}^n$, acting on the Hilbert space $\mathcal{H}$ of the quantum system.
+Quantum measurements are described by a set of \glspl{povm}, denoted by $\left\{\Pi_i\right\}_{i=1}^n$, acting on the Hilbert space $\mathcal{H}$ of the quantum system.
+Here we pewsent the two studied protocols for \gls{qse}: minimum-error (\gls{me}) and zero-error (\gls{ze}).
 
-The goal of the minimum-error (\gls{me}) protocol is miminizing the probability of excluding the target state from our hypothesis. In an \gls{sdp} formulation the problem reads,
+The goal of the \gls{me} protocol is to minimize the probability of incorrectly excluding the target state from our hypothesis.
+If we formulate it as an \gls{sdp}, the problem reads,\footnote{Note that the \gls{sdp} formulations of quantum state discrimination may differ from the exclusion ones by interchanging minimization and maximization problems.}
 \begin{align*}
 	P_{\text{\gls{me}}}^e = \min_{\left\{\Pi_i\right\}} &\sum_{i=1}^n \tr(\Pi_i \rho_i),\\
-	\text{subject to} & \sum_{i=1}^n \Pi_i = \mathds{1}, \Pi_i \geq 0 \quad \forall i \in \{1, \dots, n\}.
+	\text{subject to} \quad & \sum_{i=1}^n \Pi_i = \mathds{1}, \quad \Pi_i \geq 0 \quad \forall i \in \{1, \dots, n\}.
 \end{align*}
 
-Note that the conditions $\sum_{i=1}^n \Pi_i = \mathds{1}$ and $\Pi_i \geq 0$ define the \gls{povm} elements, ensuring positivity and completeness.
-The superscript $e$ in $P_{\text{\gls{me}}}^e$ stands for the \emph{error probability}.
+Note the constraints $\sum_{i=1}^n \Pi_i = \mathds{1}$ and $\Pi_i \geq 0$ ensure that the $\Pi_i$ form a valid POVM, since they demand positive semi-definition and form a complete measurement.
+The superscript $e$ in $P_{\text{\gls{me}}}^e$ indicates that this is the \emph{error probability}.
 
-Alternatively, the problem can be formulated in terms of the \emph{success probability} $P_{\text{\gls{me}}}^s$, which represents the probability of successful exclusion.
-This is other perspective is nothing but,
-
+Alternatively, we may formulate the problem in terms of the \emph{success probability}, denoted by $P_{\text{\gls{me}}}^s$, which quantifies the probability of a correct exclusion.
+This equivalent formulation reads,
 \begin{align*}
 	P_{\text{\gls{me}}}^s = \max_{\left\{\Pi_i\right\}} &\left(1 - \sum_{i=1}^n \tr(\Pi_i \rho_i)\right),\\
-	\text{subject to} & \sum_{i=1}^n \Pi_i = \mathds{1}, \Pi_i \geq 0 \quad \forall i \in \{1, \dots, n\}.
+	\text{subject to} \quad & \sum_{i=1}^n \Pi_i = \mathds{1}, \quad \Pi_i \geq 0 \quad \forall i \in \{1, \dots, n\}.
 \end{align*}
 
-Naturally, $P_{\text{\gls{me}}}^s + P_{\text{\gls{me}}}^e = 1$.
+Naturally, both formulations are related via:
+\begin{align*}
+P_{\text{\gls{me}}}^s + P_{\text{\gls{me}}}^e = 1.
+\end{align*}
 
-In the case of the zero-error (\gls{ze}) protocol, the \gls{povm}s must additionally satisfy the unambiguity condition i.e.
-each measurement operator $\Pi_i$ must be orthogonal to the corresponding state $\rho_i$, in other words,
+In the case of the \gls{ze} protocol, the POVMs must also satisfy an unambiguity condition, i.e.
+each measurement operator $\Pi_i$ must be orthogonal to the corresponding state $\rho_i$.
+In other words,
+\begin{align*}
+\tr(\Pi_i \rho_i) = 0 \quad \forall i \in \{1, \dots, n\}.
+\end{align*}
 
-\begin{equation*}
-\tr(\Pi_i \rho_i) = 0 \quad \forall i \in \{1, \dots, n\}.
-\end{equation*}
+To ensure completeness, we introduce an additional POVM element $\Pi_?$ representing an inconclusive result,
+\begin{align*}
+\Pi_? = \mathds{1} - \sum_{i=1}^n \Pi_i.
+\end{align*}
+If the measurement yields the outcome $\Pi_?$ (i.e., the "?" symbol), the result is inconclusive.
 
-An additional inconclusive outcome, denoted by a \gls{povm} element $\Pi_?$ (representing failure to exclude any state), must be introduced to ensure the completeness of the measurement,
-
-\begin{equation*}
-\Pi_? = \mathds{1} - \sum_{i=1}^n \Pi_i.
-\end{equation*}
-
-If the measurement outcome corresponds to $\Pi_?$ (i.e., "?" is observed), the result is inconclusive.
-The corresponding \gls{sdp} for minimizing the error probability (i.e., the probability of an inconclusive outcome) in the \gls{ze} protocol is:
-
+The corresponding \gls{sdp} for minimizing the probability of an inconclusive result (i.e., error) in the \gls{ze} protocol is:
 \begin{align*}
@@
 	\text{subject to} \quad & \sum_{i=1}^n \Pi_i + \Pi_? = \mathds{1}, \quad \Pi_? \geq 0,\\
-	& \tr(\Pi_i \rho_i) = 0, \quad \Pi_i \geq 0 \quad \forall i \in \{1, \dots, n\}.
+	& \tr(\Pi_i \rho_i) = 0, \quad \Pi_i \geq 0 \quad \forall i.
 \end{align*}
 
-Similarly, the corresponding success probability is:
-
+The corresponding success probability is naturally given by,
 \begin{align*}
@@
 	\text{subject to} \quad & \sum_{i=1}^n \Pi_i + \Pi_? = \mathds{1}, \quad \Pi_? \geq 0,\\
-	& \tr(\Pi_i \rho_i) = 0, \quad \Pi_i \geq 0 \quad \forall i \in \{1, \dots, n\}.
+	& \tr(\Pi_i \rho_i) = 0, \quad \Pi_i \geq 0 \quad \forall i.
 \end{align*}
 
-Note that this formulation is analogous to the \gls{me} protocol, except for the constraint $\tr(\Pi_i \rho_i) = 0$, which enforces unambiguous discrimination.
+This formulation is analogous to the \gls{me} protocol, with the crucial difference being the constraint $\tr(\Pi_i \rho_i) = 0$, enforcing unambiguous discrimination.
 
-Finally, we define a **group-generated ensemble** as one constructed by applying a finite group of unitary transformations to a fixed seed state.
-For example, let $U$ be a unitary operator such that $U^n = \mathds{1}$.
-Then the states of the ensemble are given by,
-
+Moreover, let $\mathcal{G} \in \mathbb{C}^{n \times n}$ be the \emph{Gram matrix} of the system, defined as the $n\times n$ positive semidefinite hermitian matrix such that,
 \begin{equation*}
-\rho_i = U^i \rho (U^\dagger)^i, \quad i = 1, \dots, n,
+	\mathcal{G} =
+	\begin{pmatrix}
+		\braket{\psi_1|\psi_1} & \braket{\psi_1|\psi_2} & \dots & \braket{\psi_1|\psi_n}\\
+		\braket{\psi_2|\psi_1} & \braket{\psi_2|\psi_2} & \dots & \braket{\psi_2|\psi_n}\\
+		\vdots & \vdots & \ddots & \vdots\\
+		\braket{\psi_n|\psi_1} & \braket{\psi_n|\psi_2} & \dots & \braket{\psi_n|\psi_n}
+	\end{pmatrix},
+\end{equation*}
+i.e., $\mathcal{G}_{i,j} = \braket{\psi_i|\psi_j}$. Since all states are normalized, we have,
+\begin{equation*}
+	\mathcal{G} =
+	\begin{pmatrix}
+		1 & \braket{\psi_1|\psi_2} & \dots & \braket{\psi_1|\psi_n}\\
+		\braket{\psi_2|\psi_1} & 1 & \dots & \braket{\psi_2|\psi_n}\\
+		\vdots & \vdots & \ddots & \vdots\\
+		\braket{\psi_n|\psi_1} & \braket{\psi_n|\psi_2} & \dots & 1
+	\end{pmatrix}.
 \end{equation*}
 
-where $\rho$ is the seed state. This forms a $\mathbb{Z}/n\mathbb{Z}$ generated ensemble.
+Notice this matrix is Hermitian by construction,
+\begin{align*}
+\mathcal{G}_{i,j}^* = (\braket{\psi_i|\psi_j})^* = \braket{\psi_j|\psi_i} = \mathcal{G}_{j,i}.
+\end{align*}
+
+The Gram matrix allows us to reframe the exclusion problem in a more abstract and basis-independent form. Since $\mathcal{G}$ is hermitian and positive semi-definite, we can write,
+\begin{align*}
+\mathcal{G} = X^\dagger X,
+\end{align*}
+for some matrix $X$ whose columns are the pure states,
+\begin{align*}
+	X = \begin{pmatrix}
+		\mid & \mid &        & \mid \\
+		\ket{\psi_1} & \ket{\psi_2} & \dots & \ket{\psi_n} \\
+		\mid & \mid &        & \mid
+	\end{pmatrix}.
+\end{align*}
+
+Let us consider an arbitrary orthonormal basis $\left\{\ket{\omega_i}\right\}_{i=1}^n$, and define the POVM elements as projectors $\Pi_i = \ket{\omega_i}\bra{\omega_i}$. Then,
+\begin{align*}
+	\tr(\Pi_i \rho_i) &= \tr\left( \ket{\omega_i}\bra{\omega_i} \ket{\psi_i}\bra{\psi_i} \right) \\
+	&= |\braket{\omega_i|\psi_i}|^2 \\
+	&= |X_{i,i}|^2.
+\end{align*}
+
+Therefore, we can reformulate the \gls{sdp} for the \gls{me} protocol as:
+\begin{align*}
+	P_{\gls{me}}^e = \min_{X} &\sum_{i=1}^n |X_{i,i}|^2,\\
+	\text{subject to} \quad & X^\dagger X = \mathcal{G}, \quad X \geq 0.
+\end{align*}
+
+Similarly, the success probability becomes:
+\begin{align*}
+	P_{\gls{me}}^s = \max_{X} &\left(1 - \sum_{i=1}^n |X_{i,i}|^2\right),\\
+	\text{subject to} \quad & X^\dagger X = \mathcal{G}, \quad X \geq 0.
+\end{align*}
+
+This reformulation highlights that if two ensembles $A$ and $B$ share the same Gram matrix, then their exclusion problems, in both \gls{me} and \gls{ze} protocols, are equivalent.
+That is, the optimal success or error probabilities are identical in both systems.
+Hence, we focus on the Gram matrix to analyze exclusion problems, rather than relying on explicit state representations.
+\section{Group Generated Ensembles}
+
+Given a quantum state $\ket{\psi}$, which we refer to as the \emph{seed state}, we define a \emph{group generated ensemble} as the set of states obtained by applying a group of unitary transformations to $\ket{\psi}$.
+Specifically, if the ensemble consists of a total of $n$ quantum states, then its elements are of the form,
+\begin{align*}
+	U_i\ket{\psi}, \quad i \in \{1, \dots, n\},
+\end{align*}
+where the set of unitary matrices $\{U_i\}_{i=1}^n$ forms a finite group under standard matrix product. In terms of density matrices, the ensemble can equivalently be written as:
+\begin{align*}
+	\rho_i = U_i \rho U_i^\dagger, \quad i \in \{1, \dots, n\},
+\end{align*}
+where $\rho = \ket{\psi}\bra{\psi}$ is the density matrix corresponding to the seed state.
+
+For instance, let $U$ be a unitary operator such that $U^n = \mathds{1}$ (i.e., $U$ generates a cyclic group of order $n$). Then, the set of states
+\begin{align*}
+	\left\{ U^i\ket{\psi} \right\}_{i=0}^{n-1}
+\end{align*}
+forms a group generated ensemble based on the cyclic group $\mathbb{Z}_n$. This type of ensemble is of particular interest in our study and will be explored in more detail in subsequent sections.
+
+Let $U \in SU(n)$ be an $n \times n$ special unitary matrix satisfying $U^n = \mathds{1}$, and let $\ket{\psi}$ be the seed state.
+The Gram matrix $G$ associated with the ensemble $\left\{U^i\ket{\psi}\right\}_{i=0}^{n-1}$ is nothing but,
+\begin{align*}
+	\mathcal{G}_{ij} = \braket{U^i\psi | U^j\psi} = \braket{\psi | U^{j-i} | \psi} = \braket{\mathcal{U}^{j-i}}_{\psi},
+\end{align*}
+where we use the shorthand notation
+\begin{align*}
+\braket{\mathcal{U}^k}_\psi := \braket{\psi | U^k | \psi}.
+\end{align*}
+
+Using this, the Gram matrix $G$ can be expressed as a circulant matrix:
+\begin{align*}
+	\mathcal{G} = \begin{pmatrix}
+ 1 & \braket{\mathcal{U}}_{\psi} & \braket{\mathcal{U}^2}_{\psi} & \cdots & \braket{\mathcal{U}^{n-1}}_{\psi} \\
+ \braket{\mathcal{U}^{n-1}}_{\psi}^* & 1 & \braket{\mathcal{U}}_{\psi} & \cdots & \braket{\mathcal{U}^{n-2}}_{\psi} \\
+ \braket{\mathcal{U}^{n-2}}_{\psi}^* & \braket{\mathcal{U}^{n-1}}_{\psi}^* & 1 & \cdots & \braket{\mathcal{U}^{n-3}}_{\psi} \\
+ \vdots & \vdots & \vdots & \ddots & \vdots \\
+ \braket{\mathcal{U}}_{\psi}^* & \braket{\mathcal{U}^{2}}_{\psi}^* & \braket{\mathcal{U}^{3}}_{\psi}^* & \cdots & 1
+\end{pmatrix}.
+\end{align*}
+
+Note the Gram matrix is Hermitian, as required, since,
+\begin{align*}
+    \braket{\mathcal{U}^{-j}}_{\psi} = \braket{\psi | U^{-j} | \psi} = \left(\braket{\psi | U^j | \psi}\right)^* = \braket{\mathcal{U}^j}_{\psi}^*.
+\end{align*}
+Additionally, by using the identity $U^n = \mathds{1}$, we can simplify terms such as,
+\begin{align*}
+    \braket{\mathcal{U}^{-n+i}}_\psi = \braket{\psi | U^{-n+i} | \psi} = \braket{\psi | U^i | \psi} = \braket{\mathcal{U}^i}_\psi.
+\end{align*}
+Therefore we may write,
+\begin{align}
+	\mathcal{G}=\begin{pmatrix}
+ 1 & \braket{\mathcal{U}}_{\psi} & \braket{\mathcal{U}^{2}}_{\psi} & \hdots &  \braket{\mathcal{U}}_{\psi}^* \\
+  \braket{\mathcal{U}}_{\psi}^* & 1 & \braket{\mathcal{U}}_{\psi} & \hdots &  \braket{\mathcal{U}^{2}}_{\psi}^* \\
+    \braket{\mathcal{U}^{2}}_{\psi}^* &  \braket{\mathcal{U}}_{\psi}^*  & 1 & \hdots &  \braket{\mathcal{U}^{3}}_{\psi}^* \\
+   \vdots & \vdots & \vdots & \ddots & \vdots \\
+  \braket{\mathcal{U}}_{\psi} & \braket{\mathcal{U}^{2}}_{\psi}  & \braket{\mathcal{U}^{3}}_{\psi}  & \hdots &  1 
+\end{pmatrix}.
+\end{align}
+
+This confirms the circulant structure of $\mathcal{G}$, where each row is a cyclic permutation of the one above it.
+In other words the Gram matrix of $\mathbb{Z}/n\mathbb{Z}$ matrices are circulant matrixes.
+This result is especially useful, as they can be diagonalized by the discrete Fourier basis, which simplifies many tasks.
 

### 2025-04-11 Manuscript/Manuscript.tex
writting

@@
 \titleformat{\subsection}
-  {\normalfont\large\bfseries\centering}
+  {\normalfont\normalsize\bfseries\centering}
   {\thesubsection}{1em}{\MakeTextUppercase}
@@
 \renewcommand{\thesection}{\Roman{section}}
-\renewcommand{\thesubsection}{\Roman{section}.\roman{subsection}}
+\renewcommand{\thesubsection}{\Roman{section}.\Roman{subsection}}
 
@@
 \section{Introduction}
+Adri guapo
+
 In many real-world scenarios, excluding a certain hypothesis can be more practical than solving the problem entirely.
@@
 
-\section{Formulation of the Problem}
+\subsection{Formulation of the Problem}
 
@@
 
-Moreover, let $\mathcal{G} \in \mathbb{C}^{n \times n}$ be the \emph{Gram matrix} of the system, defined as the $n\times n$ positive semidefinite hermitian matrix such that,
+\subsection{Gram matrix formulation}
+Let $\mathcal{G} \in \mathbb{C}^{n \times n}$ be the \emph{Gram matrix} of the system, defined as the $n\times n$ positive semidefinite hermitian matrix such that,
 \begin{equation*}
@@
 \end{align*}
+Notice the diagonal elements of $X$ are,
+\begin{align*}
+	X_{i,i}=\braket{\omega_i|\psi_i}
+\end{align*}
+For an arbitrary orthonormal basis $\left\{\ket{\omega_i}\right\}_{i=1}^n$.
+\footnote{It is important to remark that fixing the basis $\left\{\ket{\omega_i}\right\}_{i=1}^n$ fixes the decomposition of $G=X^\dagger X$ and vice versa.}
 
@@
 
-Therefore, we can reformulate the \gls{sdp} for the \gls{me} protocol as:
+Therefore, we can reformulate the \gls{sdp} for the \gls{me} protocol as,
 \begin{align*}
@@
 
-Similarly, the success probability becomes:
+Similarly, the success probability becomes, 
 \begin{align*}
@@
 Hence, we focus on the Gram matrix to analyze exclusion problems, rather than relying on explicit state representations.
-\section{Group Generated Ensembles}
+
+\subsection{Group Generated Ensembles}
 
@@
 \end{align*}
-forms a group generated ensemble based on the cyclic group $\mathbb{Z}_n$. This type of ensemble is of particular interest in our study and will be explored in more detail in subsequent sections.
+forms a group generated ensemble based on the cyclic group $\mathbb{Z}/n\mathbb{Z}$.
+This type of ensemble is of particular interest in our study and will be explored in more detail in subsequent sections.
 
@@
 In other words the Gram matrix of $\mathbb{Z}/n\mathbb{Z}$ matrices are circulant matrixes.
-This result is especially useful, as they can be diagonalized by the discrete Fourier basis, which simplifies many tasks.
+This result is especially useful, as they can be diagonalized by the discrete Fourier basis, which simplifies many tasks\cite{circulantMatrices}.
+
+Moreover we can compute the Gram matrix of a group generated ensamble by generating the Cayley table, also known as the \emph{multiplication table}, of the group.
+For instance if we consider the smallest non-commutative group $S_3$ composed by the rotations and symmetries of the triangle.
+If we denote the identity as $e$, the 3 symmetries as $p$, $q$ and $r$ and $s$ as a rotation, we know the Cayley table to be,
+\begin{table}[H]
+	\centering
+	\caption{Cayley table of the $S_3$ group.}
+	\begin{tabular}{c||c c c c c c}
+		$S_3$ & $e$ & $p$ & $q$ & $r$ & $s$ & $s^2$ \\\hline\hline
+		$e$   & $e$ & $p$ & $q$ & $r$ & $s$ & $s^2$ \\
+		$p$  & $p$ & $e$ & $s^2$ & s & $q$ & $r$ \\
+		$q$  & $q$ & $s$ & $e$ & $s^2$ & $r$ & $p$ \\
+		$r$  & $r$ & $s^2$ & $s$ & $e$ & $p$ & $q$ \\
+		$s^2$ & $s^2$ & $r$ & $p$ & $q$ & $e$ & $s$ \\
+		$s$ & $s$ & $q$ & $r$ & $p$ & $s^2$ & $e$ 
+	\end{tabular}
+\end{table}
+
+\begin{table}[H]
+    \centering
+    \caption{Cayley table of the $S_3$ group.}
+    \begin{tabular}{c||c c c c c c}
+        $S_3$ & $e$ & $p$ & $q$ & $r$ & $s$ & $s^2$ \\ \hline \hline
+        $e$   & $e$ & $p$ & $q$ & $r$ & $s$ & $s^2$ \\
+        $p$   & $p$ & $e$ & $s^2$ & $s$ & $q$ & $r$ \\
+        $q$   & $q$ & $s$ & $e$ & $s^2$ & $r$ & $p$ \\
+        $r$   & $r$ & $s^2$ & $s$ & $e$ & $p$ & $q$ \\
+        $s^2$ & $s^2$ & $r$ & $p$ & $q$ & $e$ & $s$ \\
+        $s$   & $s$ & $q$ & $r$ & $p$ & $s^2$ & $e$
+    \end{tabular}
+\end{table}
+where we enforced the diagonal of the table
 

### 2025-04-12 Manuscript/Manuscript.tex
writting

@@
 \section{Introduction}
-Adri guapo
-
 In many real-world scenarios, excluding a certain hypothesis can be more practical than solving the problem entirely.
@@
 This reformulation highlights that if two ensembles $A$ and $B$ share the same Gram matrix, then their exclusion problems, in both \gls{me} and \gls{ze} protocols, are equivalent.
-That is, the optimal success or error probabilities are identical in both systems.
+That is, the optimal success and error probabilities are identical in both systems.
 Hence, we focus on the Gram matrix to analyze exclusion problems, rather than relying on explicit state representations.
@@
 
-For instance, let $U$ be a unitary operator such that $U^n = \mathds{1}$ (i.e., $U$ generates a cyclic group of order $n$). Then, the set of states
+For instance, let $\mathcal{U}$ be a unitary operator such that $\mathcal{U}^n = \mathds{1}$ (i.e., $\mathcal{U}$ generates a cyclic group of order $n$). Then, the set of states
 \begin{align*}
-	\left\{ U^i\ket{\psi} \right\}_{i=0}^{n-1}
+	\left\{ \mathcal{U}^i\ket{\psi} \right\}_{i=0}^{n-1}
 \end{align*}
 forms a group generated ensemble based on the cyclic group $\mathbb{Z}/n\mathbb{Z}$.
-This type of ensemble is of particular interest in our study and will be explored in more detail in subsequent sections.
+This type of ensemble is of particular interest in our study and will be explored in more detail in subsequent section.
 
-Let $U \in SU(n)$ be an $n \times n$ special unitary matrix satisfying $U^n = \mathds{1}$, and let $\ket{\psi}$ be the seed state.
-The Gram matrix $G$ associated with the ensemble $\left\{U^i\ket{\psi}\right\}_{i=0}^{n-1}$ is nothing but,
+\emph{Example: The $\mathbb{Z}/n\mathbb{Z}$ group generated ensamble}: Let $\mathcal{U} \in U(n)$ be an $n \times n$ unitary matrix satisfying $\mathcal{U}^n = \mathds{1}$, and let $\ket{\psi}$ be the seed state.
+The Gram matrix $\mathcal{G}^{\mathbb{Z}/n\mathbb{Z}}$ elements associated with the ensemble $\left\{\mathcal{U}^i\ket{\psi}\right\}_{i=0}^{n-1}$ are nothing but,
 \begin{align*}
-	\mathcal{G}_{ij} = \braket{U^i\psi | U^j\psi} = \braket{\psi | U^{j-i} | \psi} = \braket{\mathcal{U}^{j-i}}_{\psi},
+	\mathcal{G}^{\mathbb{Z}/n\mathbb{Z}}_{i,j} = \braket{\mathcal{U}^i\psi | \mathcal{U}^j\psi} = \braket{\psi | \mathcal{U}^{j-i} | \psi} = \braket{\mathcal{U}^{j-i}}_{\psi},
 \end{align*}
@@
 \begin{align*}
-\braket{\mathcal{U}^k}_\psi := \braket{\psi | U^k | \psi}.
+	\braket{\mathcal{U}^k}_\psi := \braket{\psi | \mathcal{U}^k | \psi}.
 \end{align*}
 
-Using this, the Gram matrix $G$ can be expressed as a circulant matrix:
+Using this, the Gram matrix $\mathcal{G}^{\mathbb{Z}/n\mathbb{Z}}$ can be expressed as a circulant matrix,
 \begin{align*}
-	\mathcal{G} = \begin{pmatrix}
+	\mathcal{G}^{\mathbb{Z}/n\mathbb{Z}} = \begin{pmatrix}
  1 & \braket{\mathcal{U}}_{\psi} & \braket{\mathcal{U}^2}_{\psi} & \cdots & \braket{\mathcal{U}^{n-1}}_{\psi} \\
@@
 \end{align*}
-Additionally, by using the identity $U^n = \mathds{1}$, we can simplify terms such as,
+Additionally, by using the identity $\mathcal{U}^n = \mathds{1}$, we can simplify terms such as,
 \begin{align*}
-    \braket{\mathcal{U}^{-n+i}}_\psi = \braket{\psi | U^{-n+i} | \psi} = \braket{\psi | U^i | \psi} = \braket{\mathcal{U}^i}_\psi.
+	\braket{\mathcal{U}^{-n+i}}_\psi = \braket{\psi | \mathcal{U}^{-n+i} | \psi} = \braket{\psi | \mathcal{U}^i | \psi} = \braket{\mathcal{U}^i}_\psi.
 \end{align*}
 Therefore we may write,
-\begin{align}
-	\mathcal{G}=\begin{pmatrix}
+\begin{align*}
+	\mathcal{G}^{\mathbb{Z}/n\mathbb{Z}} = \begin{pmatrix}
  1 & \braket{\mathcal{U}}_{\psi} & \braket{\mathcal{U}^{2}}_{\psi} & \hdots &  \braket{\mathcal{U}}_{\psi}^* \\
@@
 \end{pmatrix}.
-\end{align}
+\end{align*}
 
@@
 Moreover we can compute the Gram matrix of a group generated ensamble by generating the Cayley table, also known as the \emph{multiplication table}, of the group.
-For instance if we consider the smallest non-commutative group $S_3$ composed by the rotations and symmetries of the triangle.
-If we denote the identity as $e$, the 3 symmetries as $p$, $q$ and $r$ and $s$ as a rotation, we know the Cayley table to be,
+For instance, let us consider the smallest non-commutative group $S_3$ composed by the rotations and symmetries of the triangle.
+If we denote the identity as $e$, the 3 symmetries as $p$, $q$ and $s$ and a rotation as $s$, we know the Cayley table to be,
 \begin{table}[H]
@@
 	\caption{Cayley table of the $S_3$ group.}
-	\begin{tabular}{c||c c c c c c}
-		$S_3$ & $e$ & $p$ & $q$ & $r$ & $s$ & $s^2$ \\\hline\hline
-		$e$   & $e$ & $p$ & $q$ & $r$ & $s$ & $s^2$ \\
-		$p$  & $p$ & $e$ & $s^2$ & s & $q$ & $r$ \\
-		$q$  & $q$ & $s$ & $e$ & $s^2$ & $r$ & $p$ \\
-		$r$  & $r$ & $s^2$ & $s$ & $e$ & $p$ & $q$ \\
-		$s^2$ & $s^2$ & $r$ & $p$ & $q$ & $e$ & $s$ \\
-		$s$ & $s$ & $q$ & $r$ & $p$ & $s^2$ & $e$ 
+	\begin{tabular}{c||c c c c c c c}
+        $S_3$ & $e$ & $s$ & $s^2$ & $p$ & $q$ & $r$ \\\hline\hline
+        $e$   & $e$ & $s$ & $s^2$ & $p$ & $q$ & $r$ \\
+        $s^2$ & $s^2$ & $e$ & $s$ & $r$ & $p$ & $q$ \\
+        $s$   & $s$ & $s^2$ & $e$ & $q$ & $r$ & $p$ \\
+        $p$ & $p$ & $r$ & $q$ & $e$ & $s^2$ & $s$ \\
+        $q$ & $q$ & $p$ & $r$ & $s$ & $e$ & $s^2$ \\
+        $r$ & $r$ & $q$ & $p$ & $s^2$ & $s$ & $e$
     \end{tabular}
@@
 
-\begin{table}[H]
-    \centering
-    \caption{Cayley table of the $S_3$ group.}
-    \begin{tabular}{c||c c c c c c}
-        $S_3$ & $e$ & $p$ & $q$ & $r$ & $s$ & $s^2$ \\ \hline \hline
-        $e$   & $e$ & $p$ & $q$ & $r$ & $s$ & $s^2$ \\
-        $p$   & $p$ & $e$ & $s^2$ & $s$ & $q$ & $r$ \\
-        $q$   & $q$ & $s$ & $e$ & $s^2$ & $r$ & $p$ \\
-        $r$   & $r$ & $s^2$ & $s$ & $e$ & $p$ & $q$ \\
-        $s^2$ & $s^2$ & $r$ & $p$ & $q$ & $e$ & $s$ \\
-        $s$   & $s$ & $q$ & $r$ & $p$ & $s^2$ & $e$
-    \end{tabular}
-\end{table}
-where we enforced the diagonal of the table
+where we have enforced the diagonal elements to be the identity.
+Subsequently if we identify $S_3$ as a group of unitary matrices \footnote{we think of each element of the group as an unitary matrix and the operation of the group as the matrix product} we immediatelly realize the Gram matrix of the $S_3$ group generated ensamble is the matrix corresponding to the expected values of the Cayley table respect a certain seed state $\ket{\psi}$.
+In other words the Gram matrix is nothing but,
+\begin{align*}
+	\mathcal{G}^{S_3}_{psi}=\begin{pmatrix}
+        1 & \braket{s}_\psi & \braket{s^2}_\psi & \braket{p}_\psi & \braket{q}_\psi & \braket{r}_\psi \\ 
+        \braket{s^2}_\psi & 1 & \braket{s}_\psi & \braket{r}_\psi & \braket{p}_\psi & \braket{q}_\psi \\
+        \braket{s}_\psi & \braket{s^2}_\psi & 1 & \braket{q}_\psi & \braket{r}_\psi & \braket{p}_\psi \\
+        \braket{p}_\psi & \braket{r}_\psi & \braket{q}_\psi & 1 & \braket{s^2}_\psi & \braket{s}_\psi \\
+        \braket{q}_\psi & \braket{p}_\psi & \braket{r}_\psi & \braket{s}_\psi & 1 & \braket{s^2}_\psi \\
+        \braket{r}_\psi & \braket{q}_\psi & \braket{p}_\psi & \braket{s^2}_\psi & \braket{s}_\psi & 1
+	\end{pmatrix}.
+\end{align*}
+Notice that, $\braket{e}_\psi=1$ since $e$ is the neutral element of the matrix product operation, i.e.
+$e=\mathds{1}$.
+Moreover in this particular example we can observe since $\mathcal{G}^{S_3}$ is hermitian we know that,
+\begin{align*}\begin{cases}
+	\braket{p}_{\psi}=&\braket{p}_{\psi}^*\\
+	\braket{q}_{\psi}=&\braket{q}_{\psi}^*\\
+\braket{r}_{\psi}=&\braket{r}_{\psi}^*\end{cases}&\quad \forall \ket{\psi}\in \mathcal{H}\\
+\Updownarrow& \\
+\braket{p}_{\psi},\braket{q}_{\psi},\braket{r}_{\psi}\in&\mathbb{R}\quad \forall \ket{\psi}\in \mathcal{H}
+\end{align*}
+i.e.
+the unitary matrices corresponding to the triangle symmetries $p$, $q$ and $r$ are hermitian.
+It is inmediate this procedure can be applied for any group $G$, whic implies that computing the Cayley table is equivalent to computin the Gram matrix of the group generated ensamble.
+
+\subsection{Dual formulation of the problem}
+Somet
+
+\subsection{Previous results}
+Enormous advances have been made in the exclusion task for group generated ensambles.
+The publication \emph{Quantum state exclusion for group-generated ensembles of pure states}\cite{MainPaper} yields a result of the actual exact success and/or error probabilities for both \gls{me} and \gls{ze} protocols for group generated ensambles.
+The result reads, let $\mathcal{G}^{G}$ the Gram matrix of the group generated ensamble corresponding to a finite group $G$, let also $\{\lambda_i\}_{i=1}^{|G|}$ be the set of eigenvalues of the Gram matrix where $|G|$ denotes the number of the group's elements.
+Additionally let us consider the set of eigenvalues $\{\lambda_i\}_{i=1}^{|G|}$ to be an ordered group, such that,
+\begin{align*}
+	i\leq j\quad\forall i,j\in\{1,...,|G|\}\Leftrightarrow \lambda_i\geq\lambda_j \forall i,j\in\{1,...,|G|\}
+\end{align*}
+i.e. the set is ordered from the lowest to highest eigenvalue. Hence, the exclusion probabilities for the minimum error (\gls{me}) protocol are,
+\begin{align*}
+	P_{\gls{me}}^e=&\max\left\{0,\left(\frac{\sqrt{\lambda_{|G|}}-\sum_{i<|G|}\sqrt{\lambda_i}}{|G|}\right)^2\right\}\\
+	P_{\gls{me}}^s=&\min\left\{1,1-\left(\frac{\sqrt{\lambda_{|G|}}-\sum_{i<|G|}\sqrt{\lambda_i}}{|G|}\right)^2\right\}.
+\end{align*}
+Additionally, the results for the zero error (\gls{ze}) protocol are,
+\begin{align*}
+	P_{\gls{ze}}^e=&\max\left\{0,\frac{\sum_{i=1}^{|G|}\sqrt{\lambda_i}\left(\sqrt{\lambda_{|G|}}-\sum_{j<|G|}\sqrt{\lambda_j}\right)}{|G|}\right\}\\
+	P_{\gls{ze}}^s=&\min\left\{1,1-\frac{\sum_{i=1}^{|G|}\sqrt{\lambda_i}\left(\sqrt{\lambda_{|G|}}-\sum_{j<|G|}\sqrt{\lambda_j}\right)}{|G|}\right\}.
+\end{align*}
 

### 2025-04-12 Manuscript/Manuscript.tex
writting

@@
 
-Let us consider an arbitrary orthonormal basis $\left\{\ket{\omega_i}\right\}_{i=1}^n$, and define the POVM elements as projectors $\Pi_i = \ket{\omega_i}\bra{\omega_i}$. Then,
+Let us consider an arbitrary orthonormal basis $\left\{\ket{\omega_i}\right\}_{i=1}^n$, and define the POVM elements as projectors $\Pi_i = \ket{\omega_i}\bra{\omega_i}$.
+Then, the \gls{sdp} formulation for the ensamble $\left\{(\rho_i,\eta_i)\right\}_{i=1}^n$ can be expressed as the following,
 \begin{align*}
@@
 \begin{align*}
-	P_{\gls{me}}^e = \min_{X} &\sum_{i=1}^n |X_{i,i}|^2,\\
+	P_{\gls{me}}^e = \min_{X} &\sum_{i=1}^n \frac{|X_{i,i}|^2}{\eta_i},\\
 	\text{subject to} \quad & X^\dagger X = \mathcal{G}, \quad X \geq 0.
@@
 \begin{align*}
-	P_{\gls{me}}^s = \max_{X} &\left(1 - \sum_{i=1}^n |X_{i,i}|^2\right),\\
+	P_{\gls{me}}^s = \max_{X} &\left(1 - \sum_{i=1}^n \frac{|X_{i,i}|^2}{\eta_i}\right),\\
 	\text{subject to} \quad & X^\dagger X = \mathcal{G}, \quad X \geq 0.
@@
 Hence, we focus on the Gram matrix to analyze exclusion problems, rather than relying on explicit state representations.
+
+Moreover, we remark we are not especially interested in the arbitrary prior probabilities $\eta_i$ scenario, since the result for equal prior probabilities $\eta_i=\frac{1}{n}$ can be easily extended to the previous case, with $n$ as the number of states.
+This extension can be performed by considering the non-normalized states
+\begin{align*}
+	\ket{\tilde{\psi_i}}=\frac{1}{\sqrt{\eta_i}}\ket{\psi_i}
+\end{align*}
+and reformulate the problem in terms of this new states forgetting about the prior probabilities since they are encoded inside the states.
+Thus, for simplicity we will consider the equal probabilities case.
 
@@
 where we have enforced the diagonal elements to be the identity.
-Subsequently if we identify $S_3$ as a group of unitary matrices \footnote{we think of each element of the group as an unitary matrix and the operation of the group as the matrix product} we immediatelly realize the Gram matrix of the $S_3$ group generated ensamble is the matrix corresponding to the expected values of the Cayley table respect a certain seed state $\ket{\psi}$.
+Subsequently if we identify $S_3$ as a group of unitary matrices \footnote{we think of each element of the group as an unitary matrix and the operation of the group as the matrix product.} we immediatelly realize the Gram matrix of the $S_3$ group generated ensamble is the matrix corresponding to the expected values of the Cayley table respect a certain seed state $\ket{\psi}$.
 In other words the Gram matrix is nothing but,
@@
 \Updownarrow& \\
-\braket{p}_{\psi},\braket{q}_{\psi},\braket{r}_{\psi}\in&\mathbb{R}\quad \forall \ket{\psi}\in \mathcal{H}
+\braket{p}_{\psi},\braket{q}_{\psi},\braket{r}_{\psi}\in&\mathbb{R}\quad \forall \ket{\psi}\in \mathcal{H}.
 \end{align*}
-i.e.
-the unitary matrices corresponding to the triangle symmetries $p$, $q$ and $r$ are hermitian.
+Therefore the unitary matrices corresponding to the triangle symmetries $p$, $q$ and $r$ are hermitian.
 It is inmediate this procedure can be applied for any group $G$, whic implies that computing the Cayley table is equivalent to computin the Gram matrix of the group generated ensamble.
 
+Additionally, we will denote the cardinality of a finite group $G$\footnote{The cardinality of a group is the same as the number elements of the group.}, as $|G|$ which implies that for our case of interest of the prior probabilities scenario we may write $\eta_i=\frac{1}{|G|}$.
+
 \subsection{Dual formulation of the problem}
-Somet
+Sometimes it is usefull to consider the dual version of each \emph{sdp} problem.
+The dual version of the exclusion task for the $\left\{\left(\rho_i,\frac{1}{n}\right)\right\}_{i=1}^n$ ensamble for the error probability with the Minimum Error (\gls{me}) protocol is,
+\begin{align*}
+	\tilde{P}_{\gls{me}}^e=\max_{\Gamma\geq0}&\tr{\Gamma}\\
+	\text{subject to }&\frac{\rho_i}{n}-\Gamma\geq 0\quad\forall i\in\{1,...,n\}
+\end{align*}
+where $\tilde{P}$ stands for the dual version of the problem. Naturally, for the success probability the problem reads,
+\begin{align*}
+	\tilde{P}_{\gls{me}}^s=\min_{\Gamma\geq0}&\left(1-\tr{\Gamma}\right)\\
+	\text{subject to }&\frac{\rho_i}{n}-\Gamma\geq 0\quad\forall i\in\{1,...,n\}.
+\end{align*}
+\textcolor{blue}{Add the dual version for the zero error protocol.}
 
+The dual version results specially usefull since if given an POVM anzatz the probabilities of the primal and dual problems coincide, i.e. $P=\tilde P$ we know we have found the optimal measurement.
+
+The dual version 
 \subsection{Previous results}
@@
 The publication \emph{Quantum state exclusion for group-generated ensembles of pure states}\cite{MainPaper} yields a result of the actual exact success and/or error probabilities for both \gls{me} and \gls{ze} protocols for group generated ensambles.
-The result reads, let $\mathcal{G}^{G}$ the Gram matrix of the group generated ensamble corresponding to a finite group $G$, let also $\{\lambda_i\}_{i=1}^{|G|}$ be the set of eigenvalues of the Gram matrix where $|G|$ denotes the number of the group's elements.
+The result reads, let $\mathcal{G}^{G}$ the Gram matrix of the group generated ensamble $\left\{\left(\rho_i,\frac{1}{|G|}\right)\right\}_{i=1}^{|G|}$ corresponding to a finite group $G$, where $|G|$ denotes the number of the group's elements, let also $\{\lambda_i\}_{i=1}^{|G|}$ be the set of eigenvalues of the Gram matrix.
 Additionally let us consider the set of eigenvalues $\{\lambda_i\}_{i=1}^{|G|}$ to be an ordered group, such that,
 \begin{align*}
-	i\leq j\quad\forall i,j\in\{1,...,|G|\}\Leftrightarrow \lambda_i\geq\lambda_j \forall i,j\in\{1,...,|G|\}
+	i\leq j\quad\forall i,j\in\{1,...,|G|\}\Leftrightarrow \lambda_i\geq\lambda_j \forall i,j\in\{1,...,|G|\},
 \end{align*}
-i.e. the set is ordered from the lowest to highest eigenvalue. Hence, the exclusion probabilities for the minimum error (\gls{me}) protocol are,
+or equivalently, the set is ordered from the lowest to highest eigenvalue. Hence, the exclusion probabilities for the minimum error (\gls{me}) protocol are,
 \begin{align*}
@@
 \end{align*}
+For us is crucial to remark one of the results' traitmarks: the probabilities are independent of the group.
+In other words, given two group generated ensambles $A$ and $B$ for 2 differnt groups $G_A$ and $G_b$ ($G_A\neq G_B$) with the same cardinality, i.e.
+$|G_A|=|G_B|$, we know that if the respective Gram matrices $\mathcal{G}^{G_A}$ and $\mathcal{G}^{G_b}$ have the same eigenvalues, then the exclusion probability for both protocols \gls{me} and \gls{ze} is the same.
+This matter is one of the cornersotnes of this project study.
+
+Additionally we do also notice the exstence of some conditions where the exclusion can be performed with no error what so ever. This can be done if,
+\begin{align}\label{equationPerfectExclusionCondition}
+	\lambda_{|G|}\leq \left(\sum_{i=1}^{|G|}\sqrt{\lambda_i}\right)^2.
+\end{align}
+The regime corresponding to this conditions is denoted as the \emph{perfect exclusion zone}.
+In this project we will prove this results to be a lower bound for the exclusion success probability for the non group generated ensambles.
+However since the lower bound for the \emph{perfect exclusion zone} it is equal to 1\footnote{The exclusion can always be performed successfully in this context.}, then a perfect exclusion can be performed for a non group generated ensamble if it fulfils the perfect exclusion condition Eq.
+(\ref{equationPerfectExclusionCondition}).
+Subsequently, the perfect exclusion regime exists for a general ensamble and at least is comphended by those ensamble that fulfil Eq.
+(\ref{equationPerfectExclusionCondition}).
+
+\section{Methodology}
+All the code is stored in the GitHub repository \cite{GitHub}.
+The workflow of the study has been the creation of the Mosek solver \cite{mosek_sdp} to numerically solve the \gls{sdp} bla bla bl bla bla blaa.
 

### 2025-04-14 Manuscript/Manuscript.tex
writting

@@
 Let us consider an arbitrary orthonormal basis $\left\{\ket{\omega_i}\right\}_{i=1}^n$, and define the POVM elements as projectors $\Pi_i = \ket{\omega_i}\bra{\omega_i}$.
-Then, the \gls{sdp} formulation for the ensamble $\left\{(\rho_i,\eta_i)\right\}_{i=1}^n$ can be expressed as the following,
+Then, the \gls{sdp} formulation for the ensemble $\left\{(\rho_i,\eta_i)\right\}_{i=1}^n$ can be expressed as the following,
 \begin{align*}
@@
 
-\subsection{Group Generated Ensembles}
+\subsection{Group Generated Ensembles}\label{sectionGroupGeneratedEnsemble}
 
@@
 
-\emph{Example: The $\mathbb{Z}/n\mathbb{Z}$ group generated ensamble}: Let $\mathcal{U} \in U(n)$ be an $n \times n$ unitary matrix satisfying $\mathcal{U}^n = \mathds{1}$, and let $\ket{\psi}$ be the seed state.
+\emph{Example: The $\mathbb{Z}/n\mathbb{Z}$ group generated ensemble}: Let $\mathcal{U} \in U(n)$ be an $n \times n$ unitary matrix satisfying $\mathcal{U}^n = \mathds{1}$, and let $\ket{\psi}$ be the seed state.
 The Gram matrix $\mathcal{G}^{\mathbb{Z}/n\mathbb{Z}}$ elements associated with the ensemble $\left\{\mathcal{U}^i\ket{\psi}\right\}_{i=0}^{n-1}$ are nothing but,
@@
 \begin{align*}
-	\mathcal{G}^{\mathbb{Z}/n\mathbb{Z}} = \begin{pmatrix}
+	\mathcal{G}^{\mathbb{Z}/n\mathbb{Z}_{\psi}} = \begin{pmatrix}
  1 & \braket{\mathcal{U}}_{\psi} & \braket{\mathcal{U}^{2}}_{\psi} & \hdots &  \braket{\mathcal{U}}_{\psi}^* \\
@@
 
-Moreover we can compute the Gram matrix of a group generated ensamble by generating the Cayley table, also known as the \emph{multiplication table}, of the group.
+Moreover we can compute the Gram matrix of a group generated ensemble by generating the Cayley table, also known as the \emph{multiplication table}, of the group.
 For instance, let us consider the smallest non-commutative group $S_3$ composed by the rotations and symmetries of the triangle.
@@
 where we have enforced the diagonal elements to be the identity.
-Subsequently if we identify $S_3$ as a group of unitary matrices \footnote{we think of each element of the group as an unitary matrix and the operation of the group as the matrix product.} we immediatelly realize the Gram matrix of the $S_3$ group generated ensamble is the matrix corresponding to the expected values of the Cayley table respect a certain seed state $\ket{\psi}$.
+Subsequently if we identify $S_3$ as a group of unitary matrices \footnote{we think of each element of the group as an unitary matrix and the operation of the group as the matrix product.} we immediatelly realize the Gram matrix of the $S_3$ group generated ensemble is the matrix corresponding to the expected values of the Cayley table respect a certain seed state $\ket{\psi}$.
 In other words the Gram matrix is nothing but,
 \begin{align*}
-	\mathcal{G}^{S_3}_{psi}=\begin{pmatrix}
+	\mathcal{G}^{S_3}_{\psi}=\begin{pmatrix}
         1 & \braket{s}_\psi & \braket{s^2}_\psi & \braket{p}_\psi & \braket{q}_\psi & \braket{r}_\psi \\ 
@@
 Therefore the unitary matrices corresponding to the triangle symmetries $p$, $q$ and $r$ are hermitian.
-It is inmediate this procedure can be applied for any group $G$, whic implies that computing the Cayley table is equivalent to computin the Gram matrix of the group generated ensamble.
+It is inmediate this procedure can be applied for any group $G$, whic implies that computing the Cayley table is equivalent to computin the Gram matrix of the group generated ensemble.
 
@@
 Sometimes it is usefull to consider the dual version of each \emph{sdp} problem.
-The dual version of the exclusion task for the $\left\{\left(\rho_i,\frac{1}{n}\right)\right\}_{i=1}^n$ ensamble for the error probability with the Minimum Error (\gls{me}) protocol is,
+The dual version of the exclusion task for the $\left\{\left(\rho_i,\frac{1}{n}\right)\right\}_{i=1}^n$ ensemble for the error probability with the Minimum Error (\gls{me}) protocol is,
 \begin{align*}
-	\tilde{P}_{\gls{me}}^e=\max_{\Gamma\geq0}&\tr{\Gamma}\\
-	\text{subject to }&\frac{\rho_i}{n}-\Gamma\geq 0\quad\forall i\in\{1,...,n\}
+	\tilde{P}_{\gls{me}}^e=\max_{\Gamma}&\tr{\Gamma}\\
+	\text{subject to }&\frac{\rho_i}{n}-\Gamma\geq 0\quad\forall i\in\{1,...,n\}\\
+	&\Gamma^\dagger=\Gamma,
 \end{align*}
@@
 \begin{align*}
-	\tilde{P}_{\gls{me}}^s=\min_{\Gamma\geq0}&\left(1-\tr{\Gamma}\right)\\
-	\text{subject to }&\frac{\rho_i}{n}-\Gamma\geq 0\quad\forall i\in\{1,...,n\}.
+	\tilde{P}_{\gls{me}}^s=\min_{\Gamma}&\left(1-\tr{\Gamma}\right)\\
+	\text{subject to }&\frac{\rho_i}{n}-\Gamma\geq 0\quad\forall i\in\{1,...,n\}\\
+	&\Gamma^\dagger=\Gamma.
 \end{align*}
@@
 
-The dual version results specially usefull since if given an POVM anzatz the probabilities of the primal and dual problems coincide, i.e. $P=\tilde P$ we know we have found the optimal measurement.
+The dual version results specially usefull since given an POVM anzatz if the probabilities of the primal and dual problems coincide, i.e. $P=\tilde P$ we know we have found the optimal measurement.
 
-The dual version 
 \subsection{Previous results}
-Enormous advances have been made in the exclusion task for group generated ensambles.
-The publication \emph{Quantum state exclusion for group-generated ensembles of pure states}\cite{MainPaper} yields a result of the actual exact success and/or error probabilities for both \gls{me} and \gls{ze} protocols for group generated ensambles.
-The result reads, let $\mathcal{G}^{G}$ the Gram matrix of the group generated ensamble $\left\{\left(\rho_i,\frac{1}{|G|}\right)\right\}_{i=1}^{|G|}$ corresponding to a finite group $G$, where $|G|$ denotes the number of the group's elements, let also $\{\lambda_i\}_{i=1}^{|G|}$ be the set of eigenvalues of the Gram matrix.
+Enormous advances have been made in the exclusion task for group generated ensembles.
+The publication \emph{Quantum state exclusion for group-generated ensembles of pure states}\cite{MainPaper} yields a result of the actual exact success and/or error probabilities for both \gls{me} and \gls{ze} protocols for group generated ensembles.
+The result reads, let $\mathcal{G}^{G}$ the Gram matrix of the group generated ensemble $\left\{\left(\rho_i,\frac{1}{|G|}\right)\right\}_{i=1}^{|G|}$ corresponding to a finite group $G$, where $|G|$ denotes the number of the group's elements, let also $\{\lambda_i\}_{i=1}^{|G|}$ be the set of eigenvalues of the Gram matrix.
 Additionally let us consider the set of eigenvalues $\{\lambda_i\}_{i=1}^{|G|}$ to be an ordered group, such that,
@@
 For us is crucial to remark one of the results' traitmarks: the probabilities are independent of the group.
-In other words, given two group generated ensambles $A$ and $B$ for 2 differnt groups $G_A$ and $G_b$ ($G_A\neq G_B$) with the same cardinality, i.e.
+In other words, given two group generated ensembles $A$ and $B$ for 2 differnt groups $G_A$ and $G_b$ ($G_A\neq G_B$) with the same cardinality, i.e.
 $|G_A|=|G_B|$, we know that if the respective Gram matrices $\mathcal{G}^{G_A}$ and $\mathcal{G}^{G_b}$ have the same eigenvalues, then the exclusion probability for both protocols \gls{me} and \gls{ze} is the same.
@@
 The regime corresponding to this conditions is denoted as the \emph{perfect exclusion zone}.
-In this project we will prove this results to be a lower bound for the exclusion success probability for the non group generated ensambles.
-However since the lower bound for the \emph{perfect exclusion zone} it is equal to 1\footnote{The exclusion can always be performed successfully in this context.}, then a perfect exclusion can be performed for a non group generated ensamble if it fulfils the perfect exclusion condition Eq.
+In this project we will prove this results to be a lower bound for the exclusion success probability for the non group generated ensembles.
+However since the lower bound for the \emph{perfect exclusion zone} it is equal to 1\footnote{The exclusion can always be performed successfully in this context.}, then a perfect exclusion can be performed for a non group generated ensemble if it fulfils the perfect exclusion condition Eq.
 (\ref{equationPerfectExclusionCondition}).
-Subsequently, the perfect exclusion regime exists for a general ensamble and at least is comphended by those ensamble that fulfil Eq.
+Subsequently, the perfect exclusion regime exists for a general ensemble and at least is comphended by those ensemble that fulfil Eq.
 (\ref{equationPerfectExclusionCondition}).
+
+\subsection{Ensembles with a prime number of elements}
+
+As we have discussed, analytical solutions have been found for the exclusion task in \gls{me} and \gls{ze} protocols.
+This solutions are independent from the intrinsc group of the ensemble and only depend on the eigenvalues of the Gram matrix.
+
+Hence if the Gram matrix for a general ensemble decomposes as,
+\begin{align}
+	\mathcal{G}= UDU^\dagger
+\end{align}
+where $U$ stands for an unitary matrix, and $D$ for a the eigenvalues diagonal matrix. Then, we are left with two options:
+\begin{itemize}
+	\item We are in the perfect exclusion regime, i.e. the eigenvalues composing the $D$ matrix fulfil Eq.(\ref{equationPerfectExclusionCondition}).
+	\item We are not in the perfect exclusion regime, i.e. the eigenvalues composing the $D$ matrix do not fulfil Eq.(\ref{equationPerfectExclusionCondition}).
+\end{itemize}
+If we are in the perfect exclusion scenario we know we can find a set of \gls{povm}s that the outcome of the measurement allows us to exclude one hypothesis from the ensemble with no mistake.
+
+Otherwise we are in the non-perfect exclusion zone.
+In this regime the solution for group generated ensembles are lower bounds of the successfull exclusion probability in both protocols (i.e.
+upperbound of the error probability of exclusion).
+
+Let us consider the 4 states ensemble case.
+In this scenario we know the result to be an exact solution for the groups $\mathbb{Z}/4\mathbb{Z}$ and $\mathbb{Z}/2\mathbb{Z}\times\mathbb{Z}/2\mathbb{Z}$\footnote{This are the only two groups of 4 elements.}.
+Then we know there are two unitary matrices  $U_{\mathbb{Z}/4\mathbb{Z}}$ and $U_{\mathbb{Z}/2\mathbb{Z}\times\mathbb{Z}/2\mathbb{Z}}$ (up to a flip of columns and/or rows) where the solution is exact.
+Since $U(n)$ is a Supposing contonuity on the solution and given a matix norm and its induced topology, there exists some neighbourhoods for each matrix $\mathcal{B}(U_{\mathbb{Z}/4\mathbb{Z}})$ and $B(U_{\mathbb{Z}/2\mathbb{Z}\times\mathbb{Z}/2\mathbb{Z}})$ arbitrarily small such that the success probabilities approaches the analytical solution as much as desired.
+However the existence of two unitary matrices that lead up to the same solution complicates the numerical analysis.
+As a matter of fact, given an ensemble of $n$ quantum states, there exist as many unitary matrices as number of groups of $n$ elements where the solution is exact.
+
+Nevertheless, if we consider the case of a prime number of states $n=p$ the task simplifies drastically since we know there only exists one group of $p$ elements and it is $\mathbb{Z}/p\mathbb{Z}$.
+
+This result is inmediate from Lagrange's theoreme.
+The theoreme garanties the order of any element of the group\footnote{The order of an element $\tau$ that belongs to a group $G$ is the minimum natural number $m$ such that $\tau^m=e$ where $e$ stands for the neutral element of the group} must divide the order of the group.
+Since $p$ is prime the order of any element is either 1 or $p$, but if the order of an element is 1 this emplies it is the identity.
+Then every element different from the identity must of order $p$ for any group of $p$ elements i.e.
+the group is cyclic.
+Since the group must be a cyclic gorup of $p$ elements we are left with only one option, the group must be $\mathbb{Z}/p\mathbb{Z}$ up to ismorfism.
+
+Therefore, for ensembles with a prime number of quantum states there only exists one unitary matrix $U$\footnote{Additionally we know the columns of this matrix are the elements of the Fourier's basis from the discussion in section Group Generated Ensembles (\ref{sectionGroupGeneratedEnsemble}) in the examble of $\mathbb{Z}/n\mathbb{Z}$ ensembles} that leads up to a Gram matrix where the given analytical results are exact.
 
@@
 All the code is stored in the GitHub repository \cite{GitHub}.
-The workflow of the study has been the creation of the Mosek solver \cite{mosek_sdp} to numerically solve the \gls{sdp} bla bla bl bla bla blaa.
+The workflow of the study has been the creation of the Mosek solver \cite{mosek_sdp} to numerically solve the \gls{sdp} using the PICOS python package\cite{PICOS}.
+
+\section{Results and discussion}
+
+For us, is particularly interesteing the case of a $\mathbb{Z}/3\mathbb{Z}$ ensemble since we know the Gram matrix to take the form of,
+\begin{align*}
+	\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}=\begin{pmatrix}
+		1 & c & c^*\\
+		c^* & 1 & c\\
+		c & c^* & 1
+	\end{pmatrix}
+\end{align*}
+with $c\in\mathbb{C}$.
+
+\begin{figure}[H]
+	\centering
+	\caption{Representation of the probability of successfull discrimination for a $\mathbb{Z}/3\mathbb{Z}$ group generated ensemble with minimum error (\gls{me}) protocol.}
+	\includegraphics[width=0.5\textwidth, trim={3.3cm 0.8cm 4.5cm 2cm}, clip]{../Plots/DiscriminationOverlapVSPhaseVSMinimumErrorProbabilityZ3HeatMap.pdf}
+\end{figure}
 

### 2025-04-16 Manuscript/Manuscript.tex
writting

@@
 \usepackage{enumitem}
+\usepackage{overpic}
 \usepackage{float}
@@
 \newacronym{ze}{ZE}{Zero Error}
+\newacronym{dof}{DoF}{Degrees of Freedom}
+\newacronym{rng}{RNG}{Random Number Generator}
+\newacronym{srm}{SRM}{Square Root Measurement}
 \glsaddall[types=\acronymtype]
@@
 
-\subsection{Formulation of the Problem}
+\subsection{Formulation of the Problem}\label{sectionFormulationOfTheProblem}
 
@@
 
-\subsection{Gram matrix formulation}
+\subsection{Gram matrix formulation}\label{sectionGramMatrixFormulation}
 Let $\mathcal{G} \in \mathbb{C}^{n \times n}$ be the \emph{Gram matrix} of the system, defined as the $n\times n$ positive semidefinite hermitian matrix such that,
@@
 
-Notice this matrix is Hermitian by construction,
+Notice the Gram matrix is Hermitian by construction,
 \begin{align*}
-\mathcal{G}_{i,j}^* = (\braket{\psi_i|\psi_j})^* = \braket{\psi_j|\psi_i} = \mathcal{G}_{j,i}.
+\mathcal{G}_{i,j}^* = (\braket{\psi_i|\psi_j})^* = \braket{\psi_j|\psi_i} = \mathcal{G}_{j,i},
+\end{align*}
+additionally is a positive semi-definite matrix since for an arbitrary state $\ket{\Phi}$ and a basis $\{\ket{i}\}_{i=1}^n$ we can prove that,
+\begin{align*}
+	\braket{\Phi|\mathcal{G}|\Phi} =& \braket{\Phi|\left(\sum_{i,j=1}^{n}\braket{\psi_i|\psi_j}\ket{i}\bra{j}\right)|\Phi} \\
+	=& \sum_{i,j=1}^{n}\braket{\psi_i|\psi_j}\braket{\Phi|i}\braket{j|\Phi}\\
+	=& \left|\left|\sum_{i=1}^{n}\braket{i|\Phi} \ket{\psi_i}\right|\right|^2\\
+	\geq& 0.
 \end{align*}
@@
 
-Moreover we can compute the Gram matrix of a group generated ensemble by generating the Cayley table, also known as the \emph{multiplication table}, of the group.
+Note the Fourier basis for a $n\times n$ circulant matrix is conformed by the set of vectors $\left\{\omega_i\right\}_{i=1}^n$, such that,
+\begin{align*}
+	\omega_i=\frac{1}{\sqrt{n}}(1,\gamma^{i},\gamma^{2i},...,\gamma^{i(n-1)})^T,
+\end{align*}
+where,
+\begin{align*}
+	\gamma=e^{\frac{2\pi i}{n}}.
+\end{align*}
+
+Moreover we can compute the Gram matrix for any group generated ensemble by generating the Cayley table\cite{CayleyTable}, also known as the \emph{multiplication table}, of the group.
 For instance, let us consider the smallest non-commutative group $S_3$ composed by the rotations and symmetries of the triangle.
@@
 
-\subsection{Previous results}
+\subsection{Previous results}\label{sectionPreviousResults}
 Enormous advances have been made in the exclusion task for group generated ensembles.
@@
 
-\subsection{Ensembles with a prime number of elements}
+\subsection{Limit case scenarios}\label{sectionLimitCaseScenarios}
+
+Let us study the Gram matrix of the limit ensemble of $n$ states, all of them beeing the same state (the state is repeated in the ensemble $n$ times)\footnote{This case might seem paradogic since there is no way to distinguish the same thing.
+Nevertheless, we present it as a limit case scenario.}, reads,
+\begin{align*}
+	\mathcal{G}^{\text{limit}}= \begin{pmatrix}
+ 1 & 1 &\cdots & 1 \\
+ 1 & 1 & \cdots & 1 \\
+ \vdots & \vdots & \ddots & \vdots \\
+ 1 & 1 & \cdots & 1 \\
+\end{pmatrix}.
+\end{align*}
+
+Therefore the eigenvalues of the Gram matrix are,
+
+\begin{align*}
+	\lambda_n=n\\
+	\lambda_{n-1}=0\\
+	\vdots\\
+	\lambda_{1}=0
+\end{align*}
+which clearly fulfil Eq.(\ref{equationPerfectExclusionCondition}) i.e.
+we are in the non-perfect exclusion regime.
+As a matter of fact, we can think of this set of states as a gorup generated ensemble by the trivial gorup\footnote{The trivial group is the one entirely comformed by the identity.}.
+Hence the probability of successfull exclusion and mistakenly exclusion in both protocols is,
+\begin{align*}
+	P_{\gls{me}}^e=P_{\gls{ze}}^e=&\frac{1}{n}\\
+	P_{\gls{me}}^s=P_{\gls{ze}}^s=&\frac{n-1}{n}.
+\end{align*}
+This result is the expected, if there is no physical way to distinguish between states the selection of the excluded state must be taken randomly with homogenious probability.
+Notice this idea is also extensible to \gls{qsd}.
+
+This result is result is the limit plausible scenario, therefore all the computed success probabilities for eighter \gls{qse} or \gls{qsd} for any protocol must be greater to $\frac{n-1}{n}$ (i.e.
+the error probabilities must be lower than $\frac{1}{n}$).
+
+The counterpart scenario is the ensemble comformed by a set of orthogonal states $\{\rho_i\}_{i=i}^{n}$. In this conditions the Gram matrix of the ensemble is the identity,
+\begin{align*}
+	\mathcal{G}=\mathds{1}.
+\end{align*}
+In this conditions, both \gls{qse} and \gls{qsd} are trivial since the set of states comformes a basis. In particular, in the space generated by the linear span of states we know that,
+\begin{align*}
+	\sum_{i=1}^{n}\rho_i=\mathds{1},
+\end{align*}
+i.e. the set of states is a POVM set itself. The outcome of this measurement will lead up to distinguishing the target state with no error, then \gls{qse} and \gls{qsd} can be performed perfectly.
+
+\subsection{Ensembles with a prime number of elements}\label{sectionEnsemblesWithPrime}
 
@@
 Then we know there are two unitary matrices  $U_{\mathbb{Z}/4\mathbb{Z}}$ and $U_{\mathbb{Z}/2\mathbb{Z}\times\mathbb{Z}/2\mathbb{Z}}$ (up to a flip of columns and/or rows) where the solution is exact.
-Since $U(n)$ is a Supposing contonuity on the solution and given a matix norm and its induced topology, there exists some neighbourhoods for each matrix $\mathcal{B}(U_{\mathbb{Z}/4\mathbb{Z}})$ and $B(U_{\mathbb{Z}/2\mathbb{Z}\times\mathbb{Z}/2\mathbb{Z}})$ arbitrarily small such that the success probabilities approaches the analytical solution as much as desired.
-However the existence of two unitary matrices that lead up to the same solution complicates the numerical analysis.
+Since $U(n)$ is a compact set, supposing contonuity on the solution and given a matix norm and its induced topology, there exists some neighbourhoods for each matrix $\mathcal{B}(U_{\mathbb{Z}/4\mathbb{Z}})$ and $B(U_{\mathbb{Z}/2\mathbb{Z}\times\mathbb{Z}/2\mathbb{Z}})$ arbitrarily small such that the success probabilities approaches the analytical solution as much as desired.
+However the existence of two unitary matrices that lead up to the same solution complicates the numerical analysis since the neighbourhoods can intersect.
 As a matter of fact, given an ensemble of $n$ quantum states, there exist as many unitary matrices as number of groups of $n$ elements where the solution is exact.
@@
 
-Therefore, for ensembles with a prime number of quantum states there only exists one unitary matrix $U$\footnote{Additionally we know the columns of this matrix are the elements of the Fourier's basis from the discussion in section Group Generated Ensembles (\ref{sectionGroupGeneratedEnsemble}) in the examble of $\mathbb{Z}/n\mathbb{Z}$ ensembles} that leads up to a Gram matrix where the given analytical results are exact.
+Therefore, for ensembles with a prime number of quantum states there only exists one unitary matrix $U$\footnote{Additionally we know the columns of this matrix are the elements of the Fourier's basis from the discussion in section \emph{Group Generated Ensembles} (\ref{sectionGroupGeneratedEnsemble}) in the examble of $\mathbb{Z}/n\mathbb{Z}$ ensembles} that leads up to a Gram matrix where the given analytical results are exact.
+This ensembles are particularly interesting and will be discussed in the Results and Discussion sestion \textcolor{blue}{Add reference}.
 
 \section{Methodology}
-All the code is stored in the GitHub repository \cite{GitHub}.
+All the code is stored in the GitHub repository \cite{GitHub}. Here you can find extra documentation on the functionality of each script and class.
+
+\subsection{\gls{sdp} solver}
+
 The workflow of the study has been the creation of the Mosek solver \cite{mosek_sdp} to numerically solve the \gls{sdp} using the PICOS python package\cite{PICOS}.
+
+\subsection{Generation of random Gram matrices}
+
+The \gls{rng} provides a set of $n$ random numbers $\{\lambda_i\}_{i=1}^n$ that are normalized such that their sum is equal to n,
+\begin{align*}
+	\sum_{i=1}^n\lambda_i=n,
+\end{align*}
+this will be the eigenvalues of the gram matrix comforming the diagonal matrix $D$.
+Then we generate a matrix $U$ such that $\mathcal{G}=UDU^\dagger$.
+At this stage we choose between a group generated enseble or a generic one.
+
+The generic ensemble is generated by a random unitary matrix $U$ such that distribution the unique measure is invariant under group multiplication, known as Haar measure\cite{haarMeasure}.
+This is acomplished by using the Francesco Mezzadri's algorithm presented in \cite{UnitaryMatricesGeneration}.
+This way we ensure the $U(n)$ set is covered homogeniously by our random unitary matrices.
+
+For a $\mathbb{Z}/n\mathbb{Z}$ group generated ensemble the unitary matix $U$ is the one that encodes the vectors of the Fourier basis as columns as discussed in section (\ref{sectionGroupGeneratedEnsemble}) Group Generated Esnemble.
+
+Other gorus are obviated since we can always set $n$ to be a prime number and impossing $\mathbb{Z}/n\mathbb{Z}$ to be the only possibile group generated ensemble.
 
@@
 
-For us, is particularly interesteing the case of a $\mathbb{Z}/3\mathbb{Z}$ ensemble since we know the Gram matrix to take the form of,
+Let us analyze the case of a $\mathbb{Z}/3\mathbb{Z}$ ensemble. We know the Gram matrix takes the form of,
 \begin{align*}
@@
 with $c\in\mathbb{C}$.
+Notice that respect the previous notation, we are writting $c=\braket{U}_{\psi}$, where $c$ and $c^*$ denotes the overlap between different states.
+Therefore we notice if we write $c=|c|e^{i\phi}$, and since we are analyzing an overlap of normalized states,
+\begin{align*}
+	|c|\in [0,1]\quad \text{and}\quad \theta\in[0,2\pi]
+\end{align*}
+we have two \gls{dof}.
+
+Since 3 is a prime number the only group of 3 elements is $\mathbb{Z}/3\mathbb{Z}$ as discussed in the section \emph{Ensembles with a prime number of elements} (\ref{sectionEnsemblesWithPrime}), then the Gram matrix can be diagonalized as,
+\begin{align*}
+	\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}=U_{\mathbb{Z}/3\mathbb{Z}}DU^\dagger_{\mathbb{Z}/3\mathbb{Z}},
+\end{align*}
+where, $U_{\mathbb{Z}/3\mathbb{Z}}$ stands for the unitary matrix with the Fourier basis as columns.
+Then the eigenvalues of the matrix are $\{\lambda_1,\lambda_2,\lambda_3\}$ where $\lambda_1\leq\lambda_2\leq\lambda_3$.
+Notice that,
+\begin{align*}
+	3=\tr{\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}}=\tr{D}=\sum_{i=1}^3\lambda_i
+\end{align*}
+which constraints the system two only 2 \gls{dof}, as expected concording with the \gls{dof} of the previous picture of the Gram matrix, where we were looking directly at the elements instead of the eigenvalues.
+Additionally, we know that,
+\begin{align*}
+	\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}\geq 0\Rightarrow \lambda_i\geq 0 \quad\forall i\in\{1,2,3\}.
+\end{align*}
+Which implies the eigenvalues are constrained to be number between $0$ and $3$.\footnote{For the general case scenario the eigenvalues are numbers between 0 and $n$.
+Also notice, this holds true even in the non-group generated ensembles.} Then,
+\begin{align*}
+	\lambda_3\in[0,3]\quad \lambda_2\in[0,\lambda_3]\quad \lambda_1=3-\lambda_3-\lambda_2
+\end{align*}
+
+This case is particularly interesting since it is the only ensemble that allows us to represent all the dependencies in each \gls{dof} and visually analyze the hole ensemble\footnote{The plots consists in 2 parameters plus the success/error exclusion probability for the respective protocol.}.
+For scenarios with more quantum states it is impossible to represent the hole picture, and for the two quantum states case we have already discussed its equivalentcy to the discrimination task in \gls{qsd}.
+
+\subsection{Comparation \gls{qsd} vs. \gls{qse} and \gls{me} vs. \gls{ze}}
+
+First of all, let us present some results for the Quantum State Discrimination (\gls{qsd}) task, in order to motivate the problem and discuss the advantages and disadvantages respect its counterpart, the \gls{qsd}, the main object of study for this project.
+In Figure (\ref{FigureQSDMEZ3ZHeatmap}) we can find a heatmap of the average successfull discrimination probability for the minimum error \gls{me} protocol for a $\mathbb{Z}/3\mathbb{Z}$ group generated ensemble.
+The probabilities are represented in terms of the modolus of the overlap ($x$-axis) and the phase ($y$-axis) that completely determine the Gram matrix of the ensemble, as discussed previousl.
+Additionally we present the case for equal prior probabilities since the results can be easily generaliced to arbitrary prior probabilities as discussed in section (\ref{sectionGramMatrixFormulation}) Gram Matrix Formulation.
+The prior probabilities scenario will the standard procedure for all the project.
 
@@
 	\centering
-	\caption{Representation of the probability of successfull discrimination for a $\mathbb{Z}/3\mathbb{Z}$ group generated ensemble with minimum error (\gls{me}) protocol.}
-	\includegraphics[width=0.5\textwidth, trim={3.3cm 0.8cm 4.5cm 2cm}, clip]{../Plots/DiscriminationOverlapVSPhaseVSMinimumErrorProbabilityZ3HeatMap.pdf}
+	\label{FigureQSDMEZ3ZHeatmap}
+	\begin{overpic}[width=0.5\textwidth, trim={2.3cm 0.8cm 4.5cm 2cm}, clip]{../Plots/DiscriminationOverlapVSPhaseVSMinimumErrorProbabilityZ3HeatMap.pdf}
+		\put(60,25){$G<0$}
+		\put(60,55){$G<0$}
+	\end{overpic}
+	\caption{Representation of the probability of successfull discrimination for a $\mathbb{Z}/3\mathbb{Z}$ group generated ensemble with Minimum Error (\gls{me}) protocol.}
 \end{figure}
+
+The colorless region comprehends the overlap values $c$ (i.e.
+$c=overlap\cdot e^{i phase}$) such that $\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}$ has negative eigenvalues values.
+The matrix generated in this region are no Gram matrices \emph{per se} since positive semi-definiteness is required as discussed in section (\ref{sectionGramMatrixFormulation}) Gram Matrix Formulation.
+
+In this conditions we know the known as \gls{srm} \footnote{a.k.a.
+pretty good measurement.} to be optimal, i.e.
+the result of the \gls{sdp} is the same as the \gls{srm}.
+This measurement is the one obtained by the decomposition of the Gram matrix the square root of an hermitian matrix $S$ as the following,
+\begin{align*}
+	\mathcal{G}=S^\dagger S=S^2.
+\end{align*}
+this measurement is the estandard in \gls{qsd} for the \gls{me} protocol \cite{OptimalitySRM}.
+
+As expected no ensemble leads to probabilities under $\frac{1}{3}$ acording to the previous discussion in section (\ref{sectionLimitCaseScenarios}) Limit Case Scenarios.
+
+Moreover we observe when the modolus of the overlap tends to 0 the success probability tends to 1.
+Naturally the observation is consistent since this limit is the one obtained with ensembles of orthogonal states and we obtain the expected result discussed in section (\ref{sectionLimitCaseScenarios}) Limit Case Scenarios.
+
+Additionally we can consider the same condition but using the Zero Error (\gls{ze}), the result are shown in Figure (\ref{FigureQSDZEZ3ZHeatmap}).
+
+\begin{figure}[H]
+	\centering
+	\label{FigureQSDZEZ3ZHeatmap}
+	\begin{overpic}[width=0.5\textwidth, trim={2.3cm 0.8cm 4.5cm 2cm}, clip]{../Plots/DiscriminationOverlapVSPhaseVSSuccessProbabilityZeroErrorZ3HeatMap.pdf}
+		\put(60,25){$G<0$}
+		\put(60,55){$G<0$}
+	\end{overpic}
+	\caption{Representation of the probability of successfull discrimination for a $\mathbb{Z}/3\mathbb{Z}$ group generated ensemble with Zero Error (\gls{ze}) protocol.}
+\end{figure}
+We observe both limit scenarios are preserved in this protocol too as expected.
+Additionally, notice the successfull exclusion probabilities are lower than the ones obtained with the Minimum Error (\gls{me}) protocol.
+This observation is explained by the \gls{sdp} construction of the problem in section (\ref{sectionFormulationOfTheProblem}) Formulation Of The Problem.
+Notice both probabilities are computed in a completely symmetric way,
+\begin{align*}
+	P^s_{\gls{me}}\sim P^s_{\gls{ze}}\sim 1-\sum_{\gls{povm}}\tr{(\Pi_i\rho_i)}.
+\end{align*}
+
+Nevertheless, in the \gls{ze} case we enforce $\tr{(\Pi_i\rho_i)}=0$ for all the \glspl{povm} except one.
+Thus, the system is more constrained in the \gls{ze} protocol, then the optimization of the probability cannot be performed up to the same point as in the \gls{me} protocol.
+Hence, the probabilities for
 

### 2025-04-16 Manuscript/Manuscript.tex
writting

@@
 
+The colorless region comprehends the overlap values $c$ (i.e.
+$c=overlap\cdot e^{i phase}$) such that $\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}$ has negative eigenvalues values.
+The matrix generated in this region are no Gram matrices \emph{per se} since positive semi-definiteness is required as discussed in section (\ref{sectionGramMatrixFormulation}) Gram Matrix Formulation.
+
 \begin{figure}[H]
@@
 
-The colorless region comprehends the overlap values $c$ (i.e.
-$c=overlap\cdot e^{i phase}$) such that $\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}$ has negative eigenvalues values.
-The matrix generated in this region are no Gram matrices \emph{per se} since positive semi-definiteness is required as discussed in section (\ref{sectionGramMatrixFormulation}) Gram Matrix Formulation.
-
-In this conditions we know the known as \gls{srm} \footnote{a.k.a.
-pretty good measurement.} to be optimal, i.e.
+In this conditions we know the known as \gls{srm} \footnote{Also known as \emph{pretty good measurement}.} to be optimal, i.e.
 the result of the \gls{sdp} is the same as the \gls{srm}.
@@
 Thus, the system is more constrained in the \gls{ze} protocol, then the optimization of the probability cannot be performed up to the same point as in the \gls{me} protocol.
-Hence, the probabilities for
+Hence, the success probabilities for \gls{me} are greater than the ones obtained with the \gls{ze} protocol.
+
+We compare both protocols as well as the outcome of the \gls{srm} in Figure (\ref{FigureQSDMEZESRM}).
+
+\begin{figure}[H]
+	\centering
+	\label{FigureQSDMEZESRM}
+	\includegraphics[width=0.5\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{../Plots/DiscriminationOverlapVSSucessProbabilitySDPvsSRMZnOverlap3Phase0.pdf}
+	\caption{Representation of the probability of successfull discrimination for a $\mathbb{Z}/3\mathbb{Z}$ group generated ensemble with Zero Error (\gls{ze}) Minimum Error (\gls{me}) protocols and the Square Root Measurement (\gls{srm}).}
+\end{figure}
+
+We observe perfect discrimination in not possible unless we impose orthogonality (i.e.
+overlap $= 0$), the trivial ensemble.
+This result is the main difference between the discrimination and exclusion task and the main motivation in the reserch on quantum state exclusion \gls{qse}.
+
+In contrast, in Figure (\ref{FigureQSEMEZ3ZHeatmap}) we present the results for the Quantum State Exclusion (\gls{qse}) for the $\mathbb{Z}/3\mathbb{Z}$ for the \gls{me} protocol in an analogously to Figure (\ref{FigureQSDMEZ3ZHeatmap}).
+
+\begin{figure}[H]
+	\centering
+	\label{FigureQSEMEZ3ZHeatmap}
+	\begin{overpic}[width=0.5\textwidth, trim={2.3cm 0.8cm 4.5cm 2cm}, clip]{../Plots/ExlusionOverlapVSPhaseVSMinimumErrorProbabilityZ3HeatMap.pdf}
+		\put(60,25){$G<0$}
+		\put(60,55){$G<0$}
+	\end{overpic}
+	\caption{Representation of the probability of successfull exclusion for a $\mathbb{Z}/3\mathbb{Z}$ group generated ensemble with Minimum Error (\gls{me}) protocol.}
+\end{figure}
+
+We observe perfect exclussion can be performed in esembles such that perfect discrimination is not possible, particularly ensembles that fulfil Eq.
+(\ref{equationPerfectExclusionCondition}).
+This regime is highlighted in Figure (\ref{FigureQSEMEZ3ZPerfectExclusion}), where both regimes are clearly distinguished.
+
+\begin{figure}[H]
+	\centering
+	\label{FigureQSEMEZ3ZPerfectExclusion}
+	\begin{overpic}[width=0.5\textwidth, trim={2.3cm 0.8cm 2.5cm 2cm}, clip]{../Plots/ExlusionOverlapVSPhaseVSPerfectExclussionZoneZ3BinaryHeatMap.pdf}
+		\put(60,25){$G<0$}
+		\put(60,60){$G<0$}
+	\end{overpic}
+	\caption{Representation of the perfect exclusion zone for a $\mathbb{Z}/3\mathbb{Z}$ group generated ensemble with Minimum Error (\gls{me}) protocol.}
+\end{figure}
 

### 2025-04-17 Manuscript/Manuscript.tex
writting

--- 2025-04-14 Manuscript/Manuscript.tex
@@
 
-\subsection{Gram matrix formulation}
-Let $\mathcal{G} \in \mathbb{C}^{n \times n}$ be the \emph{Gram matrix} of the system, defined as the $n\times n$ positive semidefinite hermitian matrix such that,
+\subsection{Gram Matrix Formulation}\label{sectionGramMatrixFormulation}
+
+Let $\mathcal{G} \in \mathbb{C}^{n \times n}$ be the \emph{Gram matrix} of the system, defined as the $n \times n$ positive semidefinite Hermitian matrix given by,
 \begin{equation*}
@@
 	\begin{pmatrix}
-		\braket{\psi_1|\psi_1} & \braket{\psi_1|\psi_2} & \dots & \braket{\psi_1|\psi_n}\\
-		\braket{\psi_2|\psi_1} & \braket{\psi_2|\psi_2} & \dots & \braket{\psi_2|\psi_n}\\
-		\vdots & \vdots & \ddots & \vdots\\
+		\braket{\psi_1|\psi_1} & \braket{\psi_1|\psi_2} & \dots & \braket{\psi_1|\psi_n} \\
+		\braket{\psi_2|\psi_1} & \braket{\psi_2|\psi_2} & \dots & \braket{\psi_2|\psi_n} \\
+		\vdots & \vdots & \ddots & \vdots \\
 		\braket{\psi_n|\psi_1} & \braket{\psi_n|\psi_2} & \dots & \braket{\psi_n|\psi_n}
@@
 \end{equation*}
-i.e., $\mathcal{G}_{i,j} = \braket{\psi_i|\psi_j}$. Since all states are normalized, we have,
+that is, $\mathcal{G}_{i,j} = \braket{\psi_i|\psi_j}$. Since all states are normalized, the diagonal elements are equal to 1, and the Gram matrix becomes,
 \begin{equation*}
@@
 	\begin{pmatrix}
-		1 & \braket{\psi_1|\psi_2} & \dots & \braket{\psi_1|\psi_n}\\
-		\braket{\psi_2|\psi_1} & 1 & \dots & \braket{\psi_2|\psi_n}\\
-		\vdots & \vdots & \ddots & \vdots\\
+		1 & \braket{\psi_1|\psi_2} & \dots & \braket{\psi_1|\psi_n} \\
+		\braket{\psi_2|\psi_1} & 1 & \dots & \braket{\psi_2|\psi_n} \\
+		\vdots & \vdots & \ddots & \vdots \\
 		\braket{\psi_n|\psi_1} & \braket{\psi_n|\psi_2} & \dots & 1
@@
 
-Notice this matrix is Hermitian by construction,
+By construction, the Gram matrix is Hermitian,
 \begin{align*}
@@
 \end{align*}
+Additionally, $\mathcal{G}$ is positive semidefinite. To see this, consider an arbitrary state $\ket{\Phi}$ and an orthonormal basis $\{\ket{i}\}_{i=1}^n$, then,
+\begin{align*}
+	\braket{\Phi|\mathcal{G}|\Phi} &= \braket{\Phi| \left( \sum_{i,j=1}^{n} \braket{\psi_i|\psi_j} \ket{i}\bra{j} \right) |\Phi} \\
+	&= \sum_{i,j=1}^{n} \braket{\psi_i|\psi_j} \braket{\Phi|i} \braket{j|\Phi} \\
+	&= \left\| \sum_{i=1}^{n} \braket{i|\Phi} \ket{\psi_i} \right\|^2 \\
+	&\geq 0.
+\end{align*}
 
-The Gram matrix allows us to reframe the exclusion problem in a more abstract and basis-independent form. Since $\mathcal{G}$ is hermitian and positive semi-definite, we can write,
+The Gram matrix allows us to reformulate the exclusion problem in a more abstract, basis-independent manner. Since $\mathcal{G}$ is Hermitian and positive semidefinite, it can be factorized as,
 \begin{align*}
@@
 \end{align*}
-for some matrix $X$ whose columns are the pure states,
+for some matrix $X$, whose columns are the pure states,
 \begin{align*}
@@
 \end{align*}
-Notice the diagonal elements of $X$ are,
+
+Let us fix an arbitrary orthonormal basis $\{\ket{\omega_i}\}_{i=1}^n$. Then, the diagonal entries of $X$ in this basis are given by,
 \begin{align*}
-	X_{i,i}=\braket{\omega_i|\psi_i}
+	X_{i,i} = \braket{\omega_i|\psi_i}.
 \end{align*}
-For an arbitrary orthonormal basis $\left\{\ket{\omega_i}\right\}_{i=1}^n$.
-\footnote{It is important to remark that fixing the basis $\left\{\ket{\omega_i}\right\}_{i=1}^n$ fixes the decomposition of $G=X^\dagger X$ and vice versa.}
-
-Let us consider an arbitrary orthonormal basis $\left\{\ket{\omega_i}\right\}_{i=1}^n$, and define the POVM elements as projectors $\Pi_i = \ket{\omega_i}\bra{\omega_i}$.
-Then, the \gls{sdp} formulation for the ensemble $\left\{(\rho_i,\eta_i)\right\}_{i=1}^n$ can be expressed as the following,
+\footnote{Note that fixing the basis $\{\ket{\omega_i}\}_{i=1}^n$ uniquely determines the decomposition $\mathcal{G} = X^\dagger X$, and vice versa.}We define the POVM elements as projectors $\Pi_i = \ket{\omega_i}\bra{\omega_i}$.
+Then, for the ensemble $\{(\rho_i, \eta_i)\}_{i=1}^n$, the corresponding semidefinite program (\gls{sdp}) constraints become,
 \begin{align*}
@@
 
-Therefore, we can reformulate the \gls{sdp} for the \gls{me} protocol as,
+Thus, we can reformulate the \gls{sdp} for the minimum-error (\gls{me}) protocol as,
 \begin{align*}
-	P_{\gls{me}}^e = \min_{X} &\sum_{i=1}^n \frac{|X_{i,i}|^2}{\eta_i},\\
+	P_{\gls{me}}^e = \min_{X} &\sum_{i=1}^n \frac{|X_{i,i}|^2}{\eta_i}, \\
 	\text{subject to} \quad & X^\dagger X = \mathcal{G}, \quad X \geq 0.
@@
 \begin{align*}
-	P_{\gls{me}}^s = \max_{X} &\left(1 - \sum_{i=1}^n \frac{|X_{i,i}|^2}{\eta_i}\right),\\
+	P_{\gls{me}}^s = \max_{X} &\left( 1 - \sum_{i=1}^n \frac{|X_{i,i}|^2}{\eta_i} \right), \\
 	\text{subject to} \quad & X^\dagger X = \mathcal{G}, \quad X \geq 0.
@@
 
-This reformulation highlights that if two ensembles $A$ and $B$ share the same Gram matrix, then their exclusion problems, in both \gls{me} and \gls{ze} protocols, are equivalent.
-That is, the optimal success and error probabilities are identical in both systems.
-Hence, we focus on the Gram matrix to analyze exclusion problems, rather than relying on explicit state representations.
+This reformulation reveals that if two ensembles $A$ and $B$ share the same Gram matrix, then their exclusion problems under both the \gls{me} and \gls{ze} protocols are equivalent.
+That is, their optimal success and error probabilities coincide.
+Consequently, we focus on the Gram matrix to study exclusion problems rather than the explicit state representations.
 
-Moreover, we remark we are not especially interested in the arbitrary prior probabilities $\eta_i$ scenario, since the result for equal prior probabilities $\eta_i=\frac{1}{n}$ can be easily extended to the previous case, with $n$ as the number of states.
-This extension can be performed by considering the non-normalized states
+Furthermore, we note that the case of arbitrary prior probabilities $\eta_i$ can be reduced to the equal prior case $\eta_i = \frac{1}{n}$ by defining non-normalized states,
 \begin{align*}
-	\ket{\tilde{\psi_i}}=\frac{1}{\sqrt{\eta_i}}\ket{\psi_i}
+	\ket{\tilde{\psi}_i} = \frac{1}{\sqrt{\eta_i}} \ket{\psi_i},
 \end{align*}
-and reformulate the problem in terms of this new states forgetting about the prior probabilities since they are encoded inside the states.
-Thus, for simplicity we will consider the equal probabilities case.
+and reformulating the problem in terms of these states.
+The prior probabilities are then absorbed into the state norm.
+Therefore, without loss of generality, in this project we will assume equal prior probabilities.
 
@@
 
-Given a quantum state $\ket{\psi}$, which we refer to as the \emph{seed state}, we define a \emph{group generated ensemble} as the set of states obtained by applying a group of unitary transformations to $\ket{\psi}$.
-Specifically, if the ensemble consists of a total of $n$ quantum states, then its elements are of the form,
+Given a quantum state $\ket{\psi}$, referred to as the \emph{seed state}, we define a \emph{group generated ensemble} as the set of states obtained by applying a group of unitary transformations to $\ket{\psi}$.
+Specifically, if the ensemble consists of $n$ quantum states, its elements are of the form
 \begin{align*}
@@
 \end{align*}
-where the set of unitary matrices $\{U_i\}_{i=1}^n$ forms a finite group under standard matrix product. In terms of density matrices, the ensemble can equivalently be written as:
+where the set of unitary matrices $\{U_i\}_{i=1}^n$ forms a finite group under standard matrix multiplication. In terms of density matrices, the ensemble can equivalently be written as,
 \begin{align*}
@@
 \begin{align*}
-	\left\{ \mathcal{U}^i\ket{\psi} \right\}_{i=0}^{n-1}
+	\left\{ \mathcal{U}^i\ket{\psi} \right\}_{i=0}^{n-1},
 \end{align*}
 forms a group generated ensemble based on the cyclic group $\mathbb{Z}/n\mathbb{Z}$.
-This type of ensemble is of particular interest in our study and will be explored in more detail in subsequent section.
+This type of ensemble is of particular interest in our study and will be explored in more detail in a subsequent section.
 
-\emph{Example: The $\mathbb{Z}/n\mathbb{Z}$ group generated ensemble}: Let $\mathcal{U} \in U(n)$ be an $n \times n$ unitary matrix satisfying $\mathcal{U}^n = \mathds{1}$, and let $\ket{\psi}$ be the seed state.
-The Gram matrix $\mathcal{G}^{\mathbb{Z}/n\mathbb{Z}}$ elements associated with the ensemble $\left\{\mathcal{U}^i\ket{\psi}\right\}_{i=0}^{n-1}$ are nothing but,
+\emph{Example: The $\mathbb{Z}/n\mathbb{Z}$ group-generated ensemble}: Let $\mathcal{U} \in U(n)$ be an $n \times n$ unitary matrix satisfying $\mathcal{U}^n = \mathds{1}$, and let $\ket{\psi}$ be the seed state.
+The Gram matrix $\mathcal{G}^{\mathbb{Z}/n\mathbb{Z}}$ elements associated with the ensemble $\left\{\mathcal{U}^i\ket{\psi}\right\}_{i=0}^{n-1}$ are
 \begin{align*}
@@
 \end{align*}
-where we use the shorthand notation
+where we use the shorthand notation,
 \begin{align*}
@@
 
-Note the Gram matrix is Hermitian, as required, since,
+Note that the Gram matrix is Hermitian, as expected, since
 \begin{align*}
-    \braket{\mathcal{U}^{-j}}_{\psi} = \braket{\psi | U^{-j} | \psi} = \left(\braket{\psi | U^j | \psi}\right)^* = \braket{\mathcal{U}^j}_{\psi}^*.
+    \braket{\mathcal{U}^{-j}}_{\psi} = \braket{\psi | \mathcal{U}^{-j} | \psi} = \left(\braket{\psi | \mathcal{U}^j | \psi}\right)^* = \braket{\mathcal{U}^j}_{\psi}^*.
 \end{align*}
-Additionally, by using the identity $\mathcal{U}^n = \mathds{1}$, we can simplify terms such as,
+Additionally, by using the identity $\mathcal{U}^n = \mathds{1}$, we can simplify expressions such as,
 \begin{align*}
@@
 \end{align*}
-Therefore we may write,
+Thus, we may write,
 \begin{align*}
-	\mathcal{G}^{\mathbb{Z}/n\mathbb{Z}_{\psi}} = \begin{pmatrix}
+	\mathcal{G}^{\mathbb{Z}/n\mathbb{Z}}_{\psi} = \begin{pmatrix}
  1 & \braket{\mathcal{U}}_{\psi} & \braket{\mathcal{U}^{2}}_{\psi} & \hdots &  \braket{\mathcal{U}}_{\psi}^* \\
@@
 
-This confirms the circulant structure of $\mathcal{G}$, where each row is a cyclic permutation of the one above it.
-In other words the Gram matrix of $\mathbb{Z}/n\mathbb{Z}$ matrices are circulant matrixes.
-This result is especially useful, as they can be diagonalized by the discrete Fourier basis, which simplifies many tasks\cite{circulantMatrices}.
+This shows the circulant structure of $\mathcal{G}$, where each row is a cyclic permutation of the previous one.
+In other words, the Gram matrices of $\mathbb{Z}/n\mathbb{Z}$-generated ensembles are circulant matrices.
+This structure is particularly useful, as circulant matrices can be diagonalized by the discrete Fourier basis, greatly simplifying many computations~\cite{circulantMatrices}.
 
-Moreover we can compute the Gram matrix of a group generated ensemble by generating the Cayley table, also known as the \emph{multiplication table}, of the group.
-For instance, let us consider the smallest non-commutative group $S_3$ composed by the rotations and symmetries of the triangle.
-If we denote the identity as $e$, the 3 symmetries as $p$, $q$ and $s$ and a rotation as $s$, we know the Cayley table to be,
+The Fourier basis for an $n \times n$ circulant matrix consists of the set of vectors $\{\omega_i\}_{i=1}^n$, where
+\begin{align*}
+	\omega_i = \frac{1}{\sqrt{n}} (1, \gamma^i, \gamma^{2i}, \ldots, \gamma^{i(n-1)})^T,
+\end{align*}
+and
+\begin{align*}
+	\gamma = e^{\frac{2\pi i}{n}}.
+\end{align*}
+
+Moreover, we can compute the Gram matrix for any group-generated ensemble by using the Cayley table~\cite{CayleyTable}, also known as the \emph{multiplication table}, of the group.
+For example, consider the smallest non-commutative group, $S_3$, consisting of the symmetries and rotations of an equilateral triangle.
+Denoting the identity as $e$, the rotations elements as $s$, $s^2$ (one being the result of 2 times the other) and the symmetries $p$, $q$, and $r$, the Cayley table is,
+
 \begin{table}[H]
@@
 	\caption{Cayley table of the $S_3$ group.}
-	\begin{tabular}{c||c c c c c c c}
+	\begin{tabular}{c||c c c c c c}
         $S_3$ & $e$ & $s$ & $s^2$ & $p$ & $q$ & $r$ \\\hline\hline
@@
 
-where we have enforced the diagonal elements to be the identity.
-Subsequently if we identify $S_3$ as a group of unitary matrices \footnote{we think of each element of the group as an unitary matrix and the operation of the group as the matrix product.} we immediatelly realize the Gram matrix of the $S_3$ group generated ensemble is the matrix corresponding to the expected values of the Cayley table respect a certain seed state $\ket{\psi}$.
-In other words the Gram matrix is nothing but,
+We now identify $S_3$ as a group of unitary matrices\footnote{We treat each group element as a unitary matrix, and the group operation as matrix multiplication.}.
+It follows that the Gram matrix of the $S_3$ group-generated ensemble is the matrix of expected values of the Cayley table entries with respect to the seed state $\ket{\psi}$.
+That is,
 \begin{align*}
-	\mathcal{G}^{S_3}_{\psi}=\begin{pmatrix}
+	\mathcal{G}^{S_3}_{\psi} = \begin{pmatrix}
         1 & \braket{s}_\psi & \braket{s^2}_\psi & \braket{p}_\psi & \braket{q}_\psi & \braket{r}_\psi \\ 
@@
 \end{align*}
-Notice that, $\braket{e}_\psi=1$ since $e$ is the neutral element of the matrix product operation, i.e.
-$e=\mathds{1}$.
-Moreover in this particular example we can observe since $\mathcal{G}^{S_3}$ is hermitian we know that,
-\begin{align*}\begin{cases}
-	\braket{p}_{\psi}=&\braket{p}_{\psi}^*\\
-	\braket{q}_{\psi}=&\braket{q}_{\psi}^*\\
-\braket{r}_{\psi}=&\braket{r}_{\psi}^*\end{cases}&\quad \forall \ket{\psi}\in \mathcal{H}\\
-\Updownarrow& \\
-\braket{p}_{\psi},\braket{q}_{\psi},\braket{r}_{\psi}\in&\mathbb{R}\quad \forall \ket{\psi}\in \mathcal{H}.
+Note that $\braket{e}_\psi = 1$ since $e = \mathds{1}$. Moreover, since $\mathcal{G}^{S_3}$ is Hermitian, we conclude:
+\begin{align*}
+\braket{p}_{\psi},\ \braket{q}_{\psi},\ \braket{r}_{\psi} \in \mathbb{R}, \quad \forall \ket{\psi} \in \mathcal{H},
 \end{align*}
-Therefore the unitary matrices corresponding to the triangle symmetries $p$, $q$ and $r$ are hermitian.
-It is inmediate this procedure can be applied for any group $G$, whic implies that computing the Cayley table is equivalent to computin the Gram matrix of the group generated ensemble.
+which implies the unitary matrices corresponding to the triangle symmetries $p$, $q$, and $r$ are Hermitian.
+As a matter of fact we know the eigenvalues of this matrices can only be $\pm 1$ and at least one of them must be $-1$.\footnote{Otherwise, they would be the identity and we know them to be different by construction.} This procedure generalizes to any finite group $G$, showing that computing the Cayley table is equivalent to computing the Gram matrix of the corresponding group-generated ensemble.
 
-Additionally, we will denote the cardinality of a finite group $G$\footnote{The cardinality of a group is the same as the number elements of the group.}, as $|G|$ which implies that for our case of interest of the prior probabilities scenario we may write $\eta_i=\frac{1}{|G|}$.
+Finally, we denote the cardinality of a finite group $G$ (i.e., the number of its elements) as $|G|$. In scenarios with uniform prior probabilities, this implies,
+\begin{align*}
+	\eta_i = \frac{1}{|G|}\quad \forall i\in\{1,...,n\}.
+\end{align*}
+\subsection{Dual Formulation of the Problem}
 
-\subsection{Dual formulation of the problem}
-Sometimes it is usefull to consider the dual version of each \emph{sdp} problem.
-The dual version of the exclusion task for the $\left\{\left(\rho_i,\frac{1}{n}\right)\right\}_{i=1}^n$ ensemble for the error probability with the Minimum Error (\gls{me}) protocol is,
+It is often useful to consider the \emph{dual} version of a \gls{sdp} problem, as it provides both conceptual insights and practical advantages for verifying optimality.
+
+Consider the ensemble $\left\{ \left( \rho_i, \frac{1}{n} \right) \right\}_{i=1}^n$, where each state $\rho_i$ appears with uniform prior probability $1/n$.
+The dual SDP corresponding to the Minimum Error (\gls{me}) exclusion protocol, when expressed in terms of the error probability, is given by,
 \begin{align*}
-	\tilde{P}_{\gls{me}}^e=\max_{\Gamma}&\tr{\Gamma}\\
-	\text{subject to }&\frac{\rho_i}{n}-\Gamma\geq 0\quad\forall i\in\{1,...,n\}\\
-	&\Gamma^\dagger=\Gamma,
+	\tilde{P}_{\gls{me}}^e = \max_{\Gamma} \quad & \tr{\Gamma} \\
+	\text{subject to} \quad & \frac{\rho_i}{n} - \Gamma \geq 0 \quad \forall i \in \{1, \dots, n\}, \\
+	& \Gamma^\dagger = \Gamma,
 \end{align*}
-where $\tilde{P}$ stands for the dual version of the problem. Naturally, for the success probability the problem reads,
+where $\tilde{P}$ denotes the dual version of the problem.
+
+Similarly, the dual SDP for the success probability in the same protocol reads:
 \begin{align*}
-	\tilde{P}_{\gls{me}}^s=\min_{\Gamma}&\left(1-\tr{\Gamma}\right)\\
-	\text{subject to }&\frac{\rho_i}{n}-\Gamma\geq 0\quad\forall i\in\{1,...,n\}\\
-	&\Gamma^\dagger=\Gamma.
+	\tilde{P}_{\gls{me}}^s = \min_{\Gamma} \quad & 1 - \tr{\Gamma} \\
+	\text{subject to} \quad & \frac{\rho_i}{n} - \Gamma \geq 0 \quad \forall i \in \{1, \dots, n\}, \\
+	& \Gamma^\dagger = \Gamma.
 \end{align*}
+
 \textcolor{blue}{Add the dual version for the zero error protocol.}
 
-The dual version results specially usefull since given an POVM anzatz if the probabilities of the primal and dual problems coincide, i.e. $P=\tilde P$ we know we have found the optimal measurement.
+In the case of the zero-error exclusion protocol, the dual SDP formulation becomes
 
-\subsection{Previous results}
-Enormous advances have been made in the exclusion task for group generated ensembles.
-The publication \emph{Quantum state exclusion for group-generated ensembles of pure states}\cite{MainPaper} yields a result of the actual exact success and/or error probabilities for both \gls{me} and \gls{ze} protocols for group generated ensembles.
-The result reads, let $\mathcal{G}^{G}$ the Gram matrix of the group generated ensemble $\left\{\left(\rho_i,\frac{1}{|G|}\right)\right\}_{i=1}^{|G|}$ corresponding to a finite group $G$, where $|G|$ denotes the number of the group's elements, let also $\{\lambda_i\}_{i=1}^{|G|}$ be the set of eigenvalues of the Gram matrix.
-Additionally let us consider the set of eigenvalues $\{\lambda_i\}_{i=1}^{|G|}$ to be an ordered group, such that,
+One of the primary uses of the dual formulation is in establishing optimality.
+If a POVM ansatz yields equal objective values for both the primal and dual problems, i.e., $P = \tilde{P}$, then strong duality holds and the measurement is guaranteed to be optimal.
+
+This duality principle not only provides a tool for verification but also suggests constructive approaches to discovering optimal measurements, especially in structured ensembles such as those generated by group actions.
+\subsection{Previous Results}\label{sectionPreviousResults}
+
+Significant progress has been made in the study of the state exclusion task for group-generated ensembles.
+In particular, the work \emph{Quantum State Exclusion for Group-Generated Ensembles of Pure States}\cite{MainPaper} presents exact analytical expressions for the success and error probabilities under both the Minimum Error \gls{me} and Zero Error \gls{ze} exclusion protocols.
+
+Let $\mathcal{G}^G$ denote the Gram matrix of a group-generated ensemble $\left\{ \left( \rho_i, \frac{1}{|G|} \right) \right\}_{i=1}^{|G|}$, where $G$ is a finite group of size $|G|$, and let $\{\lambda_i\}_{i=1}^{|G|}$ be the set of eigenvalues of $\mathcal{G}^G$.
+Assume the eigenvalues are ordered increasingly,
 \begin{align*}
-	i\leq j\quad\forall i,j\in\{1,...,|G|\}\Leftrightarrow \lambda_i\geq\lambda_j \forall i,j\in\{1,...,|G|\},
+	i \leq j \quad \Leftrightarrow \quad \lambda_i \leq \lambda_j, \quad \forall i,j \in \{1, \dots, |G|\},
 \end{align*}
-or equivalently, the set is ordered from the lowest to highest eigenvalue. Hence, the exclusion probabilities for the minimum error (\gls{me}) protocol are,
+i.e., $\lambda_1$ is the smallest and $\lambda_{|G|}$ the largest eigenvalue.
+
+The exclusion probabilities under the Minimum Error protocol are given by,
 \begin{align*}
-	P_{\gls{me}}^e=&\max\left\{0,\left(\frac{\sqrt{\lambda_{|G|}}-\sum_{i<|G|}\sqrt{\lambda_i}}{|G|}\right)^2\right\}\\
-	P_{\gls{me}}^s=&\min\left\{1,1-\left(\frac{\sqrt{\lambda_{|G|}}-\sum_{i<|G|}\sqrt{\lambda_i}}{|G|}\right)^2\right\}.
+	P_{\gls{me}}^e &= \max\left\{ 0, \left( \frac{ \sqrt{\lambda_{|G|}} - \sum_{i<|G|} \sqrt{\lambda_i} }{|G|} \right)^2 \right\}, \\
+	P_{\gls{me}}^s &= \min\left\{ 1, 1 - \left( \frac{ \sqrt{\lambda_{|G|}} - \sum_{i<|G|} \sqrt{\lambda_i} }{|G|} \right)^2 \right\}.
 \end{align*}
-Additionally, the results for the zero error (\gls{ze}) protocol are,
+
+For the Zero Error protocol, the corresponding expressions arem
 \begin{align*}
-	P_{\gls{ze}}^e=&\max\left\{0,\frac{\sum_{i=1}^{|G|}\sqrt{\lambda_i}\left(\sqrt{\lambda_{|G|}}-\sum_{j<|G|}\sqrt{\lambda_j}\right)}{|G|}\right\}\\
-	P_{\gls{ze}}^s=&\min\left\{1,1-\frac{\sum_{i=1}^{|G|}\sqrt{\lambda_i}\left(\sqrt{\lambda_{|G|}}-\sum_{j<|G|}\sqrt{\lambda_j}\right)}{|G|}\right\}.
+	P_{\gls{ze}}^e &= \max\left\{ 0, \frac{ \sum_{i=1}^{|G|} \sqrt{\lambda_i} \left( \sqrt{\lambda_{|G|}} - \sum_{j<|G|} \sqrt{\lambda_j} \right) }{|G|} \right\}, \\
+	P_{\gls{ze}}^s &= \min\left\{ 1, 1 - \frac{ \sum_{i=1}^{|G|} \sqrt{\lambda_i} \left( \sqrt{\lambda_{|G|}} - \sum_{j<|G|} \sqrt{\lambda_j} \right) }{|G|} \right\}.
 \end{align*}
-For us is crucial to remark one of the results' traitmarks: the probabilities are independent of the group.
-In other words, given two group generated ensembles $A$ and $B$ for 2 differnt groups $G_A$ and $G_b$ ($G_A\neq G_B$) with the same cardinality, i.e.
-$|G_A|=|G_B|$, we know that if the respective Gram matrices $\mathcal{G}^{G_A}$ and $\mathcal{G}^{G_b}$ have the same eigenvalues, then the exclusion probability for both protocols \gls{me} and \gls{ze} is the same.
-This matter is one of the cornersotnes of this project study.
 
-Additionally we do also notice the exstence of some conditions where the exclusion can be performed with no error what so ever. This can be done if,
+A key feature of these results is their independence from the specific group generating the ensemble.
+That is, for any two group-generated ensembles $A$ and $B$ corresponding to groups $G_A$ and $G_B$ (with $G_A \neq G_B$ but $|G_A| = |G_B|$), if their respective Gram matrices $\mathcal{G}^{G_A}$ and $\mathcal{G}^{G_B}$ share the same eigenvalues, then the exclusion probabilities for both \gls{me} and \gls{ze} protocols are identical.
+This group-independence property is a cornerstone of the present study.
+
+Another important outcome from \cite{MainPaper} is the identification of conditions under which perfect exclusion is achievable, i.e., the exclusion can be carried out with zero error.
+This occurs if the eigenvalues satisfy the inequality,
+
 \begin{align}\label{equationPerfectExclusionCondition}
-	\lambda_{|G|}\leq \left(\sum_{i=1}^{|G|}\sqrt{\lambda_i}\right)^2.
+	\lambda_{|G|} \leq \left( \sum_{i=1}^{|G|} \sqrt{\lambda_i} \right)^2.
 \end{align}
-The regime corresponding to this conditions is denoted as the \emph{perfect exclusion zone}.
-In this project we will prove this results to be a lower bound for the exclusion success probability for the non group generated ensembles.
-However since the lower bound for the \emph{perfect exclusion zone} it is equal to 1\footnote{The exclusion can always be performed successfully in this context.}, then a perfect exclusion can be performed for a non group generated ensemble if it fulfils the perfect exclusion condition Eq.
-(\ref{equationPerfectExclusionCondition}).
-Subsequently, the perfect exclusion regime exists for a general ensemble and at least is comphended by those ensemble that fulfil Eq.
-(\ref{equationPerfectExclusionCondition}).
 
-\subsection{Ensembles with a prime number of elements}
+We refer to the regime satisfying this inequality as the \emph{perfect exclusion zone}.
+Within this regime, the success probability of the exclusion task reaches one, implying that exclusion can be performed perfectly.
 
-As we have discussed, analytical solutions have been found for the exclusion task in \gls{me} and \gls{ze} protocols.
-This solutions are independent from the intrinsc group of the ensemble and only depend on the eigenvalues of the Gram matrix.
+In this project, we will extend this result by demonstrating that the perfect exclusion condition Eq.
+(\ref{equationPerfectExclusionCondition}) provides a lower bound for the success probability of exclusion even for non-group-generated ensembles.
+Since this bound equals 1, it implies that any ensemble whether or not group-generated that satisfies condition Eq.
+(\ref{equationPerfectExclusionCondition}) can achieve perfect exclusion.
+Thus, the perfect exclusion zone is not exclusive to group-generated ensembles, but also includes all ensembles that fulfill the given condition.
 
-Hence if the Gram matrix for a general ensemble decomposes as,
-\begin{align}
-	\mathcal{G}= UDU^\dagger
-\end{align}
-where $U$ stands for an unitary matrix, and $D$ for a the eigenvalues diagonal matrix. Then, we are left with two options:
+\subsection{Limit Case Scenarios}\label{sectionLimitCaseScenarios}
+
+Let us study the Gram matrix of a limit ensemble composed of $n$ identical quantum states (i.e., the same state is repeated $n$ times in the ensemble).\footnote{This case may appear paradoxical, since there is no way to distinguish between identical states.
+Nevertheless, we present it as a limiting scenario.} The Gram matrix reads:
+\begin{align*}
+	\mathcal{G}^{\text{limit}} = \begin{pmatrix}
+ 1 & 1 & \cdots & 1 \\
+ 1 & 1 & \cdots & 1 \\
+ \vdots & \vdots & \ddots & \vdots \\
+ 1 & 1 & \cdots & 1 \\
+\end{pmatrix}.
+\end{align*}
+
+The eigenvalues of this matrix are:
+\begin{align*}
+	\lambda_n &= n, \\
+	\lambda_{n-1} &= 0, \\
+	\vdots \\
+	\lambda_1 &= 0.
+\end{align*}
+
+Clearly, this set of eigenvalues does not satisfy Eq.
+(\ref{equationPerfectExclusionCondition}), i.e., we are in the non-perfect exclusion regime.
+In fact, we can interpret this ensemble as a group-generated ensemble from the \emph{trivial group},\footnote{The trivial group is the group consisting solely of the neutral/identity element.} which generates no variation.
+
+Thus, the success and error probabilities for both the \gls{me} protocol is,
+\begin{align*}
+	P_{\gls{me}}^e =& \frac{1}{n},\\
+	P_{\gls{me}}^s =& \frac{n-1}{n}.
+\end{align*}
+
+The intuition behind this result is clear.
+If there is no physical way to distinguish between states, the exclusion must be made randomly, with uniform probability.
+This observation also extends naturally to \gls{qsd}.
+
+Since this is a limiting case scenario, the success probability for either \gls{qse} or \gls{qsd} must be strictly greater than $\frac{n-1}{n}$ (i.e., the error probability must be less than $\frac{1}{n}$).
+Notice this result holds only for the \gls{me} protocol.
+Otherwise, since the exclusion cannot be accomplished without ambiguity, the successfull exclusion probability for the \gls{ze} protocol is 0 for either \gls{qse} or \gls{qsd} (i.e., the error exclusion probability is 1),
+\begin{align*}
+	P_{\gls{ze}}^e =& 1,\\
+	P_{\gls{ze}}^s =& 0.
+\end{align*}
+
+The opposite limiting case is an ensemble of $n$ orthogonal quantum states $\{\rho_i\}_{i=1}^{n}$. In this case, the Gram matrix becomes the identity,
+\begin{align*}
+	\mathcal{G} = \mathds{1}.
+\end{align*}
+
+Under these conditions, both \gls{qse} and \gls{qsd} are trivial, as the states form an orthonormal basis. In particular, in the space spanned by these states, we have,
+\begin{align*}
+	\sum_{i=1}^{n} \rho_i = \mathds{1},
+\end{align*}
+which means that the set $\{\rho_i\}$ is itself a \gls{povm}.
+The measurement corresponding to this \gls{povm} allows perfect identification (or exclusion), hence both \gls{qse} and \gls{qsd} can be performed without error.
+
+\subsection{Ensembles with a Prime Number of Elements}\label{sectionEnsemblesWithPrime}
+
+As previously discussed, analytical solutions have been found for the exclusion task under both the \gls{me} and \gls{ze} protocols.
+These solutions depend solely on the eigenvalues of the Gram matrix and are independent of the specific group structure generating the ensemble.
+
+Let the Gram matrix of an ensemble decompose as,
+\begin{align*}
+	\mathcal{G} = U D U^\dagger,
+\end{align*}
+where $U$ is a unitary matrix and $D$ is the diagonal matrix of eigenvalues. We then encounter two possibilities,
 \begin{itemize}
-	\item We are in the perfect exclusion regime, i.e. the eigenvalues composing the $D$ matrix fulfil Eq.(\ref{equationPerfectExclusionCondition}).
-	\item We are not in the perfect exclusion regime, i.e. the eigenvalues composing the $D$ matrix do not fulfil Eq.(\ref{equationPerfectExclusionCondition}).
+	\item The eigenvalues satisfy Eq.~\eqref{equationPerfectExclusionCondition}, placing the ensemble in the \emph{perfect exclusion} regime.
+	\item The eigenvalues do not satisfy Eq.~\eqref{equationPerfectExclusionCondition}, placing the ensemble in the \emph{non-perfect exclusion} regime.
 \end{itemize}
-If we are in the perfect exclusion scenario we know we can find a set of \gls{povm}s that the outcome of the measurement allows us to exclude one hypothesis from the ensemble with no mistake.
 
-Otherwise we are in the non-perfect exclusion zone.
-In this regime the solution for group generated ensembles are lower bounds of the successfull exclusion probability in both protocols (i.e.
-upperbound of the error probability of exclusion).
+In the perfect exclusion regime, the existence of a \gls{povm}, such that the measurement outcome allows exclusion of a hypothesis without error, is guaranteed.
 
-Let us consider the 4 states ensemble case.
-In this scenario we know the result to be an exact solution for the groups $\mathbb{Z}/4\mathbb{Z}$ and $\mathbb{Z}/2\mathbb{Z}\times\mathbb{Z}/2\mathbb{Z}$\footnote{This are the only two groups of 4 elements.}.
-Then we know there are two unitary matrices  $U_{\mathbb{Z}/4\mathbb{Z}}$ and $U_{\mathbb{Z}/2\mathbb{Z}\times\mathbb{Z}/2\mathbb{Z}}$ (up to a flip of columns and/or rows) where the solution is exact.
-Since $U(n)$ is a Supposing contonuity on the solution and given a matix norm and its induced topology, there exists some neighbourhoods for each matrix $\mathcal{B}(U_{\mathbb{Z}/4\mathbb{Z}})$ and $B(U_{\mathbb{Z}/2\mathbb{Z}\times\mathbb{Z}/2\mathbb{Z}})$ arbitrarily small such that the success probabilities approaches the analytical solution as much as desired.
-However the existence of two unitary matrices that lead up to the same solution complicates the numerical analysis.
-As a matter of fact, given an ensemble of $n$ quantum states, there exist as many unitary matrices as number of groups of $n$ elements where the solution is exact.
+In the non-perfect exclusion regime, the analytical results for group-generated ensembles provide lower bounds on the success probabilities (and upper bounds on the error probabilities) for general ensembles.
 
-Nevertheless, if we consider the case of a prime number of states $n=p$ the task simplifies drastically since we know there only exists one group of $p$ elements and it is $\mathbb{Z}/p\mathbb{Z}$.
+Consider, for example, the case of an ensemble of 4 quantum states.
+There are exactly two groups of four elements: $\mathbb{Z}/4\mathbb{Z}$ and $\mathbb{Z}/2\mathbb{Z} \times \mathbb{Z}/2\mathbb{Z}$.\footnote{These are the only non-isomorphic groups of order 4.} This implies that there exist two specific unitary matrices, $U_{\mathbb{Z}/4\mathbb{Z}}$ and $U_{\mathbb{Z}/2\mathbb{Z} \times \mathbb{Z}/2\mathbb{Z}}$ (up to permutation of rows and columns), for which the analytical solution holds exactly.
 
-This result is inmediate from Lagrange's theoreme.
-The theoreme garanties the order of any element of the group\footnote{The order of an element $\tau$ that belongs to a group $G$ is the minimum natural number $m$ such that $\tau^m=e$ where $e$ stands for the neutral element of the group} must divide the order of the group.
-Since $p$ is prime the order of any element is either 1 or $p$, but if the order of an element is 1 this emplies it is the identity.
-Then every element different from the identity must of order $p$ for any group of $p$ elements i.e.
-the group is cyclic.
-Since the group must be a cyclic gorup of $p$ elements we are left with only one option, the group must be $\mathbb{Z}/p\mathbb{Z}$ up to ismorfism.
+Since $U(n)$ is compact, and assuming continuity of the exclusion probabilities with respect to $U$ under a given matrix norm, for each of these unitary matrices there exist arbitrarily small neighborhoods $\mathcal{B}(U_{\mathbb{Z}/4\mathbb{Z}})$ and $\mathcal{B}(U_{\mathbb{Z}/2\mathbb{Z} \times \mathbb{Z}/2\mathbb{Z}})$ such that the exclusion probabilities within these neighborhoods approximate the analytical result as closely as desired.
+However, the existence of multiple such matrices (and intersecting neighborhoods) can complicate numerical optimization and analysis.
 
-Therefore, for ensembles with a prime number of quantum states there only exists one unitary matrix $U$\footnote{Additionally we know the columns of this matrix are the elements of the Fourier's basis from the discussion in section Group Generated Ensembles (\ref{sectionGroupGeneratedEnsemble}) in the examble of $\mathbb{Z}/n\mathbb{Z}$ ensembles} that leads up to a Gram matrix where the given analytical results are exact.
+In contrast, it is usefull to consider the case where the ensemble contains a prime number $p$ of states.
+In this scenario, the situation simplifies considerably, since there exists only one group (up to isomorphism) of order $p$, namely $\mathbb{Z}/p\mathbb{Z}$.
 
+This result follows immediately from Lagrange's theorem.
+The theorem guarantees that the order of any element in a finite group\footnote{The order of an element $\tau$ in a group $G$ is the smallest positive integer $m$ such that $\tau^m = e$, where $e$ denotes the identity/neutral element of the group.} must divide the order of the group.
+Since $p$ is a prime number, the only positive integers dividing $p$ are either $1$ or $p$ itself.
+Therefore, the order of any group element must be either $1$ or $p$.
+An element of order $1$ must be the identity, so every non-identity element in the group must have order $p$.
+This implies that all non-identity elements generate the entire group, i.e., the group is cyclic.
+As a result, any group of prime order $p$ is necessarily cyclic and isomorphic to $\mathbb{Z}/p\mathbb{Z}$.
+
+Consequently, for an ensemble of $p$ quantum states, there exists a unique unitary matrix $U_{\mathbb{Z}/p\mathbb{Z}}$ (up to reordering) that diagonalizes the Gram matrix in such a way that the analytical results are exact.
+\footnote{Moreover, the columns of this matrix correspond to the elements of the Fourier basis, as discussed in Section~\ref{sectionGroupGeneratedEnsemble}, particularly in the example involving $\mathbb{Z}/n\mathbb{Z}$.}
+
+Ensembles of prime cardinality are thus of particular interest and will be further explored in the Results and Discussion section. \textcolor{blue}{Add reference to Results section}
 \section{Methodology}
-All the code is stored in the GitHub repository \cite{GitHub}.
-The workflow of the study has been the creation of the Mosek solver \cite{mosek_sdp} to numerically solve the \gls{sdp} using the PICOS python package\cite{PICOS}.
 
-\section{Results and discussion}
+All the code used in this project is hosted in the GitHub repository \cite{GitHub}, where additional documentation is available detailing the functionality and structure of each script and class involved in the implementation.
 
-For us, is particularly interesteing the case of a $\mathbb{Z}/3\mathbb{Z}$ ensemble since we know the Gram matrix to take the form of,
+\subsection{\gls{sdp} Solver}
+
+The core of the numerical analysis is the implementation of a Semi-Definite Programming (\gls{sdp}) solver based on the MOSEK optimization suite \cite{mosek_sdp}, interfaced through the Python-based PICOS optimization library \cite{PICOS}.
+
+\subsection{Generation of Random Gram Matrices}
+
+To analyze both group-generated and generic quantum state ensembles, we developed a method for generating random Gram matrices with prescribed spectral properties.
+
+A Numpy \gls{rng} produces a set of $n$ non-negative real numbers $\{\lambda_i\}_{i=1}^n$ that are normalized to satisfy the trace condition,
+\begin{align*}
+	\sum_{i=1}^n \lambda_i = n.
+\end{align*}
+These values are used as the eigenvalues of the Gram matrix, forming the diagonal matrix $D = \operatorname{diag}(\lambda_1, \dots, \lambda_n)$.
+
+Next, we generate a unitary matrix $U$ and construct the Gram matrix as,
+\begin{align*}
+	\mathcal{G} = U D U^\dagger.
+\end{align*}
+
+At this point, we choose whether the ensemble is to be group-generated or generic.
+
+For a generic ensemble, the unitary matrix $U$ is drawn randomly according to the Haar measure \cite{haarMeasure}, which defines the unique uniform probability measure on the unitary group $U(n)$ that is invariant under group multiplication.
+To ensure this uniformity, we use the algorithm introduced by Francesco Mezzadri in \cite{UnitaryMatricesGeneration}, which provides an efficient and accurate way of sampling unitary matrices while uniformly covering $U(n)$.
+
+In the case of a group-generated ensemble, we restrict ourselves to ensembles generated by the cyclic group $\mathbb{Z}/n\mathbb{Z}$.
+The corresponding unitary matrix $U$ is constructed such that its columns are the vectors of the discrete Fourier basis, as discussed in Section~\ref{sectionGroupGeneratedEnsemble} (\emph{Group-Generated Ensemble}).
+
+Other groups are omitted in our analysis since we can always choose $n$ to be a prime number, in which case the only group of order $n$ (up to isomorphism) is the cyclic group $\mathbb{Z}/n\mathbb{Z}$.
+This significantly simplifies the group structure and ensures that the only group-generated ensemble under consideration corresponds to a well-defined, unique construction.
+
+This methodology provides a flexible yet rigorous foundation for both exploring generic quantum ensembles and benchmarking them against analytically tractable group-generated cases.
+
+\section{Results and Discussion}
+
+Let us analyze the case of a $\mathbb{Z}/3\mathbb{Z}$ ensemble. The Gram matrix in this case takes the form,
 \begin{align*}
@@
 \end{align*}
-with $c\in\mathbb{C}$.
+with $c \in \mathbb{C}$.
+Note that, with respect to previous notation, we write $c = \braket{U}_{\psi}$, where $c$ and $c^*$ denote the overlap between different states.
+We can parametrize $c$ as $c = |c|e^{i\phi}$, and since we are analyzing normalized states,
+\begin{align*}
+	|c|\in [0,1], \quad \phi\in[0,2\pi]
+\end{align*}
+we observe two \gls{dof}.
+
+Since 3 is a prime number, the only group of order 3 is $\mathbb{Z}/3\mathbb{Z}$, as discussed in Section (\ref{sectionEnsemblesWithPrime}). The Gram matrix can be diagonalized as,
+\begin{align*}
+	\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}} = U_{\mathbb{Z}/3\mathbb{Z}} D U_{\mathbb{Z}/3\mathbb{Z}}^\dagger,
+\end{align*}
+where $U_{\mathbb{Z}/3\mathbb{Z}}$ is the unitary matrix with Fourier basis vectors as columns.
+The eigenvalues of the matrix are denoted as $\{\lambda_1,\lambda_2,\lambda_3\}$ with $\lambda_1 \leq \lambda_2 \leq \lambda_3$.
+Since,
+\begin{align*}
+	\tr(\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}) = \tr(D) = \sum_{i=1}^3 \lambda_i = 3
+\end{align*}
+we again find only two \glspl{dof}, consistent with our earlier parameterization. Furthermore, since $\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}} \geq 0$, we have,
+\begin{align*}
+	\lambda_i \geq 0 \quad \forall i \in \{1,2,3\},
+\end{align*}
+implying the eigenvalues must lie in the interval $[0,3]$.\footnote{In general, eigenvalues lie in $[0,n]$ for an $n$-dimensional ensemble, even for non-group-generated ensembles.} Therefore,
+\begin{align*}
+	\lambda_3 \in [0,3], \quad \lambda_2 \in [0,\lambda_3], \quad \lambda_1 = 3 - \lambda_2 - \lambda_3.
+\end{align*}
+
+This scenario is particularly interesting as it is the only ensemble with a small enough dimension to fully visualize all parameter dependencies and study the ensemble structure.\footnote{Visualizations include two parameters along with the success/exclusion probability of the respective protocol.} Higher-dimensional cases are too complex for full representation, while two-state cases reduce to standard quantum state discrimination (\gls{qsd}) as previously discussed.
+
+\subsection{Comparison \gls{qsd} vs. \gls{qse}, and \gls{me} vs. \gls{ze}}
+
+We first present results for the Quantum State Discrimination (\gls{qsd}) task to motivate the problem and highlight contrasts with the Quantum State Exclusion (\gls{qse}) task, which is the focus of this study.
+
+Figure (\ref{FigureQSDMEZ3ZHeatmap}) shows a heatmap of the average successful discrimination probability under the Minimum Error (\gls{me}) protocol for a $\mathbb{Z}/3\mathbb{Z}$ group-generated ensemble.
+Probabilities are shown as functions of the modulus ($x$-axis) and phase ($y$-axis) of the overlap $c$, which fully determine the Gram matrix.
+We assume equal prior probabilities, as generalization to arbitrary priors is discussed in Section (\ref{sectionGramMatrixFormulation}).
+Note, equal priors are presuposed throughout this work unless stated otherwise.
+
+The colorless regions correspond to parameters where $\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}$ is not positive semi-definite, and leading up yo non-valid Gram matrices, since positive semi-definition is inherent to a Gram matrix.
 
@@
 	\centering
-	\caption{Representation of the probability of successfull discrimination for a $\mathbb{Z}/3\mathbb{Z}$ group generated ensemble with minimum error (\gls{me}) protocol.}
-	\includegraphics[width=0.5\textwidth, trim={3.3cm 0.8cm 4.5cm 2cm}, clip]{../Plots/DiscriminationOverlapVSPhaseVSMinimumErrorProbabilityZ3HeatMap.pdf}
+	\label{FigureQSDMEZ3ZHeatmap}
+	\begin{overpic}[width=0.5\textwidth, trim={2.3cm 0.8cm 4.5cm 2cm}, clip]{../Plots/DiscriminationOverlapVSPhaseVSMinimumErrorProbabilityZ3HeatMap.pdf}
+		\put(60,25){$G<0$}
+		\put(60,55){$G<0$}
+	\end{overpic}
+	\caption{Heatmap of the success probability for minimum error (\gls{me}) quantum state discrimination for a $\mathbb{Z}/3\mathbb{Z}$ group-generated ensemble.}
 \end{figure}
+
+In these conditions, the \gls{srm}\footnote{Also known as the Pretty Good Measurement.} is optimal, i.e.
+the result of the \gls{sdp} matches the one obtained from the \gls{srm}.
+In particular, the \gls{srm} is obtained from the square root decomposition of the Gram matrix,
+\begin{align*}
+	\mathcal{G} = S^\dagger S = S^2
+\end{align*}
+and is the standard in \gls{qsd} under the \gls{me} protocol \cite{OptimalitySRM}.
+
+As expected, no ensemble yields a success probability below $1/3$, consistent with the discussion in Section (\ref{sectionLimitCaseScenarios}).
+Moreover, as the modulus of the overlap approaches zero, the success probability approaches one, corresponding to orthogonal states, again matching expectations.
+
+Figure (\ref{FigureQSDZEZ3ZHeatmap}) shows results for the Zero Error (\gls{ze}) protocol under the same conditions.
+
+\begin{figure}[H]
+	\centering
+	\label{FigureQSDZEZ3ZHeatmap}
+	\begin{overpic}[width=0.5\textwidth, trim={2.3cm 0.8cm 4.5cm 2cm}, clip]{../Plots/DiscriminationOverlapVSPhaseVSSuccessProbabilityZeroErrorZ3HeatMap.pdf}
+		\put(60,25){$G<0$}
+		\put(60,55){$G<0$}
+	\end{overpic}
+	\caption{Heatmap of the success probability for zero-error (\gls{ze}) quantum state discrimination for a $\mathbb{Z}/3\mathbb{Z}$ group-generated ensemble.}
+\end{figure}
+
+Both limiting behaviors remain valid.
+However, the \gls{ze} success probabilities are lower than those of the \gls{me} protocol.
+This is explained by the stricter constraints imposed in the \gls{ze} scenario, where $\tr(\Pi_i\rho_i) = 0$ is enforced for all POVM elements except one.
+Notice both probabilities are computed in a completely symmetric way,
+\begin{align*}
+	P^s_{\gls{me}}\sim P^s_{\gls{ze}}\sim 1-\sum_{\gls{povm}}\tr{(\Pi_i\rho_i)}.
+\end{align*}
+
+Nevertheless, in the \gls{ze} case we enforce $\tr{(\Pi_i\rho_i)}=0$ for all the \glspl{povm} except one.
+Thus, the system is more constrained in the \gls{ze} protocol, then the optimization of the probability cannot be performed up to the same point as in the \gls{me} protocol.
+Hence, the success probabilities for \gls{me} are greater than the ones obtained with the \gls{ze} protocol.
+
+Figure (\ref{FigureQSDMEZESRM}) compares the performance of the ME, ZE, and SRM protocols.
+
+\begin{figure}[H]
+	\centering
+	\label{FigureQSDMEZESRM}
+	\includegraphics[width=0.5\textwidth]{../Plots/DiscriminationOverlapVSSucessProbabilitySDPvsSRMZnOverlap3Phase0.pdf}
+	\caption{Comparison of successful discrimination probabilities for ME, ZE, and SRM protocols in a $\mathbb{Z}/3\mathbb{Z}$ ensemble.}
+\end{figure}
+
+As expected, perfect discrimination is only achieved when the overlap is zero (orthogonal states), and the \gls{srm} success probability matches the one obtained from the numerical \gls{sdp}.
+This highlights the motivation behind the study of \gls{qse}, which allows for perfect exclusion in cases where discrimination is impossible.
+
+Figure (\ref{FigureQSEMEZ3ZHeatmap}) presents the ME protocol results for the \gls{qse} task, analogous to Figure (\ref{FigureQSDMEZ3ZHeatmap}).
+
+\begin{figure}[H]
+	\centering
+	\label{FigureQSEMEZ3ZHeatmap}
+	\begin{overpic}[width=0.5\textwidth, trim={2.3cm 0.8cm 4.5cm 2cm}, clip]{../Plots/ExlusionOverlapVSPhaseVSMinimumErrorProbabilityZ3HeatMap.pdf}
+		\put(60,25){$G<0$}
+		\put(60,55){$G<0$}
+	\end{overpic}
+	\caption{Heatmap of the success probability for minimum error (\gls{me}) quantum state exclusion in a $\mathbb{Z}/3\mathbb{Z}$ ensemble.}
+\end{figure}
+
+The ZE protocol for \gls{qse} is shown in Figure (\ref{FigureQSEZEZ3ZHeatmap}).
+
+\begin{figure}[H]
+	\centering
+	\label{FigureQSEZEZ3ZHeatmap}
+	\begin{overpic}[width=0.5\textwidth, trim={2.3cm 0.8cm 4.5cm 2cm}, clip]{../Plots/ExlusionOverlapVSPhaseVSZeroErrorProbabilityZ3HeatMap.pdf}
+		\put(60,25){$G<0$}
+		\put(60,55){$G<0$}
+	\end{overpic}
+	\caption{Heatmap of the success probability for zero-error (\gls{ze}) quantum state exclusion in a $\mathbb{Z}/3\mathbb{Z}$ ensemble.}
+\end{figure}
+
+Again, the ZE protocol yields lower probabilities due to its constraints and the limit case scenarios match with the previos discussion in Section (\ref{sectionLimitCaseScenarios}).
+However, crucially, perfect exclusion is possible even when perfect discrimination is not.
+Figure (\ref{FigureQSEMEZ3ZPerfectExclusion}) highlights the regions where perfect exclusion is achieved, even outside the perfect discrimination regime.
+
+\begin{figure}[H]
+	\centering
+	\label{FigureQSEMEZ3ZPerfectExclusion}
+	\begin{overpic}[width=0.5\textwidth, trim={2.3cm 0.8cm 2.5cm 2cm}, clip]{../Plots/ExlusionOverlapVSPhaseVSPerfectExclussionZoneZ3BinaryHeatMap.pdf}
+		\put(60,25){$G<0$}
+		\put(60,60){$G<0$}
+	\end{overpic}
+	\caption{Perfect exclusion zone for a $\mathbb{Z}/3\mathbb{Z}$ ensemble under the minimum error (\gls{me}) protocol.}
+\end{figure}
+
+This property of \gls{qse} is a major motivation for its study.
+For example, in a regime where perfect exclusion is possible, having access to multiple copies of a target state enables hybrid exclusion-discrimination protocols that can outperform purely discriminative strategies.
+Even partial information, such as the exclusion of a single quantum state, has value in certain quantum information theories.
+These features make \gls{qse} a fertile ground for further theoretical and applied research.
 

### 2025-04-17 Scripts/PlotExclusionZeroError.py

@@ -1,0 +1,48 @@
+import QSExSetUp
+import numpy as np
+import matplotlib.pyplot as plt
+from mpl_toolkits.mplot3d import Axes3D
+from tqdm import tqdm
+
+NumberOfMatrices              = 3
+MatrixDimension               = 3
+MatrixGenerationMethod        = "ZnEigenValues"
+ProbabliltiesGenerationMethod = "Equal"
+IterationsPerfectExclusion    = 50000
+DataPerfectExlusionProbability= []
+DataPerfectExlusionZone       = []
+
+for iIteration in tqdm(range(IterationsPerfectExclusion),"Computing plots for the perfect exclusion zone"):
+    EigenValues                   = np.random.rand(NumberOfMatrices)
+    EigenValuesNormalized         = [iEigenValue*NumberOfMatrices/sum(EigenValues) for iEigenValue in EigenValues]
+    Conditions                    = QSExSetUp.GramGeneratedStates.GramGeneratedStatesClass(NumberOfMatrices,MatrixDimension,MatrixGenerationMethod, QSExSetUp.GramGeneratedStates.ZnGramMatrixConditionsEigenValues(EigenValuesNormalized, NumberOfMatrices), ProbabilitiesContructionMethod = ProbabliltiesGenerationMethod)
+    Overlap,Phase                 = Conditions.getOverlapsAndPhases()
+    DataPerfectExlusionProbability.append((Overlap[1],Phase[1],Conditions.getPerfectExlusionLowerBoundZeroError()))
+    DataPerfectExlusionZone.append((Overlap[1],Phase[1],int(Conditions.getPerfectExlusion())))
+
+Overlap_values, Phase_values, SuccessProb_values = zip(*DataPerfectExlusionProbability)
+
+fig = plt.figure(figsize=(10, 7))
+ax = fig.add_subplot(111, projection='3d')
+
+sc = ax.scatter(Overlap_values, Phase_values, SuccessProb_values, c=SuccessProb_values, cmap='jet')
+
+ax.set_xlabel("Overlap")
+ax.set_ylabel("Phase (radians)")
+ax.set_zlabel("Exclusion probability")
+# ax.set_title(f"Overlap vs. Phase vs. Probability of excluding correctly with minimum error procedure for Z{NumberOfMatrices} group generated ensambles")
[…]

### 2025-04-18 Manuscript/Manuscript.tex
writting

@@
 \vspace*{\fill} 
+\newpage
+\thispagestyle{empty}
+\mbox{} 
 \newpage
@@
 
-A Numpy \gls{rng} produces a set of $n$ non-negative real numbers $\{\lambda_i\}_{i=1}^n$ that are normalized to satisfy the trace condition,
+A Numpy \gls{rng}\cite{numpyRNG} produces a set of $n$ non-negative real numbers $\{\lambda_i\}_{i=1}^n$ that are normalized to satisfy the trace condition,
 \begin{align*}
@@
 	\begin{overpic}[width=0.5\textwidth, trim={2.3cm 0.8cm 4.5cm 2cm}, clip]{../Plots/DiscriminationOverlapVSPhaseVSMinimumErrorProbabilityZ3HeatMap.pdf}
-		\put(60,25){$G<0$}
-		\put(60,55){$G<0$}
+		\put(60,25){$\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}<0$}
+		\put(60,55){$\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}<0$}
 	\end{overpic}
@@
 	\begin{overpic}[width=0.5\textwidth, trim={2.3cm 0.8cm 4.5cm 2cm}, clip]{../Plots/DiscriminationOverlapVSPhaseVSSuccessProbabilityZeroErrorZ3HeatMap.pdf}
-		\put(60,25){$G<0$}
-		\put(60,55){$G<0$}
+		\put(60,25){$\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}<0$}
+		\put(60,55){$\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}<0$}
 	\end{overpic}
@@
 	\includegraphics[width=0.5\textwidth]{../Plots/DiscriminationOverlapVSSucessProbabilitySDPvsSRMZnOverlap3Phase0.pdf}
-	\caption{Comparison of successful discrimination probabilities for ME, ZE, and SRM protocols in a $\mathbb{Z}/3\mathbb{Z}$ ensemble.}
+	\caption{Comparison of successful discrimination probabilities for ME, ZE, and SRM protocols in a $\mathbb{Z}/3\mathbb{Z}$ ensemble impossing phase=$0$.}
 \end{figure}
@@
 
-Figure (\ref{FigureQSEMEZ3ZHeatmap}) presents the ME protocol results for the \gls{qse} task, analogous to Figure (\ref{FigureQSDMEZ3ZHeatmap}).
-
 \begin{figure}[H]
@@
 	\begin{overpic}[width=0.5\textwidth, trim={2.3cm 0.8cm 4.5cm 2cm}, clip]{../Plots/ExlusionOverlapVSPhaseVSMinimumErrorProbabilityZ3HeatMap.pdf}
-		\put(60,25){$G<0$}
-		\put(60,55){$G<0$}
+		\put(60,25){$\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}<0$}
+		\put(60,55){$\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}<0$}
 	\end{overpic}
@@
 \end{figure}
+
+Figure (\ref{FigureQSEMEZ3ZHeatmap}) presents the ME protocol results for the \gls{qse} task, analogous to Figure (\ref{FigureQSDMEZ3ZHeatmap}).
 
@@
 	\begin{overpic}[width=0.5\textwidth, trim={2.3cm 0.8cm 4.5cm 2cm}, clip]{../Plots/ExlusionOverlapVSPhaseVSZeroErrorProbabilityZ3HeatMap.pdf}
-		\put(60,25){$G<0$}
-		\put(60,55){$G<0$}
+		\put(60,25){$\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}<0$}
+		\put(60,55){$\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}<0$}
 	\end{overpic}
@@
 \end{figure}
-
-Again, the ZE protocol yields lower probabilities due to its constraints and the limit case scenarios match with the previos discussion in Section (\ref{sectionLimitCaseScenarios}).
-However, crucially, perfect exclusion is possible even when perfect discrimination is not.
-Figure (\ref{FigureQSEMEZ3ZPerfectExclusion}) highlights the regions where perfect exclusion is achieved, even outside the perfect discrimination regime.
 
@@
 	\begin{overpic}[width=0.5\textwidth, trim={2.3cm 0.8cm 2.5cm 2cm}, clip]{../Plots/ExlusionOverlapVSPhaseVSPerfectExclussionZoneZ3BinaryHeatMap.pdf}
-		\put(60,25){$G<0$}
-		\put(60,60){$G<0$}
+		\put(70,27){$\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}<0$}
+		\put(70,60){$\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}<0$}
 	\end{overpic}
@@
 \end{figure}
+
+Again, the ZE protocol yields lower probabilities due to its constraints and the limit case scenarios match with the previos discussion in Section (\ref{sectionLimitCaseScenarios}).
+However, crucially, perfect exclusion is possible even when perfect discrimination is not, in this regime seems to correspond to the ensembles such that the modulus of the overlap between two ensembles do not overtakes $\frac{1}{2}$.
+Nevertheless, this description is purely observational, we will give a better description in Section (\ref{sectionPerfectExclusionRegimeAndGeneralEnsembles}).
+Notice Figure (\ref{FigureQSEMEZ3ZPerfectExclusion}) highlights the regions where perfect exclusion is achieved, even outside the perfect discrimination regime.
 
@@
 These features make \gls{qse} a fertile ground for further theoretical and applied research.
+
+\subsection{The perfect exclusion regime and general ensembles}\label{sectionPerfectExclusionRegimeAndGeneralEnsembles}
+
+Although the $Overlap modulus - phase$ spectrum might seem as the most intuituve representation, the spectrum of Gram's matrix eigenvalues results the most appropriate representation for the perfect exclusion zone as well as the discussion and its comparison for general ensembles.
+Carrying on with the previos discussion, one can check the two \gls{dof} now appear as two of the eigenvalues.
+In the Figure (\ref{FigureQSEMEZ3ZEigenValues}) the results for the exclusion task under the \gls{me} protocol for the $\mathbb{Z}/3\mathbb{Z}$ group-generated ensemble are represented.
+The axis represent two of the eigenvalues of the Gram matrix and a heatmap presents the probability for a perfect exclusion in the given conditions.
+
+\begin{figure}[H]
+	\centering
+	\label{FigureQSEMEZ3ZEigenValues}
+	\begin{overpic}[width=0.5\textwidth, trim={2.3cm 0.8cm 4.4cm 2cm}, clip]{../Plots/ExclusionEignevaluesGroupGeneratedLowerBoundZ3.pdf}
+		\put(20,25){\footnotesize{Perfect exclusion}}
+		\put(50,50){$\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}<0$}
+	\end{overpic}
+	\caption{Plot of the success exclusion probability in the eigenvalues spectrum for the \gls{me} protocol for a $\mathbb{Z}/3\mathbb{Z}$ group-generated ensemble.}
+\end{figure}
+
+The order in eigenvalues is obviated in the representation, i.e. we can find conditions such that $\lambda_i>\lambda_j$ and others conditions such that $\lambda_i<\lambda_j$ for $i,j\in\{1,2,3\}$
+
+Notice the missing eigenvalue is determined by the other two via,
+\begin{align*}
+	\lambda_3=3-\lambda_1-\lambda_2.
+\end{align*}
+Since the Gram matrix is a positive semidefinite matrix we know that $\lambda_3\geq0$, the limit case scenario $\lambda_3=0$ defines the line,
+\begin{align*}
+\lambda_2=3-\lambda_1,
+\end{align*}
+that constraints the possible eigenvalues to only reach values under this line.
+Otherwise the remaining value would be negative leading up to non-valid Gram matrices as discussed in the previos plots.
+Naturally, we also know $\lambda_1,\lambda_2>0$, then the region $\Omega$ where the system leads up to consistent Gram matrices is,
+\begin{align*}
+	\Omega=\left\{(\lambda_1,\lambda_2)\in\mathbb{R}^2\left|\lambda_1\geq0,\lambda_2\geq0,\lambda_1+\lambda_2\leq3\right.\right\}.
+\end{align*}
+This region $\Omega$ is depicted in the Figure (\ref{FigureQSEMEZ3ZEigenValues}) as boottom left triangle, where our system is recluded.
+Inside this region we can find the perfect exclusion zone, i.e.
+the eigenvalues such that Eq.(\ref{equationPerfectExclusionCondition}) is fulfilled.
+In particular,if we set $\lambda_i$ with $i\in\{1,2,3\}$ to be the greatest eigenvalues and denote $\lambda_j,\lambda_k$ as the remaining 2 eigenvalues, we know perfect exclusion to be archived if,
+\begin{align*}
+	\sqrt{\lambda_i}\leq \sqrt{\lambda_j}+\sqrt{\lambda_k}.
+\end{align*}
+With a little bit of algebra and recalling that $\lambda_3=3-\lambda_1-\lambda_2$ we can derive the regime of perfect exclusion denoted as $\Delta$ comprehends the eigenvalues such that,
+\begin{align*}
+	(\lambda_1,\lambda_2&)\in \Delta\\
+	\Updownarrow& \\
+	4\lambda_1^2 + 4\lambda_2^2 + 4\lambda_1\lambda_2 - &12\lambda_1 - 12\lambda_i + 9 \leq 0
+\end{align*}
+Figure (\ref{FigurePerfectExclusionZ3Z}) shows the $\Delta$ region. It is inmediate that this region corresponds to the colorless perfect exclusion regime in Figure (\ref{FigureQSEMEZ3ZEigenValues}).
+\begin{figure}[H]
+	\centering
+	\label{FigurePerfectExclusionZ3Z}
+	\begin{overpic}[width=0.5\textwidth, trim={1.8cm 0.8cm 2cm 2cm}, clip]{GeneralSources/PerfectExclusionZoneZ3Z.pdf}
+	\end{overpic}
+	\caption{Plot of the $\Delta$ region.}
+\end{figure}
+
+Naturally we can prove the perfect exclusion zone to be a subset of valid Gram matrixes i.e. $\Delta\subset \Omega$.Then the non-perfect exclusion regime is the remaining part of the triangle i.e.,
+\begin{align*}
+	\text{Non-perfect exclusion regime}=\Omega\setminus \Delta.
+\end{align*}
+The limit case scenarios corresponding to $\lambda_i=3$ and $\lambda_j,\lambda_k=0$ are situated in the vertex of the triangle\footnote{Remember this case correspond to sets with the same state repeated 3 times discussed in Section (\ref{sectionLimitCaseScenarios})}.
+Then the cases corresponding to the edges are those with one state repeated 2 times and one different from the other 2.
+This ensembles can also be underestood as a limit case scenario systems.
+
+In practice this scenario is entirely equivalent to a 2 quantum states exclusion (\gls{qse}) system.
+Nevertheless we know this to be equivalent to a 2 quantum states discrimination system (\gls{qsd}), therefore perfect discrimination/exclusion cannot be archived unless the states are orthogonal.
+This last case corresponds to the intersection of the elipse $\Delta$ with the triangles edges, this can be described as the ensembles with associated Gram matrices whose eigenvalues $\lambda_i,\lambda_j,\lambda_k$ are,
+\begin{align*}
+	\lambda_i=&\lambda_j=\frac{3}{2}\\
+	\lambda_k=&0.
+\end{align*}
+
+Additionally, we observe that no ensembles seem to have a lower exclusion success probability $P_{\gls{me}}^s$ under $\frac{1}{3}$ as expected from the discussion in Section (\ref{sectionLimitCaseScenarios}).
+
+Hence the results for the \gls{ze} protocol in \gls{qse} for a $\mathbb{Z}/3\mathbb{Z}$ ensemble are presented in Figure (\ref{FigureQSEZEZ3ZEigenValues}).
+
+\begin{figure}[H]
+	\centering
+	\label{FigureQSEZEZ3ZEigenValues}
+	\begin{overpic}[width=0.5\textwidth, trim={2.3cm 0.8cm 4.4cm 2cm}, clip]{../Plots/ExclusionEignevaluesGroupGeneratedLowerBoundZ3ZeroError.pdf}
+		\put(20,25){\footnotesize{Perfect exclusion}}
+		\put(50,50){$\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}<0$}
+	\end{overpic}
+	\caption{Plot of the success exclusion probability in the eigenvalues spectrum for the \gls{ze} protocol for a $\mathbb{Z}/3\mathbb{Z}$ group-generated ensemble.}
+\end{figure}
+
+The result is consistent with all the previos observations and we can also observe the worst case scenario to tend to a 0 successfull exclusion probability as expected.
+Also, the probabilities remain with lower values than the ones obtained with the Minimum Error (\gls{me}) protocol.
+
+Hence, we present the result for randomly generated ensembles in Figure (\ref{FigureQSEMEGenericEigenValues}).
+
+\begin{figure}[H]
+	\centering
+	\label{FigureQSEMEGenericEigenValues}
+	\begin{overpic}[width=0.5\textwidth, trim={2.3cm 0.8cm 4.4cm 2cm}, clip]{../Plots/ExclusionEignevalueRandom3.pdf}
+		\put(20,25){\footnotesize{Perfect exclusion}}
+		\put(50,50){$\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}<0$}
+	\end{overpic}
+	\caption{Plot of the success exclusion probability in the eigenvalues spectrum for the \gls{me} protocol for a generic ensemble.}
+\end{figure}
+
+A remarcable feature is that each ensemble has been checked to not have a successfull exclusion probability that overtakes the value from the $\mathbb{Z}/3\mathbb{Z}$ group-generated ensemble pointing this value to be this a lower bound for the general case scenario.
 

### 2025-04-18 Manuscript/GeneralSources/PerfectExclussionZonePlot.py

@@ -1,0 +1,29 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib.patches as mpatches
+
+# Define the function
+def f(x, y):
+    return 4*x**2+4*y**2+4*x*y-12*x-12*y+9
+# Create a grid of x and y values
+x = np.linspace(-10, 10, 400)
+y = np.linspace(-10, 10, 400)
+X, Y = np.meshgrid(x, y)
+
+# Evaluate the function on the grid
+Z = f(X, Y)
+
+# Plot the implicit curve f(x, y) = 0
+plt.figure(figsize = (10, 7))
+plt.contourf(X, Y, Z, levels=[-1000, 0], colors="aqua")
+plt.contour(X, Y, Z, levels=[0], colors="turquoise")
+plt.axhline(0, color='black', linewidth=0.5)
+plt.axvline(0, color='black', linewidth=0.5)
+plt.xlabel('$\lambda_1$')
+plt.ylabel('$\lambda_2$')
+plt.xlim(0, 3)
+plt.ylim(0, 3)
+filled_region = mpatches.Patch(color='aqua', label=r'$\Delta$')
+plt.legend(handles=[filled_region], loc='upper right')
+plt.show()
+plt.savefig("PerfectExclusionZoneZ3Z.pdf")

### 2025-04-18 Scripts/PlotExclusionRandomEigenValues.py

@@ -24,6 +24,7 @@ EigenValue0                   = []
 EigenValue1                   = []
 SDPMinimumErrorList           = []
 LowerBound                    = []
+LowerBoundZE                  = []
 
 for iIteration in tqdm(range(IterationsRandomSets),"Computing points for the Minimum Error plot"):
     EigenValues             = np.random.rand(NumberOfMatrices)
@@ -36,30 +37,41 @@ for iIteration in tqdm(range(IterationsRandomSets),"Computing points for the Min
     EigenValue1.append(EigenValuesNormalized[1])
     SDPMinimumErrorList.append(SDPMinimumError)
     LowerBound.append(Conditions.getPerfectExlusionLowerBoundMinimumError())
+    LowerBoundZE.append(Conditions.getPerfectExlusionLowerBoundZeroError())
     DataMinimumError.append((EigenValuesNormalized[0],EigenValuesNormalized[1],SDPMinimumError,Conditions.getPerfectExlusionLowerBoundMinimumError()))
 
 fig, ax = plt.subplots(figsize=(12, 7))
 sc = ax.scatter(EigenValue0, EigenValue1, c=LowerBound, cmap='jet', s=50)
 plt.colorbar(sc, ax=ax, label="Exclusion probability")
 
-ax.set_xlabel("$\lambda_0$")
-ax.set_ylabel("$\lambda_1$")
+ax.set_xlabel("$\lambda_1$")
+ax.set_ylabel("$\lambda_2$")
 
 plt.savefig(f"../Plots/ExclusionEignevaluesGroupGeneratedLowerBoundZ{NumberOfMatrices}.pdf")
+plt.close()
+
+fig, ax = plt.subplots(figsize=(12, 7))
+sc = ax.scatter(EigenValue0, EigenValue1, c=LowerBoundZE, cmap='jet', s=50)
+plt.colorbar(sc, ax=ax, label="Exclusion probability")
+
+ax.set_xlabel("$\lambda_1$")
+ax.set_ylabel("$\lambda_2$")
+
+plt.savefig(f"../Plots/ExclusionEignevaluesGroupGeneratedLowerBoundZ{NumberOfMatrices}ZeroError.pdf")
 plt.close()
 
 fig, ax = plt.subplots(figsize=(12, 7))
 sc = ax.scatter(EigenValue0, EigenValue1, c=SDPMinimumErrorList, cmap='jet', s=50)
[…]

### 2025-04-20 Manuscript/Manuscript.tex
writting

@@
 
-Since this is a limiting case scenario, the success probability for either \gls{qse} or \gls{qsd} must be strictly greater than $\frac{n-1}{n}$ (i.e., the error probability must be less than $\frac{1}{n}$).
+Since this is a limiting case scenario, the success probability for \gls{qse} must be strictly greater than $\frac{n-1}{n}$ (i.e., the error probability must be less than $\frac{1}{n}$) and for \gls{qsd} the success probabilities must be strictly greater than $\frac{1}{n}$ (i.e., the error probability must be less than $\frac{n-1}{n}$)\footnote{In this case scenario the discrimination task is the counterpart of the exclusion task.}.
 Notice this result holds only for the \gls{me} protocol.
@@
 
+\begin{figure}[H]
+	\centering
+	\begin{overpic}[width=0.5\textwidth, trim={2.3cm 0.8cm 4.5cm 2cm}, clip]{../Plots/DiscriminationOverlapVSPhaseVSMinimumErrorProbabilityZ3HeatMap.pdf}
+		\put(60,25){$\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}<0$}
+		\put(60,55){$\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}<0$}
+	\end{overpic}
+	\caption{Heatmap of the success probability for minimum error (\gls{me}) quantum state discrimination for a $\mathbb{Z}/3\mathbb{Z}$ group-generated ensemble.}
+	\label{FigureQSDMEZ3ZHeatmap}
+\end{figure}
+
 Figure (\ref{FigureQSDMEZ3ZHeatmap}) shows a heatmap of the average successful discrimination probability under the Minimum Error (\gls{me}) protocol for a $\mathbb{Z}/3\mathbb{Z}$ group-generated ensemble.
@@
 
-\begin{figure}[H]
-	\centering
-	\label{FigureQSDMEZ3ZHeatmap}
-	\begin{overpic}[width=0.5\textwidth, trim={2.3cm 0.8cm 4.5cm 2cm}, clip]{../Plots/DiscriminationOverlapVSPhaseVSMinimumErrorProbabilityZ3HeatMap.pdf}
-		\put(60,25){$\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}<0$}
-		\put(60,55){$\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}<0$}
-	\end{overpic}
-	\caption{Heatmap of the success probability for minimum error (\gls{me}) quantum state discrimination for a $\mathbb{Z}/3\mathbb{Z}$ group-generated ensemble.}
-\end{figure}
-
 In these conditions, the \gls{srm}\footnote{Also known as the Pretty Good Measurement.} is optimal, i.e.
-the result of the \gls{sdp} matches the one obtained from the \gls{srm}.
+the result of the \gls{sdp} matches the one obtained from the \gls{sdp} in \gls{me} protocol.
 In particular, the \gls{srm} is obtained from the square root decomposition of the Gram matrix,
@@
 and is the standard in \gls{qsd} under the \gls{me} protocol \cite{OptimalitySRM}.
+From section (\ref{sectionGramMatrixFormulation}) we know the success probability for a successful discrimination with \gls{srm} reeds,
+\begin{align*}
+	P_{\gls{srm}}^s=\frac{1}{n}\sum_{i=0}^nS_{i,i}^2
+\end{align*}
+were $S_{i,i}$ denotes the diagonal elements of $S$ and $n$ the number of quantum states\footnote{In this case we are taking $n=3$.}.
 
@@
 
-Figure (\ref{FigureQSDZEZ3ZHeatmap}) shows results for the Zero Error (\gls{ze}) protocol under the same conditions.
+Figure (\ref{FigureQSDZEZ3ZHeatmap}) shows analogous results for the Zero Error (\gls{ze}) protocol under the same conditions.
 
@@
 	\centering
-	\label{FigureQSDZEZ3ZHeatmap}
 	\begin{overpic}[width=0.5\textwidth, trim={2.3cm 0.8cm 4.5cm 2cm}, clip]{../Plots/DiscriminationOverlapVSPhaseVSSuccessProbabilityZeroErrorZ3HeatMap.pdf}
@@
 	\caption{Heatmap of the success probability for zero-error (\gls{ze}) quantum state discrimination for a $\mathbb{Z}/3\mathbb{Z}$ group-generated ensemble.}
+	\label{FigureQSDZEZ3ZHeatmap}
 \end{figure}
@@
 	\centering
-	\label{FigureQSDMEZESRM}
 	\includegraphics[width=0.5\textwidth]{../Plots/DiscriminationOverlapVSSucessProbabilitySDPvsSRMZnOverlap3Phase0.pdf}
 	\caption{Comparison of successful discrimination probabilities for ME, ZE, and SRM protocols in a $\mathbb{Z}/3\mathbb{Z}$ ensemble impossing phase=$0$.}
+	\label{FigureQSDMEZESRM}
 \end{figure}
@@
 
+Figure (\ref{FigureQSEMEZ3ZHeatmap}) presents the ME protocol results for the \gls{qse} task, analogous to Figure (\ref{FigureQSDMEZ3ZHeatmap}).
+Furthermore the results of the ZE protocol for \gls{qse} are shown in Figure (\ref{FigureQSEZEZ3ZHeatmap}).
+
 \begin{figure}[H]
 	\centering
-	\label{FigureQSEMEZ3ZHeatmap}
 	\begin{overpic}[width=0.5\textwidth, trim={2.3cm 0.8cm 4.5cm 2cm}, clip]{../Plots/ExlusionOverlapVSPhaseVSMinimumErrorProbabilityZ3HeatMap.pdf}
@@
 	\caption{Heatmap of the success probability for minimum error (\gls{me}) quantum state exclusion in a $\mathbb{Z}/3\mathbb{Z}$ ensemble.}
+	\label{FigureQSEMEZ3ZHeatmap}
 \end{figure}
-
-Figure (\ref{FigureQSEMEZ3ZHeatmap}) presents the ME protocol results for the \gls{qse} task, analogous to Figure (\ref{FigureQSDMEZ3ZHeatmap}).
-
-The ZE protocol for \gls{qse} is shown in Figure (\ref{FigureQSEZEZ3ZHeatmap}).
 
@@
 	\centering
-	\label{FigureQSEZEZ3ZHeatmap}
 	\begin{overpic}[width=0.5\textwidth, trim={2.3cm 0.8cm 4.5cm 2cm}, clip]{../Plots/ExlusionOverlapVSPhaseVSZeroErrorProbabilityZ3HeatMap.pdf}
@@
 	\caption{Heatmap of the success probability for zero-error (\gls{ze}) quantum state exclusion in a $\mathbb{Z}/3\mathbb{Z}$ ensemble.}
+	\label{FigureQSEZEZ3ZHeatmap}
 \end{figure}
@@
 	\centering
-	\label{FigureQSEMEZ3ZPerfectExclusion}
 	\begin{overpic}[width=0.5\textwidth, trim={2.3cm 0.8cm 2.5cm 2cm}, clip]{../Plots/ExlusionOverlapVSPhaseVSPerfectExclussionZoneZ3BinaryHeatMap.pdf}
@@
 	\end{overpic}
-	\caption{Perfect exclusion zone for a $\mathbb{Z}/3\mathbb{Z}$ ensemble under the minimum error (\gls{me}) protocol.}
+	\caption{Perfect exclusion zone for a $\mathbb{Z}/3\mathbb{Z}$ ensemble in terms of the overlap's modulus and phase.}
+	\label{FigureQSEMEZ3ZPerfectExclusion}
 \end{figure}
@@
 Nevertheless, this description is purely observational, we will give a better description in Section (\ref{sectionPerfectExclusionRegimeAndGeneralEnsembles}).
+
 Notice Figure (\ref{FigureQSEMEZ3ZPerfectExclusion}) highlights the regions where perfect exclusion is achieved, even outside the perfect discrimination regime.
@@
 
+In Figure (\ref{FigureQSEMEZESRM}) we present de dependency on the modulus of the overlap in the $\mathbb{Z}/3\mathbb{Z}$ group-generated ensemble impossing the phase being equal to 0.
+The result is analogous to Figure (\ref{FigureQSDMEZESRM}) but in the exclusion task.
+The existence existence of the perfect exclusion zone appears in overlap values between 0 and $\frac{1}{2}$.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.5\textwidth]{../Plots/ExclusionOverlapVSSucessProbabilitySDPvsSRMZnOverlap3Phase0.pdf}
+	\caption{Plot of the successful exclusion probabilities for the \gls{sdp} results for the \gls{me}, \gls{ze} protocols in a $\mathbb{Z}/3\mathbb{Z}$ ensemble impossing phase=$0$ as well as the results given by the analytical expressions.}
+	\label{FigureQSEMEZESRM}
+\end{figure}
+
+We highlight the good performance of the \gls{me} protocol up to limit values were the result tends to $\frac{2}{3}$ when the ensemble is made of indistingible states (i.e.
+the same state).
+Naturally everything matches with the previos observations and discussions.
+
+Moreover, the results in \gls{qse} are substancially better, the exclusion can be performed with higher precission than the discrimination.
+This observations is expected.
+Let us suppose we perform a correct guess in the discrimination of our target state, then if we know to which state is correlated our target state, we know which states is not correlated to, in other words
+\begin{align*}
+	\text{correct discrimination}\Rightarrow\text{correct exclusion}.
+\end{align*}
+However, let us suppose we perform a correct guess in the exclusion task, still we are ignoring which is our target state, then,
+\begin{align*}
+	\text{correct exclusion}\nRightarrow\text{correct discrimination}.
+\end{align*}
+Hence, archiving a correct outcome in the discrimination task implies a correct outcome in the exclusion task but the reciprocal is untrue.
+This trivial discussion explains the differences in the results and reinforces the potential of \gls{qse}.
+
 \subsection{The perfect exclusion regime and general ensembles}\label{sectionPerfectExclusionRegimeAndGeneralEnsembles}
 
-Although the $Overlap modulus - phase$ spectrum might seem as the most intuituve representation, the spectrum of Gram's matrix eigenvalues results the most appropriate representation for the perfect exclusion zone as well as the discussion and its comparison for general ensembles.
+Although the \emph{Overlap modulus - phase} spectrum might seem as the most intuituve representation, the spectrum of Gram's matrix eigenvalues results the most appropriate representation for the perfect exclusion zone as well as the discussion and its comparison for general ensembles.
 Carrying on with the previos discussion, one can check the two \gls{dof} now appear as two of the eigenvalues.
@@
 	\centering
-	\label{FigureQSEMEZ3ZEigenValues}
 	\begin{overpic}[width=0.5\textwidth, trim={2.3cm 0.8cm 4.4cm 2cm}, clip]{../Plots/ExclusionEignevaluesGroupGeneratedLowerBoundZ3.pdf}
@@
 	\caption{Plot of the success exclusion probability in the eigenvalues spectrum for the \gls{me} protocol for a $\mathbb{Z}/3\mathbb{Z}$ group-generated ensemble.}
+	\label{FigureQSEMEZ3ZEigenValues}
 \end{figure}
@@
 	\centering
-	\label{FigurePerfectExclusionZ3Z}
 	\begin{overpic}[width=0.5\textwidth, trim={1.8cm 0.8cm 2cm 2cm}, clip]{GeneralSources/PerfectExclusionZoneZ3Z.pdf}
@@
 	\caption{Plot of the $\Delta$ region.}
+	\label{FigurePerfectExclusionZ3Z}
 \end{figure}
@@
 \end{align*}
-The limit case scenarios corresponding to $\lambda_i=3$ and $\lambda_j,\lambda_k=0$ are situated in the vertex of the triangle\footnote{Remember this case correspond to sets with the same state repeated 3 times discussed in Section (\ref{sectionLimitCaseScenarios})}.
+The limit case scenarios corresponding to $\lambda_i=3$ and $\lambda_j,\lambda_k=0$ are located in the vertex of the triangle\footnote{Remember this case correspond to sets with the same state repeated 3 times discussed in Section (\ref{sectionLimitCaseScenarios})}.
 Then the cases corresponding to the edges are those with one state repeated 2 times and one different from the other 2.
@@
 
-Additionally, we observe that no ensembles seem to have a lower exclusion success probability $P_{\gls{me}}^s$ under $\frac{1}{3}$ as expected from the discussion in Section (\ref{sectionLimitCaseScenarios}).
+Additionally, we observe that no ensembles seem to have a lower exclusion success probability $P_{\gls{me}}^s$ under $\frac{2}{3}$ as expected from the discussion in Section (\ref{sectionLimitCaseScenarios}).
 
@@
 
+The result is consistent with all the previos observations and we can also observe the worst case scenario to tend to a 0 successfull exclusion probability as expected.
+Also, the probabilities remain with lower values than the ones obtained with the Minimum Error (\gls{me}) protocol.
+
 \begin{figure}[H]
 	\centering
-	\label{FigureQSEZEZ3ZEigenValues}
 	\begin{overpic}[width=0.5\textwidth, trim={2.3cm 0.8cm 4.4cm 2cm}, clip]{../Plots/ExclusionEignevaluesGroupGeneratedLowerBoundZ3ZeroError.pdf}
@@
 	\caption{Plot of the success exclusion probability in the eigenvalues spectrum for the \gls{ze} protocol for a $\mathbb{Z}/3\mathbb{Z}$ group-generated ensemble.}
+	\label{FigureQSEZEZ3ZEigenValues}
 \end{figure}
-
-The result is consistent with all the previos observations and we can also observe the worst case scenario to tend to a 0 successfull exclusion probability as expected.
-Also, the probabilities remain with lower values than the ones obtained with the Minimum Error (\gls{me}) protocol.
 
@@
 
+A remarcable feature is that each ensemble has been checked to not have a successfull exclusion probability that overtakes the value from the $\mathbb{Z}/3\mathbb{Z}$ group-generated ensemble pointing this value to be this a lower bound for the general case scenario.
+
 \begin{figure}[H]
 	\centering
-	\label{FigureQSEMEGenericEigenValues}
 	\begin{overpic}[width=0.5\textwidth, trim={2.3cm 0.8cm 4.4cm 2cm}, clip]{../Plots/ExclusionEignevalueRandom3.pdf}
@@
 	\caption{Plot of the success exclusion probability in the eigenvalues spectrum for the \gls{me} protocol for a generic ensemble.}
+	\label{FigureQSEMEGenericEigenValues}
 \end{figure}
 
-A remarcable feature is that each ensemble has been checked to not have a successfull exclusion probability that overtakes the value from the $\mathbb{Z}/3\mathbb{Z}$ group-generated ensemble pointing this value to be this a lower bound for the general case scenario.
+\begin{figure}[H]
+	\centering
+	\begin{overpic}[width=0.5\textwidth, trim={6.5cm 2cm 4.4cm 2cm}, clip]{../Plots/ExclusionEignevalueRandom33D.pdf}
+	\end{overpic}
+	\caption{3D Plot of the success exclusion probability in the eigenvalues spectrum for the \gls{me} protocol for a group-generated and generic ensembles.}
+	\label{FigureQSEMEGenericEigenValues3D}
+\end{figure}
+
+In Figure (\ref{FigureQSEMEGenericEigenValues3D}) we present a 3D plot for the comparison of the success probability for exclusion for ensembles of 3 states between generic and group-generated ensembles.
+The $x$ and $y$ axis representing de eigenvalues of the Gram matrix are analogous to previos figures.
+Nevertheless the $z$ axis shows the success probability for exclusion insted of the previos heatmaps.
+Here we can observe how the randomly generated states raise the probabilities over the group-generated values.
+The generation of unitary matrices that fill $U(n)$ ensures the Gram matrices we are generating comprehend the entire set of possible Gram matrices homogeniously.
+
+\section*{Acknowledgements}
+
+I am grateful to Dr.
+Ramón Muñoz Tapia for allowing me to be one of his pupils and for presenting this project.
+I am also deeply grateful to Dr.
+Santiago Llorens Fernández for being the lighthouse that illuminates my path throughout this journey.
+
+I would like to acknowledge my mother and sister for their unconditional support, and my father for the values he taught me.
+Additionally, I would like to thank my friends Francisco Montaño, David Muñoz and Manel Martin for listening to my monologues about my excitement for Quantum State Exclusion.
 

### 2025-04-20 Scripts/PlotExclusionRandomEigenValues.py

@@ -18,7 +18,7 @@ NumberOfMatrices              = 3
 MatrixDimension               = 3
 MatrixGenerationMethod        = "Random"
 ProbabliltiesGenerationMethod = "Equal"
-IterationsRandomSets          = 50000
+IterationsRandomSets          = 10000
 DataMinimumError              = []
 EigenValue0                   = []
 EigenValue1                   = []
@@ -40,39 +40,39 @@ for iIteration in tqdm(range(IterationsRandomSets),"Computing points for the Min
     LowerBoundZE.append(Conditions.getPerfectExlusionLowerBoundZeroError())
     DataMinimumError.append((EigenValuesNormalized[0],EigenValuesNormalized[1],SDPMinimumError,Conditions.getPerfectExlusionLowerBoundMinimumError()))
 
-fig, ax = plt.subplots(figsize=(12, 7))
-sc = ax.scatter(EigenValue0, EigenValue1, c=LowerBound, cmap='jet', s=50)
-plt.colorbar(sc, ax=ax, label="Exclusion probability")
-
-ax.set_xlabel("$\lambda_1$")
-ax.set_ylabel("$\lambda_2$")
-
-plt.savefig(f"../Plots/ExclusionEignevaluesGroupGeneratedLowerBoundZ{NumberOfMatrices}.pdf")
-plt.close()
-
-fig, ax = plt.subplots(figsize=(12, 7))
-sc = ax.scatter(EigenValue0, EigenValue1, c=LowerBoundZE, cmap='jet', s=50)
-plt.colorbar(sc, ax=ax, label="Exclusion probability")
-
-ax.set_xlabel("$\lambda_1$")
-ax.set_ylabel("$\lambda_2$")
-
-plt.savefig(f"../Plots/ExclusionEignevaluesGroupGeneratedLowerBoundZ{NumberOfMatrices}ZeroError.pdf")
-plt.close()
-
-fig, ax = plt.subplots(figsize=(12, 7))
-sc = ax.scatter(EigenValue0, EigenValue1, c=SDPMinimumErrorList, cmap='jet', s=50)
-plt.colorbar(sc, ax=ax, label="Exclusion probability")
-
-ax.set_xlabel("$\lambda_1$")
-ax.set_ylabel("$\lambda_2$")
-
[…]

### 2025-04-20 Scripts/PlotOverlapVSSuccessProbability.py

@@ -7,6 +7,69 @@
 #                                                                                                      #
 ########################################################################################################
 
+# import QSExSetUp
+# import matplotlib.pyplot as plt
+# from tqdm import tqdm
+# import numpy as np
+# from mpl_toolkits.mplot3d import Axes3D
+#
+#
+# ############################ SDP vs SRM #################################
+#
+# Group                         = 3
+# MatrixGenerationMethod        = "ZnOverlap"
+# ProbabliltiesGenerationMethod = "Equal"
+# Acuracy                       = 100
+# PhaseList                     = [1]
+# OverlapLimit                  = 1
+# NumberOfMatrices              = Group
+# MatrixDimension               = Group
+# Overlap                       = 0
+# SuccesProbabilitySRM          = []
+# SuccesProbabilityMinimumError = []
+# SuccesProbabilityZeroError    = []
+# OverlapsList                  = []
+#
+# for iPoint in tqdm(range(1,Acuracy),"Computing the points"):
+#     Overlap     += OverlapLimit/Acuracy
+#     OverlapList = [Overlap]
+#     GenerationConditions = QSExSetUp.GramGeneratedStates.ZnGramMatrixConditionsOverlap(OverlapList, PhaseList, NumberOfMatrices)
+#     Conditions  = QSExSetUp.GramGeneratedStates.GramGeneratedStatesClass(NumberOfMatrices,
+#                                                                          MatrixDimension,
+#                                                                          MatrixGenerationMethod, GenerationConditions, 
+#                                                                          ProbabilitiesContructionMethod = ProbabliltiesGenerationMethod)
+#     SolutionMinimumError = QSExSetUp.SDPSolver.SolveSDPDualMinimumError(Conditions)
+#     SolutionZeroError    = QSExSetUp.SDPSolver.SolveSDPDualZeroError(Conditions)
+#
+#     SuccesProbabilitySRM.append(Conditions.getSRMSuccessProbability())
+#     OverlapsList.append(Overlap)
+#     SuccesProbabilityMinimumError.append(round(SolutionMinimumError['SDPSolution'],8))
[…]

### 2025-05-17 Manuscript/Manuscript.tex
Postulates

@@
 Given a quantum state known to be prepared from a finite ensemble, \gls{qsd} seeks to identify which specific state from the ensemble corresponds to the given system.
-In contrast, \gls{qse}~\cite{PhysicsExclusionSource} adopts the opposite perspective: it aims to determine which states from the ensemble do not correspond to the prepared state.
+In contrast, \gls{qse}~\cite{PhysicsExclusionSource} adopts the opposite perspective, it aims to determine which states from the ensemble do not correspond to the prepared state.
 While \gls{qsd} has been deeply studied in recent years\cite{DiscriminationArticle}, with significant advances since its inception~\cite{helstromBook}, \gls{qse} offers a complementary framework with distinct advantages.
@@
 
-The exclusion task can be carried out under two main protocols: \gls{me} and \gls{ze}\footnote{Also known as \emph{unambiguous exclusion}.}.
+The exclusion task can be carried out under two main protocols, \gls{me} and \gls{ze}\footnote{Also known as \emph{unambiguous exclusion}.}.
 In the Minimum Error scenario, the goal is to minimize the probability of mistakenly excluding the actual prepared state.
@@
 Furthermore, we investigate improved bounds for the general case based on how closely a given ensemble resembles a group generated one\footnote{The notion of "how close" will be formally defined in Section~\textcolor{blue}{add section}.}.
+
+\subsection{Preamble}
+
+This project is entirely situated within the quantum realm. Therefore, we begin by contextualizing some foundational postulates, notation, and elements upon which the rest of the project relies.
+
+\textbf{Postulate I:} A quantum state provides a complete description of a physical system.
+In quantum mechanics, a state can be represented by a normalized vector $\ket{\psi}$ in a Hilbert space $\mathcal{H}$.
+Hence, each physical system corresponds to a unique Hilbert space.
+
+\textbf{Postulate II:} An observable $O$ is a measurable property of a physical system. Mathematically, observables are represented by hermitian operators.
+
+\textbf{Postulate III:} The eigenvalues $o_i$ of a hermitian operator $O = \sum_{i} o_i P_i$ represent the possible outcomes of measuring the observable $O$.
+Upon measuring $O$ and obtaining the result $o_i$, the quantum state $\ket{\psi}$ collapses to the state
+\begin{align*}
+	\frac{P_i\ket{\psi}}{\sqrt{p_i}},
+\end{align*}
+where $P_i$ is the projector onto the eigenspace associated with the eigenvalue $o_i$, and $p_i = \left\|P_i\ket{\psi}\right\|^2$ is the normalization factor.
+
+\textbf{Postulate IV:} The probability $p_i$ of obtaining outcome $o_i$ when measuring the observable $O = \sum_{i} o_i P_i$ on a system described by the quantum state $\ket{\psi}$ is given by
+\begin{align*}
+	p_i = \text{Tr}\left(P_i \ket{\psi}\bra{\psi}\right) = \left\|P_i\ket{\psi}\right\|^2 = \braket{\psi|P_i|\psi}.
+\end{align*}
+
+Note that if $\ket{\psi'} = e^{i\theta}\ket{\psi}$ for some global phase $\theta \in \mathbb{R}$, the observable outcomes and probabilities remain unchanged.
+Therefore, quantum states differing only by a global phase are physically indistinguishable.
+
+In relation to Postulate I, it is often convenient to represent quantum states using the \emph{density matrix} formalism, where the state is described by $\rho = \ket{\psi}\bra{\psi}$ instead of $\ket{\psi}$.
+In this formalism, the global phase ambiguity disappears, since if $\ket{\psi'} = e^{i\theta}\ket{\psi}$, then
+\begin{align*}
+	\rho' = \ket{\psi'}\bra{\psi'} = \ket{\psi}\bra{\psi} = \rho.
+\end{align*}
+
+Using this representation, Postulates III and IV are reformulated. The post-measurement state has a density matrix
+\begin{align*}
+	\frac{P_i \rho P_i}{p_i},
+\end{align*}
+and the probability of obtaining outcome $o_i$ is
+\begin{align*}
+	p_i = \text{Tr}(P_i \rho).
+\end{align*}
+
+Both formulations are equivalent, though one may be more convenient than the other depending on the context.
+Furthermore, the density matrix formalism naturally introduces the concept of \emph{mixed states}.
+Until now, we have implicitly dealt only with \emph{pure states}, i.e., states of the form $\rho = \ket{\psi}\bra{\psi}$.
+
+Suppose now that, for reasons we ignore, the system is prepared in one of several pure states $\{\rho_i\}_{i=1}^n$ with probabilities $\{\eta_i\}_{i=1}^n$.
+Then the overall state of the system is described by the mixed state
+\begin{align*}
+	\rho = \sum_{i=1}^n \eta_i \rho_i.
+\end{align*}
+
+For the purposes of this project, we focus exclusively on pure states and do not address scenarios involving mixed states.
+
+In relation to the observable postulate, we now define a \gls{povm} as a collection of measurement operators $\{O_i\}_{i=1}^n$ that satisfy,
+\begin{itemize}
+	\item Each $O_i$ is positive semi-definite, meaning all its eigenvalues $o_j^{(i)}$ satisfy $o_j^{(i)} \geq 0$.
+	\item The operators satisfy the completeness relation,
+\begin{align*}
+	\sum_{i=1}^n O_i = \mathds{1},
+\end{align*}
+where $\mathds{1}$ denotes the identity operator on the Hilbert space $\mathcal{H}$.
+\end{itemize}
+
+Unlike projective measurements, the operators $O_i$ in a POVM are not necessarily orthogonal projectors.
+This allows the number of measurement outcomes to exceed the dimensionality of the Hilbert space, making POVMs particularly useful in tasks such as \gls{qse} and \gls{qsd}.
 
@@
 \begin{align}\label{equationPerfectExclusionCondition}
-	\lambda_{|G|} \leq \left( \sum_{i=1}^{|G|} \sqrt{\lambda_i} \right)^2.
+	\lambda_{|G|} \leq \left( \sum_{i<|G|} \sqrt{\lambda_i} \right)^2.
 \end{align}
@@
 The generation of unitary matrices that fill $U(n)$ ensures the Gram matrices we are generating comprehend the entire set of possible Gram matrices homogeniously.
+\subsection{Intuition behind the results}
+
+The intuition behind the exclusion task for group-generated ensembles being the worst case scenario for this task, thus yielding a lower bound for the probability of excluding a hypothesis state in the general case is as follows.
+Consider an ensemble $\{\ket{\psi_i}\}_{i=1}^n$ with a certain degree of symmetry, and a state $\ket{\psi_j}$ known to be a member of this ensemble.
+Our goal is to perform the exclusion task, i.e., to identify a state $\ket{\psi_k} \in \{\ket{\psi_i}\}_{i=1}^n$ such that we \emph{suspect} $\ket{\psi_k} \neq \ket{\psi_j}$\footnote{We emphasize the word \emph{suspect} because in many scenarios we are not certain about $\ket{\psi_k} \neq \ket{\psi_j}$, which corresponds to the \emph{non-perfect exclusion} case.}.
+
+Due to the symmetric nature of the ensemble, the states are very similar to each other.
+This makes it especially difficult to identify which state is different from the target state.
+In contrast, if the ensemble includes a state $\ket{\tilde{\psi}}$ that is very different from the others, it becomes easier to determine whether $\ket{\tilde{\psi}}$ matches the target or not.
+Thus, when the symmetry is broken, exclusion can be performed more accurately.
+
+To illustrate this more concretely, consider the following ensamble involving qubit states,
+\[
+\{\ket{\textcolor{red}{\uparrow}}, \ket{\textcolor{blue}{\uparrow}}, \ket{\textcolor{green}{\uparrow}}\}.
+\]
+These are represented on a Bloch circle\footnote{The Bloch circle is a projection of the Bloch sphere onto a plane.} in Figure~\ref{FigureIntuitionExample}.
+
+\begin{figure}[H]
+	\centering
+	\begin{tikzpicture}[scale = 1]
+	\draw[thick] (0,0) circle(1cm);
+  	\draw[line width=1.5pt,->,>=stealth, red] (0,0) -- (0,1);
+  	\draw[line width=1.5pt,->,>=stealth, blue] (0,0) -- (0.17365,-0.9848);
+  	\draw[line width=1.5pt,->,>=stealth, green] (0,0) -- (-0.17365,-0.9848);
+	\end{tikzpicture}
+	\caption{Representation of the ensemble states as projections on the Bloch circle.}
+	\label{FigureIntuitionExample}
+\end{figure}
+
+It is evident that $\ket{\textcolor{red}{\uparrow}}$ is noticeably different from the other two states.
+The red arrow points in the opposite direction to the blue and green arrows.
+Therefore, given an unknown state $\ket{\uparrow}$ from this ensemble, it is relatively easy to determine whether $\ket{\uparrow} = \ket{\textcolor{red}{\uparrow}}$ or $\ket{\uparrow} \neq \ket{\textcolor{red}{\uparrow}}$.
+If $\ket{\uparrow} = \ket{\textcolor{red}{\uparrow}}$, we can exclude either $\ket{\textcolor{blue}{\uparrow}}$ or $\ket{\textcolor{green}{\uparrow}}$; otherwise, we can exclude $\ket{\textcolor{red}{\uparrow}}$.
+In both cases, the exclusion is straightforward.
+
+This is closely related to the task of quantum state discrimination (\gls{qsd}).
+If $\ket{\uparrow} = \ket{\textcolor{red}{\uparrow}}$, the exclusion and discrimination tasks are practically equivalent.
+However, if $\ket{\uparrow} \neq \ket{\textcolor{red}{\uparrow}}$, it becomes very difficult to determine whether $\ket{\uparrow} = \ket{\textcolor{blue}{\uparrow}}$ or $\ket{\uparrow} = \ket{\textcolor{green}{\uparrow}}$, as these states are almost indistinguishable.
+Thus, in this ensemble, the exclusion task may be more feasible than discrimination, showcasing its strength in certain scenarios.
+
+%From an analytical perspective, consider the Gram matrix $\mathcal{G}$ for this ensemble. We have,
+%\\begin{align*}
+%\braket{\textcolor{blue}{\uparrow}|\textcolor{red}{\uparrow}} \approx \braket{\textcolor{green}{\uparrow}|\textcolor{red}{\uparrow}} = \epsilon, \quad \braket{\textcolor{blue}{\uparrow}|\textcolor{green}{\uparrow}} = 1 - \epsilon, \quad \text{with } |\epsilon|^2 \approx 0.
+%\end{align*}
+%The states are normalized, so,
+%\begin{align*}
+%\braket{\textcolor{red}{\uparrow}|\textcolor{red}{\uparrow}} = \braket{\textcolor{blue}{\uparrow}|\textcolor{blue}{\uparrow}} = \braket{\textcolor{green}{\uparrow}|\textcolor{green}{\uparrow}} = 1.
+%\end{align*}
+%Hence, the Gram matrix is approximately,
+%\begin{align*}
+%\mathcal{G} = 
+%\begin{pmatrix}
+%1 & \epsilon & \epsilon^* \\
+%\epsilon^* & 1 & 1 - \epsilon \\
+%\epsilon & 1 - \epsilon^* & 1
+%\end{pmatrix}.
+%\end{align*}
+%Neglecting terms of order $\epsilon^2$, the eigenvalues of $\mathcal{G}$ are approximately,
+%\begin{align*}
+%\{2 + \Re(\epsilon), 1, -2\Re(\epsilon)\}.
+%\end{align*}
+
+Now contrast this with a symmetric ensemble, as shown in Figure~\ref{FigureIntuitionExample2}:
+
+\begin{figure}[H]
+	\centering
+	\begin{tikzpicture}[scale = 1]
+	\draw[thick] (0,0) circle(1cm);
+  	\draw[line width=1.5pt,->,>=stealth, red] (0,0) -- (0,1);
+  	\draw[line width=1.5pt,->,>=stealth, blue] (0,0) -- (0.866,-0.5);
+  	\draw[line width=1.5pt,->,>=stealth, green] (0,0) -- (-0.866,-0.5);
+	\end{tikzpicture}
+	\caption{Symmetric ensemble represented on the Bloch circle.}
+	\label{FigureIntuitionExample2}
+\end{figure}
+
+This configuration exhibits perfect symmetry. Define a unitary operator $\mathcal{U}$ such that:
+\[
+\mathcal{U} \ket{\textcolor{red}{\uparrow}} = \ket{\textcolor{blue}{\uparrow}},
+\]
+then by symmetry:
+\[
+\mathcal{U} \ket{\textcolor{blue}{\uparrow}} = \ket{\textcolor{green}{\uparrow}}, \quad \mathcal{U} \ket{\textcolor{green}{\uparrow}} = \ket{\textcolor{red}{\uparrow}}.
+\]
+Hence,
+\[
+\mathcal{U}^3 = \mathds{1}|_{\text{Bloch circle}},
+\]
+where $\mathds{1}|_{\text{Bloch circle}}$ denotes the identity operator restricted to this subspace.
+This implies that the ensemble is generated by a cyclic group of order 3, i.e., $\mathbb{Z}/3\mathbb{Z}$.
+
+In such a group-generated ensemble, distinguishing any pair of states is equally difficult due to symmetry.
+Therefore, exclusion becomes more challenging, representing a worst-case scenario compared to the asymmetric case.
+
+\section{Conclusions}
 
@@
 Ramón Muñoz Tapia for allowing me to be one of his pupils and for presenting this project.
-I am also deeply grateful to Dr.
+I am also deeply grateful to PhD.
 Santiago Llorens Fernández for being the lighthouse that illuminates my path throughout this journey.

### 2025-05-17 Scripts/GramGeneratedStates.py

@@ -29,6 +29,7 @@ class GramGeneratedStatesClass:
         self.MatrixConstructionMethod       = MatrixConstructionMethod
         self.ProbabilitiesContructionMethod = ProbabilitiesContructionMethod
         self.PriorProbabilities             = GramGeneratedFunctions.SetOfProbabilities(ProbabilitiesContructionMethod,NumberOfMatrices)
+        self.GramGeneratingConditions       = GenerationConditions
         GramMatrixAndUnitaryMatrix          = GramGeneratedFunctions.GenerateGramMatrix(NumberOfMatrices,MatrixConstructionMethod, GenerationConditions)
         self.GramMatrix                     = GramMatrixAndUnitaryMatrix["GramMatrix"]
         self.SquareRoot                     = picos.Constant(sqrtm(self.GramMatrix))
@@ -52,7 +53,8 @@ class GramGeneratedStatesClass:
             'DensityMatrices'                : self.DensityMatrices,
             'SquareRootSuccessProbability'   : self.SquareRootSuccessProbability,
             'PerfectExlusion'                : self.PerfectExlusion,
-            'UnitaryMatrix'                  : self.UnitaryMatrix
+            'UnitaryMatrix'                  : self.UnitaryMatrix,
+            'GramGeneratingConditions'       : self.GramGeneratingConditions
         }
     def __getitem__(self, key):
         return self.to_dict()[key]
@@ -105,6 +107,42 @@ class GramGeneratedStatesClass:
     
     def getUnitaryMatrix(self):
         return self.to_dict()['UnitaryMatrix']
+    
+    def getGramGeneratingConditions(self):
+        return self.to_dict()['GramGeneratingConditions']
+    
+    def variationUnitaryGramMatrix(self, epsilon):
+        if not isinstance (epsilon, (int, float)):
+            raise TypeError("The given value of 'epsilon' must be an integer or a float.")
+        def diagonalMatrix(diagonal,n):
+            diagonalMatrixList = []
+            for iElement in range(n):
+                diagonalMatrixRow = []
+                for jElement in range(n):
+                    if jElement == iElement:
+                        diagonalMatrixRow.append(diagonal[jElement])
+                        continue
+                    diagonalMatrixRow.append(0)
+                diagonalMatrixList.append(diagonalMatrixRow)
+            return picos.Constant(diagonalMatrixList)
[…]

### 2025-05-17 Scripts/PlotExclusionRandomEigenValues.py

@@ -13,6 +13,7 @@ import matplotlib.pyplot as plt
 from mpl_toolkits.mplot3d import Axes3D
 from tqdm import tqdm
 import mpltern
+import picos
 
 NumberOfMatrices              = 3
 MatrixDimension               = 3
@@ -30,6 +31,8 @@ for iIteration in tqdm(range(IterationsRandomSets),"Computing points for the Min
     EigenValues             = np.random.rand(NumberOfMatrices)
     EigenValuesNormalized   = [iEigenValue*NumberOfMatrices/sum(EigenValues) for iEigenValue in EigenValues]
     Conditions              = QSExSetUp.GramGeneratedStates.GramGeneratedStatesClass(NumberOfMatrices,MatrixDimension,MatrixGenerationMethod, QSExSetUp.GramGeneratedStates.ZnGramMatrixConditionsEigenValues(EigenValuesNormalized, NumberOfMatrices), ProbabilitiesContructionMethod = ProbabliltiesGenerationMethod)
+    print("UwU\n",Conditions.getGramMatrix())
+    print("Yay\n",picos.trace(Conditions.getGramMatrix()))
     if Conditions.getPerfectExlusion():
         continue
     SDPMinimumError = round(QSExSetUp.SDPSolver.SolveSDPExclusionMinimumError(Conditions)['SDPSolution'],8)

### 2025-05-17 Scripts/Testing2.py

@@ -13,16 +13,19 @@ import numpy as np
 import matplotlib.pyplot as plt
 from tqdm import tqdm
 
-NumberOfMatrices              = 5
-MatrixDimension               = 5
-MatrixGenerationMethod        = "Random"
+NumberOfMatrices              = 11
+MatrixDimension               = 11
+MatrixGenerationMethod        = "ZnEigenValues"
 ProbabliltiesGenerationMethod = "Equal"
 EigenValues                   = [0.1 for i in range(NumberOfMatrices - 1)]
 EigenValues.append(100)
 EigenValuesNormalized         = [iEigenValue*NumberOfMatrices/sum(EigenValues) for iEigenValue in EigenValues]
-Iterations                    = 10000
-GroupGeneratedConditions      = QSExSetUp.GramGeneratedStates.GramGeneratedStatesClass(NumberOfMatrices,MatrixDimension, "ZnEigenValues", QSExSetUp.GramGeneratedStates.ZnGramMatrixConditionsEigenValues(EigenValuesNormalized, NumberOfMatrices), ProbabilitiesContructionMethod = ProbabliltiesGenerationMethod)
+Iterations                    = 10
+StaticIterations              = 50
+Conditions                    = QSExSetUp.GramGeneratedStates.GramGeneratedStatesClass(NumberOfMatrices,MatrixDimension, MatrixGenerationMethod, QSExSetUp.GramGeneratedStates.ZnGramMatrixConditionsEigenValues(EigenValuesNormalized, NumberOfMatrices), ProbabilitiesContructionMethod = ProbabliltiesGenerationMethod)
+GroupGeneratedConditions      = QSExSetUp.GramGeneratedStates.GramGeneratedStatesClass(NumberOfMatrices,MatrixDimension, MatrixGenerationMethod, QSExSetUp.GramGeneratedStates.ZnGramMatrixConditionsEigenValues(EigenValuesNormalized, NumberOfMatrices), ProbabilitiesContructionMethod = ProbabliltiesGenerationMethod)
 
+epsilon = 0.001
 
 DistanceFrobenius             = []
 Distance1                     = []
@@ -32,21 +35,26 @@ DistanceNuclear               = []
 ExlusionSuccessProbability    = []
 
 for iIteration in tqdm(range(Iterations),"Computing SDP"):
[…]

### 2025-05-17 Scripts/Testing3.py

@@ -1,52 +1,33 @@
+#######################################################################################################
+#                                                                                                      #
+#  Project:  Physics TFG                                                                               #
+#  Author:   Sergio Castañeiras Morales                                                                #
+#  Date:     24/01/2025                                                                                #
+#  Purpose:  Testing                                                                                   #
+#                                                                                                      #
+########################################################################################################
+
+
+import picos
 import QSExSetUp
 import numpy as np
-import picos
 from tqdm import tqdm
-from scipy.stats import unitary_group
 
-NumberOfMatrices              = 5
-MatrixDimension               = 5
-MatrixGenerationMethod        = "Random"
+NumberOfMatrices              = 3
+MatrixDimension               = 3
+MatrixGenerationMethod        = "ZnEigenValues"
 ProbabliltiesGenerationMethod = "Equal"
-EigenValues                   = [0.1,0.1,0.1,0.1,100]
+EigenValues                   = [0.1 for i in range(NumberOfMatrices - 1)]
+EigenValues.append(100)
 EigenValuesNormalized         = [iEigenValue*NumberOfMatrices/sum(EigenValues) for iEigenValue in EigenValues]
-Iterations                    = 10000
-GroupGeneratedConditions      = QSExSetUp.GramGeneratedStates.GramGeneratedStatesClass(NumberOfMatrices,MatrixDimension, "ZnEigenValues", QSExSetUp.GramGeneratedStates.ZnGramMatrixConditionsEigenValues(EigenValuesNormalized, NumberOfMatrices), ProbabilitiesContructionMethod = ProbabliltiesGenerationMethod)
+GroupGeneratedConditions      = QSExSetUp.GramGeneratedStates.GramGeneratedStatesClass(NumberOfMatrices,MatrixDimension, MatrixGenerationMethod, QSExSetUp.GramGeneratedStates.ZnGramMatrixConditionsEigenValues(EigenValuesNormalized, NumberOfMatrices), ProbabilitiesContructionMethod = ProbabliltiesGenerationMethod)
 
[…]

### 2025-05-27 Manuscript/Lower bounds of the success probability in quantum state exclusion for general ensembles.tex
Writthing

--- 2025-05-17 Manuscript/Manuscript.tex
@@
 \usepackage{float}
-\usepackage{chemfig}
 \usepackage{yfonts}
@@
 \titleformat{\section}
-  {\normalfont\normalsize\bfseries\centering} % font size, bold, centered
+  {\normalfont\large\bfseries\centering} % font size, bold, centered
   {\thesection}{1em}{\MakeTextUppercase} % uppercase text
@@
 % --- Roman numerals for numbering ---
-\renewcommand{\thesection}{\Roman{section}}
-\renewcommand{\thesubsection}{\Roman{section}.\Roman{subsection}}
+\renewcommand{\baselinestretch}{1.1} 
+%\renewcommand{\thesection}{\Roman{section}}
+%\renewcommand{\thesubsection}{\Roman{section}.\Roman{subsection}}
 
@@
 
+\usepackage[skip=10pt , indent=20pt]{parskip}
 %\setlength{\parindent}{0.0in}
@@
 \newcommand\course{}
-\newcommand\subject{Final Degree Project}
+\newcommand\subject{End of Degree Project}
 \newcommand\degree{Bachelor's Degree in Physics}
@@
     \end{tabular}
-    \normalsize \vspace*{5\baselineskip}
+    \normalsize \vspace*{4.5\baselineskip}
 		}
@@
 \newpage
+\thispagestyle{empty}
+\cfoot{}
+\tableofcontents
 
@@
 \setcounter{page}{1}
-\begin{multicols}{2}[\begin{center}
+\begin{center}
 \begin{abstract}
@@
 \end{center}
-Keywords: \emph{SDP, Quantum state exclusion , \textcolor{blue}{Add keywords}}.
-]
+%Keywords: \emph{SDP, Quantum state exclusion , \textcolor{blue}{Add keywords}}.
 \section{Introduction}
-In many real-world scenarios, excluding a certain hypothesis can be more practical than solving the problem entirely.
-For instance, in disease diagnosis, ruling out potential diseases often serves as the first step in identifying the actual condition.
-Similarly, when repairing a machine, it is sometimes more efficient to identify the components that are functioning correctly, which narrows down the search for the faulty part.
-
-In this project, we project this idea into the quantum realm by focusing on \gls{qse}.
-Rather than determining the exact state of a quantum system, we aim to eliminate one or more possible candidates from a known ensemble of states.
-Notice, this approach can be more suitable or efficient in certain quantum information tasks.
-
-Given a quantum state known to be prepared from a finite ensemble, \gls{qsd} seeks to identify which specific state from the ensemble corresponds to the given system.
-In contrast, \gls{qse}~\cite{PhysicsExclusionSource} adopts the opposite perspective, it aims to determine which states from the ensemble do not correspond to the prepared state.
-While \gls{qsd} has been deeply studied in recent years\cite{DiscriminationArticle}, with significant advances since its inception~\cite{helstromBook}, \gls{qse} offers a complementary framework with distinct advantages.
-
-Although the tasks of exclusion and discrimination coincide for ensembles containing only two states \footnote{Since for the two states case excluding one necessarily implies identifying the other.}, when dealing with ensembles of three or more states, the two problems diverge in both approach and complexity.
-One of the most significant features of \gls{qse} is the possibility of achieving \emph{perfect exclusion}, where certain states can be ruled out with zero probability of error in cases where \emph{perfect discrimination} is impossible\cite{OptimalitySRM}.
-
-This capability opens new frontiers in quantum information theory, particularly in the context of partial information retrieval from quantum systems.
-By excluding certain states, it is possible to gain insight into the encoded information without needing to fully determine the original state.
-
-As with \gls{qsd}, obtaining a general analytical solution for \gls{qse} remains an open problem.
-However, analytical results have been found in specific cases when the ensemble of quantum states exhibits a certain degree of symmetry.
-In particular, when the ensemble is generated by the action of a finite group, the problem becomes more tractable and exact solutions have been derived.
-
-The exclusion task can be carried out under two main protocols, \gls{me} and \gls{ze}\footnote{Also known as \emph{unambiguous exclusion}.}.
+
+\hspace{20pt}In many real-world scenarios, excluding a certain hypothesis can be more practical than solving the problem entirely.
+For instance, in disease diagnosis, ruling out potential illnesses is often the first step toward identifying the actual condition.
+Similarly, in the context of detecting a gas leak in a complex pipe system, excluding the possibility of the gas being chlorine, a toxic substance, can guide the search for the faulty pipe by narrowing down the potential sources and providing critical information about the gas's toxicity.
+In numerous everyday situations, the strategy of excluding specific possibilities forms a natural and often effective initial approach to the problem.
+
+In the quantum realm, a similar line of reasoning can be applied in some problmes.
+One of the fundamental tasks in quantum information theory is the identification of an unknown quantum state known to belong to a given ensemble of possible states.
+This task is referred to as Quantum State Discrimination (\gls{qsd}), and it has been extensively studied in the literature \cite{DiscriminationArticle}.
+However, instead of aiming to identify the exact state, we may take another approach by applying the hypothesis exclusion idea.
+That is, given a quantum state known to be one among a certain ensemble, the goal becomes to conclusively rule out the possibility of the unknown state being a specific member of that ensemble.
+This alternative task is known as Quantum State Exclusion (\gls{qse}) \cite{PhysicsExclusionSource}, and it offers a distinct framework with its own set of advantages \cite{piani2020quantum} with respect to its counterpart \gls{qsd}.
+
+We can approach \gls{qse} task under several protocols, depending on the context within we perform the hypothesis exclusion we can prefer one or another.
+In this project, we focus on two main protocols, Minimum Error (\gls{me}) and Zero Error (\gls{ze})\footnote{Also known as \emph{unambiguous exclusion}.}, i.e.
+the protocols for which analytical results have been presented \cite{MainPaper}.
 In the Minimum Error scenario, the goal is to minimize the probability of mistakenly excluding the actual prepared state.
-In contrast, the Zero Error approach seeks to exclude a state with absolute certainty, even if that means sometimes the procedure yields an inconclusive result.
-
-Building on recent results that provide exact solutions for exclusion tasks in group generated ensembles \cite{MainPaper}, this project undertakes a numerical study of such results as lower bounds for more general, randomly generated ensembles.
-To this end, we employ \gls{sdp} to explore \gls{qse} performance in arbitrary settings.
-Furthermore, we investigate improved bounds for the general case based on how closely a given ensemble resembles a group generated one\footnote{The notion of "how close" will be formally defined in Section~\textcolor{blue}{add section}.}.
-
-\subsection{Preamble}
-
-This project is entirely situated within the quantum realm. Therefore, we begin by contextualizing some foundational postulates, notation, and elements upon which the rest of the project relies.
+In contrast, the Zero Error approach seeks to exclude a state with absolute certainty, although this procedure sometimes yields an inconclusive result when perfect exclusion cannot be accomplished.
+
+While \gls{qsd} has seen significant progress over the years \cite{bae2015quantum, helstromBook}, \gls{qse} has remained relatively underexplored until recently.
+New analytical results have emerged \cite{MainPaper} for both the \gls{me} and \gls{ze} protocols, particularly when the ensemble of quantum states possesses a certain degree of symmetry.
+In particular, when the ensemble is generated through the action of a finite algebraic group, the problem becomes more tractable, highlighting \gls{qse} as a worthwhile object of study.
+
+Although the tasks of exclusion and discrimination coincide for ensembles containing only two states\footnote{Since for the two states case excluding one necessarily implies identifying the other.}, when dealing with ensembles of three or more states, the two problems diverge in both approach and complexity.
+Though this work primarily focuses on \gls{qse}, we include a comparative discussion of both tasks and protocols to further motivate the interest in \gls{qse} and discuss the main differences with \gls{qsd} in Appendix \ref{appendixComparisonQSDvsQSE}.
+One of the key features of \gls{qse} is the possibility of achieving \emph{perfect exclusion}, i.e.
+confidently ruling out a candidate state with complete certainty that it is not the unknown state.
+In contrast, \emph{perfect discrimination} is generally not achievable, meaning that one cannot identify the unknown state with absolute certainty in most settings\cite{OptimalitySRM}.
+
+This capacity for perfect exclusion opens new avenues in quantum information theory, especially in scenarios involving partial information retrieval from quantum systems \cite{gour2020weight}.
+By eliminating certain hypotheses, one can extract meaningful information from a quantum system without requiring full state identification.
+
+Building upon the recent results for the probability of a correct exclusion for group-generated ensembles \cite{MainPaper},\footnote{A proper definition of a \emph{group generated ensemble} will be given in the \emph{Group generated ensembles} section \ref{sectionGroupGeneratedEnsemble}, for the time being, we can identify them as ensembles that comprehend set of states that exhibit a certain symmetry.} this project undertakes a numerical investigation into \gls{qse}, highlighting the analytical results from group-generated ensembles as lower bounds for more general cases.
+The project comences with a preliminaries section that outlines the mathematical framework underlying the \gls{qse} task, along with the essential tools used in our analysis.
+We then present results for the probability of correct hypothesis exclusion in ensembles consisting of three quantum states, the simplest case.
+Furthermore, we explore the distribution of correct exclusion probabilities for randomly generated ensembles sampled according to Haar measure.\footnote{The importance of the generic ensembles generation being performed according to Haar measure is a key for the numerical analysis and it is discussed in the \emph{Methodology} section (\ref{sectionMethodology})}
+
+To carry out our numerical analysis, we employ \gls{sdp} techniques, which allow us to cast the \gls{qse} task as a convex optimization problem.
+The \gls{sdp} approach has proven particularly effective for problems of this kind \cite{bandyopadhyay2014conclusive}.
+Finally, ve conclude by providing some theoretical intuition and insights based on our results.
+
+\newpage
+\section{Preliminaries}
+
+In this section we introduce some mathematical formalism of the postulates of Quantum Mechanics as well as some relevant objects in order to introduce the mathematical framework of \gls{qse} in a \gls{sdp} form.
+Additionally we define the Haar measure and discuss its importance for a proper generation of generic ensembles.
+
+\subsection{Postulates and definitions}
+
+This project is entirely situated within the quantum realm. Therefore, we begin by contextualizing the foundational postulates, notation, and elements upon which the rest of the project relies on.
 
@@
 
-Note that if $\ket{\psi'} = e^{i\theta}\ket{\psi}$ for some global phase $\theta \in \mathbb{R}$, the observable outcomes and probabilities remain unchanged.
+%Note that if $\ket{\psi'} = e^{i\theta}\ket{\psi}$ for some global phase $\theta \in \mathbb{R}$, the observable outcomes and probabilities remain unchanged.
 Therefore, quantum states differing only by a global phase are physically indistinguishable.
 
-In relation to Postulate I, it is often convenient to represent quantum states using the \emph{density matrix} formalism, where the state is described by $\rho = \ket{\psi}\bra{\psi}$ instead of $\ket{\psi}$.
-In this formalism, the global phase ambiguity disappears, since if $\ket{\psi'} = e^{i\theta}\ket{\psi}$, then
-\begin{align*}
-	\rho' = \ket{\psi'}\bra{\psi'} = \ket{\psi}\bra{\psi} = \rho.
-\end{align*}
+In relation to Postulate I, it is often convenient to represent quantum states using the \emph{density matrix} formalism, where a pure  state is described by $\rho = \ket{\psi}\bra{\psi}$ instead of $\ket{\psi}$.
+
+%In this formalism, the global phase ambiguity disappears, since if $\ket{\psi'} = e^{i\theta}\ket{\psi}$, then
+%\begin{align*}
+%	\rho = \ket{\psi'}\bra{\psi'} = \ket{\psi}\bra{\psi} .
+%\end{align*}
 
@@
 Until now, we have implicitly dealt only with \emph{pure states}, i.e., states of the form $\rho = \ket{\psi}\bra{\psi}$.
-
 Suppose now that, for reasons we ignore, the system is prepared in one of several pure states $\{\rho_i\}_{i=1}^n$ with probabilities $\{\eta_i\}_{i=1}^n$.
@@
 
-In relation to the observable postulate, we now define a \gls{povm} as a collection of measurement operators $\{O_i\}_{i=1}^n$ that satisfy,
+In relation to the observable postulate, we now define a \gls{povm} as a collection of measurement operators $\{\Pi_i\}_{i=1}^n$ that satisfy,
 \begin{itemize}
-	\item Each $O_i$ is positive semi-definite, meaning all its eigenvalues $o_j^{(i)}$ satisfy $o_j^{(i)} \geq 0$.
+	\item Each $\Pi_i$ is positive semi-definite hermitian operator, meaning all its eigenvalues $\pi_j^{(i)}$ satisfy $\pi_j^{(i)} \geq 0$.
 	\item The operators satisfy the completeness relation,
 \begin{align*}
-	\sum_{i=1}^n O_i = \mathds{1},
+	\sum_{i=1}^n \Pi_i = \mathds{1},
 \end{align*}
@@
 
-Unlike projective measurements, the operators $O_i$ in a POVM are not necessarily orthogonal projectors.
-This allows the number of measurement outcomes to exceed the dimensionality of the Hilbert space, making POVMs particularly useful in tasks such as \gls{qse} and \gls{qsd}.
-
-\subsection{Formulation of the Problem}\label{sectionFormulationOfTheProblem}
+Unlike projective measurements, the operators $\Pi_i$ in a POVM are not necessarily orthogonal projectors.
+This allows the number of measurement outcomes to exceed the dimensionality of the Hilbert space, extending the previos orthogonal measurement to a more generic status and making POVMs particularly useful in tasks such as \gls{qse} and \gls{qsd}.
+
+\subsection{Formulation of the problem}\label{sectionFormulationOfTheProblem}
 
 Let $\left\{(\rho_i, \eta_i)\right\}_{i=1}^n$ be an ensemble of $n$ quantum states, where each $\rho_i$ denotes a pure state density matrix\footnote{This formulation hols true for mixed states but the project will only discuss the pure state scenario.}, i.e., $\rho_i = \ket{\psi_i}\bra{\psi_i}$, and $\eta_i$ represents the prior probability of occurrence of the state $\rho_i$.
-Let $\rho_j$ be the target state from this ensemble.
-Our objective is to develop a procedure to identify another state $\rho_k \in \left\{\rho_i\right\}_{i=1}^n$, such that $\rho_k \neq \rho_j$.
+Let $\tilde{\rho}$ be a state from this ensemble.
+Our objective is to develop a procedure to identify another state $\rho_j \in \left\{\rho_i\right\}_{i=1}^n$, such that $\rho_j \neq \tilde{\rho}$.
 
 Quantum measurements are described by a set of \glspl{povm}, denoted by $\left\{\Pi_i\right\}_{i=1}^n$, acting on the Hilbert space $\mathcal{H}$ of the quantum system.
-Here we pewsent the two studied protocols for \gls{qse}: minimum-error (\gls{me}) and zero-error (\gls{ze}).
-
-The goal of the \gls{me} protocol is to minimize the probability of incorrectly excluding the target state from our hypothesis.
-If we formulate it as an \gls{sdp}, the problem reads,\footnote{Note that the \gls{sdp} formulations of quantum state discrimination may differ from the exclusion ones by interchanging minimization and maximization problems.}
-\begin{align*}
-	P_{\text{\gls{me}}}^e = \min_{\left\{\Pi_i\right\}} &\sum_{i=1}^n \tr(\Pi_i \rho_i),\\
+Here we present the two studied protocols for \gls{qse}: minimum-error (\gls{me}) and zero-error (\gls{ze}).
+
+As previously discussed the goal of the \gls{me} protocol is to minimize the probability of incorrectly excluding the unknown state from our hypothesis.
+If we formulate it as an \gls{sdp}, the \gls{sdp} minimization of the error probability reads,\footnote{Note that the \gls{sdp} formulations of quantum state discrimination may differ from the exclusion ones by interchanging minimization and maximization problems.}
+\begin{align*}
+	P_{\text{\gls{me}}}^e = \min_{\left\{\Pi_i\right\}} &\sum_{i=1}^n \eta_i \tr(\Pi_i \rho_i),\\
 	\text{subject to} \quad & \sum_{i=1}^n \Pi_i = \mathds{1}, \quad \Pi_i \geq 0 \quad \forall i \in \{1, \dots, n\}.
@@
 
-Note the constraints $\sum_{i=1}^n \Pi_i = \mathds{1}$ and $\Pi_i \geq 0$ ensure that the $\Pi_i$ form a valid POVM, since they demand positive semi-definition and form a complete measurement.
+Note the constraints $\sum_{i=1}^n \Pi_i = \mathds{1}$ and $\Pi_i \geq 0$ ensure that the set $\{\Pi_i\}_{i=1}^n$ form a valid \gls{povm}, raising a proper probability distribution.
 The superscript $e$ in $P_{\text{\gls{me}}}^e$ indicates that this is the \emph{error probability}.
@@
 \begin{align*}
-	P_{\text{\gls{me}}}^s = \max_{\left\{\Pi_i\right\}} &\left(1 - \sum_{i=1}^n \tr(\Pi_i \rho_i)\right),\\
+	P_{\text{\gls{me}}}^s = \max_{\left\{\Pi_i\right\}} &\left(1 - \sum_{i=1}^n \eta_i\tr(\Pi_i \rho_i)\right),\\
 	\text{subject to} \quad & \sum_{i=1}^n \Pi_i = \mathds{1}, \quad \Pi_i \geq 0 \quad \forall i \in \{1, \dots, n\}.
@@
 
-Naturally, both formulations are related via:
+Naturally, both formulations are related via,
 \begin{align*}
@@
 
-In the case of the \gls{ze} protocol, the POVMs must also satisfy an unambiguity condition, i.e.
+In the case of the \gls{ze} protocol, the objective is to exclude with total accuracy a state known to be different from the unkown state.
+However, the protocol might lead to inconclusive result.
+In order to do so, the \gls{povm}s must also satisfy an unambiguity condition, i.e.
 each measurement operator $\Pi_i$ must be orthogonal to the corresponding state $\rho_i$.
@@
 
-To ensure completeness, we introduce an additional POVM element $\Pi_?$ representing an inconclusive result,
+To ensure completeness, we introduce an additional \gls{povm} element $\Pi_?$ representing an inconclusive result,
 \begin{align*}
@@
 \end{align*}
-If the measurement yields the outcome $\Pi_?$ (i.e., the "?" symbol), the result is inconclusive.
-
-The corresponding \gls{sdp} for minimizing the probability of an inconclusive result (i.e., error) in the \gls{ze} protocol is:
-\begin{align*}
-	P_{\text{\gls{ze}}}^e = \min_{\left\{\Pi_i\right\}} &\sum_{i=1}^n \tr(\Pi_? \rho_i),\\
+If the measurement yields the outcome $\Pi_?$, i.e., the "?" label, the result is inconclusive.
+
+The corresponding \gls{sdp} for minimizing the probability of an inconclusive result, i.e. error, in the \gls{ze} protocol is,
+\begin{align*}
+	P_{\text{\gls{ze}}}^e = \min_{\left\{\Pi_i\right\}} &\sum_{i=1}^n \eta_i\tr(\Pi_? \rho_i),\\
 	\text{subject to} \quad & \sum_{i=1}^n \Pi_i + \Pi_? = \mathds{1}, \quad \Pi_? \geq 0,\\
@@
 
-The corresponding success probability is naturally given by,
-\begin{align*}
-	P_{\text{\gls{ze}}}^s = \max_{\left\{\Pi_i\right\}} &\left(1 - \sum_{i=1}^n \tr(\Pi_? \rho_i)\right),\\
-	\text{subject to} \quad & \sum_{i=1}^n \Pi_i + \Pi_? = \mathds{1}, \quad \Pi_? \geq 0,\\
-	& \tr(\Pi_i \rho_i) = 0, \quad \Pi_i \geq 0 \quad \forall i.
-\end{align*}
-
-This formulation is analogous to the \gls{me} protocol, with the crucial difference being the constraint $\tr(\Pi_i \rho_i) = 0$, enforcing unambiguous discrimination.
+The corresponding success probability is naturally given by, the maximization of $1-P_{\text{\gls{ze}}}^e$ under the same constraints.
+
+Notice this formulation is analogous to the \gls{me} protocol, with the crucial difference being the constraint $\tr(\Pi_i \rho_i) = 0$, enforcing unambiguous discrimination.
+
+Additionally, in some cases it is useful to consider the dual formulation of the problem, as solving the dual version of the \gls{sdp} can often be more computationally efficient.
+Moreover, one may consider an ansatz, i.e.
+a candidate set of \gls{povm}s, and compute the exclusion success probability under a given protocol.
+This provides a lower bound for the success probability, since in principle we cannot guarantee that this ansatz is optimal, i.e.
+there may exist another set of \gls{povm}s yielding a higher success rate.
+
+However, by evaluating the same set of \gls{povm}s within the dual formulation, we can obtain an upper bound on the success probability.
+If the upper and lower bounds coincide, we can conclude that the chosen \gls{povm} set is indeed optimal.
+For this reason, we present the dual formulation of the problem in Appendix~\ref{sectionDualFormulationOfTheProblem}.
+This procedure is standard for verifying the optimality of a given \gls{povm} set and closely resembles the internal computations performed by a \gls{sdp} solver.
 
 \subsection{Gram Matrix Formulation}\label{sectionGramMatrixFormulation}
-
-Let $\mathcal{G} \in \mathbb{C}^{n \times n}$ be the \emph{Gram matrix} of the system, defined as the $n \times n$ positive semidefinite Hermitian matrix given by,
+The Gram matrix formulation recasts the \gls{sdp} problems associated with the exclusion task in a more basis-independent manner.
+This approach reveals that the exclusion tasks for certain ensembles can be equivalent to those of others.
+As such, we adopt this formulation in our analysis, as it offers valuable insight into the underlying relationships between the quantum states in the ensemble.
+
+Given an ensemble $\left\{(\rho_i, \eta_i)\right\}_{i=1}^n$ of $n$ quantum states we define the $\mathcal{G} \in \mathbb{C}^{n \times n}$ be the \emph{Gram matrix} of the ensemble, as the $n \times n$ positive semidefinite Hermitian matrix given by,
 \begin{equation*}
@@
 	\begin{pmatrix}
-		\braket{\psi_1|\psi_1} & \braket{\psi_1|\psi_2} & \dots & \braket{\psi_1|\psi_n} \\
-		\braket{\psi_2|\psi_1} & \braket{\psi_2|\psi_2} & \dots & \braket{\psi_2|\psi_n} \\
+		\eta_1 & \sqrt{\eta_1\eta_2}\braket{\psi_1|\psi_2} & \dots & \sqrt{\eta_1\eta_n}\braket{\psi_1|\psi_n} \\
+		\sqrt{\eta_2\eta_1}\braket{\psi_2|\psi_1} & \eta_2 & \dots & \sqrt{\eta_2\eta_n}\braket{\psi_2|\psi_n} \\
 		\vdots & \vdots & \ddots & \vdots \\
-		\braket{\psi_n|\psi_1} & \braket{\psi_n|\psi_2} & \dots & \braket{\psi_n|\psi_n}
+		\sqrt{\eta_n\eta_1}\braket{\psi_n|\psi_1} & \sqrt{\eta_n\eta_2}\braket{\psi_n|\psi_2} & \dots & \eta_n
 	\end{pmatrix},
 \end{equation*}
-that is, $\mathcal{G}_{i,j} = \braket{\psi_i|\psi_j}$. Since all states are normalized, the diagonal elements are equal to 1, and the Gram matrix becomes,
-\begin{equation*}
-	\mathcal{G} =
-	\begin{pmatrix}
-		1 & \braket{\psi_1|\psi_2} & \dots & \braket{\psi_1|\psi_n} \\
-		\braket{\psi_2|\psi_1} & 1 & \dots & \braket{\psi_2|\psi_n} \\
-		\vdots & \vdots & \ddots & \vdots \\
-		\braket{\psi_n|\psi_1} & \braket{\psi_n|\psi_2} & \dots & 1
-	\end{pmatrix}.
-\end{equation*}
+that is, $\mathcal{G}_{i,j} = \sqrt{\eta_i\eta_j}\braket{\psi_i|\psi_j}$. Since all states are normalized, the diagonal elements are equal to $\eta_i$.
 
@@
 \begin{align*}
-	\mathcal{G}_{i,j}^* = (\braket{\psi_i|\psi_j})^* = \braket{\psi_j|\psi_i} = \mathcal{G}_{j,i}.
+	\mathcal{G}_{i,j}^* = \left( \sqrt{\eta_i\eta_j}\braket{\psi_i|\psi_j}\right)^* =  \sqrt{\eta_j\eta_i}\braket{\psi_j|\psi_i} = \mathcal{G}_{j,i}.
 \end{align*}
@@
 \begin{align*}
-	\braket{\Phi|\mathcal{G}|\Phi} &= \braket{\Phi| \left( \sum_{i,j=1}^{n} \braket{\psi_i|\psi_j} \ket{i}\bra{j} \right) |\Phi} \\
-	&= \sum_{i,j=1}^{n} \braket{\psi_i|\psi_j} \braket{\Phi|i} \braket{j|\Phi} \\
-	&= \left\| \sum_{i=1}^{n} \braket{i|\Phi} \ket{\psi_i} \right\|^2 \\
+	\braket{\Phi|\mathcal{G}|\Phi} &= \braket{\Phi| \left( \sum_{i,j=1}^{n} \sqrt{\eta_i\eta_j}\braket{\psi_i|\psi_j} \ket{i}\bra{j} \right) |\Phi} \\
+	&= \sum_{i,j=1}^{n} \sqrt{\eta_i\eta_j}\braket{\psi_i|\psi_j} \braket{\Phi|i} \braket{j|\Phi} \\
+	&= \left\| \sum_{i=1}^{n} \eta_i\braket{i|\Phi} \ket{\psi_i} \right\|\\
 	&\geq 0.
@@
 
-The Gram matrix allows us to reformulate the exclusion problem in a more abstract, basis-independent manner. Since $\mathcal{G}$ is Hermitian and positive semidefinite, it can be factorized as,
+Since $\mathcal{G}$ is Hermitian and positive semidefinite, it can be factorized as,
+
 \begin{align*}
@@
 \end{align*}
+
 for some matrix $X$, whose columns are the pure states,
+
 \begin{align*}
@@
 		\mid & \mid &        & \mid \\
-		\ket{\psi_1} & \ket{\psi_2} & \dots & \ket{\psi_n} \\
+		\sqrt{\eta_i}\ket{\psi_1} & \sqrt{\eta_2}\ket{\psi_2} & \dots & \sqrt{\eta_n}\ket{\psi_n} \\
 		\mid & \mid &        & \mid
@@
 \begin{align*}
-	X_{i,i} = \braket{\omega_i|\psi_i}.
+	X_{i,i} = \sqrt{\eta_i}\braket{\omega_i|\psi_i}.
 \end{align*}
 \footnote{Note that fixing the basis $\{\ket{\omega_i}\}_{i=1}^n$ uniquely determines the decomposition $\mathcal{G} = X^\dagger X$, and vice versa.}We define the POVM elements as projectors $\Pi_i = \ket{\omega_i}\bra{\omega_i}$.
-Then, for the ensemble $\{(\rho_i, \eta_i)\}_{i=1}^n$, the corresponding semidefinite program (\gls{sdp}) constraints become,
-\begin{align*}
-	\tr(\Pi_i \rho_i) &= \tr\left( \ket{\omega_i}\bra{\omega_i} \ket{\psi_i}\bra{\psi_i} \right) \\
-	&= |\braket{\omega_i|\psi_i}|^2 \\
+Then, for the ensemble $\{(\rho_i, \eta_i)\}_{i=1}^n$, the corresponding semidefinite program (\gls{sdp}) constrains become,
+\begin{align*}
+	\eta_i\tr(\Pi_i \rho_i) &= \eta_i\tr\left( \ket{\omega_i}\bra{\omega_i} \ket{\psi_i}\bra{\psi_i} \right) \\
+	&= |\sqrt{\eta_i}\braket{\omega_i|\psi_i}|^2 \\
 	&= |X_{i,i}|^2.
@@
 \begin{align*}
-	P_{\gls{me}}^e = \min_{X} &\sum_{i=1}^n \frac{|X_{i,i}|^2}{\eta_i}, \\
+	P_{\gls{me}}^e = \min_{X} &\sum_{i=1}^n |X_{i,i}|^2, \\
 	\text{subject to} \quad & X^\dagger X = \mathcal{G}, \quad X \geq 0.
@@
 \begin{align*}
-	P_{\gls{me}}^s = \max_{X} &\left( 1 - \sum_{i=1}^n \frac{|X_{i,i}|^2}{\eta_i} \right), \\
+	P_{\gls{me}}^s = \max_{X} &\left( 1 - \sum_{i=1}^n |X_{i,i}|^2 \right), \\
 	\text{subject to} \quad & X^\dagger X = \mathcal{G}, \quad X \geq 0.
@@
 
-Furthermore, we note that the case of arbitrary prior probabilities $\eta_i$ can be reduced to the equal prior case $\eta_i = \frac{1}{n}$ by defining non-normalized states,
-\begin{align*}
-	\ket{\tilde{\psi}_i} = \frac{1}{\sqrt{\eta_i}} \ket{\psi_i},
-\end{align*}
-and reformulating the problem in terms of these states.
-The prior probabilities are then absorbed into the state norm.
-Therefore, without loss of generality, in this project we will assume equal prior probabilities.
+%Furthermore, we note that the case of arbitrary prior probabilities $\eta_i$ can be reduced to the equal prior case $\eta_i = \frac{1}{n}$ by defining non-normalized states,
+%\begin{align*}
+%	\ket{\tilde{\psi}_i} = \frac{1}{\sqrt{\eta_i}} \ket{\psi_i},
+%\end{align*}
+%and reformulating the problem in terms of these states. The prior probabilities are then absorbed into the state norm.
 
@@
 
+As we have mentioned before, analytical results have been found for the exclusion task in both protocols \gls{me} and \gls{ze} for ensembles that exhibit a certain degree of symmetry\cite{MainPaper}, that is for \emph{group-generated} ensembles.
+In this section we present a proper definition for a group-generated ensemble as well as a brief discussion on this ensembles generated by a cyclic group, a key type of grop-generated ensembles in our analysis.
+
 Given a quantum state $\ket{\psi}$, referred to as the \emph{seed state}, we define a \emph{group generated ensemble} as the set of states obtained by applying a group of unitary transformations to $\ket{\psi}$.
-Specifically, if the ensemble consists of $n$ quantum states, its elements are of the form
+Specifically, if the ensemble consists of $n$ quantum states, its elements are of the form,
+
 \begin{align*}
@@
 \end{align*}
+
 where the set of unitary matrices $\{U_i\}_{i=1}^n$ forms a finite group under standard matrix multiplication. In terms of density matrices, the ensemble can equivalently be written as,
+
 \begin{align*}
@@
 \end{align*}
+
 where $\rho = \ket{\psi}\bra{\psi}$ is the density matrix corresponding to the seed state.
@@
 forms a group generated ensemble based on the cyclic group $\mathbb{Z}/n\mathbb{Z}$.
-This type of ensemble is of particular interest in our study and will be explored in more detail in a subsequent section.
-
-\emph{Example: The $\mathbb{Z}/n\mathbb{Z}$ group-generated ensemble}: Let $\mathcal{U} \in U(n)$ be an $n \times n$ unitary matrix satisfying $\mathcal{U}^n = \mathds{1}$, and let $\ket{\psi}$ be the seed state.
-The Gram matrix $\mathcal{G}^{\mathbb{Z}/n\mathbb{Z}}$ elements associated with the ensemble $\left\{\mathcal{U}^i\ket{\psi}\right\}_{i=0}^{n-1}$ are
-\begin{align*}
-	\mathcal{G}^{\mathbb{Z}/n\mathbb{Z}}_{i,j} = \braket{\mathcal{U}^i\psi | \mathcal{U}^j\psi} = \braket{\psi | \mathcal{U}^{j-i} | \psi} = \braket{\mathcal{U}^{j-i}}_{\psi},
-\end{align*}
+This type of ensemble is of particular interest in our study and will be explored in more detail at the end of this section.
+Additionally, in Appendix \ref{appendixComputationGroupGeneratedGramMatrices} we present a general procedure to compute the Gram Matrix for any group-generated ensemble.
+
+\subsubsection*{The $\mathbb{Z}/n\mathbb{Z}$ group-generated ensemble}
+
+Here we discuss the particular case for a $\mathbb{Z}/n\mathbb{Z}$ group-generated ensemble a key type of ensemble for our project.\footnote{The relevance of this type of ensembles relies on the fact that for a prime number of states, the possible group-generated group ensemble } Let $\mathcal{U} \in U(n)$ be an $n \times n$ unitary matrix satisfying $\mathcal{U}^n = \mathds{1}$, and let $\ket{\psi}$ be the seed state.
+The Gram matrix $\mathcal{G}^{\mathbb{Z}/n\mathbb{Z}}$ elements associated with the ensemble $\left\{\mathcal{U}^i\ket{\psi}\right\}_{i=0}^{n-1}$ are,
+\begin{align*}
+	\mathcal{G}^{\mathbb{Z}/n\mathbb{Z}}_{i,j} = \sqrt{\eta_i \eta_j}\braket{\mathcal{U}^i\psi | \mathcal{U}^j\psi} = \sqrt{\eta_i \eta_j}\braket{\psi | \mathcal{U}^{j-i} | \psi} = \sqrt{\eta_i \eta_j}\braket{\mathcal{U}^{j-i}}_{\psi},
+\end{align*}
+
 where we use the shorthand notation,
@@
 	\mathcal{G}^{\mathbb{Z}/n\mathbb{Z}} = \begin{pmatrix}
- 1 & \braket{\mathcal{U}}_{\psi} & \braket{\mathcal{U}^2}_{\psi} & \cdots & \braket{\mathcal{U}^{n-1}}_{\psi} \\
- \braket{\mathcal{U}^{n-1}}_{\psi}^* & 1 & \braket{\mathcal{U}}_{\psi} & \cdots & \braket{\mathcal{U}^{n-2}}_{\psi} \\
- \braket{\mathcal{U}^{n-2}}_{\psi}^* & \braket{\mathcal{U}^{n-1}}_{\psi}^* & 1 & \cdots & \braket{\mathcal{U}^{n-3}}_{\psi} \\
+ \eta_1 & \sqrt{\eta_1 \eta_2}\braket{\mathcal{U}}_{\psi} & \sqrt{\eta_1 \eta_3}\braket{\mathcal{U}^2}_{\psi} & \cdots & \sqrt{\eta_1 \eta_n}\braket{\mathcal{U}^{n-1}}_{\psi} \\
+ \sqrt{\eta_2 \eta_1}\braket{\mathcal{U}^{n-1}}_{\psi}^* & \eta_2 & \sqrt{\eta_2 \eta_3}\braket{\mathcal{U}}_{\psi} & \cdots & \sqrt{\eta_2 \eta_n}\braket{\mathcal{U}^{n-2}}_{\psi} \\
+ \sqrt{\eta_1 \eta_3}\braket{\mathcal{U}^{n-2}}_{\psi}^* & \sqrt{\eta_2 \eta_3}\braket{\mathcal{U}^{n-1}}_{\psi}^* & \eta_3 & \cdots & \sqrt{\eta_3 \eta_n}\braket{\mathcal{U}^{n-3}}_{\psi} \\
  \vdots & \vdots & \vdots & \ddots & \vdots \\
- \braket{\mathcal{U}}_{\psi}^* & \braket{\mathcal{U}^{2}}_{\psi}^* & \braket{\mathcal{U}^{3}}_{\psi}^* & \cdots & 1
+ \sqrt{\eta_1 \eta_n}\braket{\mathcal{U}}_{\psi} & \sqrt{\eta_2 \eta_n}\braket{\mathcal{U}^{2}}_{\psi} & \sqrt{\eta_3 \eta_n}\braket{\mathcal{U}^{3}}_{\psi} & \cdots & \eta_n
 \end{pmatrix}.
@@
 \begin{align*}
-	\mathcal{G}^{\mathbb{Z}/n\mathbb{Z}}_{\psi} = \begin{pmatrix}
- 1 & \braket{\mathcal{U}}_{\psi} & \braket{\mathcal{U}^{2}}_{\psi} & \hdots &  \braket{\mathcal{U}}_{\psi}^* \\
- \braket{\mathcal{U}}_{\psi}^* & 1 & \braket{\mathcal{U}}_{\psi} & \hdots &  \braket{\mathcal{U}^{2}}_{\psi}^* \\
- \braket{\mathcal{U}^{2}}_{\psi}^* & \braket{\mathcal{U}}_{\psi}^* & 1 & \hdots &  \braket{\mathcal{U}^{3}}_{\psi}^* \\
+	\mathcal{G}^{\mathbb{Z}/n\mathbb{Z}} = \begin{pmatrix}
+ \eta_1 & \sqrt{\eta_1 \eta_2}\braket{\mathcal{U}}_{\psi} & \sqrt{\eta_1 \eta_3}\braket{\mathcal{U}^2}_{\psi} & \cdots & \sqrt{\eta_1 \eta_n}\braket{\mathcal{U}}^*_{\psi} \\
+ \sqrt{\eta_2 \eta_1}\braket{\mathcal{U}}^*_{\psi} & \eta_2 & \sqrt{\eta_2 \eta_3}\braket{\mathcal{U}}_{\psi} & \cdots & \sqrt{\eta_2 \eta_n}\braket{\mathcal{U}}^*_{\psi} \\
+ \sqrt{\eta_1 \eta_3}\braket{\mathcal{U}^2}^*_{\psi} & \sqrt{\eta_2 \eta_3}\braket{\mathcal{U}}^*_{\psi} & \eta_3 & \cdots & \sqrt{\eta_3 \eta_n}\braket{\mathcal{U}}^*_{\psi} \\
  \vdots & \vdots & \vdots & \ddots & \vdots \\
- \braket{\mathcal{U}}_{\psi} & \braket{\mathcal{U}^{2}}_{\psi} & \braket{\mathcal{U}^{3}}_{\psi} & \hdots & 1 
+ \sqrt{\eta_1 \eta_n}\braket{\mathcal{U}}_{\psi} & \sqrt{\eta_2 \eta_n}\braket{\mathcal{U}^{2}}_{\psi} & \sqrt{\eta_3 \eta_n}\braket{\mathcal{U}^{3}}_{\psi} & \cdots & \eta_n
 \end{pmatrix}.
@@
 
-This shows the circulant structure of $\mathcal{G}$, where each row is a cyclic permutation of the previous one.
-In other words, the Gram matrices of $\mathbb{Z}/n\mathbb{Z}$-generated ensembles are circulant matrices.
+This shows the circulant structure of $\mathcal{G}$ for a equal prior probability case, where each row is a cyclic permutation of the previous one.
+In other words, the Gram matrices of $\mathbb{Z}/n\mathbb{Z}$-generated ensembles are circulant matrices when taking equal priors probabilities.
 This structure is particularly useful, as circulant matrices can be diagonalized by the discrete Fourier basis, greatly simplifying many computations~\cite{circulantMatrices}.
@@
 
-Moreover, we can compute the Gram matrix for any group-generated ensemble by using the Cayley table~\cite{CayleyTable}, also known as the \emph{multiplication table}, of the group.
-For example, consider the smallest non-commutative group, $S_3$, consisting of the symmetries and rotations of an equilateral triangle.
-Denoting the identity as $e$, the rotations elements as $s$, $s^2$ (one being the result of 2 times the other) and the symmetries $p$, $q$, and $r$, the Cayley table is,
-
-\begin{table}[H]
-	\centering
-	\caption{Cayley table of the $S_3$ group.}
-	\begin{tabular}{c||c c c c c c}
-        $S_3$ & $e$ & $s$ & $s^2$ & $p$ & $q$ & $r$ \\\hline\hline
-        $e$   & $e$ & $s$ & $s^2$ & $p$ & $q$ & $r$ \\
-        $s^2$ & $s^2$ & $e$ & $s$ & $r$ & $p$ & $q$ \\
-        $s$   & $s$ & $s^2$ & $e$ & $q$ & $r$ & $p$ \\
-        $p$   & $p$ & $r$ & $q$ & $e$ & $s^2$ & $s$ \\
-        $q$   & $q$ & $p$ & $r$ & $s$ & $e$ & $s^2$ \\
-        $r$   & $r$ & $q$ & $p$ & $s^2$ & $s$ & $e$
-    \end{tabular}
-\end{table}
-
-We now identify $S_3$ as a group of unitary matrices\footnote{We treat each group element as a unitary matrix, and the group operation as matrix multiplication.}.
-It follows that the Gram matrix of the $S_3$ group-generated ensemble is the matrix of expected values of the Cayley table entries with respect to the seed state $\ket{\psi}$.
-That is,
-\begin{align*}
-	\mathcal{G}^{S_3}_{\psi} = \begin{pmatrix}
-        1 & \braket{s}_\psi & \braket{s^2}_\psi & \braket{p}_\psi & \braket{q}_\psi & \braket{r}_\psi \\ 
-        \braket{s^2}_\psi & 1 & \braket{s}_\psi & \braket{r}_\psi & \braket{p}_\psi & \braket{q}_\psi \\
-        \braket{s}_\psi & \braket{s^2}_\psi & 1 & \braket{q}_\psi & \braket{r}_\psi & \braket{p}_\psi \\
-        \braket{p}_\psi & \braket{r}_\psi & \braket{q}_\psi & 1 & \braket{s^2}_\psi & \braket{s}_\psi \\
-        \braket{q}_\psi & \braket{p}_\psi & \braket{r}_\psi & \braket{s}_\psi & 1 & \braket{s^2}_\psi \\
-        \braket{r}_\psi & \braket{q}_\psi & \braket{p}_\psi & \braket{s^2}_\psi & \braket{s}_\psi & 1
-	\end{pmatrix}.
-\end{align*}
-Note that $\braket{e}_\psi = 1$ since $e = \mathds{1}$. Moreover, since $\mathcal{G}^{S_3}$ is Hermitian, we conclude:
-\begin{align*}
-\braket{p}_{\psi},\ \braket{q}_{\psi},\ \braket{r}_{\psi} \in \mathbb{R}, \quad \forall \ket{\psi} \in \mathcal{H},
-\end{align*}
-which implies the unitary matrices corresponding to the triangle symmetries $p$, $q$, and $r$ are Hermitian.
-As a matter of fact we know the eigenvalues of this matrices can only be $\pm 1$ and at least one of them must be $-1$.\footnote{Otherwise, they would be the identity and we know them to be different by construction.} This procedure generalizes to any finite group $G$, showing that computing the Cayley table is equivalent to computing the Gram matrix of the corresponding group-generated ensemble.
-
-Finally, we denote the cardinality of a finite group $G$ (i.e., the number of its elements) as $|G|$. In scenarios with uniform prior probabilities, this implies,
+Finally, we denote the cardinality of a finite group $G$, i.e. the number of its elements of the group, as $|G|$. In scenarios with uniform prior probabilities, this implies,
 \begin{align*}
@@
 \end{align*}
-\subsection{Dual Formulation of the Problem}
-
-It is often useful to consider the \emph{dual} version of a \gls{sdp} problem, as it provides both conceptual insights and practical advantages for verifying optimality.
-
-Consider the ensemble $\left\{ \left( \rho_i, \frac{1}{n} \right) \right\}_{i=1}^n$, where each state $\rho_i$ appears with uniform prior probability $1/n$.
-The dual SDP corresponding to the Minimum Error (\gls{me}) exclusion protocol, when expressed in terms of the error probability, is given by,
-\begin{align*}
-	\tilde{P}_{\gls{me}}^e = \max_{\Gamma} \quad & \tr{\Gamma} \\
-	\text{subject to} \quad & \frac{\rho_i}{n} - \Gamma \geq 0 \quad \forall i \in \{1, \dots, n\}, \\
-	& \Gamma^\dagger = \Gamma,
-\end{align*}
-where $\tilde{P}$ denotes the dual version of the problem.
-
-Similarly, the dual SDP for the success probability in the same protocol reads:
-\begin{align*}
-	\tilde{P}_{\gls{me}}^s = \min_{\Gamma} \quad & 1 - \tr{\Gamma} \\
-	\text{subject to} \quad & \frac{\rho_i}{n} - \Gamma \geq 0 \quad \forall i \in \{1, \dots, n\}, \\
-	& \Gamma^\dagger = \Gamma.
-\end{align*}
-
-\textcolor{blue}{Add the dual version for the zero error protocol.}
-
-In the case of the zero-error exclusion protocol, the dual SDP formulation becomes
-
-One of the primary uses of the dual formulation is in establishing optimality.
-If a POVM ansatz yields equal objective values for both the primal and dual problems, i.e., $P = \tilde{P}$, then strong duality holds and the measurement is guaranteed to be optimal.
-
-This duality principle not only provides a tool for verification but also suggests constructive approaches to discovering optimal measurements, especially in structured ensembles such as those generated by group actions.
 \subsection{Previous Results}\label{sectionPreviousResults}
@@
 Significant progress has been made in the study of the state exclusion task for group-generated ensembles.
-In particular, the work \emph{Quantum State Exclusion for Group-Generated Ensembles of Pure States}\cite{MainPaper} presents exact analytical expressions for the success and error probabilities under both the Minimum Error \gls{me} and Zero Error \gls{ze} exclusion protocols.
-
-Let $\mathcal{G}^G$ denote the Gram matrix of a group-generated ensemble $\left\{ \left( \rho_i, \frac{1}{|G|} \right) \right\}_{i=1}^{|G|}$, where $G$ is a finite group of size $|G|$, and let $\{\lambda_i\}_{i=1}^{|G|}$ be the set of eigenvalues of $\mathcal{G}^G$.
-Assume the eigenvalues are ordered increasingly,
+In particular, the work \emph{Quantum State Exclusion for Group-Generated Ensembles of Pure States}\cite{MainPaper} presents exact analytical expressions for the success and error probabilities under both the Minimum Error (\gls{me}) and Zero Error (\gls{ze}) exclusion protocols.
+In this section we present this results and comment some key aspects of this results regarding our project, in particular we present the concept of \emph{perfect exclusion region} and we discuss the case of ensembles with a prime number of states.
+
+Let $\mathcal{G}^G$ denote the Gram matrix of a group-generated ensemble $\left\{ \left( \rho_i, \frac{1}{|G|} \right) \right\}_{i=1}^{|G|}$, where $G$ is a finite group of size $|G|$, and let $\{\lambda_i\}_{i=1}^{|G|}$ be the set of eigenvalues of $\mathcal{G}^G$, the Gram Matrix of the group.
+Assume the eigenvalues $\left\{\frac{\lambda_i}{|G|}|1\leq i \leq n\right\}$ are ordered increasingly,
 \begin{align*}
@@
 \end{align*}
-i.e., $\lambda_1$ is the smallest and $\lambda_{|G|}$ the largest eigenvalue.
+i.e., $\frac{\lambda_1}{|G|}$ is the smallest and $\lambda_{|G|}$ the largest eigenvalue.
+Notice that since we are in the equal probability scenario, we can factor out a $\frac{1}{|G|}$ factor from the Gram Matrix and consider the matrix $|G|\mathcal{G}^G$ instead of $\mathcal{G}^G$, i.e.
+the eigenvalues of this matrix simply are $\left\{\lambda_i\right\}_{i=1}^n$.
+This is a standard choice for simplicity, when we dealing with equal prior probabilities.
 
@@
 A key feature of these results is their independence from the specific group generating the ensemble.
-That is, for any two group-generated ensembles $A$ and $B$ corresponding to groups $G_A$ and $G_B$ (with $G_A \neq G_B$ but $|G_A| = |G_B|$), if their respective Gram matrices $\mathcal{G}^{G_A}$ and $\mathcal{G}^{G_B}$ share the same eigenvalues, then the exclusion probabilities for both \gls{me} and \gls{ze} protocols are identical.
+That is, for any two group-generated ensembles $A$ and $B$ corresponding to groups $G_A$ and $G_B$, with $G_A \neq G_B$ but $|G_A| = |G_B|$, if their respective Gram matrices $\mathcal{G}^{G_A}$ and $\mathcal{G}^{G_B}$ share the same eigenvalues, then the exclusion probabilities for both \gls{me} and \gls{ze} protocols are identical.
 This group-independence property is a cornerstone of the present study.
@@
 
-\subsection{Limit Case Scenarios}\label{sectionLimitCaseScenarios}
-
-Let us study the Gram matrix of a limit ensemble composed of $n$ identical quantum states (i.e., the same state is repeated $n$ times in the ensemble).\footnote{This case may appear paradoxical, since there is no way to distinguish between identical states.
-Nevertheless, we present it as a limiting scenario.} The Gram matrix reads:
-\begin{align*}
-	\mathcal{G}^{\text{limit}} = \begin{pmatrix}
- 1 & 1 & \cdots & 1 \\
- 1 & 1 & \cdots & 1 \\
- \vdots & \vdots & \ddots & \vdots \\
- 1 & 1 & \cdots & 1 \\
-\end{pmatrix}.
-\end{align*}
-
-The eigenvalues of this matrix are:
-\begin{align*}
-	\lambda_n &= n, \\
-	\lambda_{n-1} &= 0, \\
-	\vdots \\
-	\lambda_1 &= 0.
-\end{align*}
-
-Clearly, this set of eigenvalues does not satisfy Eq.
-(\ref{equationPerfectExclusionCondition}), i.e., we are in the non-perfect exclusion regime.
-In fact, we can interpret this ensemble as a group-generated ensemble from the \emph{trivial group},\footnote{The trivial group is the group consisting solely of the neutral/identity element.} which generates no variation.
-
-Thus, the success and error probabilities for both the \gls{me} protocol is,
-\begin{align*}
-	P_{\gls{me}}^e =& \frac{1}{n},\\
-	P_{\gls{me}}^s =& \frac{n-1}{n}.
-\end{align*}
-
-The intuition behind this result is clear.
-If there is no physical way to distinguish between states, the exclusion must be made randomly, with uniform probability.
-This observation also extends naturally to \gls{qsd}.
-
-Since this is a limiting case scenario, the success probability for \gls{qse} must be strictly greater than $\frac{n-1}{n}$ (i.e., the error probability must be less than $\frac{1}{n}$) and for \gls{qsd} the success probabilities must be strictly greater than $\frac{1}{n}$ (i.e., the error probability must be less than $\frac{n-1}{n}$)\footnote{In this case scenario the discrimination task is the counterpart of the exclusion task.}.
-Notice this result holds only for the \gls{me} protocol.
-Otherwise, since the exclusion cannot be accomplished without ambiguity, the successfull exclusion probability for the \gls{ze} protocol is 0 for either \gls{qse} or \gls{qsd} (i.e., the error exclusion probability is 1),
-\begin{align*}
-	P_{\gls{ze}}^e =& 1,\\
-	P_{\gls{ze}}^s =& 0.
-\end{align*}
-
-The opposite limiting case is an ensemble of $n$ orthogonal quantum states $\{\rho_i\}_{i=1}^{n}$. In this case, the Gram matrix becomes the identity,
-\begin{align*}
-	\mathcal{G} = \mathds{1}.
-\end{align*}
-
-Under these conditions, both \gls{qse} and \gls{qsd} are trivial, as the states form an orthonormal basis. In particular, in the space spanned by these states, we have,
-\begin{align*}
-	\sum_{i=1}^{n} \rho_i = \mathds{1},
-\end{align*}
-which means that the set $\{\rho_i\}$ is itself a \gls{povm}.
-The measurement corresponding to this \gls{povm} allows perfect identification (or exclusion), hence both \gls{qse} and \gls{qsd} can be performed without error.
-
-\subsection{Ensembles with a Prime Number of Elements}\label{sectionEnsemblesWithPrime}
-
-As previously discussed, analytical solutions have been found for the exclusion task under both the \gls{me} and \gls{ze} protocols.
-These solutions depend solely on the eigenvalues of the Gram matrix and are independent of the specific group structure generating the ensemble.
-
-Let the Gram matrix of an ensemble decompose as,
+Furthermore, we might highlight a key aspect of the analytical solutions for the \gls{qse} task form \gls{me} and \gls{ze} protocols.
+These results depend solely on the eigenvalues of the Gram matrix and are independent of the specific group structure generating the ensemble.
+Hence, let the Gram matrix of an ensemble decompose as,
 \begin{align*}
@@
 
-In the non-perfect exclusion regime, the analytical results for group-generated ensembles provide lower bounds on the success probabilities (and upper bounds on the error probabilities) for general ensembles.
+In the non-perfect exclusion regime, the analytical results for group-generated ensembles provide lower bounds on the success probabilities, and upper bounds on the error probabilities for general ensembles.
 
 Consider, for example, the case of an ensemble of 4 quantum states.
-There are exactly two groups of four elements: $\mathbb{Z}/4\mathbb{Z}$ and $\mathbb{Z}/2\mathbb{Z} \times \mathbb{Z}/2\mathbb{Z}$.\footnote{These are the only non-isomorphic groups of order 4.} This implies that there exist two specific unitary matrices, $U_{\mathbb{Z}/4\mathbb{Z}}$ and $U_{\mathbb{Z}/2\mathbb{Z} \times \mathbb{Z}/2\mathbb{Z}}$ (up to permutation of rows and columns), for which the analytical solution holds exactly.
+There are exactly two groups of four elements, $\mathbb{Z}/4\mathbb{Z}$ and $\mathbb{Z}/2\mathbb{Z} \times \mathbb{Z}/2\mathbb{Z}$.\footnote{These are the only non-isomorphic groups of order 4.} This implies that there exist two specific unitary matrices, $U_{\mathbb{Z}/4\mathbb{Z}}$ and $U_{\mathbb{Z}/2\mathbb{Z} \times \mathbb{Z}/2\mathbb{Z}}$ (up to permutation of rows and columns), for which the analytical solution holds exactly.
 
 Since $U(n)$ is compact, and assuming continuity of the exclusion probabilities with respect to $U$ under a given matrix norm, for each of these unitary matrices there exist arbitrarily small neighborhoods $\mathcal{B}(U_{\mathbb{Z}/4\mathbb{Z}})$ and $\mathcal{B}(U_{\mathbb{Z}/2\mathbb{Z} \times \mathbb{Z}/2\mathbb{Z}})$ such that the exclusion probabilities within these neighborhoods approximate the analytical result as closely as desired.
-However, the existence of multiple such matrices (and intersecting neighborhoods) can complicate numerical optimization and analysis.
+However, the existence of multiple such matrices, and intersecting neighborhoods, can complicate numerical optimization and analysis.
 
 In contrast, it is usefull to consider the case where the ensemble contains a prime number $p$ of states.
-In this scenario, the situation simplifies considerably, since there exists only one group (up to isomorphism) of order $p$, namely $\mathbb{Z}/p\mathbb{Z}$.
+In this scenario, the situation simplifies considerably, since there exists only one group, up to isomorphism, of order $p$, namely $\mathbb{Z}/p\mathbb{Z}$.
 
 This result follows immediately from Lagrange's theorem.
-The theorem guarantees that the order of any element in a finite group\footnote{The order of an element $\tau$ in a group $G$ is the smallest positive integer $m$ such that $\tau^m = e$, where $e$ denotes the identity/neutral element of the group.} must divide the order of the group.
+The theorem guarantees the order of any element in a finite group\footnote{The order of an element $\tau$ in a group $G$ is the smallest positive integer $m$ such that $\tau^m = e$, where $e$ denotes the identity/neutral element of the group.} must divide the order of the group.
 Since $p$ is a prime number, the only positive integers dividing $p$ are either $1$ or $p$ itself.
@@
 
-Ensembles of prime cardinality are thus of particular interest and will be further explored in the Results and Discussion section. \textcolor{blue}{Add reference to Results section}
-\section{Methodology}
+Ensembles containing a prime number of states are of particular interest, as the analytical result can be guaranteed to be exact for only one specific ensemble.
+Consequently, when interpreting the results for the case of generic ensembles in the following sections we can be ensure the analytical result is exact in only one instance.
+Moreover, there is no overlap with other Gram matrices for which the result would also hold exactly.
+
+\newpage
+\section{Methodology}\label{sectionMethodology}
 
 All the code used in this project is hosted in the GitHub repository \cite{GitHub}, where additional documentation is available detailing the functionality and structure of each script and class involved in the implementation.
-
-\subsection{\gls{sdp} Solver}
+The numerical analysis is performed by generating ensembles uniformly distributed taking into account all possibilities and then solving the \gls{sdp} problems presented in Section \ref{sectionFormulationOfTheProblem}.
 
@@
 
-\subsection{Generation of Random Gram Matrices}
-
 To analyze both group-generated and generic quantum state ensembles, we developed a method for generating random Gram matrices with prescribed spectral properties.
@@
 \begin{align*}
-	\sum_{i=1}^n \lambda_i = n.
+	\sum_{i=1}^n \lambda_i = 1.
 \end{align*}
@@
 
+This aspect is crucial: if the random generation of unitary matrices did not uniformly cover U(n), the numerical analysis would be fundamentally flawed.
+It would lead to an overrepresentation of certain types of ensembles, potentially missing rare or atypical configurations.
+As a result, ensembles that might violate the theoretical lower bound could be systematically avoided, rendering the conclusions of the analysis unreliable.
+
 In the case of a group-generated ensemble, we restrict ourselves to ensembles generated by the cyclic group $\mathbb{Z}/n\mathbb{Z}$.
@@
 
-\section{Results and Discussion}
-
-Let us analyze the case of a $\mathbb{Z}/3\mathbb{Z}$ ensemble. The Gram matrix in this case takes the form,
-\begin{align*}
-	\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}=\begin{pmatrix}
+\newpage
+\section{Results and Discussion}\label{sectionResultsAndDiscussion}
+
+The begining of the analysis consists in showing up the key differences between \gls{me} and \gls{ze} protocols, and the concordance of the \gls{sdp}'s numerical results with the analytical results given in \ref{sectionPreviousResults}.
+
+The case of ensembles conformed by 3 states is one of the main objects of study, that is because it is the only ensemble that we can entirely represent 2 dimensional plots with.
+In orther to show up this fact, let us analyze the case of a $\mathbb{Z}/3\mathbb{Z}$ ensemble for equal priors probabilities.
+The Gram matrix in this case takes the form,
+
+\begin{align*}
+	\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}=\frac{1}{3}\begin{pmatrix}
 		1 & c & c^*\\
@@
 \end{align*}
+
 with $c \in \mathbb{C}$.
@@
 
-Since 3 is a prime number, the only group of order 3 is $\mathbb{Z}/3\mathbb{Z}$, as discussed in Section (\ref{sectionEnsemblesWithPrime}). The Gram matrix can be diagonalized as,
+Since 3 is a prime number, the only group of order 3 is $\mathbb{Z}/3\mathbb{Z}$, as discussed in Section (\ref{sectionLimitCaseScenarios}). The Gram matrix can be diagonalized as,
 \begin{align*}
@@
 where $U_{\mathbb{Z}/3\mathbb{Z}}$ is the unitary matrix with Fourier basis vectors as columns.
-The eigenvalues of the matrix are denoted as $\{\lambda_1,\lambda_2,\lambda_3\}$ with $\lambda_1 \leq \lambda_2 \leq \lambda_3$.
+The eigenvalues of the simplified matrix, i.e.
+$3\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}$ matrix are denoted as $\{\lambda_1,\lambda_2,\lambda_3\}$ with $\lambda_1 \leq \lambda_2 \leq \lambda_3$.
 Since,
 \begin{align*}
-	\tr(\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}) = \tr(D) = \sum_{i=1}^3 \lambda_i = 3
-\end{align*}
+	\sum_{i=1}^3 \lambda_i = 3
+\end{align*}
+
 we again find only two \glspl{dof}, consistent with our earlier parameterization. Furthermore, since $\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}} \geq 0$, we have,
+
 \begin{align*}
@@
 
-\subsection{Comparison \gls{qsd} vs. \gls{qse}, and \gls{me} vs. \gls{ze}}
-
-We first present results for the Quantum State Discrimination (\gls{qsd}) task to motivate the problem and highlight contrasts with the Quantum State Exclusion (\gls{qse}) task, which is the focus of this study.
+\subsection{Comparison \gls{me} vs. \gls{ze}}
+
+Here we present a comparison between both protocols for \gls{ze} and \gls{me} giving insights on the protocols's essence and contextualising the problem in a visual way.
+
+In Figure (\ref{FigureQSEMEZ3ZHeatmap})  we presents the \gls{me} (left) and \gls{ze} (right) protocols results for the \gls{qse} task.
+In particular Figure (\ref{FigureQSEMEZ3ZHeatmap}) shows two heatmaps of the average successful exclusion probability under the Minimum Error (\gls{me}) protocol for a $\mathbb{Z}/3\mathbb{Z}$ group-generated ensemble.
+Probabilities are shown as functions of the modulus $|c|$ ($x$-axis) and phase $\theta$ ($y$-axis) of the overlap $c=|c|^{i\theta}$, which fully determine the Gram matrix.
+Notice we take equal prior probabilities, as discussed in the analytical results in Section (\ref{sectionPreviousResults}).
 
@@
 	\centering
-	\begin{overpic}[width=0.5\textwidth, trim={2.3cm 0.8cm 4.5cm 2cm}, clip]{../Plots/DiscriminationOverlapVSPhaseVSMinimumErrorProbabilityZ3HeatMap.pdf}
+	\begin{overpic}[width=0.49\textwidth, trim={2.3cm 0.8cm 4.3cm 2cm}, clip]{../Plots/ExlusionOverlapVSPhaseVSMinimumErrorProbabilityZ3HeatMap.pdf}
 		\put(60,25){$\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}<0$}
@@
 	\end{overpic}
-	\caption{Heatmap of the success probability for minimum error (\gls{me}) quantum state discrimination for a $\mathbb{Z}/3\mathbb{Z}$ group-generated ensemble.}
-	\label{FigureQSDMEZ3ZHeatmap}
-\end{figure}
-
-Figure (\ref{FigureQSDMEZ3ZHeatmap}) shows a heatmap of the average successful discrimination probability under the Minimum Error (\gls{me}) protocol for a $\mathbb{Z}/3\mathbb{Z}$ group-generated ensemble.
-Probabilities are shown as functions of the modulus ($x$-axis) and phase ($y$-axis) of the overlap $c$, which fully determine the Gram matrix.
-We assume equal prior probabilities, as generalization to arbitrary priors is discussed in Section (\ref{sectionGramMatrixFormulation}).
-Note, equal priors are presuposed throughout this work unless stated otherwise.
-
-The colorless regions correspond to parameters where $\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}$ is not positive semi-definite, and leading up yo non-valid Gram matrices, since positive semi-definition is inherent to a Gram matrix.
-
-In these conditions, the \gls{srm}\footnote{Also known as the Pretty Good Measurement.} is optimal, i.e.
-the result of the \gls{sdp} matches the one obtained from the \gls{sdp} in \gls{me} protocol.
-In particular, the \gls{srm} is obtained from the square root decomposition of the Gram matrix,
-\begin{align*}
-	\mathcal{G} = S^\dagger S = S^2
-\end{align*}
-and is the standard in \gls{qsd} under the \gls{me} protocol \cite{OptimalitySRM}.
-From section (\ref{sectionGramMatrixFormulation}) we know the success probability for a successful discrimination with \gls{srm} reeds,
-\begin{align*}
-	P_{\gls{srm}}^s=\frac{1}{n}\sum_{i=0}^nS_{i,i}^2
-\end{align*}
-were $S_{i,i}$ denotes the diagonal elements of $S$ and $n$ the number of quantum states\footnote{In this case we are taking $n=3$.}.
-
-As expected, no ensemble yields a success probability below $1/3$, consistent with the discussion in Section (\ref{sectionLimitCaseScenarios}).
-Moreover, as the modulus of the overlap approaches zero, the success probability approaches one, corresponding to orthogonal states, again matching expectations.
-
-Figure (\ref{FigureQSDZEZ3ZHeatmap}) shows analogous results for the Zero Error (\gls{ze}) protocol under the same conditions.
-
-\begin{figure}[H]
-	\centering
-	\begin{overpic}[width=0.5\textwidth, trim={2.3cm 0.8cm 4.5cm 2cm}, clip]{../Plots/DiscriminationOverlapVSPhaseVSSuccessProbabilityZeroErrorZ3HeatMap.pdf}
+		\begin{overpic}[width=0.49\textwidth, trim={2.3cm 0.8cm 4.5cm 2cm}, clip]{../Plots/ExlusionOverlapVSPhaseVSZeroErrorProbabilityZ3HeatMap.pdf}
 		\put(60,25){$\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}<0$}
@@
 	\end{overpic}
-	\caption{Heatmap of the success probability for zero-error (\gls{ze}) quantum state discrimination for a $\mathbb{Z}/3\mathbb{Z}$ group-generated ensemble.}
-	\label{FigureQSDZEZ3ZHeatmap}
+	\caption{Heatmap of the success probability for Minimum Error (\gls{me}) (left) and Zero Error (\gls{ze}) (right) quantum state exclusion in a $\mathbb{Z}/3\mathbb{Z}$ ensemble with equal prior probabilities.}
+	\label{FigureQSEMEZ3ZHeatmap}
 \end{figure}
 
-Both limiting behaviors remain valid.
-However, the \gls{ze} success probabilities are lower than those of the \gls{me} protocol.
-This is explained by the stricter constraints imposed in the \gls{ze} scenario, where $\tr(\Pi_i\rho_i) = 0$ is enforced for all POVM elements except one.
+The colorless regions correspond to parameters where $\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}$ is not positive semi-definite, and leading up to non-valid Gram matrices, since positive semi-definition is inherent to a Gram matrix.
+
+At this stage, we have developed some intuition behind these results.
+Consider an ensemble of highly similar quantum states.
+When the modulus of the overlap between any two states in the ensemble is given by $|\braket{\psi_i|\psi_j}|^2 = |c|,$ and $|c| \to 1$, the states become nearly indistinguishable.
+In this limiting case, the ensemble effectively consists of identical states.\footnote{One might argue this ensemble corresponds to a group-generated ensemble from the trivial group.}
+
+Since all the states are approximately the same, it becomes impossible to distinguish between them.
+The best approach we can take is to guess randomly.
+Consequently, the probability of correctly excluding a state different from the actual (unknown) target state by random guessing is $\frac{n - 1}{n}$.
+In this case, when $n = 3$, this probability is $\frac{2}{3}$.
+Therefore, in this limit, this is the best achievable performance, and the success probability for the Minimum Error (\gls{me}) exclusion protocol is $\frac{2}{3}$.
+
+On the other hand, since the states are indistinguishable, we can never be certain that the excluded state is not the unknown target state.
+Thus, the probability of successful exclusion in the Zero Error (\gls{ze}) protocol is $0$, i.e.
+we cannot perform unambiguous exclusion.
+
+A more detailed analytical discussion is provided in Appendix~\ref{sectionLimitCaseScenarios}, where we explore this limiting case by computing the Gram matrix and connecting the analytical results to the intuitive arguments presented here.
+
+Thus, we observe this intuition clearly corresponds to the results from Figure (\ref{FigureQSEMEZ3ZHeatmap}).
+For the limit case scenario of $|c|=1$ in the \gls{me} protocol we can never do better than taking a random guess, i.e.
+the probabilities spectrum consists in the interval $[\frac{2}{3},1]$.
+Notice this random exclusion procedure only remains valid for the equal prior probabilities case, if we want to extend this idea to a generic ensemble the best approach can take is a random exclusion with different probabilities.
+In particular if the state $\rho_i$ has a prior probability of $\eta_i$ we exclude the state $\rho_i$ state with a probability of $\eta_i$.
+All in all the final $P_{\gls{me}}^s$ is the same in the equal and non-equal prior probabilities i.e.
+$\frac{2}{3}$.
+
+Still, the \gls{ze} success probabilities always remain under those of the \gls{me} protocol.
+This is explained by the stricter constraints imposed in the \gls{ze} scenario, where $\tr(\Pi_i\rho_i) = 0$ is enforced for all \gls{povm} elements except one.
 Notice both probabilities are computed in a completely symmetric way,
@@
 
-Nevertheless, in the \gls{ze} case we enforce $\tr{(\Pi_i\rho_i)}=0$ for all the \glspl{povm} except one.
+Nevertheless, in the \gls{ze} case we enforce $\tr{(\Pi_i\rho_i)}=0$ for all the \glspl{povm} except one\footnote{Naturally the \gls{povm} that is not enforced to be orthogonal is the one that yields to an inconclusive result, i.e.
+$\Pi_?$.}.
 Thus, the system is more constrained in the \gls{ze} protocol, then the optimization of the probability cannot be performed up to the same point as in the \gls{me} protocol.
@@
 
-Figure (\ref{FigureQSDMEZESRM}) compares the performance of the ME, ZE, and SRM protocols.
+%At this stage we have some intuition behind this results.
+If we have an ensemble of similar states, the overlap's modulus of two states, i.e.
+$|\braket{\psi_i|\psi_j}|^2=c$, will tend to 1.
+In this limit case scenario we are dealing with ensembles conformed by the same state\footnote{In some way one might argue this is a grup-generated ensemble from the trivial group.}.
+Hence, since we are dealing with the same state there is no actual way to distinguish between them and we cannot do any better than guessing randomly.
+Thus the probability of discarding a state different from the target state taking by doing a random guess is $\frac{n-1}{n}$, in particular, for $n=3$ we have this probability being $\frac{2}{3}$.
+Hence in the limit case scenario this is the better we can do and the outcome of the state \gls{me} protocol for the probability of a successful exclusion is $\frac{2}{3}$.
+Additionally, we can never ensure we have discarded a different state state from our unknown state, hence, the probability for the successful exclusion for the \gls{ze} protocol is 0, i.e.
+we can not exclude without unambiguity.
+A much deeper analytical discussion is provided in appendix \ref{sectionLimitCaseScenarios}, where we take discuss this limit case scenarios computing the Gram Matrix and we connect with the analytical resutls the previous results.
+
+%Furthermore the results of the ZE protocol for \gls{qse} are shown in Figure (\ref{FigureQSEZEZ3ZHeatmap}).
+
+%\begin{figure}[H]
+%	\centering
+%	\begin{overpic}[width=0.5\textwidth, trim={2.3cm 0.8cm 4.5cm 2cm}, clip]{../Plots/ExlusionOverlapVSPhaseVSZeroErrorProbabilityZ3HeatMap.pdf}
+%		\put(60,25){$\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}<0$}
+%		\put(60,55){$\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}<0$}
+%	\end{overpic}
+%	\caption{Heatmap of the success probability for zero-error (\gls{ze}) quantum state exclusion in a $\mathbb{Z}/3\mathbb{Z}$ ensemble.}
+%	\label{FigureQSEZEZ3ZHeatmap}
+%\end{figure}
 
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{../Plots/DiscriminationOverlapVSSucessProbabilitySDPvsSRMZnOverlap3Phase0.pdf}
-	\caption{Comparison of successful discrimination probabilities for ME, ZE, and SRM protocols in a $\mathbb{Z}/3\mathbb{Z}$ ensemble impossing phase=$0$.}
-	\label{FigureQSDMEZESRM}
-\end{figure}
-
-As expected, perfect discrimination is only achieved when the overlap is zero (orthogonal states), and the \gls{srm} success probability matches the one obtained from the numerical \gls{sdp}.
-This highlights the motivation behind the study of \gls{qse}, which allows for perfect exclusion in cases where discrimination is impossible.
-
-Figure (\ref{FigureQSEMEZ3ZHeatmap}) presents the ME protocol results for the \gls{qse} task, analogous to Figure (\ref{FigureQSDMEZ3ZHeatmap}).
-Furthermore the results of the ZE protocol for \gls{qse} are shown in Figure (\ref{FigureQSEZEZ3ZHeatmap}).
-
-\begin{figure}[H]
-	\centering
-	\begin{overpic}[width=0.5\textwidth, trim={2.3cm 0.8cm 4.5cm 2cm}, clip]{../Plots/ExlusionOverlapVSPhaseVSMinimumErrorProbabilityZ3HeatMap.pdf}
-		\put(60,25){$\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}<0$}
-		\put(60,55){$\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}<0$}
-	\end{overpic}
-	\caption{Heatmap of the success probability for minimum error (\gls{me}) quantum state exclusion in a $\mathbb{Z}/3\mathbb{Z}$ ensemble.}
-	\label{FigureQSEMEZ3ZHeatmap}
-\end{figure}
-
-\begin{figure}[H]
-	\centering
-	\begin{overpic}[width=0.5\textwidth, trim={2.3cm 0.8cm 4.5cm 2cm}, clip]{../Plots/ExlusionOverlapVSPhaseVSZeroErrorProbabilityZ3HeatMap.pdf}
-		\put(60,25){$\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}<0$}
-		\put(60,55){$\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}<0$}
-	\end{overpic}
-	\caption{Heatmap of the success probability for zero-error (\gls{ze}) quantum state exclusion in a $\mathbb{Z}/3\mathbb{Z}$ ensemble.}
-	\label{FigureQSEZEZ3ZHeatmap}
-\end{figure}
-
-\begin{figure}[H]
-	\centering
-	\begin{overpic}[width=0.5\textwidth, trim={2.3cm 0.8cm 2.5cm 2cm}, clip]{../Plots/ExlusionOverlapVSPhaseVSPerfectExclussionZoneZ3BinaryHeatMap.pdf}
+	\begin{overpic}[width=0.49\textwidth, trim={2.3cm 0.8cm 2.5cm 2cm}, clip]{../Plots/ExlusionOverlapVSPhaseVSPerfectExclussionZoneZ3BinaryHeatMap.pdf}
 		\put(70,27){$\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}<0$}
@@
 	\end{overpic}
-	\caption{Perfect exclusion zone for a $\mathbb{Z}/3\mathbb{Z}$ ensemble in terms of the overlap's modulus and phase.}
+		\includegraphics[width=0.49\textwidth]{../Plots/ExclusionOverlapVSSucessProbabilitySDPvsSRMZnOverlap3Phase0.pdf}
+	\caption{Plot of the successful exclusion probabilities for the \gls{sdp} results for the \gls{me}, \gls{ze} protocols in a $\mathbb{Z}/3\mathbb{Z}$ ensemble impossing phase=$0$ as well as the results given by the analytical expressions (left).
+Perfect exclusion zone for a $\mathbb{Z}/3\mathbb{Z}$ ensemble in terms of the overlap's modulus and phase (right).}
+	%\caption{Perfect exclusion zone for a $\mathbb{Z}/3\mathbb{Z}$ ensemble in terms of the overlap's modulus and phase.}
 	\label{FigureQSEMEZ3ZPerfectExclusion}
@@
 
-Again, the ZE protocol yields lower probabilities due to its constraints and the limit case scenarios match with the previos discussion in Section (\ref{sectionLimitCaseScenarios}).
-However, crucially, perfect exclusion is possible even when perfect discrimination is not, in this regime seems to correspond to the ensembles such that the modulus of the overlap between two ensembles do not overtakes $\frac{1}{2}$.
+Crucially, we observe perfect exclusion is possible even when perfect discrimination is not \footnote{See section Comparison \gls{qsd} VS.
+\gls{qse} (\ref{appendixComparisonQSDvsQSE})}, in this regime seems to correspond to the ensembles such that the modulus of the overlap between two ensembles do not overtakes $\frac{1}{2}$.
 Nevertheless, this description is purely observational, we will give a better description in Section (\ref{sectionPerfectExclusionRegimeAndGeneralEnsembles}).
-
-Notice Figure (\ref{FigureQSEMEZ3ZPerfectExclusion}) highlights the regions where perfect exclusion is achieved, even outside the perfect discrimination regime.
-
-This property of \gls{qse} is a major motivation for its study.
-For example, in a regime where perfect exclusion is possible, having access to multiple copies of a target state enables hybrid exclusion-discrimination protocols that can outperform purely discriminative strategies.
-Even partial information, such as the exclusion of a single quantum state, has value in certain quantum information theories.
-These features make \gls{qse} a fertile ground for further theoretical and applied research.
-
-In Figure (\ref{FigureQSEMEZESRM}) we present de dependency on the modulus of the overlap in the $\mathbb{Z}/3\mathbb{Z}$ group-generated ensemble impossing the phase being equal to 0.
+In Figure (\ref{FigureQSEMEZ3ZPerfectExclusion}) (left) we highlight the regions where perfect exclusion is achieved, i.e.
+the red zone, even outside the perfect discrimination regime.
+Notice this regime appears in both protocols \gls{ze} and \gls{me}.
+
+In Figure (\ref{FigureQSEMEZ3ZPerfectExclusion}) (right) we present de dependency on the modulus of the overlap in the $\mathbb{Z}/3\mathbb{Z}$ group-generated ensemble impossing the phase being equal to 0.
 The result is analogous to Figure (\ref{FigureQSDMEZESRM}) but in the exclusion task.
-The existence existence of the perfect exclusion zone appears in overlap values between 0 and $\frac{1}{2}$.
+The existence of the perfect exclusion zone appears in overlap values between 0 and $\frac{1}{2}$.
+
+%\begin{figure}[H]
+%	\centering
+%	\includegraphics[width=0.49\textwidth]{../Plots/ExclusionOverlapVSSucessProbabilitySDPvsSRMZnOverlap3Phase0.pdf}
+%	\caption{Plot of the successful exclusion probabilities for the \gls{sdp} results for the \gls{me}, \gls{ze} protocols in a $\mathbb{Z}/3\mathbb{Z}$ ensemble impossing phase=$0$ as well as the results given by the analytical expressions.}
+%	\label{FigureQSEMEZESRM}
+%\end{figure}
+
+We highlight the good performance of the \gls{me} protocol up to limit values were the result tends to $\frac{2}{3}$ when the ensemble is made of indistingible states (i.e. the same state).
+
+\subsection{The perfect exclusion regime and general ensembles}\label{sectionPerfectExclusionRegimeAndGeneralEnsembles}
+
+In this section, we present the results for ensembles generated by the group $\mathbb{Z}/3\mathbb{Z}$, analyzed across the spectrum of eigenvalues, i.e.
+the analogus results from the previos section in the eigenvalues spectum.
+We also explicitly show the conditions for perfect exclusion, we give a proper analysis of this regime, and provide an initial exploration of the results for general ensembles being low bounded by the group-generated results of three quantum states.
+
+Although the \emph{Overlap modulus - phase} spectrum might seem as the most intuituve representation, the spectrum of Gram's matrix eigenvalues results the most appropriate representation for the perfect exclusion zone as well as the discussion and its comparison for general ensembles.
+Carrying on with the previos discussion, one can check the two \gls{dof} now appear as two of the eigenvalues.
+In the Figure (\ref{FigureQSEMEZ3ZEigenValues}) the results for the exclusion task under the \gls{me} protocol (left) and \gls{ze} protocol (right) for the $\mathbb{Z}/3\mathbb{Z}$ group-generated ensemble are represented.
+The axis represent two of the eigenvalues of the Gram matrix and a heatmap presents the probability for a perfect exclusion in the given conditions.
 
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{../Plots/ExclusionOverlapVSSucessProbabilitySDPvsSRMZnOverlap3Phase0.pdf}
-	\caption{Plot of the successful exclusion probabilities for the \gls{sdp} results for the \gls{me}, \gls{ze} protocols in a $\mathbb{Z}/3\mathbb{Z}$ ensemble impossing phase=$0$ as well as the results given by the analytical expressions.}
-	\label{FigureQSEMEZESRM}
-\end{figure}
-
-We highlight the good performance of the \gls{me} protocol up to limit values were the result tends to $\frac{2}{3}$ when the ensemble is made of indistingible states (i.e.
-the same state).
-Naturally everything matches with the previos observations and discussions.
-
-Moreover, the results in \gls{qse} are substancially better, the exclusion can be performed with higher precission than the discrimination.
-This observations is expected.
-Let us suppose we perform a correct guess in the discrimination of our target state, then if we know to which state is correlated our target state, we know which states is not correlated to, in other words
-\begin{align*}
-	\text{correct discrimination}\Rightarrow\text{correct exclusion}.
-\end{align*}
-However, let us suppose we perform a correct guess in the exclusion task, still we are ignoring which is our target state, then,
-\begin{align*}
-	\text{correct exclusion}\nRightarrow\text{correct discrimination}.
-\end{align*}
-Hence, archiving a correct outcome in the discrimination task implies a correct outcome in the exclusion task but the reciprocal is untrue.
-This trivial discussion explains the differences in the results and reinforces the potential of \gls{qse}.
-
-\subsection{The perfect exclusion regime and general ensembles}\label{sectionPerfectExclusionRegimeAndGeneralEnsembles}
-
-Although the \emph{Overlap modulus - phase} spectrum might seem as the most intuituve representation, the spectrum of Gram's matrix eigenvalues results the most appropriate representation for the perfect exclusion zone as well as the discussion and its comparison for general ensembles.
-Carrying on with the previos discussion, one can check the two \gls{dof} now appear as two of the eigenvalues.
-In the Figure (\ref{FigureQSEMEZ3ZEigenValues}) the results for the exclusion task under the \gls{me} protocol for the $\mathbb{Z}/3\mathbb{Z}$ group-generated ensemble are represented.
-The axis represent two of the eigenvalues of the Gram matrix and a heatmap presents the probability for a perfect exclusion in the given conditions.
-
-\begin{figure}[H]
-	\centering
-	\begin{overpic}[width=0.5\textwidth, trim={2.3cm 0.8cm 4.4cm 2cm}, clip]{../Plots/ExclusionEignevaluesGroupGeneratedLowerBoundZ3.pdf}
+	\begin{overpic}[width=0.49\textwidth, trim={2.3cm 0.8cm 4.4cm 2cm}, clip]{../Plots/ExclusionEignevaluesGroupGeneratedLowerBoundZ3.pdf}
 	\put(20,25){\footnotesize{Perfect exclusion}}
@@
 	\end{overpic}
-	\caption{Plot of the success exclusion probability in the eigenvalues spectrum for the \gls{me} protocol for a $\mathbb{Z}/3\mathbb{Z}$ group-generated ensemble.}
+	\begin{overpic}[width=0.49\textwidth, trim={2.3cm 0.8cm 4.4cm 2cm}, clip]{../Plots/ExclusionEignevaluesGroupGeneratedLowerBoundZ3ZeroError.pdf}
+	\put(20,25){\footnotesize{Perfect exclusion}}
+	\put(50,50){$\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}<0$}
+	\end{overpic}
+	\caption{Plot of the success exclusion probability in the eigenvalues spectrum for the \gls{me} (left) and \gls{ze} (right) protocol for a $\mathbb{Z}/3\mathbb{Z}$ group-generated ensemble.}
 	\label{FigureQSEMEZ3ZEigenValues}
@@
 
-Notice the missing eigenvalue is determined by the other two via,
+Notice the missing eigenvalue is determined by the other two via,\footnote{Recall we are factoring out the constant prior probability from the standard Gram Matrix, i.e.
+the actual eigenvalues from the Gram Matrix defined in Section \ref{sectionGramMatrixFormulation} are $\left\{\frac{\lambda_i}{3}\right\}_{i=1}^n$.}
 \begin{align*}
@@
 \end{align*}
+
 Since the Gram matrix is a positive semidefinite matrix we know that $\lambda_3\geq0$, the limit case scenario $\lambda_3=0$ defines the line,
@@
 \end{align*}
+
 that constraints the possible eigenvalues to only reach values under this line.
@@
 \end{align*}
+
 This region $\Omega$ is depicted in the Figure (\ref{FigureQSEMEZ3ZEigenValues}) as boottom left triangle, where our system is recluded.
@@
 the eigenvalues such that Eq.(\ref{equationPerfectExclusionCondition}) is fulfilled.
-In particular,if we set $\lambda_i$ with $i\in\{1,2,3\}$ to be the greatest eigenvalues and denote $\lambda_j,\lambda_k$ as the remaining 2 eigenvalues, we know perfect exclusion to be archived if,
+In particular, if we set $\lambda_i$ with $i\in\{1,2,3\}$ to be the greatest eigenvalues and denote $\lambda_j,\lambda_k$ as the remaining 2 eigenvalues, we know perfect exclusion to be archived if,
 \begin{align*}
@@
 \end{align*}
+
 With a little bit of algebra and recalling that $\lambda_3=3-\lambda_1-\lambda_2$ we can derive the regime of perfect exclusion denoted as $\Delta$ comprehends the eigenvalues such that,
 \begin{align*}
-	(\lambda_1,\lambda_2&)\in \Delta\\
-	\Updownarrow& \\
-	4\lambda_1^2 + 4\lambda_2^2 + 4\lambda_1\lambda_2 - &12\lambda_1 - 12\lambda_i + 9 \leq 0
-\end{align*}
-Figure (\ref{FigurePerfectExclusionZ3Z}) shows the $\Delta$ region. It is inmediate that this region corresponds to the colorless perfect exclusion regime in Figure (\ref{FigureQSEMEZ3ZEigenValues}).
-\begin{figure}[H]
-	\centering
-	\begin{overpic}[width=0.5\textwidth, trim={1.8cm 0.8cm 2cm 2cm}, clip]{GeneralSources/PerfectExclusionZoneZ3Z.pdf}
-	\end{overpic}
-	\caption{Plot of the $\Delta$ region.}
-	\label{FigurePerfectExclusionZ3Z}
-\end{figure}
-
-Naturally we can prove the perfect exclusion zone to be a subset of valid Gram matrixes i.e. $\Delta\subset \Omega$.Then the non-perfect exclusion regime is the remaining part of the triangle i.e.,
+	(\lambda_1,\lambda_2)\in \Delta\Leftrightarrow\lambda_1^2 + 4\lambda_2^2 + 4\lambda_1\lambda_2 - 12\lambda_1 - 12\lambda_2 + 9 \leq 0
+\end{align*}
+
+By plotting the $\Delta$ regio it turns out inmediatly this region corresponds to the colorless perfect exclusion regime in Figure (\ref{FigureQSEMEZ3ZEigenValues}).
+
+%Figure (\ref{FigurePerfectExclusionZ3Z}) shows the $\Delta$ region. 
+%\begin{figure}[H]
+%	\centering
+%	\begin{overpic}[width=0.5\textwidth, trim={1.8cm 0.8cm 2cm 2cm}, clip]{GeneralSources/PerfectExclusionZoneZ3Z.pdf}
+%	\end{overpic}
+%	\caption{Plot of the $\Delta$ region.}
+%	\label{FigurePerfectExclusionZ3Z}
+%\end{figure}
+
+Naturally we can prove the perfect exclusion zone to be a subset of valid Gram matrixes i.e. $\Delta\subset \Omega$. Then, the non-perfect exclusion regime is the remaining part of the triangle i.e.,
 \begin{align*}
@@
 The limit case scenarios corresponding to $\lambda_i=3$ and $\lambda_j,\lambda_k=0$ are located in the vertex of the triangle\footnote{Remember this case correspond to sets with the same state repeated 3 times discussed in Section (\ref{sectionLimitCaseScenarios})}.
-Then the cases corresponding to the edges are those with one state repeated 2 times and one different from the other 2.
+Additionally, the cases corresponding to the edges are those with one state repeated 2 times and one different from the other 2.
 This ensembles can also be underestood as a limit case scenario systems.
@@
 \begin{align*}
-	\lambda_i=&\lambda_j=\frac{3}{2}\\
-	\lambda_k=&0.
+	\lambda_i=\lambda_j=\frac{3}{2}\quad\lambda_k=0.
 \end{align*}
@@
 
-Hence the results for the \gls{ze} protocol in \gls{qse} for a $\mathbb{Z}/3\mathbb{Z}$ ensemble are presented in Figure (\ref{FigureQSEZEZ3ZEigenValues}).
-
-The result is consistent with all the previos observations and we can also observe the worst case scenario to tend to a 0 successfull exclusion probability as expected.
+% Hence the results for the \gls{ze} protocol in \gls{qse} for a $\mathbb{Z}/3\mathbb{Z}$ ensemble are presented in Figure (\ref{FigureQSEZEZ3ZEigenValues}).
+
+%\begin{figure}[H]
+%	\centering
+%	\begin{overpic}[width=0.75\textwidth, trim={2.3cm 0.8cm 4.4cm 2cm}, clip]{../Plots/ExclusionEignevaluesGroupGeneratedLowerBoundZ3ZeroError.pdf}
+%		\put(20,25){\footnotesize{Perfect exclusion}}
+%		\put(50,50){$\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}<0$}
+%	\end{overpic}
+%	\caption{Plot of the success exclusion probability in the eigenvalues spectrum for the \gls{ze} protocol for a $\mathbb{Z}/3\mathbb{Z}$ group-generated ensemble.}
+%	\label{FigureQSEZEZ3ZEigenValues}
+%\end{figure}
+
+Regarding the \gls{ze} protocol result, i.e.
+Figure (\ref{FigureQSEMEZ3ZEigenValues}) right, we observe the result is consistent with all the previos observations and we can also observe the worst case scenario to tend to a 0 successfull exclusion probability as expected.
 Also, the probabilities remain with lower values than the ones obtained with the Minimum Error (\gls{me}) protocol.
+Still the perfect exclusion regions are the same.
+
+Hence, we present the result for randomly generated ensembles, i.e. a general ensembles  in Figure (\ref{FigureQSEMEGenericEigenValues}).
 
@@
 	\centering
-	\begin{overpic}[width=0.5\textwidth, trim={2.3cm 0.8cm 4.4cm 2cm}, clip]{../Plots/ExclusionEignevaluesGroupGeneratedLowerBoundZ3ZeroError.pdf}
+	\begin{overpic}[width=0.59\textwidth, trim={2.3cm 0.8cm 4.4cm 2cm}, clip]{../Plots/ExclusionEignevalueRandom3.pdf}
 		\put(20,25){\footnotesize{Perfect exclusion}}
@@
 	\end{overpic}
-	\caption{Plot of the success exclusion probability in the eigenvalues spectrum for the \gls{ze} protocol for a $\mathbb{Z}/3\mathbb{Z}$ group-generated ensemble.}
-	\label{FigureQSEZEZ3ZEigenValues}
+	\begin{overpic}[width=0.39\textwidth, trim={6.5cm 2cm 4.4cm 2cm}, clip]{../Plots/ExclusionEignevalueRandom33D.pdf}
+	\end{overpic}
+	\caption{Heat map plot of the success exclusion probability in the eigenvalues spectrum for the \gls{me} protocol for a generic ensemble (left) and 3D Plot of the success exclusion probability in the eigenvalues spectrum for the \gls{me} protocol for a group-generated and generic ensembles (right)}
+	\label{FigureQSEMEGenericEigenValues}
 \end{figure}
 
-Hence, we present the result for randomly generated ensembles in Figure (\ref{FigureQSEMEGenericEigenValues}).
-
-A remarcable feature is that each ensemble has been checked to not have a successfull exclusion probability that overtakes the value from the $\mathbb{Z}/3\mathbb{Z}$ group-generated ensemble pointing this value to be this a lower bound for the general case scenario.
+A remarcable feature is that each ensemble has been checked to not have a successful exclusion probability that overtakes the value from the $\mathbb{Z}/3\mathbb{Z}$ group-generated ensemble pointing this value to be a lower bound for the general case scenario.
+
+%\begin{figure}[H]
+%	\centering
+%	\caption{3D Plot of the success exclusion probability in the eigenvalues spectrum for the \gls{me} protocol for a group-generated and generic ensembles.}
+%	\label{FigureQSEMEGenericEigenValues3D}
+%\end{figure}
+
+In Figure (\ref{FigureQSEMEGenericEigenValues}) we present a 3D plot for the comparison of the success probability for exclusion for ensembles of 3 states between generic and group-generated ensembles.
+The $x$ and $y$ axis representing de eigenvalues of the Gram matrix are analogous to previous figures.
+Nevertheless the $z$ axis shows the success probability for exclusion instead of the previous heat maps.
+Here we can observe how the randomly generated states raise the probabilities over the group-generated values.
+The generation of unitary matrices that fill $U(n)$ according Haar measure ensures the Gram matrices we are generating comprehend the entire set of possible Gram matrices homogeneously.
+Furthermore, we observe how the group-generated results lay under the results for general ensembles \gls{sdp}s, i.e.
+this results are bounded by the group-generated results.
+
+\subsection{Distribution of the general ensembles success exclusion probability}
+Here we present the main results of the project.
+Hence we show an analytical results for generic ensembles and how the success exclusion probability ensembles are distributed over the results for group-generate ensembles, i.e.
+the lower bound.
+
+We know every Gram Matrix $\mathcal{G}$ can be written as $\mathcal{G}=UDU^\dagger$.
+By fixing the eigenvalues $\{g_i\}_{i=1}^n$, i.e.
+the elements of the diagonal matrix $D$\footnote{Note we have changed the notation respect the previous  eigenvalues since before we were taking the eigenvalues of the Gram Matrix where factoring out $\frac{1}{n}$ in the equal prior probabilities scenario.
+This eigenvalues were normalised to $n$, so we change the notation for avoiding any possible confusion.}, as normalised elements,
+\begin{align*}
+\sum_{i=1}^ng_i=1
+\end{align*}
+
+With this elements we can compute the lower bound given in section (\ref{sectionPreviousResults}) and find whether they are in the perfect exclusion region or not.
+If they are, any Gram matrix generated via $G=UDU^\dagger$ would represent a set of ensembles such that perfect exclusion can be archived and the lower bound would be the exact result.
+Otherwise, if we are in the non-perfect exclusion region by interchanging the unitary matrices $U$ we can generate different sets of Gram matrices such that
+
+Since the algorithm introduced by Francesco Mezzadri in \cite{UnitaryMatricesGeneration}
 
@@
 	\centering
-	\begin{overpic}[width=0.5\textwidth, trim={2.3cm 0.8cm 4.4cm 2cm}, clip]{../Plots/ExclusionEignevalueRandom3.pdf}
-		\put(20,25){\footnotesize{Perfect exclusion}}
-		\put(50,50){$\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}<0$}
-	\end{overpic}
-	\caption{Plot of the success exclusion probability in the eigenvalues spectrum for the \gls{me} protocol for a generic ensemble.}
-	\label{FigureQSEMEGenericEigenValues}
+	\includegraphics[width=0.75\textwidth, trim={1.0cm 0.3cm 2.4cm 1.5cm}, clip]{../Plots/ExclusionMinimumErrorRandomDistributionZ3Prob0.962.pdf}
+	\caption{Hisotgram depicting the distribution of the generated Gram Matrices over the }
+	\label{FigureDistZ5ME0.962}
 \end{figure}
@@
 	\centering
-	\begin{overpic}[width=0.5\textwidth, trim={6.5cm 2cm 4.4cm 2cm}, clip]{../Plots/ExclusionEignevalueRandom33D.pdf}
-	\end{overpic}
-	\caption{3D Plot of the success exclusion probability in the eigenvalues spectrum for the \gls{me} protocol for a group-generated and generic ensembles.}
-	\label{FigureQSEMEGenericEigenValues3D}
+	\includegraphics[width=0.75\textwidth, trim={1.0cm 0.3cm 2.4cm 1.5cm}, clip]{../Plots/ExclusionZeroErrorRandomDistributionZ3Prob0.5.pdf}
+	\caption{Hisotgram of the group genearation }
+	\label{FigureDistZ5ZE0.5}
 \end{figure}
 
-In Figure (\ref{FigureQSEMEGenericEigenValues3D}) we present a 3D plot for the comparison of the success probability for exclusion for ensembles of 3 states between generic and group-generated ensembles.
-The $x$ and $y$ axis representing de eigenvalues of the Gram matrix are analogous to previos figures.
-Nevertheless the $z$ axis shows the success probability for exclusion insted of the previos heatmaps.
-Here we can observe how the randomly generated states raise the probabilities over the group-generated values.
-The generation of unitary matrices that fill $U(n)$ ensures the Gram matrices we are generating comprehend the entire set of possible Gram matrices homogeniously.
 \subsection{Intuition behind the results}
@@
 Due to the symmetric nature of the ensemble, the states are very similar to each other.
-This makes it especially difficult to identify which state is different from the target state.
-In contrast, if the ensemble includes a state $\ket{\tilde{\psi}}$ that is very different from the others, it becomes easier to determine whether $\ket{\tilde{\psi}}$ matches the target or not.
+This makes it especially difficult to identify which state is different from the unknown state.
+In contrast, if the ensemble includes a state $\ket{\tilde{\psi}}$ that is very different from the others, it becomes easier to determine whether $\ket{\tilde{\psi}}$ matches the unknown state or not.
 Thus, when the symmetry is broken, exclusion can be performed more accurately.
 
-To illustrate this more concretely, consider the following ensamble involving qubit states,
-\[
+To illustrate this more concretely, consider the following ensemble involving qubit states,
+\begin{align}
 \{\ket{\textcolor{red}{\uparrow}}, \ket{\textcolor{blue}{\uparrow}}, \ket{\textcolor{green}{\uparrow}}\}.
-\]
-These are represented on a Bloch circle\footnote{The Bloch circle is a projection of the Bloch sphere onto a plane.} in Figure~\ref{FigureIntuitionExample}.
+\end{align}
+
+These are represented on a Bloch circle\footnote{The Bloch circle is a projection of the Bloch sphere onto a plane.} in Figure (\ref{FigureIntuitionExample}).
 
@@
 Therefore, given an unknown state $\ket{\uparrow}$ from this ensemble, it is relatively easy to determine whether $\ket{\uparrow} = \ket{\textcolor{red}{\uparrow}}$ or $\ket{\uparrow} \neq \ket{\textcolor{red}{\uparrow}}$.
-If $\ket{\uparrow} = \ket{\textcolor{red}{\uparrow}}$, we can exclude either $\ket{\textcolor{blue}{\uparrow}}$ or $\ket{\textcolor{green}{\uparrow}}$; otherwise, we can exclude $\ket{\textcolor{red}{\uparrow}}$.
+If $\ket{\uparrow} = \ket{\textcolor{red}{\uparrow}}$, we can exclude either $\ket{\textcolor{blue}{\uparrow}}$ or $\ket{\textcolor{green}{\uparrow}}$, otherwise, we can exclude $\ket{\textcolor{red}{\uparrow}}$.
 In both cases, the exclusion is straightforward.
@@
 
+For a more analytical result, and regarding previos results in section (\ref{sectionPerfectExclusionRegimeAndGeneralEnsembles}), the success probability of this ensemble would be represented as a dot close to an edge of the triangle of Figure (\ref{FigureQSEMEGenericEigenValues}).
 %From an analytical perspective, consider the Gram matrix $\mathcal{G}$ for this ensemble. We have,
@@
 
-Now contrast this with a symmetric ensemble, as shown in Figure~\ref{FigureIntuitionExample2}:
+Now contrast this with a symmetric ensemble, as shown in Figure (\ref{FigureIntuitionExample2}).
 
@@
 
-This configuration exhibits perfect symmetry. Define a unitary operator $\mathcal{U}$ such that:
-\[
+This configuration exhibits perfect symmetry. Define a unitary operator $\mathcal{U}$ such that,
+\begin{align*}
 \mathcal{U} \ket{\textcolor{red}{\uparrow}} = \ket{\textcolor{blue}{\uparrow}},
-\]
-then by symmetry:
-\[
+\end{align*}
+then by symmetry,
+\begin{align*}
 \mathcal{U} \ket{\textcolor{blue}{\uparrow}} = \ket{\textcolor{green}{\uparrow}}, \quad \mathcal{U} \ket{\textcolor{green}{\uparrow}} = \ket{\textcolor{red}{\uparrow}}.
-\]
+\end{align*}
 Hence,
-\[
+\begin{align*}
 \mathcal{U}^3 = \mathds{1}|_{\text{Bloch circle}},
-\]
+\end{align*}
 where $\mathds{1}|_{\text{Bloch circle}}$ denotes the identity operator restricted to this subspace.
-This implies that the ensemble is generated by a cyclic group of order 3, i.e., $\mathbb{Z}/3\mathbb{Z}$.
+This implies the ensemble is generated by a cyclic group of order 3, i.e., $\mathbb{Z}/3\mathbb{Z}$.
 
@@
 
+\newpage
 \section{Conclusions}
 
-\section*{Acknowledgements}
-
-I am grateful to Dr.
-Ramón Muñoz Tapia for allowing me to be one of his pupils and for presenting this project.
-I am also deeply grateful to PhD.
-Santiago Llorens Fernández for being the lighthouse that illuminates my path throughout this journey.
-
-I would like to acknowledge my mother and sister for their unconditional support, and my father for the values he taught me.
-Additionally, I would like to thank my friends Francisco Montaño, David Muñoz and Manel Martin for listening to my monologues about my excitement for Quantum State Exclusion.
+We have numerically verified the analytical results for the success and error probabilities for exclusion of group-generated ensembles, presented in Section~(\ref{sectionPreviousResults}), serve as lower bounds for these probabilities in the general case.
+Additionally, we have provided insights and intuition supporting why these results act as lower bounds for random ensembles.
+
+Furthermore, we have deeply discussed and presented the specific case of $\mathbb{Z}/3\mathbb{Z}$, which is the only group-generated ensemble that can be represented in a two-dimensional plot.
+
+Finally, we have highlighted the advantages of Quantum State Exclusion (\gls{qse}) over its counterpart, Quantum State Discrimination (\gls{qsd}), thereby motivating further research into hybrid protocols that combine \gls{qse} and \gls{qsd}.
+Such hybrid approaches may lead to more optimal protocols in certain scenarios.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+\newpage
 \bibliographystyle{plain}
@@
 
-\end{multicols}
+\section*{Acknowledgements}
+
+I am grateful to Dr.
+Ramón Muñoz Tapia for allowing me to be one of his pupils and for presenting this project.
+I am also deeply grateful to PhD.
+student Santiago Llorens Fernández for being the lighthouse that illuminates my path throughout this journey.
+
+I would like to acknowledge my mother and sister for their unconditional support, and my father for the values he taught me.
+Additionally, I would like to thank my friends Francisco Montaño, David Muñoz and Manel Martin for listening to my monologues about my excitement for Quantum State Exclusion.
+
+\newpage
+\appendix
+
+\section{Dual Formulation of the Problem}\label{sectionDualFormulationOfTheProblem}
+
+It is often useful to consider the \emph{dual} version of a \gls{sdp} problem, as it provides both conceptual insights and practical advantages for verifying optimality.
+
+Consider the ensemble $\left\{ \left( \rho_i, \frac{1}{n} \right) \right\}_{i=1}^n$, where each state $\rho_i$ appears with uniform prior probability $1/n$.
+The dual SDP corresponding to the Minimum Error (\gls{me}) exclusion protocol, when expressed in terms of the error probability, is given by,
+\begin{align*}
+	\tilde{P}_{\gls{me}}^e = \max_{\Gamma} \quad & \tr{\Gamma} \\
+	\text{subject to} \quad & \frac{\rho_i}{n} - \Gamma \geq 0 \quad \forall i \in \{1, \dots, n\}, \\
+	& \Gamma^\dagger = \Gamma,
+\end{align*}
+where $\tilde{P}$ denotes the dual version of the problem.
+
+Similarly, the dual SDP for the success probability in the same protocol reads,
+\begin{align*}
+	\tilde{P}_{\gls{me}}^s = \min_{\Gamma} \quad & 1 - \tr{\Gamma} \\
+	\text{subject to} \quad & \frac{\rho_i}{n} - \Gamma \geq 0 \quad \forall i \in \{1, \dots, n\}, \\
+	& \Gamma^\dagger = \Gamma.
+\end{align*}
+
+For the \gls{ze} protocol the dual version of the \gls{sdp} for the error probability is,
+\begin{align*}
+	\tilde{P}_{\gls{ze}}^s = \max_{X\geq 0} \quad & 1-\tr{X} \\
+	\text{subject to} \quad & \sum_{g\in\mathcal{G}}U_gXU_g^\dagger+ \nu\ket{\psi}\bra{\psi}-\Omega \geq 0 \quad \nu \in \mathbb{R}.
+\end{align*}
+
+Hence the success probability is,
+
+\begin{align*}
+	\tilde{P}_{\gls{ze}}^s = \min_{X\geq 0} \quad & \tr{X} \\
+	\text{subject to} \quad & \sum_{g\in\mathcal{G}}U_gXU_g^\dagger+ \nu\ket{\psi}\bra{\psi}-\Omega \geq 0 \quad \nu \in \mathbb{R}.
+\end{align*}
+
+One of the primary uses of the dual formulation is in establishing optimality.
+If a POVM ansatz yields equal objective values for both the primal and dual problems, i.e., $P = \tilde{P}$, then strong duality holds and the measurement is guaranteed to be optimal.
+
+This duality principle not only provides a tool for verification but also suggests constructive approaches to discovering optimal measurements, especially in structured ensembles such as those generated by group actions.
+
+\section{Computation of Gram Matrices for a group-generated ensembles}\label{appendixComputationGroupGeneratedGramMatrices}
+
+We can compute the Gram matrix for any group-generated ensemble by using the Cayley table~\cite{CayleyTable}, also known as the \emph{multiplication table}, of the group.
+For example, consider the smallest non-commutative group, $S_3$, consisting of the symmetries and rotations of an equilateral triangle.
+Denoting the identity as $e$, the rotations elements as $s$, $s^2$ (one being the result of 2 times the other) and the symmetries $p$, $q$, and $r$, the Cayley table is,
+
+\begin{table}[H]
+	\centering
+	\caption{Cayley table of the $S_3$ group.}
+	\begin{tabular}{c||c c c c c c}
+        $S_3$ & $e$ & $s$ & $s^2$ & $p$ & $q$ & $r$ \\\hline\hline
+        $e$   & $e$ & $s$ & $s^2$ & $p$ & $q$ & $r$ \\
+        $s^2$ & $s^2$ & $e$ & $s$ & $r$ & $p$ & $q$ \\
+        $s$   & $s$ & $s^2$ & $e$ & $q$ & $r$ & $p$ \\
+        $p$   & $p$ & $r$ & $q$ & $e$ & $s^2$ & $s$ \\
+        $q$   & $q$ & $p$ & $r$ & $s$ & $e$ & $s^2$ \\
+        $r$   & $r$ & $q$ & $p$ & $s^2$ & $s$ & $e$
+    \end{tabular}
+\end{table}
+
+We now identify $S_3$ as a group of unitary matrices\footnote{We treat each group element as a unitary matrix, and the group operation as matrix multiplication.}.
+It follows that the Gram matrix of the $S_3$ group-generated ensemble is the matrix of expected values of the Cayley table entries with respect to the seed state $\ket{\psi}$.
+That is,
+\begin{align*}
+	\mathcal{G}^{S_3}_{\psi} = \frac{1}{6}\begin{pmatrix}
+        1 & \braket{s}_\psi & \braket{s^2}_\psi & \braket{p}_\psi & \braket{q}_\psi & \braket{r}_\psi \\ 
+        \braket{s^2}_\psi & 1 & \braket{s}_\psi & \braket{r}_\psi & \braket{p}_\psi & \braket{q}_\psi \\
+        \braket{s}_\psi & \braket{s^2}_\psi & 1 & \braket{q}_\psi & \braket{r}_\psi & \braket{p}_\psi \\
+        \braket{p}_\psi & \braket{r}_\psi & \braket{q}_\psi & 1 & \braket{s^2}_\psi & \braket{s}_\psi \\
+        \braket{q}_\psi & \braket{p}_\psi & \braket{r}_\psi & \braket{s}_\psi & 1 & \braket{s^2}_\psi \\
+        \braket{r}_\psi & \braket{q}_\psi & \braket{p}_\psi & \braket{s^2}_\psi & \braket{s}_\psi & 1
+	\end{pmatrix}.
+\end{align*}
+Notice we have assumed equal prior probabilities, i.e.
+$\eta_i = \eta_j = \frac{1}{6}$.
+In the non-equal prior probabilities regime we only need to multiply each element for $\sqrt{\eta_i\eta_j}$ insted of $\frac{1}{6}$.
+Additionally, note that $\braket{e}_\psi = 1$ since $e = \mathds{1}$.
+Moreover, since $\mathcal{G}^{S_3}$ is Hermitian, we conclude,
+\begin{align*}
+\braket{p}_{\psi},\ \braket{q}_{\psi},\ \braket{r}_{\psi} \in \mathbb{R}, \quad \forall \ket{\psi} \in \mathcal{H},
+\end{align*}
+which implies the unitary matrices corresponding to the triangle symmetries $p$, $q$, and $r$ are Hermitian.
+As a matter of fact we know the eigenvalues of this matrices can only be $\pm 1$ and at least one of them must be $-1$.\footnote{Otherwise, they would be the identity and we know them to be different by construction.} This procedure generalizes to any finite group $G$, showing that computing the Cayley table is equivalent to computing the Gram matrix of the corresponding group-generated ensemble.
+
+\section{Comparison \gls{qsd} vs. \gls{qse}}\label{appendixComparisonQSDvsQSE}
+
+Here we present the results for the Quantum State Discrimination (\gls{qsd}) task to motivate the problem and highlight contrasts with the Quantum State Exclusion (\gls{qse}) task, which is the focus of this study.
+
+\begin{figure}[H]
+	\centering
+	\begin{overpic}[width=0.5\textwidth, trim={2.3cm 0.8cm 4.5cm 2cm}, clip]{../Plots/DiscriminationOverlapVSPhaseVSMinimumErrorProbabilityZ3HeatMap.pdf}
+		\put(60,25){$\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}<0$}
+		\put(60,55){$\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}<0$}
+	\end{overpic}
+	\caption{Heatmap of the success probability for minimum error (\gls{me}) quantum state discrimination for a $\mathbb{Z}/3\mathbb{Z}$ group-generated ensemble.}
+	\label{FigureQSDMEZ3ZHeatmap}
+\end{figure}
+
+In these conditions, the \gls{srm}\footnote{Also known as the Pretty Good Measurement.} is optimal, i.e.
+the result of the \gls{sdp} matches the one obtained from the \gls{sdp} in \gls{me} protocol.
+In particular, the \gls{srm} is obtained from the square root decomposition of the Gram matrix,
+\begin{align*}
+	\mathcal{G} = S^\dagger S = S^2
+\end{align*}
+and is the standard in \gls{qsd} under the \gls{me} protocol \cite{OptimalitySRM}.
+From section (\ref{sectionGramMatrixFormulation}) we know the success probability for a successful discrimination with \gls{srm} reeds,
+\begin{align*}
+	P_{\gls{srm}}^s=\frac{1}{n}\sum_{i=0}^nS_{i,i}^2
+\end{align*}
+were $S_{i,i}$ denotes the diagonal elements of $S$ and $n$ the number of quantum states\footnote{In this case we are taking $n=3$.}.
+
+As expected, no ensemble yields a success probability below $1/3$, consistent with the discussion in Section (\ref{sectionLimitCaseScenarios}).
+Moreover, as the modulus of the overlap approaches zero, the success probability approaches one, corresponding to orthogonal states, again matching expectations.
+
+Figure (\ref{FigureQSDZEZ3ZHeatmap}) shows analogous results for the Zero Error (\gls{ze}) protocol under the same conditions.
+
+\begin{figure}[H]
+	\centering
+	\begin{overpic}[width=0.5\textwidth, trim={2.3cm 0.8cm 4.5cm 2cm}, clip]{../Plots/DiscriminationOverlapVSPhaseVSSuccessProbabilityZeroErrorZ3HeatMap.pdf}
+		\put(60,25){$\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}<0$}
+		\put(60,55){$\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}<0$}
+	\end{overpic}
+	\caption{Heatmap of the success probability for zero-error (\gls{ze}) quantum state discrimination for a $\mathbb{Z}/3\mathbb{Z}$ group-generated ensemble.}
+	\label{FigureQSDZEZ3ZHeatmap}
+\end{figure}
+
+Again, the ZE protocol yields lower probabilities due to its constraints and the limit case scenarios match with the previos discussion in Section (\ref{sectionLimitCaseScenarios}) and Section (\ref{sectionResultsAndDiscussion}).
+
+Figure (\ref{FigureQSDMEZESRM}) compares the performance of the ME, ZE, and SRM protocols.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.5\textwidth]{../Plots/DiscriminationOverlapVSSucessProbabilitySDPvsSRMZnOverlap3Phase0.pdf}
+	\caption{Comparison of successful discrimination probabilities for ME, ZE, and SRM protocols in a $\mathbb{Z}/3\mathbb{Z}$ ensemble impossing phase=$0$.}
+	\label{FigureQSDMEZESRM}
+\end{figure}
+
+As expected, perfect discrimination is only achieved when the overlap is zero (orthogonal states), and the \gls{srm} success probability matches the one obtained from the numerical \gls{sdp}.
+
+Moreover, we observe the results in \gls{qse} are substancially better, the exclusion can be performed with higher precission than the discrimination.
+This observations is expected.
+Let us suppose we perform a correct guess in the discrimination of our unknown state, then if we know to which state is correlated our unknown state, we know which states is not correlated to, in other words
+\begin{align*}
+	\text{correct discrimination}\Rightarrow\text{correct exclusion}.
+\end{align*}
+
+However, let us suppose we perform a correct guess in the exclusion task, still we are ignoring which is our unknown state, then,
+\begin{align*}
+	\text{correct exclusion}\nRightarrow\text{correct discrimination}.
+\end{align*}
+
+Hence, archiving a correct outcome in the discrimination task implies a correct outcome in the exclusion task but the reciprocal is untrue.
+This trivial discussion explains the differences in the results and reinforces the potential of \gls{qse}.
+
+This highlights the motivation behind the study of \gls{qse}, which allows for perfect exclusion in cases where discrimination is impossible.
+The possibility perfect exclusion for \gls{qse} is a major motivation for its study.
+For example, in a regime where perfect exclusion is possible, having access to multiple copies of a unknown state enables hybrid exclusion-discrimination protocols that can outperform purely discriminative strategies.
+Even partial information, such as the exclusion of a single quantum state, has value in certain quantum information theories.
+These features make \gls{qse} a fertile ground for further theoretical and applied research.
+
+\section{Limit Case Scenarios}\label{sectionLimitCaseScenarios}
+
+Let us study the Gram matrix of a limit ensemble composed of $n$ identical quantum states with equal probabilities, i.e.
+the same state is repeated $n$ times in the ensemble with the same probability.\footnote{This case may appear paradoxical, since there is no way to distinguish between identical states.
+Nevertheless, we present it as a limiting scenario.} The Gram matrix reads:
+\begin{align*}
+	\mathcal{G}^{\text{limit}} = \frac{1}{n}\begin{pmatrix}
+ 1 & 1 & \cdots & 1 \\
+ 1 & 1 & \cdots & 1 \\
+ \vdots & \vdots & \ddots & \vdots \\
+ 1 & 1 & \cdots & 1 \\
+\end{pmatrix}.
+\end{align*}
+
+The eigenvalues of this matrix are:
+\begin{align*}
+	\lambda_n &= 1, \\
+	\lambda_{n-1} &= 0, \\
+	\vdots \\
+	\lambda_1 &= 0.
+\end{align*}
+
+Clearly, this set of eigenvalues does not satisfy Eq.
+(\ref{equationPerfectExclusionCondition}), i.e., we are in the non-perfect exclusion regime.
+In fact, we can interpret this ensemble as a group-generated ensemble from the \emph{trivial group},\footnote{The trivial group is the group consisting solely of the neutral/identity element.} which generates no variation.
+
+Thus, the success and error probabilities for both the \gls{me} protocol is,
+\begin{align*}
+	P_{\gls{me}}^e =& \frac{1}{n},\\
+	P_{\gls{me}}^s =& \frac{n-1}{n}.
+\end{align*}
+
+The intuition behind this result is clear.
+If there is no physical way to distinguish between states, the exclusion must be made randomly, with uniform probability.
+This observation also extends naturally to \gls{qsd}.
+
+Since this is a limiting case scenario, the success probability for \gls{qse} must be strictly greater than $\frac{n-1}{n}$ (i.e., the error probability must be less than $\frac{1}{n}$) and for \gls{qsd} the success probabilities must be strictly greater than $\frac{1}{n}$ (i.e., the error probability must be less than $\frac{n-1}{n}$)\footnote{In this case scenario the discrimination task is the counterpart of the exclusion task.}.
+Notice this result holds only for the \gls{me} protocol.
+Otherwise, since the exclusion cannot be accomplished without ambiguity, the successfull exclusion probability for the \gls{ze} protocol is 0 for either \gls{qse} or \gls{qsd} (i.e., the error exclusion probability is 1),
+\begin{align*}
+	P_{\gls{ze}}^e =& 1,\\
+	P_{\gls{ze}}^s =& 0.
+\end{align*}
+
+The opposite limiting case is an ensemble of $n$ orthogonal quantum states $\{\rho_i\}_{i=1}^{n}$. In this case, the Gram matrix becomes the identity,
+\begin{align*}
+	\mathcal{G} = \mathds{1}.
+\end{align*}
+
+Under these conditions, both \gls{qse} and \gls{qsd} are trivial, as the states form an orthonormal basis. In particular, in the space spanned by these states, we have,
+\begin{align*}
+	\sum_{i=1}^{n} \rho_i = \mathds{1},
+\end{align*}
+which means that the set $\{\rho_i\}$ is itself a \gls{povm}.
+The measurement corresponding to this \gls{povm} allows perfect identification, or exclusion, hence both \gls{qse} and \gls{qsd} can be performed without error.
+
 \end{document}

### 2025-05-27 Manuscript/Manuscript.tex
Writthing

@@
 \begin{align*}
-	\rho' = \ket{\psi'}\bra{\psi'} = \ket{\psi}\bra{\psi} = \rho.
+	\rho = \ket{\psi'}\bra{\psi'} = \ket{\psi}\bra{\psi} .
 \end{align*}
@@
 
-Note the constraints $\sum_{i=1}^n \Pi_i = \mathds{1}$ and $\Pi_i \geq 0$ ensure that the $\Pi_i$ form a valid POVM, since they demand positive semi-definition and form a complete measurement.
+Note the constraints $\sum_{i=1}^n \Pi_i = \mathds{1}$ and $\Pi_i \geq 0$ ensure that the set $\{\Pi_i\}_{i=1}^n$ form a valid \gls{povm}, since they demand positive semi-definition and form a complete measurement.
 The superscript $e$ in $P_{\text{\gls{me}}}^e$ indicates that this is the \emph{error probability}.
@@
 
-In the case of the \gls{ze} protocol, the POVMs must also satisfy an unambiguity condition, i.e.
+In the case of the \gls{ze} protocol, the objective is to exclude with total accuracy a state known to be different from the target state.
+However, the protocol might lead to inconclusive result.
+In order to do so, the \gls{povm}s must also satisfy an unambiguity condition, i.e.
 each measurement operator $\Pi_i$ must be orthogonal to the corresponding state $\rho_i$.
@@
 \footnote{Note that fixing the basis $\{\ket{\omega_i}\}_{i=1}^n$ uniquely determines the decomposition $\mathcal{G} = X^\dagger X$, and vice versa.}We define the POVM elements as projectors $\Pi_i = \ket{\omega_i}\bra{\omega_i}$.
-Then, for the ensemble $\{(\rho_i, \eta_i)\}_{i=1}^n$, the corresponding semidefinite program (\gls{sdp}) constraints become,
+Then, for the ensemble $\{(\rho_i, \eta_i)\}_{i=1}^n$, the corresponding semidefinite program (\gls{sdp}) constrains become,
 \begin{align*}
@@
 Given a quantum state $\ket{\psi}$, referred to as the \emph{seed state}, we define a \emph{group generated ensemble} as the set of states obtained by applying a group of unitary transformations to $\ket{\psi}$.
-Specifically, if the ensemble consists of $n$ quantum states, its elements are of the form
+Specifically, if the ensemble consists of $n$ quantum states, its elements are of the form,
 \begin{align*}
@@
 \emph{Example: The $\mathbb{Z}/n\mathbb{Z}$ group-generated ensemble}: Let $\mathcal{U} \in U(n)$ be an $n \times n$ unitary matrix satisfying $\mathcal{U}^n = \mathds{1}$, and let $\ket{\psi}$ be the seed state.
-The Gram matrix $\mathcal{G}^{\mathbb{Z}/n\mathbb{Z}}$ elements associated with the ensemble $\left\{\mathcal{U}^i\ket{\psi}\right\}_{i=0}^{n-1}$ are
+The Gram matrix $\mathcal{G}^{\mathbb{Z}/n\mathbb{Z}}$ elements associated with the ensemble $\left\{\mathcal{U}^i\ket{\psi}\right\}_{i=0}^{n-1}$ are,
 \begin{align*}
@@
 \end{align*}
-Note that $\braket{e}_\psi = 1$ since $e = \mathds{1}$. Moreover, since $\mathcal{G}^{S_3}$ is Hermitian, we conclude:
+Note that $\braket{e}_\psi = 1$ since $e = \mathds{1}$. Moreover, since $\mathcal{G}^{S_3}$ is Hermitian, we conclude,
 \begin{align*}
@@
 
-Finally, we denote the cardinality of a finite group $G$ (i.e., the number of its elements) as $|G|$. In scenarios with uniform prior probabilities, this implies,
+Finally, we denote the cardinality of a finite group $G$, i.e. the number of its elements of the group, as $|G|$. In scenarios with uniform prior probabilities, this implies,
 \begin{align*}
@@
 Significant progress has been made in the study of the state exclusion task for group-generated ensembles.
-In particular, the work \emph{Quantum State Exclusion for Group-Generated Ensembles of Pure States}\cite{MainPaper} presents exact analytical expressions for the success and error probabilities under both the Minimum Error \gls{me} and Zero Error \gls{ze} exclusion protocols.
-
-Let $\mathcal{G}^G$ denote the Gram matrix of a group-generated ensemble $\left\{ \left( \rho_i, \frac{1}{|G|} \right) \right\}_{i=1}^{|G|}$, where $G$ is a finite group of size $|G|$, and let $\{\lambda_i\}_{i=1}^{|G|}$ be the set of eigenvalues of $\mathcal{G}^G$.
+In particular, the work \emph{Quantum State Exclusion for Group-Generated Ensembles of Pure States}\cite{MainPaper} presents exact analytical expressions for the success and error probabilities under both the Minimum Error (\gls{me}) and Zero Error (\gls{ze}) exclusion protocols.
+
+Let $\mathcal{G}^G$ denote the Gram matrix of a group-generated ensemble $\left\{ \left( \rho_i, \frac{1}{|G|} \right) \right\}_{i=1}^{|G|}$, where $G$ is a finite group of size $|G|$, and let $\{\lambda_i\}_{i=1}^{|G|}$ be the set of eigenvalues of $\mathcal{G}^G$, the Gram Matrix of the group.
 Assume the eigenvalues are ordered increasingly,
@@
 
-Let us study the Gram matrix of a limit ensemble composed of $n$ identical quantum states (i.e., the same state is repeated $n$ times in the ensemble).\footnote{This case may appear paradoxical, since there is no way to distinguish between identical states.
+Let us study the Gram matrix of a limit ensemble composed of $n$ identical quantum states, i.e.
+the same state is repeated $n$ times in the ensemble.\footnote{This case may appear paradoxical, since there is no way to distinguish between identical states.
 Nevertheless, we present it as a limiting scenario.} The Gram matrix reads:
@@
 which means that the set $\{\rho_i\}$ is itself a \gls{povm}.
-The measurement corresponding to this \gls{povm} allows perfect identification (or exclusion), hence both \gls{qse} and \gls{qsd} can be performed without error.
+The measurement corresponding to this \gls{povm} allows perfect identification, or exclusion, hence both \gls{qse} and \gls{qsd} can be performed without error.
 
@@
 
-Ensembles of prime cardinality are thus of particular interest and will be further explored in the Results and Discussion section. \textcolor{blue}{Add reference to Results section}
+Ensembles of prime cardinality are thus of particular interest and will be further explored in the Results and Discussion (section \ref{sectionResultsAndDiscussion}).
+
 \section{Methodology}
@@
 
-\section{Results and Discussion}
+\section{Results and Discussion}\label{sectionResultsAndDiscussion}
 
@@
 
-The colorless regions correspond to parameters where $\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}$ is not positive semi-definite, and leading up yo non-valid Gram matrices, since positive semi-definition is inherent to a Gram matrix.
+The colorless regions correspond to parameters where $\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}$ is not positive semi-definite, and leading up to non-valid Gram matrices, since positive semi-definition is inherent to a Gram matrix.
 
@@
 However, the \gls{ze} success probabilities are lower than those of the \gls{me} protocol.
-This is explained by the stricter constraints imposed in the \gls{ze} scenario, where $\tr(\Pi_i\rho_i) = 0$ is enforced for all POVM elements except one.
+This is explained by the stricter constraints imposed in the \gls{ze} scenario, where $\tr(\Pi_i\rho_i) = 0$ is enforced for all \gls{povm} elements except one.
 Notice both probabilities are computed in a completely symmetric way,
@@
 	\Updownarrow& \\
-	4\lambda_1^2 + 4\lambda_2^2 + 4\lambda_1\lambda_2 - &12\lambda_1 - 12\lambda_i + 9 \leq 0
+	4\lambda_1^2 + 4\lambda_2^2 + 4\lambda_1\lambda_2 - &12\lambda_1 - 12\lambda_2 + 9 \leq 0
 \end{align*}
@@
 \]
-These are represented on a Bloch circle\footnote{The Bloch circle is a projection of the Bloch sphere onto a plane.} in Figure~\ref{FigureIntuitionExample}.
+These are represented on a Bloch circle\footnote{The Bloch circle is a projection of the Bloch sphere onto a plane.} in Figure (\ref{FigureIntuitionExample}).
 
@@
 
+For a more analytical result, and regarding previos results in section (\ref{sectionPerfectExclusionRegimeAndGeneralEnsembles}), the success probability of this ensamble would be represented as a dot close to an edge of the triangle of Figure (\ref{FigureQSEMEGenericEigenValues}).
 %From an analytical perspective, consider the Gram matrix $\mathcal{G}$ for this ensemble. We have,
@@
 \section{Conclusions}
+
+We have numerically verified the analytical results for the success and error probabilities for exclusion of group-generated ensembles, presented in Section~(\ref{sectionPreviousResults}), serve as lower bounds for these probabilities in the general case.
+Additionally, we have provided insights and intuition supporting why these results act as lower bounds for random ensembles.
+
+Furthermore, we have deeply discussed and presented the specific case of $\mathbb{Z}/3\mathbb{Z}$, which is the only group-generated ensemble that can be represented in a two-dimensional plot.
+
+Finally, we have highlighted the advantages of Quantum State Exclusion (\gls{qse}) over its counterpart, Quantum State Discrimination (\gls{qsd}), thereby motivating further research into hybrid protocols that combine \gls{qse} and \gls{qsd}.
+Such hybrid approaches may lead to more optimal protocols in certain scenarios.
 

### 2025-05-27 Scripts/NormVSExclussionProbability.py

@@ -12,11 +12,11 @@ import numpy as np
 import matplotlib.pyplot as plt
 from tqdm import tqdm
 
-NumberOfMatrices              = 51
-MatrixDimension               = 51
+NumberOfMatrices              = 3
+MatrixDimension               = 3
 MatrixGenerationMethod        = "Random"
 ProbabliltiesGenerationMethod = "Equal"
-EigenValues                   = [10 for i in range(NumberOfMatrices - 1)]
+EigenValues                   = [1 for i in range(NumberOfMatrices - 1)]
 EigenValues.append(100)
 EigenValuesNormalized         = [iEigenValue*NumberOfMatrices/sum(EigenValues) for iEigenValue in EigenValues]
 Iterations                    = 1000
@@ -33,7 +33,7 @@ ExlusionSuccessProbability    = []
 for iIteration in tqdm(range(Iterations),"Computing SDP"):
     Conditions = QSExSetUp.GramGeneratedStates.GramGeneratedStatesClass(NumberOfMatrices,MatrixDimension,MatrixGenerationMethod, QSExSetUp.GramGeneratedStates.ZnGramMatrixConditionsEigenValues(EigenValuesNormalized, NumberOfMatrices), ProbabilitiesContructionMethod = ProbabliltiesGenerationMethod)
     Solution = QSExSetUp.SDPSolver.SolveSDPExclusionMinimumError(Conditions)
-    ExlusionSuccessProbability.append(round(Solution['SDPSolution'],10))
+    ExlusionSuccessProbability.append(round(Solution['SDPSolution'],4))
     DistanceFrobenius.append(picos.Norm(GroupGeneratedConditions.getUnitaryMatrix() - Conditions.getUnitaryMatrix(),2))
     Distance1.append(picos.Norm(GroupGeneratedConditions.getUnitaryMatrix() - Conditions.getUnitaryMatrix(),1))
     DistanceInfinite.append(picos.Norm(GroupGeneratedConditions.getUnitaryMatrix() - Conditions.getUnitaryMatrix(),float("inf")))
@@ -49,6 +49,6 @@ plt.scatter(DistanceNuclear,ExlusionSuccessProbability, label = "Nuclear")
 plt.xlabel("Norm Distance")
 plt.ylabel("Exclusion success probability")
 plt.legend(loc='upper right')
-plt.savefig(f"../Plots/ExclusionNormPlots{NumberOfMatrices}.pdf")
[…]

### 2025-05-27 Scripts/PlotDistributionProbability.py

@@ -1,0 +1,97 @@
+########################################################################################################
+#                                                                                                      #
+#  Project:  Physics TFG                                                                               #
+#  Author:   Sergio Castañeiras Morales                                                                #
+#  Date:     23/05/2025                                                                                #
+#  Purpose:  Plot                                                                                      #
+#                                                                                                      #
+########################################################################################################
+
+import QSExSetUp
+import numpy as np
+import matplotlib.pyplot as plt
+from mpl_toolkits.mplot3d import Axes3D
+from tqdm import tqdm
+import mpltern
+import picos
+from collections import Counter
+
+NumberOfMatrices              = 3
+MatrixDimension               = 3
+MatrixGenerationMethod        = "Random"
+ProbabliltiesGenerationMethod = "Equal"
+IterationsRandomSets          = 10
+DataMinimumError              = []
+EigenValue0                   = []
+EigenValue1                   = []
+SDPMinimumErrorList           = []
+SDPZeroErrorList              = []
+LowerBound                    = []
+LowerBoundZE                  = []
+data                          = []
+for iIteration in range (500):
+    EigenValues = [1 for i in range (NumberOfMatrices-1)]
+    EigenValues.append(iIteration^3)
+    # EigenValues             = np.random.rand(NumberOfMatrices)
+    EigenValuesNormalized   = [iEigenValue*NumberOfMatrices/sum(EigenValues) for iEigenValue in EigenValues]
+    # while (Conditions.getPerfectExlusion()):
+    #     EigenValues             = np.random.rand(NumberOfMatrices)
+    #     EigenValuesNormalized   = [iEigenValue*NumberOfMatrices/sum(EigenValues) for iEigenValue in EigenValues]
+    #     print("UwU")
[…]

### 2025-05-27 Scripts/PlotDistributionProbability2D.py

@@ -1,0 +1,72 @@
+########################################################################################################
+#                                                                                                      #
+#  Project:  Physics TFG                                                                               #
+#  Author:   Sergio Castañeiras Morales                                                                #
+#  Date:     23/05/2025                                                                                #
+#  Purpose:  Plot                                                                                      #
+#                                                                                                      #
+########################################################################################################
+
+import QSExSetUp
+import numpy as np
+import matplotlib.pyplot as plt
+from mpl_toolkits.mplot3d import Axes3D
+from tqdm import tqdm
+import mpltern
+import picos
+from collections import Counter
+from picos.modeling.problem import SolutionFailure  
+
+
+NumberOfMatrices              = 5
+MatrixDimension               = 5
+MatrixGenerationMethod        = "Random"
+ProbabliltiesGenerationMethod = "Equal"
+IterationsRandomSets          = 10000
+DataMinimumError              = []
+EigenValue0                   = []
+EigenValue1                   = []
+SDPMinimumErrorList           = []
+SDPZeroErrorList              = []
+LowerBound                    = []
+LowerBoundZE                  = []
+EigenValues = [1 for i in range (NumberOfMatrices-1)]
+EigenValues.append(50000)
+EigenValuesNormalized   = [iEigenValue*NumberOfMatrices/sum(EigenValues) for iEigenValue in EigenValues]
+
+
+for iIteration in tqdm(range(IterationsRandomSets),f"Computing points for the Minimum Error plot"):
+    Conditions = QSExSetUp.GramGeneratedStates.GramGeneratedStatesClass(NumberOfMatrices,MatrixDimension,MatrixGenerationMethod, QSExSetUp.GramGeneratedStates.ZnGramMatrixConditionsEigenValues(EigenValuesNormalized, NumberOfMatrices), ProbabilitiesContructionMethod = ProbabliltiesGenerationMethod)
+    if Conditions.getPerfectExlusion():
+        continue
+
[…]

### 2025-05-27 Scripts/Testing2.py

@@ -13,11 +13,11 @@ import numpy as np
 import matplotlib.pyplot as plt
 from tqdm import tqdm
 
-NumberOfMatrices              = 11
-MatrixDimension               = 11
+NumberOfMatrices              = 3
+MatrixDimension               = 3
 MatrixGenerationMethod        = "ZnEigenValues"
 ProbabliltiesGenerationMethod = "Equal"
-EigenValues                   = [0.1 for i in range(NumberOfMatrices - 1)]
+EigenValues                   = [1 for i in range(NumberOfMatrices - 1)]
 EigenValues.append(100)
 EigenValuesNormalized         = [iEigenValue*NumberOfMatrices/sum(EigenValues) for iEigenValue in EigenValues]
 Iterations                    = 10
@@ -25,7 +25,7 @@ StaticIterations              = 50
 Conditions                    = QSExSetUp.GramGeneratedStates.GramGeneratedStatesClass(NumberOfMatrices,MatrixDimension, MatrixGenerationMethod, QSExSetUp.GramGeneratedStates.ZnGramMatrixConditionsEigenValues(EigenValuesNormalized, NumberOfMatrices), ProbabilitiesContructionMethod = ProbabliltiesGenerationMethod)
 GroupGeneratedConditions      = QSExSetUp.GramGeneratedStates.GramGeneratedStatesClass(NumberOfMatrices,MatrixDimension, MatrixGenerationMethod, QSExSetUp.GramGeneratedStates.ZnGramMatrixConditionsEigenValues(EigenValuesNormalized, NumberOfMatrices), ProbabilitiesContructionMethod = ProbabliltiesGenerationMethod)
 
-epsilon = 0.001
+epsilon = 0.01
 
 DistanceFrobenius             = []
 Distance1                     = []
@@ -34,20 +34,28 @@ DistanceSpectral              = []
 DistanceNuclear               = []
 ExlusionSuccessProbability    = []
 
+MinimumErrorLowerBound = (round(Conditions.getPerfectExlusionLowerBoundMinimumError(),3))
+
+PossibleErrors = open(f"../Plots/PlotsExclusionNormPlots{NumberOfMatrices}.txt", "w")
+
 for iIteration in tqdm(range(Iterations),"Computing SDP"):
     for jIteration in range(StaticIterations):
[…]

### 2025-05-27 Scripts/idk.py

@@ -1,0 +1,39 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+# Example data: list of [x, y] pairs
+data = [
+    [1.0, 2.0],
+    [1.0, 2.0],
+    [2.0, 3.0],
+    [1.5, 2.5],
+    [2.0, 3.0],
+    [1.0, 2.0],
+    [2.0, 3.0],
+    [1.5, 2.5],
+]
+
+# Convert to NumPy array
+data = np.array(data)
+x = data[:, 0]
+y = data[:, 1]
+
+# Create 2D histogram
+x_bins = 10
+y_bins = 10
+heatmap, xedges, yedges = np.histogram2d(x, y, bins=[x_bins, y_bins])
+
+# Plot
+plt.figure(figsize=(8, 6))
+plt.imshow(
+    heatmap.T,
+    origin='lower',
+    aspect='auto',
+    extent=[xedges[0], xedges[-1], yedges[0], yedges[-1]],
+    cmap='hot'
+)
+plt.colorbar(label='Frequency')
+plt.xlabel('X')
+plt.ylabel('Y')
+plt.title('2D Heatmap of Frequency')
+plt.show()

### 2025-05-29 Manuscript/Lower bounds of the success probability in quantum state exclusion for general ensembles.tex
Stuff

@@
 
+\interfootnotelinepenalty=10000
+
 %%%%%%%%%%%%%%% CODELISTINGS %%%%%%%%%%%%%%%%
@@
 
-In this section we introduce some mathematical formalism of the postulates of Quantum Mechanics as well as some relevant objects in order to introduce the mathematical framework of \gls{qse} in a \gls{sdp} form.
+\hspace{20pt}In this section we introduce some mathematical formalism of the postulates of Quantum Mechanics as well as some relevant objects in order to introduce the mathematical framework of \gls{qse} in a \gls{sdp} form.
 Additionally we define the Haar measure and discuss its importance for a proper generation of generic ensembles.
@@
 
-This project is entirely situated within the quantum realm. Therefore, we begin by contextualizing the foundational postulates, notation, and elements upon which the rest of the project relies on.
+\hspace{20pt}This project is entirely situated within the quantum realm.
+Therefore, we begin by contextualizing the foundational postulates, notation, and elements upon which the rest of the project relies on.
 
@@
 
-Let $\left\{(\rho_i, \eta_i)\right\}_{i=1}^n$ be an ensemble of $n$ quantum states, where each $\rho_i$ denotes a pure state density matrix\footnote{This formulation hols true for mixed states but the project will only discuss the pure state scenario.}, i.e., $\rho_i = \ket{\psi_i}\bra{\psi_i}$, and $\eta_i$ represents the prior probability of occurrence of the state $\rho_i$.
+\hspace{20pt}Let $\left\{(\rho_i, \eta_i)\right\}_{i=1}^n$ be an ensemble of $n$ quantum states, where each $\rho_i$ denotes a pure state density matrix\footnote{This formulation hols true for mixed states but the project will only discuss the pure state scenario.}, i.e., $\rho_i = \ket{\psi_i}\bra{\psi_i}$, and $\eta_i$ represents the prior probability of occurrence of the state $\rho_i$.
 Let $\tilde{\rho}$ be a state from this ensemble.
@@
 \end{align*}
+
 If the measurement yields the outcome $\Pi_?$, i.e., the "?" label, the result is inconclusive.
@@
 \subsection{Gram Matrix Formulation}\label{sectionGramMatrixFormulation}
-The Gram matrix formulation recasts the \gls{sdp} problems associated with the exclusion task in a more basis-independent manner.
+\hspace{20pt}The Gram matrix formulation recasts the \gls{sdp} problems associated with the exclusion task in a more basis-independent manner.
 This approach reveals that the exclusion tasks for certain ensembles can be equivalent to those of others.
@@
 \end{equation*}
+
 that is, $\mathcal{G}_{i,j} = \sqrt{\eta_i\eta_j}\braket{\psi_i|\psi_j}$. Since all states are normalized, the diagonal elements are equal to $\eta_i$.
@@
 
-As we have mentioned before, analytical results have been found for the exclusion task in both protocols \gls{me} and \gls{ze} for ensembles that exhibit a certain degree of symmetry\cite{MainPaper}, that is for \emph{group-generated} ensembles.
+\hspace{20pt}As we have mentioned before, analytical results have been found for the exclusion task in both protocols \gls{me} and \gls{ze} for ensembles that exhibit a certain degree of symmetry\cite{MainPaper}, that is for \emph{group-generated} ensembles.
 In this section we present a proper definition for a group-generated ensemble as well as a brief discussion on this ensembles generated by a cyclic group, a key type of grop-generated ensembles in our analysis.
@@
 \end{align*}
+
 forms a group generated ensemble based on the cyclic group $\mathbb{Z}/n\mathbb{Z}$.
@@
 
-Here we discuss the particular case for a $\mathbb{Z}/n\mathbb{Z}$ group-generated ensemble a key type of ensemble for our project.\footnote{The relevance of this type of ensembles relies on the fact that for a prime number of states, the possible group-generated group ensemble } Let $\mathcal{U} \in U(n)$ be an $n \times n$ unitary matrix satisfying $\mathcal{U}^n = \mathds{1}$, and let $\ket{\psi}$ be the seed state.
+\hspace{20pt}Here we discuss the particular case for a $\mathbb{Z}/n\mathbb{Z}$ group-generated ensemble a key type of ensemble for our project.\footnote{The relevance of this type of ensembles relies on the fact that for a prime number of states, the possible group-generated group ensemble } Let $\mathcal{U} \in U(n)$ be an $n \times n$ unitary matrix satisfying $\mathcal{U}^n = \mathds{1}$, and let $\ket{\psi}$ be the seed state.
 The Gram matrix $\mathcal{G}^{\mathbb{Z}/n\mathbb{Z}}$ elements associated with the ensemble $\left\{\mathcal{U}^i\ket{\psi}\right\}_{i=0}^{n-1}$ are,
@@
 \end{align*}
+
 Additionally, by using the identity $\mathcal{U}^n = \mathds{1}$, we can simplify expressions such as,
@@
 \end{align*}
+
 Thus, we may write,
@@
 \end{align*}
+
 and
@@
 
-Significant progress has been made in the study of the state exclusion task for group-generated ensembles.
+\hspace{20pt}Significant progress has been made in the study of the state exclusion task for group-generated ensembles.
 In particular, the work \emph{Quantum State Exclusion for Group-Generated Ensembles of Pure States}\cite{MainPaper} presents exact analytical expressions for the success and error probabilities under both the Minimum Error (\gls{me}) and Zero Error (\gls{ze}) exclusion protocols.
@@
 \end{align*}
+
 i.e., $\frac{\lambda_1}{|G|}$ is the smallest and $\lambda_{|G|}$ the largest eigenvalue.
@@
 \end{align*}
+
 where $U$ is a unitary matrix and $D$ is the diagonal matrix of eigenvalues. We then encounter two possibilities,
@@
 
-All the code used in this project is hosted in the GitHub repository \cite{GitHub}, where additional documentation is available detailing the functionality and structure of each script and class involved in the implementation.
+\hspace{20pt}All the code used in this project is hosted in the GitHub repository \cite{GitHub}, where additional documentation is available detailing the functionality and structure of each script and class involved in the implementation.
 The numerical analysis is performed by generating ensembles uniformly distributed taking into account all possibilities and then solving the \gls{sdp} problems presented in Section \ref{sectionFormulationOfTheProblem}.
@@
 \end{align*}
+
 These values are used as the eigenvalues of the Gram matrix, forming the diagonal matrix $D = \operatorname{diag}(\lambda_1, \dots, \lambda_n)$.
@@
 
-The begining of the analysis consists in showing up the key differences between \gls{me} and \gls{ze} protocols, and the concordance of the \gls{sdp}'s numerical results with the analytical results given in \ref{sectionPreviousResults}.
+\hspace{20pt}The begining of the analysis consists in showing up the key differences between \gls{me} and \gls{ze} protocols, and the concordance of the \gls{sdp}'s numerical results with the analytical results given in \ref{sectionPreviousResults}.
 
@@
 
-Here we present a comparison between both protocols for \gls{ze} and \gls{me} giving insights on the protocols's essence and contextualising the problem in a visual way.
+\hspace{20pt}Here we present a comparison between both protocols for \gls{ze} and \gls{me} giving insights on the protocols's essence and contextualising the problem in a visual way.
 
@@
 In particular Figure (\ref{FigureQSEMEZ3ZHeatmap}) shows two heatmaps of the average successful exclusion probability under the Minimum Error (\gls{me}) protocol for a $\mathbb{Z}/3\mathbb{Z}$ group-generated ensemble.
-Probabilities are shown as functions of the modulus $|c|$ ($x$-axis) and phase $\theta$ ($y$-axis) of the overlap $c=|c|^{i\theta}$, which fully determine the Gram matrix.
+Probabilities are shown as functions of the modulus $|c|$ ($x$-axis) and phase $\theta$ ($y$-axis) of the overlap $c=|c|^{i\theta}$, which fully determines the Gram matrix.
 Notice we take equal prior probabilities, as discussed in the analytical results in Section (\ref{sectionPreviousResults}).
@@
 
-In this section, we present the results for ensembles generated by the group $\mathbb{Z}/3\mathbb{Z}$, analyzed across the spectrum of eigenvalues, i.e.
+\hspace{20pt}In this section, we present the results for ensembles generated by the group $\mathbb{Z}/3\mathbb{Z}$, analyzed across the spectrum of eigenvalues, i.e.
 the analogus results from the previos section in the eigenvalues spectum.
@@
 \end{align*}
+
 The limit case scenarios corresponding to $\lambda_i=3$ and $\lambda_j,\lambda_k=0$ are located in the vertex of the triangle\footnote{Remember this case correspond to sets with the same state repeated 3 times discussed in Section (\ref{sectionLimitCaseScenarios})}.
@@
 \subsection{Distribution of the general ensembles success exclusion probability}
-Here we present the main results of the project.
-Hence we show an analytical results for generic ensembles and how the success exclusion probability ensembles are distributed over the results for group-generate ensembles, i.e.
-the lower bound.
-
-We know every Gram Matrix $\mathcal{G}$ can be written as $\mathcal{G}=UDU^\dagger$.
-By fixing the eigenvalues $\{g_i\}_{i=1}^n$, i.e.
-the elements of the diagonal matrix $D$\footnote{Note we have changed the notation respect the previous  eigenvalues since before we were taking the eigenvalues of the Gram Matrix where factoring out $\frac{1}{n}$ in the equal prior probabilities scenario.
-This eigenvalues were normalised to $n$, so we change the notation for avoiding any possible confusion.}, as normalised elements,
-\begin{align*}
-\sum_{i=1}^ng_i=1
-\end{align*}
-
-With this elements we can compute the lower bound given in section (\ref{sectionPreviousResults}) and find whether they are in the perfect exclusion region or not.
-If they are, any Gram matrix generated via $G=UDU^\dagger$ would represent a set of ensembles such that perfect exclusion can be archived and the lower bound would be the exact result.
-Otherwise, if we are in the non-perfect exclusion region by interchanging the unitary matrices $U$ we can generate different sets of Gram matrices such that
-
-Since the algorithm introduced by Francesco Mezzadri in \cite{UnitaryMatricesGeneration}
+
+\hspace{20pt}In this section, we present the main results of the project.
+Specifically, we provide analytical results for generic ensembles and examine how the success probabilities for quantum state exclusion are distributed in relation to the lower bound defined by group-generated ensembles.
+
+We begin by recalling that any Gram matrix $ \mathcal{G} $ can be decomposed as $ \mathcal{G} = U D U^\dagger $, where $ D $ is a diagonal matrix containing the eigenvalues $\{g_i\geq0\}_{i=1}^n $.
+We fix these eigenvalues such that
+\begin{align*}
+\sum_{i=1}^n g_i = 1,
+\end{align*}
+ensuring they are normalized.\footnote{Note that this eigenvalue notation differs from that used earlier in the document, where the eigenvalues of the Gram matrix were considered with an overall normalization factor of \( \frac{1}{n} \), assuming equal prior probabilities and were normalised to $n$.
+To avoid confusion, we change the notation for normalised eigenvalues that sum up to 1 for the general prior probabilities case.}
+
+With this eigenvalue spectrum, we compute the analytical lower bound introduced in Section~\ref{sectionPreviousResults} and determine whether it falls within the perfect exclusion region.
+If it does, then any Gram matrix generated as $ \mathcal{G} = U D U^\dagger $ represents an ensemble for which perfect exclusion is feasible, and the lower bound is in fact the success probability, i.e.
+both are 1.
+Conversely, if the lower bound lies outside the perfect exclusion region, we explore different unitary matrices $ U $ to generate alternative Gram matrices that share the same eigenvalues, thus preserving the lower bound, while corresponding to distinct ensembles.
+
+We use the algorithm proposed in~\cite{UnitaryMatricesGeneration} to generate unitary matrices sampled uniformly from \( U(n) \).
+This ensures a comprehensive exploration of the space of possible Gram matrices, i.e., ensembles, corresponding to a fixed lower bound.
+
+It is important to highlight that this method also implicitly generates random prior probabilities for each state, since the diagonal elements of the Gram matrix are the priors probabilities, and generally will differ from one to another.
+Nevertheless, the analytical lower bound remains valid, as we will show in the following results.
 
@@
 	\includegraphics[width=0.75\textwidth, trim={1.0cm 0.3cm 2.4cm 1.5cm}, clip]{../Plots/ExclusionMinimumErrorRandomDistributionZ3Prob0.962.pdf}
-	\caption{Hisotgram depicting the distribution of the generated Gram Matrices over the }
+	\caption{Hisotgram depicting the distribution of generated Gram Matrices via the success probability for \gls{me} protocol with a lower bound of 0.962 for 5 states ensembles of random priors probabilities.}
 	\label{FigureDistZ5ME0.962}
 \end{figure}
+
+Figure (\ref{FigureDistZ5ME0.962}) shows the distribution of success probabilities for quantum state exclusion using the \gls{me} protocol computed via semidefinite programming (\gls{sdp}) for 5 states ensembles and random priors probabilities.
+The histogram's $x$-axis represents the exclusion success probability, while the $y$-axis indicates the frequency of occurrence across sampled ensembles.
+Additionally the dashed blue line marks the analytical lower bound.
+
+We emphasize that each computed result has been verified not to fall below this analytical lower bound.
+Although a few discrepancies were observed, these occurred only at the fifth decimal place, where numerical precision limitations in the \gls{sdp} solver can affect reliability.
+These cases are treated as inconclusive due to numerical problems, and no inconsistencies have been found exceeding a deviation in the fourth decimal.
+
+From the results in Figure (\ref{FigureDistZ5ME0.962}), we observe the ensembles are broadly distributed across a range of success probabilities.
+However, a significant clustering occurs near a success probability of 1 under the \gls{me} protocol, indicating that perfect exclusion is achievable for a substantial subset of these randomly generated ensembles.
+
+These ensembles were generated uniformly by sampling unitary matrices $ U $ from $U(n)$, which determine the Gram matrices via the decomposition $\mathcal{G} = U D U^\dagger$.
+Ensembles with Gram matrices structurally similar to those of group-generated ensembles, particularly those diagonalized in the Fourier basis\footnote{Recall that we are working with ensembles of a prime number of states, for which the only known analytical result corresponds to the Gram matrix generated by $\mathbb{Z}/n\mathbb{Z}$, which is diagonalized in the Fourier basis.
+A more complete study would consider other group-generated cases.}, yield lower success probabilities.
+
+Interestingly, there exists a threshold of deviation from the Fourier basis beyond which all ensembles yield a success probability of 1.
+In other words, beyond a certain \emph{distance} from the group-generated case, i.e.
+the Fourier basis, the ensembles become sufficiently distinguishable to allow perfect exclusion, regardless of the specific basis in which their Gram matrices are diagonalised.
+
+At this stage we can observe the crucial importance of the generation of the unitary matrices uniformly covering  $U(n)$, i.e.
+being generated according to the Haar measure.
+If we could not ensure we are exploring all the possible ensembles this observations and the study of the generic ensembles case would be completely pointless since we can overrepresent one specific kind of ensambles respect to others.
+
+In Figure (\ref{FigureDistZ5ZE0.5}) we present the analogous results for the \gls{ze} protocol for ensembles consisting in 5 states with eigenvalues that lead to an analytical lower bound for success probability of $0.5$ in this protocol.
 
@@
 	\includegraphics[width=0.75\textwidth, trim={1.0cm 0.3cm 2.4cm 1.5cm}, clip]{../Plots/ExclusionZeroErrorRandomDistributionZ3Prob0.5.pdf}
-	\caption{Hisotgram of the group genearation }
+	\caption{Hisotgram depicting the distribution of generated Gram Matrices via the success probability for \gls{ze} protocol with a lower bound of 0.5 for 5 states ensembles of random priors probabilities.}
 	\label{FigureDistZ5ZE0.5}
@@
 
+Thus, we observe a similar behaviour respect to Figure (\ref{FigureDistZ5ME0.962}), still we attribute the pick of ensembles where perfect exclusion is feasible to the threshold of the \emph{distance} from the group generated case as previously discussed.
+Still some remarkable aspect of this protocol is the constant is the constant decay in the frequency for higher exclusion probabilities.
+
+As before, no ensembles yields lower success exclusion probabilities than the lower bound, proving this as a lower bound of the generic case scenario.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.49\textwidth, trim={1.0cm 0.3cm 2.4cm 1.5cm}, clip]{../Plots/ExclusionMinimumErrorRandomDistributionZ7Prob0.924.pdf}
+	\includegraphics[width=0.49\textwidth, trim={1.0cm 0.3cm 2.4cm 1.5cm}, clip]{../Plots/ExclusionMinimumErrorRandomDistributionZ11Prob0.926.pdf}
+	\caption{Hisotgram depicting the distribution of generated Gram Matrices via the success probability for \gls{me} protocol with a lower bound of 0.92 for 7 states (left) and 11 states (right) ensembles of random priors probabilities.}
+	\label{FigureDistZ5ZE0.5}
+\end{figure}
+
 \subsection{Intuition behind the results}
 
-The intuition behind the exclusion task for group-generated ensembles being the worst case scenario for this task, thus yielding a lower bound for the probability of excluding a hypothesis state in the general case is as follows.
+\hspace{20pt}The intuition behind the exclusion task for group-generated ensembles being the worst case scenario for this task, thus yielding a lower bound for the probability of excluding a hypothesis state in the general case is as follows.
 Consider an ensemble $\{\ket{\psi_i}\}_{i=1}^n$ with a certain degree of symmetry, and a state $\ket{\psi_j}$ known to be a member of this ensemble.
@@
 
-We have numerically verified the analytical results for the success and error probabilities for exclusion of group-generated ensembles, presented in Section~(\ref{sectionPreviousResults}), serve as lower bounds for these probabilities in the general case.
-Additionally, we have provided insights and intuition supporting why these results act as lower bounds for random ensembles.
-
-Furthermore, we have deeply discussed and presented the specific case of $\mathbb{Z}/3\mathbb{Z}$, which is the only group-generated ensemble that can be represented in a two-dimensional plot.
-
-Finally, we have highlighted the advantages of Quantum State Exclusion (\gls{qse}) over its counterpart, Quantum State Discrimination (\gls{qsd}), thereby motivating further research into hybrid protocols that combine \gls{qse} and \gls{qsd}.
-Such hybrid approaches may lead to more optimal protocols in certain scenarios.
+\hspace{20pt}We have presented a robust protocol for generating ensembles of quantum states, along with their corresponding prior probabilities, in a manner that uniformly samples the full space of possible ensembles.
+This approach ensures a comprehensive and unbiased exploration for the study of Quantum State Exclusion (\gls{qse}).
+Using this ensemble generation method, we have computed the corresponding Semidefinite Programming (\gls{sdp}) optimization problems, allowing us to numerically verify and support the analytical results obtained for the success and error probabilities associated with group-generated ensembles.
+
+The analytical results, presented in Section~\ref{sectionPreviousResults} \emph{Previous Results}, for the success probability in Quantum State Exclusion (\gls{qse}) for the Minimum Error (\gls{me}) and Zero Error (\gls{ze}) protocols for equal prior probabilities for group-generated ensambles have provide lower bounds for the success probability in Quantum State Exclusion (\gls{qse}) the same protocols.
+Our numerical simulations confirm that these group-generated ensembles consistently achieve the lowest exclusion success probabilities, thus validating their role as theoretical lower bounds when compared to the broader set of randomly generated ensembles.
+We have also offered conceptual insights into the intuition of why these bounds persist in the general case, including a geometric interpretation based on Gram matrix structure and ensemble distinguishability.
+
+In addition, we have explored in detail the specific case of the cyclic group $\mathbb{Z}/3\mathbb{Z}$, the only group-generated ensemble that can be faithfully represented in two dimensions.
+This visualization not only has provided intuition but also demonstrates the practical advantage of \gls{qse} over its counterpart, Quantum State Discrimination (\gls{qsd}).
+These results strengthen the case for employing \gls{qse} in quantum information tasks where conventional discrimination strategies fall short.
+
+The observations made in this project open the door to further analytical and numerical investigations.
+Extending this analysis to more generic ensembles, that may reveal new structural properties and exclusion capabilities.
+Furthermore, from the results and discussions in this project it results obvious that research in hybrid protocols that interpolate between Minimum Error \gls{me} and Zero Error \gls{ze} protocols as well as \gls{qse} and \gls{qsd} could potentially yield more optimal performance in practical applications.
+
+In summary, this work contributes both rigorous numerical evidence and conceptual motivation for viewing group-generated ensembles as the worst case scenario in the study of quantum state exclusion, i.e.
+leading up to a lower bound in the exclusion probability.
+It also highlights promising directions for future work, including the development of tighter bounds, hybrid exclusion strategies, and generalizations of the analitical results.
 
@@
 
-I am grateful to Dr.
+\hspace{20pt}I am grateful to Dr.
 Ramón Muñoz Tapia for allowing me to be one of his pupils and for presenting this project.
@@
 
-It is often useful to consider the \emph{dual} version of a \gls{sdp} problem, as it provides both conceptual insights and practical advantages for verifying optimality.
+\hspace{20pt}It is often useful to consider the \emph{dual} version of a \gls{sdp} problem, as it provides both conceptual insights and practical advantages for verifying optimality.
 
@@
 
-We can compute the Gram matrix for any group-generated ensemble by using the Cayley table~\cite{CayleyTable}, also known as the \emph{multiplication table}, of the group.
+\hspace{20pt}We can compute the Gram matrix for any group-generated ensemble by using the Cayley table~\cite{CayleyTable}, also known as the \emph{multiplication table}, of the group.
 For example, consider the smallest non-commutative group, $S_3$, consisting of the symmetries and rotations of an equilateral triangle.
@@
 \end{align*}
+
 Notice we have assumed equal prior probabilities, i.e.
@@
 \end{align*}
+
 which implies the unitary matrices corresponding to the triangle symmetries $p$, $q$, and $r$ are Hermitian.
@@
 
-Here we present the results for the Quantum State Discrimination (\gls{qsd}) task to motivate the problem and highlight contrasts with the Quantum State Exclusion (\gls{qse}) task, which is the focus of this study.
+\hspace{20pt}Here we present the results for the Quantum State Discrimination (\gls{qsd}) task to motivate the problem and highlight contrasts with the Quantum State Exclusion (\gls{qse}) task, which is the focus of this study.
 
@@
 \end{align*}
+
 and is the standard in \gls{qsd} under the \gls{me} protocol \cite{OptimalitySRM}.
@@
 \end{align*}
+
 were $S_{i,i}$ denotes the diagonal elements of $S$ and $n$ the number of quantum states\footnote{In this case we are taking $n=3$.}.
@@
 
-Let us study the Gram matrix of a limit ensemble composed of $n$ identical quantum states with equal probabilities, i.e.
+\hspace{20pt}Let us study the Gram matrix of a limit ensemble composed of $n$ identical quantum states with equal probabilities, i.e.
 the same state is repeated $n$ times in the ensemble with the same probability.\footnote{This case may appear paradoxical, since there is no way to distinguish between identical states.
@@
 \end{align*}
+
 which means that the set $\{\rho_i\}$ is itself a \gls{povm}.

### 2025-05-29 Scripts/PlotDistributionProbability2D.py

@@ -18,11 +18,11 @@ from collections import Counter
 from picos.modeling.problem import SolutionFailure  
 
 
-NumberOfMatrices              = 5
-MatrixDimension               = 5
+NumberOfMatrices              = 7
+MatrixDimension               = 7
 MatrixGenerationMethod        = "Random"
 ProbabliltiesGenerationMethod = "Equal"
-IterationsRandomSets          = 10000
+IterationsRandomSets          = 100000
 DataMinimumError              = []
 EigenValue0                   = []
 EigenValue1                   = []
@@ -31,42 +31,53 @@ SDPZeroErrorList              = []
 LowerBound                    = []
 LowerBoundZE                  = []
 EigenValues = [1 for i in range (NumberOfMatrices-1)]
-EigenValues.append(50000)
+EigenValues.append(70)
 EigenValuesNormalized   = [iEigenValue*NumberOfMatrices/sum(EigenValues) for iEigenValue in EigenValues]
 
+mode = "ZE"
 
 for iIteration in tqdm(range(IterationsRandomSets),f"Computing points for the Minimum Error plot"):
     Conditions = QSExSetUp.GramGeneratedStates.GramGeneratedStatesClass(NumberOfMatrices,MatrixDimension,MatrixGenerationMethod, QSExSetUp.GramGeneratedStates.ZnGramMatrixConditionsEigenValues(EigenValuesNormalized, NumberOfMatrices), ProbabilitiesContructionMethod = ProbabliltiesGenerationMethod)
+    if (iIteration == 0):
+        print("Minimum Error Lower Bound: ",round(Conditions.getPerfectExlusionLowerBoundMinimumError(),4))
+        print("Minimum Error random gess: ",(NumberOfMatrices-1)/NumberOfMatrices)
+        print("Zero Error Lower Bound:    ",round(Conditions.getPerfectExlusionLowerBoundZeroError(),4))
+
     if Conditions.getPerfectExlusion():
         continue
+    if mode == "ME" or mode == "both":
+        MinimumErrorResult = round(QSExSetUp.SDPSolver.SolveSDPExclusionMinimumError(Conditions)['SDPSolution'],4)
+        if (MinimumErrorResult < round(Conditions.getPerfectExlusionLowerBoundMinimumError(),4)):
[…]

### 2025-05-29 Manuscript/Lower bounds of the success probability in quantum state exclusion for general ensembles.tex
Stuff

@@
 
+\subsection{Haar Measure}
+\hspace{20pt}In this section, we introduce the concept of a measure on a topological space and define the Haar measure.
+This is one of the key theoretical tools underlying this project, as we use the Haar measure to ensure a uniform and unbiased sampling of ensembles when generating Gram matrices for general ensembles.
+
+Let \( \Omega \) be a set, and let \( \Sigma \) be a \( \sigma \)-algebra over \( \Omega \).
+A measure \( \mu \) on the measurable space \( (\Omega, \Sigma) \) is a set function \( \mu : \Sigma \to \mathbb{R}_{\geq 0} \) that satisfies the following properties:
+\begin{itemize}
+	\item Positive semidefiniteness, i.e. for any $\chi\in\Sigma$ we have $\mu(\chi)\geq 0$.
+	\item $\mu(\emptyset)=0$.
+	\item Sigma additivity, i.e.
+given a countable set $\{\chi_i\in\Sigma|i\in\mathbb{N}\}$ of pairwise-disjoint sets\footnote{This means that $\chi_i\cap\chi_j=\emptyset$ for any $i,j\in\mathbb{N}$ if $i\neq j$.} $\mu$ fulfils,
+	\begin{align*}
+		\mu\left(\bigcup_{i=1}^\infty \chi_i\right)=\sum_{i=1}^\infty \mu(\chi_i).
+	\end{align*}
+\end{itemize}
+
+Now, let \( \Omega \) be a topological group.
+A Haaar measure \( \mu \) on a set \( \Omega \) is a measure defined on the Borel \( \sigma \)-algebra \( \Upsilon \) of \( \Omega \)\footnote{A full definition of Borel sets is beyond the scope of this work, it is enough to say they are sets generated from the open sets of \( \Omega \) through countable unions, intersections, and complements.}, satisfying the following properties:
+\begin{itemize}
+	\item Invariance under transition, i.e. for any $\omega \in \Omega$ and $\upsilon \in \Upsilon$ we have $\mu(\omega\upsilon)=\mu(\upsilon)$.
+	\item The measure is finite for any compact Borel subset, i.e. for any $\upsilon\in\Upsilon$ compact we have that $\mu(\upsilon)<\infty$.
+	\item $\mu$ is outer regular, i.e. for any $\upsilon\in\Upsilon$
+		\begin{align*}
+			\mu(\upsilon)=\inf_{\vartheta\:\text{open}}\{\mu(\vartheta)|\upsilon\subseteq\vartheta\}
+		\end{align*}
+	\item $\mu$ is inner regular, i.e. for any open $\upsilon\in\Upsilon$,
+		\begin{align*}
+			\mu(\upsilon)=\sup_{\vartheta\:\text{compact}}\{\mu(\vartheta)|\vartheta\subseteq\upsilon\}
+		\end{align*}
+\end{itemize}
+
+It can be shown that the Haar measure is unique up to a constant multiple. In particular, since we are working with the set of unitary matrices,
+\begin{align*}
+	U(n) = \{ U \in \mathbb{C}^{n \times n} \mid U^\dagger U = \mathds{1} \},
+\end{align*}
+
+which is compact in the usual topology, from the secon property we know the Haar measure \( \mu \) on \( U(n) \) to be finite.
+Therefore, we can normalize it so that \( \mu(U(n)) = 1 \), fully determining the measure.
+Moreover, since from the first property we know \( \mu \) is invariant under group multiplication, it is uniformly distributed over \( U(n) \).
+This allows us to generate unitary matrices that are randomly and uniformly distributed with respect to the Haar measure.
+
 \newpage
@@
 
-\hspace{20pt}All the code used in this project is hosted in the GitHub repository \cite{GitHub}, where additional documentation is available detailing the functionality and structure of each script and class involved in the implementation.
+\hspace{20pt}All the used code in this project is hosted in the GitHub repository \cite{GitHub}, where additional documentation is available detailing the functionality and structure of each script and class involved in the implementation.
 The numerical analysis is performed by generating ensembles uniformly distributed taking into account all possibilities and then solving the \gls{sdp} problems presented in Section \ref{sectionFormulationOfTheProblem}.
@@
 	\includegraphics[width=0.49\textwidth, trim={1.0cm 0.3cm 2.4cm 1.5cm}, clip]{../Plots/ExclusionMinimumErrorRandomDistributionZ11Prob0.926.pdf}
-	\caption{Hisotgram depicting the distribution of generated Gram Matrices via the success probability for \gls{me} protocol with a lower bound of 0.92 for 7 states (left) and 11 states (right) ensembles of random priors probabilities.}
-	\label{FigureDistZ5ZE0.5}
+	\caption{Hisotgram depicting the distribution of generated Gram Matrices via the success probability for \gls{me} protocol with a lower bound of 0.926 for 7 states (left) and 11 states (right) ensembles of random priors probabilities.}
+	\label{FigureDistZ7Z11}
 \end{figure}
+In Figure~\ref{FigureDistZ7Z11}, we present the corresponding results for the \gls{me} protocol applied to ensembles composed of 7 (left) and 11 (right) quantum states, with a lower bound on the success exclusion probability of 0.926.
+As the number of states increases, the distribution approaches a Landau shape \cite{landau}.
+For ensembles of 7 elements, we still observe the phenomenon of accumulation near the perfect exclusion region.
+However, in the case of 11 states, only a small fraction of ensembles reach the perfect exclusion regime since the peak of the distribution is more narrow and the ensembles tend to agglomerate exclusion probabilities arround this peak.
 
@@
 Denoting the identity as $e$, the rotations elements as $s$, $s^2$ (one being the result of 2 times the other) and the symmetries $p$, $q$, and $r$, the Cayley table is,
-
 \begin{table}[H]
@@
     \caption{Cayley table of the $S_3$ group.}
-	\begin{tabular}{c||c c c c c c}
-        $S_3$ & $e$ & $s$ & $s^2$ & $p$ & $q$ & $r$ \\\hline\hline
+    \label{tab:Cayley-S3}
+    \setlength{\tabcolsep}{12pt}
+    \renewcommand{\arraystretch}{1.3}
+    \begin{tabular}{|>{\columncolor{gray!20}}c||c|c|c|c|c|c|}
+        \hline
+        \rowcolor{gray!20}
+        $S_3$ & $e$ & $s$ & $s^2$ & $p$ & $q$ & $r$ \\
+        \hline\hline
         $e$   & $e$ & $s$ & $s^2$ & $p$ & $q$ & $r$ \\
@@
         $q$   & $q$ & $p$ & $r$ & $s$ & $e$ & $s^2$ \\
-        $r$   & $r$ & $q$ & $p$ & $s^2$ & $s$ & $e$
+        $r$   & $r$ & $q$ & $p$ & $s^2$ & $s$ & $e$ \\
+        \hline
     \end{tabular}

### 2025-06-02 Manuscript/Lower bounds of the success probability in quantum state exclusion for general ensembles.tex
Stuff

@@
 \usepackage{url}
-\usepackage{natbib}
+%\usepackage{natbib}
+\usepackage[numbers,square]{natbib}
+\bibliographystyle{unsrtnat}
+%\usepackage[style=numeric,sorting=none]{biblatex}
+
 \usepackage[normalem]{ulem}
@@
 \newpage
+\pagestyle{empty}
+\headheight 35pt
+\lhead{\NetIDb}    
+\rhead{\subject}
+\cfoot{}
+\headsep 1.5em
+
+\section*{abstract}
+\vspace{1cm}
+\hspace{20pt}Unlike the well-studied problem of \gls{qsd}, which aims to identify an unknown quantum state from a known ensemble, \gls{qse} focuses on confidently ruling out one or more possible candidates.
+This approach becomes particularly valuable in scenarios where exclusion can be achieved without error.
+
+This project investigates \gls{qse} under two principal protocols, \gls{me}, which aims to minimize the risk of incorrectly excluding the true state, and \gls{ze}, which seeks to guarantee perfect exclusion at the cost of potentially inconclusive outcomes.
+Building on recent analytical results for group generated ensembles in these protocols \cite{MainPaper}, we carry out a numerical study of \gls{qse} task using \gls{sdp} techniques, analyzing general ensembles and benchmarking them against the  group generated cases, i.e.
+the lower bound.
+
+We begin by introducing the mathematical formulation of the \gls{qse} problem and the theoretical tools necessary to interpret our results.
+We also describe a protocol for generating random generic ensembles in a homogeneous manner according to the Haar measure.
+
+Our findings confirm that the analytical bounds established for group generated ensembles serve as effective lower bounds for more general cases.
+We present detailed results for three-state ensembles and examine the statistical distribution of correct exclusion probabilities for randomly sampled ensembles.
+Furthermore, we provide theoretical insights and intuition to support the observed behavior.
+
+These results underscore the unique role of \gls{qse} in quantum information theory, particularly in contexts where partial state inference and hypothesis elimination are more feasible or desirable than full state identification.
+
+\newpage
 \thispagestyle{empty}
@@
 \setcounter{page}{1}
-\begin{center}
-\begin{abstract}
-Given a quantum state known to be prepared from an ensemble of two or more states, quantum state exclusion aims to rule out the possibility that it was prepared in a particular state from the ensemble.
-Using the known solution for group generated ensembles \cite{MainPaper}, we study this result as a lower bound for randomly generated ensembles via semidefinite programming.
-\end{abstract}
-\end{center}
 %Keywords: \emph{SDP, Quantum state exclusion , \textcolor{blue}{Add keywords}}.
-\section{Introduction}
+\section{Introduction}	\label{sectionIntroduction}
 
@@
 
-In the quantum realm, a similar line of reasoning can be applied in some problmes.
+In the quantum realm, a similar line of reasoning can be applied in some tasks in this field.
 One of the fundamental tasks in quantum information theory is the identification of an unknown quantum state known to belong to a given ensemble of possible states.
@@
 However, instead of aiming to identify the exact state, we may take another approach by applying the hypothesis exclusion idea.
-That is, given a quantum state known to be one among a certain ensemble, the goal becomes to conclusively rule out the possibility of the unknown state being a specific member of that ensemble.
+That is, given a quantum state known to be one among a certain ensemble, the goal becomes to rule out the possibility of the unknown state being a specific member of that ensemble.
 This alternative task is known as Quantum State Exclusion (\gls{qse}) \cite{PhysicsExclusionSource}, and it offers a distinct framework with its own set of advantages \cite{piani2020quantum} with respect to its counterpart \gls{qsd}.
@@
 the protocols for which analytical results have been presented \cite{MainPaper}.
-In the Minimum Error scenario, the goal is to minimize the probability of mistakenly excluding the actual prepared state.
-In contrast, the Zero Error approach seeks to exclude a state with absolute certainty, although this procedure sometimes yields an inconclusive result when perfect exclusion cannot be accomplished.
+In the \gls{me} scenario, the goal is to minimize the probability of mistakenly excluding the actual prepared state.
+In contrast, the \gls{ze} approach seeks to exclude a state with absolute certainty, although this procedure sometimes yields an inconclusive result when perfect exclusion cannot be accomplished.
 
 While \gls{qsd} has seen significant progress over the years \cite{bae2015quantum, helstromBook}, \gls{qse} has remained relatively underexplored until recently.
-New analytical results have emerged \cite{MainPaper} for both the \gls{me} and \gls{ze} protocols, particularly when the ensemble of quantum states possesses a certain degree of symmetry.
+New analytical results have emerged \cite{MainPaper} for both the \gls{me} and \gls{ze} protocols.
 In particular, when the ensemble is generated through the action of a finite algebraic group, the problem becomes more tractable, highlighting \gls{qse} as a worthwhile object of study.
@@
 Although the tasks of exclusion and discrimination coincide for ensembles containing only two states\footnote{Since for the two states case excluding one necessarily implies identifying the other.}, when dealing with ensembles of three or more states, the two problems diverge in both approach and complexity.
-Though this work primarily focuses on \gls{qse}, we include a comparative discussion of both tasks and protocols to further motivate the interest in \gls{qse} and discuss the main differences with \gls{qsd} in Appendix \ref{appendixComparisonQSDvsQSE}.
+In order to further motivate the interest in \gls{qse} and discuss the main differences, we include a brief comparison of both tasks and protocols  with \gls{qsd} in Appendix \ref{appendixComparisonQSDvsQSE}.
 One of the key features of \gls{qse} is the possibility of achieving \emph{perfect exclusion}, i.e.
-confidently ruling out a candidate state with complete certainty that it is not the unknown state.
+confidently ruling out a candidate state with complete certainty that it is different from our given unknown state.
 In contrast, \emph{perfect discrimination} is generally not achievable, meaning that one cannot identify the unknown state with absolute certainty in most settings\cite{OptimalitySRM}.
@@
 
-Building upon the recent results for the probability of a correct exclusion for group-generated ensembles \cite{MainPaper},\footnote{A proper definition of a \emph{group generated ensemble} will be given in the \emph{Group generated ensembles} section \ref{sectionGroupGeneratedEnsemble}, for the time being, we can identify them as ensembles that comprehend set of states that exhibit a certain symmetry.} this project undertakes a numerical investigation into \gls{qse}, highlighting the analytical results from group-generated ensembles as lower bounds for more general cases.
+Building upon the recent results for the probability of a correct exclusion for group generated ensembles \cite{MainPaper},\footnote{A proper definition of a \emph{group generated ensemble} will be given in the \emph{Group generated ensembles} section \ref{sectionGroupGeneratedEnsemble}, for the time being, we can identify them as ensembles that comprehend set of states that exhibit a certain symmetry.} this project undertakes a numerical investigation into \gls{qse}, highlighting the analytical results from group generated ensembles as lower bounds for more general cases.
 The project comences with a preliminaries section that outlines the mathematical framework underlying the \gls{qse} task, along with the essential tools used in our analysis.
@@
 
-To carry out our numerical analysis, we employ \gls{sdp} techniques, which allow us to cast the \gls{qse} task as a convex optimization problem.
-The \gls{sdp} approach has proven particularly effective for problems of this kind \cite{bandyopadhyay2014conclusive}.
-Finally, ve conclude by providing some theoretical intuition and insights based on our results.
+To carry out our numerical analysis, we employ \gls{sdp} techniques,\cite{vandenberghe1996semidefinite} which enable us to formulate the \gls{qse} task as a convex optimization problem.
+The \gls{sdp} approach has proven particularly effective for problems of this nature \cite{bandyopadhyay2014conclusive}.
+Finally, we conclude by providing some theoretical intuition and insights based on our results.
 
@@
 
-Unlike projective measurements, the operators $\Pi_i$ in a POVM are not necessarily orthogonal projectors.
+Unlike projective measurements, the operators $\Pi_i$ in a \gls{povm} are not necessarily orthogonal projectors.
 This allows the number of measurement outcomes to exceed the dimensionality of the Hilbert space, extending the previos orthogonal measurement to a more generic status and making POVMs particularly useful in tasks such as \gls{qse} and \gls{qsd}.
@@
 
-\hspace{20pt}Let $\left\{(\rho_i, \eta_i)\right\}_{i=1}^n$ be an ensemble of $n$ quantum states, where each $\rho_i$ denotes a pure state density matrix\footnote{This formulation hols true for mixed states but the project will only discuss the pure state scenario.}, i.e., $\rho_i = \ket{\psi_i}\bra{\psi_i}$, and $\eta_i$ represents the prior probability of occurrence of the state $\rho_i$.
+\hspace{20pt}Let $\left\{(\rho_i, \eta_i)\right\}_{i=1}^n$ be an ensemble of $n$ quantum states, where each $\rho_i$ denotes a pure state density matrix\footnote{This formulation holds true for mixed states but the project will only consider the pure state scenario.}, i.e., $\rho_i = \ket{\psi_i}\bra{\psi_i}$, and $\eta_i$ represents the prior probability of occurrence of the state $\rho_i$.
 Let $\tilde{\rho}$ be a state from this ensemble.
@@
 
-Quantum measurements are described by a set of \glspl{povm}, denoted by $\left\{\Pi_i\right\}_{i=1}^n$, acting on the Hilbert space $\mathcal{H}$ of the quantum system.
-Here we present the two studied protocols for \gls{qse}: minimum-error (\gls{me}) and zero-error (\gls{ze}).
+Additionally, let $\left\{\Pi_i\right\}_{i=1}^n$ be a set of \glspl{povm} acting on the Hilbert space $\mathcal{H}$ of the quantum system.
+Here we present the two studied protocols for \gls{qse}: Minimum Error (\gls{me}) and Zero Error (\gls{ze}).
 
 As previously discussed the goal of the \gls{me} protocol is to minimize the probability of incorrectly excluding the unknown state from our hypothesis.
-If we formulate it as an \gls{sdp}, the \gls{sdp} minimization of the error probability reads,\footnote{Note that the \gls{sdp} formulations of quantum state discrimination may differ from the exclusion ones by interchanging minimization and maximization problems.}
+If we formulate the error probability as an \gls{sdp}, we obtain,\footnote{Note that SDP formulations for quantum state discrimination may differ from exclusion tasks by interchanging minimization and maximization objectives.}
 \begin{align*}
@@
 
-In the case of the \gls{ze} protocol, the objective is to exclude with total accuracy a state known to be different from the unkown state.
+In the case of the \gls{ze} protocol, the objective is to exclude with total certainty a state known to be different from the unkown state.
 However, the protocol might lead to inconclusive result.
@@
 
-If the measurement yields the outcome $\Pi_?$, i.e., the "?" label, the result is inconclusive.
+If the measurement yields the outcome "?" , the result is inconclusive.
 
@@
 That is, their optimal success and error probabilities coincide.
-Consequently, we focus on the Gram matrix to study exclusion problems rather than the explicit state representations.
+Consequently, we focus on the Gram matrix to study exclusion problems rather than the explicit state representations, as it encodes all the relevant information.
 
@@
 
-\hspace{20pt}As we have mentioned before, analytical results have been found for the exclusion task in both protocols \gls{me} and \gls{ze} for ensembles that exhibit a certain degree of symmetry\cite{MainPaper}, that is for \emph{group-generated} ensembles.
-In this section we present a proper definition for a group-generated ensemble as well as a brief discussion on this ensembles generated by a cyclic group, a key type of grop-generated ensembles in our analysis.
+\hspace{20pt}As we have mentioned before (Section \ref{sectionIntroduction}), analytical results have been found for the exclusion task in both protocols \gls{me} and \gls{ze} for ensembles that exhibit a certain degree of symmetry\cite{MainPaper}, that is for \emph{group generated} ensembles.
+In this section we present a proper definition for a group generated ensemble as well as a brief discussion on this ensembles generated by a cyclic group, a key type of group generated ensembles in our analysis.
 
@@
 This type of ensemble is of particular interest in our study and will be explored in more detail at the end of this section.
-Additionally, in Appendix \ref{appendixComputationGroupGeneratedGramMatrices} we present a general procedure to compute the Gram Matrix for any group-generated ensemble.
-
-\subsubsection*{The $\mathbb{Z}/n\mathbb{Z}$ group-generated ensemble}
-
-\hspace{20pt}Here we discuss the particular case for a $\mathbb{Z}/n\mathbb{Z}$ group-generated ensemble a key type of ensemble for our project.\footnote{The relevance of this type of ensembles relies on the fact that for a prime number of states, the possible group-generated group ensemble } Let $\mathcal{U} \in U(n)$ be an $n \times n$ unitary matrix satisfying $\mathcal{U}^n = \mathds{1}$, and let $\ket{\psi}$ be the seed state.
+Nonetheless, in Appendix \ref{appendixComputationGroupGeneratedGramMatrices} we present a general procedure to compute the Gram Matrix for any group generated ensemble.
+
+\subsubsection*{The $\mathbb{Z}/n\mathbb{Z}$ group generated ensemble}
+
+\hspace{20pt}Here we discuss the particular case for a $\mathbb{Z}/n\mathbb{Z}$ group generated ensemble a key type of ensemble for our project.\footnote{The relevance of this type of ensembles relies on the fact that for a prime number of states, the possible group generated group ensemble } Let $\mathcal{U} \in U(n)$ be an $n \times n$ unitary matrix satisfying $\mathcal{U}^n = \mathds{1}$, and let $\ket{\psi}$ be the seed state.
 The Gram matrix $\mathcal{G}^{\mathbb{Z}/n\mathbb{Z}}$ elements associated with the ensemble $\left\{\mathcal{U}^i\ket{\psi}\right\}_{i=0}^{n-1}$ are,
@@
 
-This shows the circulant structure of $\mathcal{G}$ for a equal prior probability case, where each row is a cyclic permutation of the previous one.
-In other words, the Gram matrices of $\mathbb{Z}/n\mathbb{Z}$-generated ensembles are circulant matrices when taking equal priors probabilities.
+For instance, the $\mathbb{Z}/4\mathbb{Z}$ group generated gram matrix with equal prior probabilities is,
+
+\begin{align*}
+\mathcal{G}^{\mathbb{Z}/n\mathbb{Z}} = \frac{1}{4}\begin{pmatrix}1 & c_1 & c_2 & c_1^* \\c_1^* & 1 & c_1 & c_2  \\c_2 & c_1^* & 1 & c_1\\c_1 & c_2 & c_1^* & 1  \\\end{pmatrix},
+\end{align*}
+
+where we have denoted $\braket{\mathcal{U}^i}_{\psi}$ as $c_i$.
+This shows the circulant structure of $\mathcal{G}$ for an equal prior probability case, where each row is a cyclic permutation of the previous one.
+In other words, the Gram matrices of $\mathbb{Z}/n\mathbb{Z}$ goup generated ensembles are circulant matrices when taking equal priors probabilities.
 This structure is particularly useful, as circulant matrices can be diagonalized by the discrete Fourier basis, greatly simplifying many computations~\cite{circulantMatrices}.
@@
 \end{align*}
+
+\newpage
 \subsection{Previous Results}\label{sectionPreviousResults}
 
-\hspace{20pt}Significant progress has been made in the study of the state exclusion task for group-generated ensembles.
-In particular, the work \emph{Quantum State Exclusion for Group-Generated Ensembles of Pure States}\cite{MainPaper} presents exact analytical expressions for the success and error probabilities under both the Minimum Error (\gls{me}) and Zero Error (\gls{ze}) exclusion protocols.
+\hspace{20pt}Significant progress has been made in the study of the state exclusion task for group generated ensembles.
+In particular, the work \emph{Quantum State Exclusion for group generated Ensembles of Pure States}\cite{MainPaper} presents exact analytical expressions for the success and error probabilities under both the Minimum Error (\gls{me}) and Zero Error (\gls{ze}) exclusion protocols.
 In this section we present this results and comment some key aspects of this results regarding our project, in particular we present the concept of \emph{perfect exclusion region} and we discuss the case of ensembles with a prime number of states.
 
-Let $\mathcal{G}^G$ denote the Gram matrix of a group-generated ensemble $\left\{ \left( \rho_i, \frac{1}{|G|} \right) \right\}_{i=1}^{|G|}$, where $G$ is a finite group of size $|G|$, and let $\{\lambda_i\}_{i=1}^{|G|}$ be the set of eigenvalues of $\mathcal{G}^G$, the Gram Matrix of the group.
+Let $\mathcal{G}^G$ denote the Gram matrix of a group generated ensemble $\left\{ \left( \rho_i, \frac{1}{|G|} \right) \right\}_{i=1}^{|G|}$, where $G$ is a finite group of size $|G|$, and let $\{\lambda_i\}_{i=1}^{|G|}$ be the set of eigenvalues of $\mathcal{G}^G$, the Gram Matrix of the group.
 Assume the eigenvalues $\left\{\frac{\lambda_i}{|G|}|1\leq i \leq n\right\}$ are ordered increasingly,
@@
 \begin{align*}
-	P_{\gls{me}}^e &= \max\left\{ 0, \left( \frac{ \sqrt{\lambda_{|G|}} - \sum_{i<|G|} \sqrt{\lambda_i} }{|G|} \right)^2 \right\}, \\
 	P_{\gls{me}}^s &= \min\left\{ 1, 1 - \left( \frac{ \sqrt{\lambda_{|G|}} - \sum_{i<|G|} \sqrt{\lambda_i} }{|G|} \right)^2 \right\}.
@@
 
-For the Zero Error protocol, the corresponding expressions arem
-\begin{align*}
-	P_{\gls{ze}}^e &= \max\left\{ 0, \frac{ \sum_{i=1}^{|G|} \sqrt{\lambda_i} \left( \sqrt{\lambda_{|G|}} - \sum_{j<|G|} \sqrt{\lambda_j} \right) }{|G|} \right\}, \\
+For the Zero Error protocol, the corresponding expressions are,
+\begin{align*}
 	P_{\gls{ze}}^s &= \min\left\{ 1, 1 - \frac{ \sum_{i=1}^{|G|} \sqrt{\lambda_i} \left( \sqrt{\lambda_{|G|}} - \sum_{j<|G|} \sqrt{\lambda_j} \right) }{|G|} \right\}.
@@
 A key feature of these results is their independence from the specific group generating the ensemble.
-That is, for any two group-generated ensembles $A$ and $B$ corresponding to groups $G_A$ and $G_B$, with $G_A \neq G_B$ but $|G_A| = |G_B|$, if their respective Gram matrices $\mathcal{G}^{G_A}$ and $\mathcal{G}^{G_B}$ share the same eigenvalues, then the exclusion probabilities for both \gls{me} and \gls{ze} protocols are identical.
+That is, for any two group generated ensembles $A$ and $B$ corresponding to groups $G_A$ and $G_B$, with $G_A \neq G_B$ but $|G_A| = |G_B|$, if their respective Gram matrices $\mathcal{G}^{G_A}$ and $\mathcal{G}^{G_B}$ share the same eigenvalues, then the exclusion probabilities for both \gls{me} and \gls{ze} protocols are identical.
 This group-independence property is a cornerstone of the present study.
@@
 
-In this project, we will extend this result by demonstrating that the perfect exclusion condition Eq.
-(\ref{equationPerfectExclusionCondition}) provides a lower bound for the success probability of exclusion even for non-group-generated ensembles.
-Since this bound equals 1, it implies that any ensemble whether or not group-generated that satisfies condition Eq.
+In this project, we will extend this result by showcasing that the perfect exclusion condition Eq.
+(\ref{equationPerfectExclusionCondition}) provides a lower bound for the success probability of exclusion even for non-group generated ensembles.
+Since this bound equals 1, it implies that any ensemble whether or not group generated that satisfies condition Eq.
 (\ref{equationPerfectExclusionCondition}) can achieve perfect exclusion.
-Thus, the perfect exclusion zone is not exclusive to group-generated ensembles, but also includes all ensembles that fulfill the given condition.
+Thus, the perfect exclusion zone is not exclusive to group generated ensembles, but also includes all ensembles that fulfil the given condition.
 
@@
 
-In the non-perfect exclusion regime, the analytical results for group-generated ensembles provide lower bounds on the success probabilities, and upper bounds on the error probabilities for general ensembles.
+In the non-perfect exclusion regime, the analytical results for group generated ensembles provide lower bounds on the success probabilities, and upper bounds on the error probabilities for general ensembles.
 
@@
 
-Since $U(n)$ is compact, and assuming continuity of the exclusion probabilities with respect to $U$ under a given matrix norm, for each of these unitary matrices there exist arbitrarily small neighborhoods $\mathcal{B}(U_{\mathbb{Z}/4\mathbb{Z}})$ and $\mathcal{B}(U_{\mathbb{Z}/2\mathbb{Z} \times \mathbb{Z}/2\mathbb{Z}})$ such that the exclusion probabilities within these neighborhoods approximate the analytical result as closely as desired.
-However, the existence of multiple such matrices, and intersecting neighborhoods, can complicate numerical optimization and analysis.
-
-In contrast, it is usefull to consider the case where the ensemble contains a prime number $p$ of states.
+Since $U(n)$ is compact, and assuming continuity of the exclusion probabilities with respect to $U$ under a given matrix norm, for each of these unitary matrices there exist arbitrarily small neighbourhoods $\mathcal{B}(U_{\mathbb{Z}/4\mathbb{Z}})$ and $\mathcal{B}(U_{\mathbb{Z}/2\mathbb{Z} \times \mathbb{Z}/2\mathbb{Z}})$ such that the exclusion probabilities within these neighborhoods approximate the analytical result as closely as desired.
+However, the existence of multiple such matrices, and intersecting neighbourhoods, can complicate numerical optimization and analysis.
+
+In contrast, it is useful to consider the case where the ensemble contains a prime number $p$ of states.
 In this scenario, the situation simplifies considerably, since there exists only one group, up to isomorphism, of order $p$, namely $\mathbb{Z}/p\mathbb{Z}$.
 
-This result follows immediately from Lagrange's theorem.
+This result follows immediately from Lagrange's theorem\cite{LagrangeTheoreme}.
 The theorem guarantees the order of any element in a finite group\footnote{The order of an element $\tau$ in a group $G$ is the smallest positive integer $m$ such that $\tau^m = e$, where $e$ denotes the identity/neutral element of the group.} must divide the order of the group.
@@
 \hspace{20pt}In this section, we introduce the concept of a measure on a topological space and define the Haar measure.
-This is one of the key theoretical tools underlying this project, as we use the Haar measure to ensure a uniform and unbiased sampling of ensembles when generating Gram matrices for general ensembles.
+This is one of the key theoretical tools underlying this project, as we use the Haar measure to ensure a uniform sampling of ensembles when generating Gram matrices for general ensembles.
 
 Let \( \Omega \) be a set, and let \( \Sigma \) be a \( \sigma \)-algebra over \( \Omega \).
-A measure \( \mu \) on the measurable space \( (\Omega, \Sigma) \) is a set function \( \mu : \Sigma \to \mathbb{R}_{\geq 0} \) that satisfies the following properties:
+A measure \( \mu \) on the measurable space \( (\Omega, \Sigma) \) is a set function \( \mu : \Sigma \to \mathbb{R}\) that satisfies the following properties:
 \begin{itemize}
@@
 	\begin{align*}
-		\mu\left(\bigcup_{i=1}^\infty \chi_i\right)=\sum_{i=1}^\infty \mu(\chi_i).
+		\mu\left(\bigsqcup_{i=1}^\infty \chi_i\right)=\sum_{i=1}^\infty \mu(\chi_i).
 	\end{align*}
@@
 Now, let \( \Omega \) be a topological group.
-A Haaar measure \( \mu \) on a set \( \Omega \) is a measure defined on the Borel \( \sigma \)-algebra \( \Upsilon \) of \( \Omega \)\footnote{A full definition of Borel sets is beyond the scope of this work, it is enough to say they are sets generated from the open sets of \( \Omega \) through countable unions, intersections, and complements.}, satisfying the following properties:
+A Haaar measure $\mu $ on a set $\Omega$ is a measure defined on the Borel $\sigma$-algebra $\Upsilon$ of $\Omega$\footnote{A full definition of Borel sets is beyond the scope of this work, it is enough to say they are sets generated from the open sets of \( \Omega \) through countable unions, intersections, and complements.}, satisfying the following properties:
 \begin{itemize}
@@
 
-which is compact in the usual topology, from the secon property we know the Haar measure \( \mu \) on \( U(n) \) to be finite.
-Therefore, we can normalize it so that \( \mu(U(n)) = 1 \), fully determining the measure.
-Moreover, since from the first property we know \( \mu \) is invariant under group multiplication, it is uniformly distributed over \( U(n) \).
-This allows us to generate unitary matrices that are randomly and uniformly distributed with respect to the Haar measure.
+which is compact in the usual topology, from the secon property we know the Haar measure $\mu$ on $U(n)$ to be finite.
+Therefore, we can normalize it so that $\mu(U(n)) = 1$, fully determining the measure.
+Moreover, since from the first property we know $\mu $ is invariant under group multiplication, it is uniformly distributed over $U(n)$.
+Hence, this invariance allows us to generate unitary matrices that are randomly and uniformly distributed over $U(n)$.
+This property is one of the cornerstones of our project, as it allows us to convert the uniform distribution of random unitary matrices into a uniform distribution over general ensembles of quantum states.\footnote{We present this conversion in the Methodology section (Section~\ref{sectionMethodology}).}
 
@@
 
-To analyze both group-generated and generic quantum state ensembles, we developed a method for generating random Gram matrices with prescribed spectral properties.
+To analyze both group generated and generic quantum state ensembles, we developed a method for generating random Gram matrices with prescribed spectral properties.
 
@@
 
-At this point, we choose whether the ensemble is to be group-generated or generic.
+At this point, we choose whether the ensemble is to be group generated or generic.
 
@@
 
-In the case of a group-generated ensemble, we restrict ourselves to ensembles generated by the cyclic group $\mathbb{Z}/n\mathbb{Z}$.
-The corresponding unitary matrix $U$ is constructed such that its columns are the vectors of the discrete Fourier basis, as discussed in Section~\ref{sectionGroupGeneratedEnsemble} (\emph{Group-Generated Ensemble}).
+In the case of a group generated ensemble, we restrict ourselves to ensembles generated by the cyclic group $\mathbb{Z}/n\mathbb{Z}$.
+The corresponding unitary matrix $U$ is constructed such that its columns are the vectors of the discrete Fourier basis, as discussed in Section~\ref{sectionGroupGeneratedEnsemble} (\emph{group generated Ensemble}).
 
 Other groups are omitted in our analysis since we can always choose $n$ to be a prime number, in which case the only group of order $n$ (up to isomorphism) is the cyclic group $\mathbb{Z}/n\mathbb{Z}$.
-This significantly simplifies the group structure and ensures that the only group-generated ensemble under consideration corresponds to a well-defined, unique construction.
-
-This methodology provides a flexible yet rigorous foundation for both exploring generic quantum ensembles and benchmarking them against analytically tractable group-generated cases.
+This significantly simplifies the group structure and ensures that the only group generated ensemble under consideration corresponds to a well-defined, unique construction.
+
+This methodology provides a flexible yet rigorous foundation for both exploring generic quantum ensembles and benchmarking them against analytically tractable group generated cases.
 
@@
 
-\hspace{20pt}The begining of the analysis consists in showing up the key differences between \gls{me} and \gls{ze} protocols, and the concordance of the \gls{sdp}'s numerical results with the analytical results given in \ref{sectionPreviousResults}.
+\hspace{20pt}The beginning of the analysis consists in showing up the key differences between \gls{me} and \gls{ze} protocols, and the concordance of the \gls{sdp}'s numerical results with the analytical results given in \ref{sectionPreviousResults}.
 
 The case of ensembles conformed by 3 states is one of the main objects of study, that is because it is the only ensemble that we can entirely represent 2 dimensional plots with.
-In orther to show up this fact, let us analyze the case of a $\mathbb{Z}/3\mathbb{Z}$ ensemble for equal priors probabilities.
+In other to show up this fact, let us analyze the case of a $\mathbb{Z}/3\mathbb{Z}$ ensemble for equal priors probabilities.
 The Gram matrix in this case takes the form,
@@
 
-Since 3 is a prime number, the only group of order 3 is $\mathbb{Z}/3\mathbb{Z}$, as discussed in Section (\ref{sectionLimitCaseScenarios}). The Gram matrix can be diagonalized as,
+Since 3 is a prime number, the only group of order 3 is $\mathbb{Z}/3\mathbb{Z}$, as discussed in Appendix (\ref{sectionLimitCaseScenarios})\footnote{In dis appendix we discuss the limit case scenarios for general ensembles.}.
+The Gram matrix can be diagonalized as,
 \begin{align*}
@@
 \end{align*}
-implying the eigenvalues must lie in the interval $[0,3]$.\footnote{In general, eigenvalues lie in $[0,n]$ for an $n$-dimensional ensemble, even for non-group-generated ensembles.} Therefore,
+implying the eigenvalues must lie in the interval $[0,3]$.\footnote{In general, eigenvalues lie in $[0,n]$ for an $n$-dimensional ensemble, even for non-group generated ensembles.} Therefore,
 \begin{align*}
@@
 
-In Figure (\ref{FigureQSEMEZ3ZHeatmap})  we presents the \gls{me} (left) and \gls{ze} (right) protocols results for the \gls{qse} task.
-In particular Figure (\ref{FigureQSEMEZ3ZHeatmap}) shows two heatmaps of the average successful exclusion probability under the Minimum Error (\gls{me}) protocol for a $\mathbb{Z}/3\mathbb{Z}$ group-generated ensemble.
+In Figure (\ref{FigureQSEMEZ3ZHeatmap})  we present the \gls{me} (left) and \gls{ze} (right) protocols results for the \gls{qse} task.
+In particular Figure (\ref{FigureQSEMEZ3ZHeatmap}) shows two heatmaps of the average successful exclusion probability under the Minimum Error (\gls{me}) protocol for a $\mathbb{Z}/3\mathbb{Z}$ group generated ensemble.
 Probabilities are shown as functions of the modulus $|c|$ ($x$-axis) and phase $\theta$ ($y$-axis) of the overlap $c=|c|^{i\theta}$, which fully determines the Gram matrix.
@@
 When the modulus of the overlap between any two states in the ensemble is given by $|\braket{\psi_i|\psi_j}|^2 = |c|,$ and $|c| \to 1$, the states become nearly indistinguishable.
-In this limiting case, the ensemble effectively consists of identical states.\footnote{One might argue this ensemble corresponds to a group-generated ensemble from the trivial group.}
+In this limiting case, the ensemble effectively consists of identical states.\footnote{One might argue this ensemble corresponds to a group generated ensemble from the trivial group.}
 
@@
 In this case, when $n = 3$, this probability is $\frac{2}{3}$.
-Therefore, in this limit, this is the best achievable performance, and the success probability for the Minimum Error (\gls{me}) exclusion protocol is $\frac{2}{3}$.
+Therefore, in this limit, this is the best achievable performance, and the success probability for the \gls{me} exclusion protocol is $\frac{2}{3}$.
 
 On the other hand, since the states are indistinguishable, we can never be certain that the excluded state is not the unknown target state.
-Thus, the probability of successful exclusion in the Zero Error (\gls{ze}) protocol is $0$, i.e.
+Thus, the probability of successful exclusion in the \gls{ze} protocol is $0$, i.e.
 we cannot perform unambiguous exclusion.
@@
 
-Still, the \gls{ze} success probabilities always remain under those of the \gls{me} protocol.
-This is explained by the stricter constraints imposed in the \gls{ze} scenario, where $\tr(\Pi_i\rho_i) = 0$ is enforced for all \gls{povm} elements except one.
+Still, the \gls{ze} success probabilities are always lower than those of the \gls{me} protocol.
+This is explained by the stricter constraints imposed in the \gls{ze} scenario.
 Notice both probabilities are computed in a completely symmetric way,
 \begin{align*}
-	P^s_{\gls{me}}\sim P^s_{\gls{ze}}\sim 1-\sum_{\gls{povm}}\tr{(\Pi_i\rho_i)}.
-\end{align*}
-
-Nevertheless, in the \gls{ze} case we enforce $\tr{(\Pi_i\rho_i)}=0$ for all the \glspl{povm} except one\footnote{Naturally the \gls{povm} that is not enforced to be orthogonal is the one that yields to an inconclusive result, i.e.
+	P^s_{\gls{me}}\sim P^s_{\gls{ze}}\sim 1-\sum_{i=1}^n\tr{(\Pi_i\rho_i)}.
+\end{align*}
+
+Nevertheless, in the \gls{ze} case we enforce $\tr{(\Pi_i\rho_i)}=0$ for all the \gls{povm}'s elements except one\footnote{Naturally the \gls{povm} element that is not enforced to be orthogonal is the one that yields to an inconclusive result, i.e.
 $\Pi_?$.}.
@@
 	\centering
-	\begin{overpic}[width=0.49\textwidth, trim={2.3cm 0.8cm 2.5cm 2cm}, clip]{../Plots/ExlusionOverlapVSPhaseVSPerfectExclussionZoneZ3BinaryHeatMap.pdf}
+	\begin{overpic}[width=0.49\textwidth, trim={1.8cm 0.8cm 2.5cm 2cm}, clip]{../Plots/ExlusionOverlapVSPhaseVSPerfectExclussionZoneZ3BinaryHeatMap.pdf}
 		\put(70,27){$\mathcal{G}^{\mathbb{Z}/3\mathbb{Z}}<0$}
@@
 	\end{overpic}
-		\includegraphics[width=0.49\textwidth]{../Plots/ExclusionOverlapVSSucessProbabilitySDPvsSRMZnOverlap3Phase0.pdf}
+		\includegraphics[width=0.49\textwidth, trim={0.5cm 0.2cm 1.5cm 1.3cm}, clip]{../Plots/ExclusionOverlapVSSucessProbabilitySDPvsSRMZnOverlap3Phase0.pdf}
 	\caption{Plot of the successful exclusion probabilities for the \gls{sdp} results for the \gls{me}, \gls{ze} protocols in a $\mathbb{Z}/3\mathbb{Z}$ ensemble impossing phase=$0$ as well as the results given by the analytical expressions (left).
@@
 
-Crucially, we observe perfect exclusion is possible even when perfect discrimination is not \footnote{See section Comparison \gls{qsd} VS.
-\gls{qse} (\ref{appendixComparisonQSDvsQSE})}, in this regime seems to correspond to the ensembles such that the modulus of the overlap between two ensembles do not overtakes $\frac{1}{2}$.
+Crucially, we observe perfect exclusion is possible even when perfect discrimination is not \footnote{See Appendix (\ref{appendixComparisonQSDvsQSE}) Comparison \gls{qsd} VS.
+\gls{qse} }, in this regime seems to correspond to the ensembles such that the modulus of the overlap between two ensembles do not overtakes $\frac{1}{2}$.
 Nevertheless, this description is purely observational, we will give a better description in Section (\ref{sectionPerfectExclusionRegimeAndGeneralEnsembles}).
@@
 
-In Figure (\ref{FigureQSEMEZ3ZPerfectExclusion}) (right) we present de dependency on the modulus of the overlap in the $\mathbb{Z}/3\mathbb{Z}$ group-generated ensemble impossing the phase being equal to 0.
+In Figure (\ref{FigureQSEMEZ3ZPerfectExclusion}) (right) we present de dependency on the modulus of the overlap in the $\mathbb{Z}/3\mathbb{Z}$ group generated ensemble impossing the phase being equal to 0.
 The result is analogous to Figure (\ref{FigureQSDMEZESRM}) but in the exclusion task.
@@
 \hspace{20pt}In this section, we present the results for ensembles generated by the group $\mathbb{Z}/3\mathbb{Z}$, analyzed across the spectrum of eigenvalues, i.e.
-the analogus results from the previos section in the eigenvalues spectum.
-We also explicitly show the conditions for perfect exclusion, we give a proper analysis of this regime, and provide an initial exploration of the results for general ensembles being low bounded by the group-generated results of three quantum states.
-
-Although the \emph{Overlap modulus - phase} spectrum might seem as the most intuituve representation, the spectrum of Gram's matrix eigenvalues results the most appropriate representation for the perfect exclusion zone as well as the discussion and its comparison for general ensembles.
-Carrying on with the previos discussion, one can check the two \gls{dof} now appear as two of the eigenvalues.
-In the Figure (\ref{FigureQSEMEZ3ZEigenValues}) the results for the exclusion task under the \gls{me} protocol (left) and \gls{ze} protocol (right) for the $\mathbb{Z}/3\mathbb{Z}$ group-generated ensemble are represented.
+the analogous results from the previous section in the eigenvalues spectrum.
+We also explicitly show the conditions for perfect exclusion, we give a proper analysis of this regime, and provide an initial exploration of the probabilities excluding successfully for general ensembles being bounded from below by the group generated results of three quantum states.
+
+Although the \emph{Overlap modulus - phase} spectrum might seem as the most intuitive representation, the spectrum of Gram's matrix eigenvalues results the most appropriate representation for the perfect exclusion zone as well as the discussion and its comparison for general ensembles.
+Carrying on with the previous discussion, one can check the two \gls{dof} now appear as two of the eigenvalues.
+In the Figure (\ref{FigureQSEMEZ3ZEigenValues}) the results for the exclusion task under the \gls{me} protocol (left) and \gls{ze} protocol (right) for the $\mathbb{Z}/3\mathbb{Z}$ group generated ensemble are represented.
 The axis represent two of the eigenvalues of the Gram matrix and a heatmap presents the probability for a perfect exclusion in the given conditions.
@@
 	\end{overpic}
-	\caption{Plot of the success exclusion probability in the eigenvalues spectrum for the \gls{me} (left) and \gls{ze} (right) protocol for a $\mathbb{Z}/3\mathbb{Z}$ group-generated ensemble.}
+	\caption{Plot of the success exclusion probability in the eigenvalues spectrum for the \gls{me} (left) and \gls{ze} (right) protocol for a $\mathbb{Z}/3\mathbb{Z}$ group generated ensemble.}
 	\label{FigureQSEMEZ3ZEigenValues}
@@
 
-This region $\Omega$ is depicted in the Figure (\ref{FigureQSEMEZ3ZEigenValues}) as boottom left triangle, where our system is recluded.
+This region $\Omega$ is depicted in the Figure (\ref{FigureQSEMEZ3ZEigenValues}) as bottom left triangle, where our system is precluded.
 Inside this region we can find the perfect exclusion zone, i.e.
@@
 
-By plotting the $\Delta$ regio it turns out inmediatly this region corresponds to the colorless perfect exclusion regime in Figure (\ref{FigureQSEMEZ3ZEigenValues}).
+By plotting the $\Delta$ region it turns out immediately this region corresponds to the colourless perfect exclusion regime in Figure (\ref{FigureQSEMEZ3ZEigenValues}).
 
@@
 
-The limit case scenarios corresponding to $\lambda_i=3$ and $\lambda_j,\lambda_k=0$ are located in the vertex of the triangle\footnote{Remember this case correspond to sets with the same state repeated 3 times discussed in Section (\ref{sectionLimitCaseScenarios})}.
+The limit case scenarios corresponding to $\lambda_i=3$ and $\lambda_j,\lambda_k=0$ are located in the vertex of the triangle\footnote{Remember this case correspond to sets with the same state repeated 3 times discussed in Appendix (\ref{sectionLimitCaseScenarios})}.
 Additionally, the cases corresponding to the edges are those with one state repeated 2 times and one different from the other 2.
@@
 
-Additionally, we observe that no ensembles seem to have a lower exclusion success probability $P_{\gls{me}}^s$ under $\frac{2}{3}$ as expected from the discussion in Section (\ref{sectionLimitCaseScenarios}).
+Additionally, we observe that no ensembles yield to lower exclusion success probabilities $P_{\gls{me}}^s$ than $\frac{2}{3}$ as expected from the discussion in Appendix \ref{sectionLimitCaseScenarios}.
 
@@
 %	\end{overpic}
-%	\caption{Plot of the success exclusion probability in the eigenvalues spectrum for the \gls{ze} protocol for a $\mathbb{Z}/3\mathbb{Z}$ group-generated ensemble.}
+%	\caption{Plot of the success exclusion probability in the eigenvalues spectrum for the \gls{ze} protocol for a $\mathbb{Z}/3\mathbb{Z}$ group generated ensemble.}
 %	\label{FigureQSEZEZ3ZEigenValues}
@@
 	\end{overpic}
-	\caption{Heat map plot of the success exclusion probability in the eigenvalues spectrum for the \gls{me} protocol for a generic ensemble (left) and 3D Plot of the success exclusion probability in the eigenvalues spectrum for the \gls{me} protocol for a group-generated and generic ensembles (right)}
+	\caption{Heat map plot of the success exclusion probability in the eigenvalues spectrum for the \gls{me} protocol for generic ensembles (left) and 3D Plot of the success exclusion probability in the eigenvalues spectrum for the \gls{me} protocol for a group generated and generic ensembles (right)}
 	\label{FigureQSEMEGenericEigenValues}
@@
 
-A remarcable feature is that each ensemble has been checked to not have a successful exclusion probability that overtakes the value from the $\mathbb{Z}/3\mathbb{Z}$ group-generated ensemble pointing this value to be a lower bound for the general case scenario.
+A remarcable feature is that each ensemble has been checked to not have a successful exclusion probability that overtakes the value from the $\mathbb{Z}/3\mathbb{Z}$ group generated ensemble pointing this value to be a lower bound for the general case scenario.
 
@@
 %	\centering
-%	\caption{3D Plot of the success exclusion probability in the eigenvalues spectrum for the \gls{me} protocol for a group-generated and generic ensembles.}
+%	\caption{3D Plot of the success exclusion probability in the eigenvalues spectrum for the \gls{me} protocol for a group generated and generic ensembles.}
 %	\label{FigureQSEMEGenericEigenValues3D}
@@
 
-In Figure (\ref{FigureQSEMEGenericEigenValues}) we present a 3D plot for the comparison of the success probability for exclusion for ensembles of 3 states between generic and group-generated ensembles.
+In Figure (\ref{FigureQSEMEGenericEigenValues}) we present a 3D plot for the comparison of the success probability for exclusion for ensembles of 3 states between generic and group generated ensembles.
 The $x$ and $y$ axis representing de eigenvalues of the Gram matrix are analogous to previous figures.
 Nevertheless the $z$ axis shows the success probability for exclusion instead of the previous heat maps.
-Here we can observe how the randomly generated states raise the probabilities over the group-generated values.
-The generation of unitary matrices that fill $U(n)$ according Haar measure ensures the Gram matrices we are generating comprehend the entire set of possible Gram matrices homogeneously.
-Furthermore, we observe how the group-generated results lay under the results for general ensembles \gls{sdp}s, i.e.
-this results are bounded by the group-generated results.
+Here we can observe how the randomly generated states raise the probabilities over the group generated values.
+As we have mentioned in the \emph{Methodology section} (i.e.
+Section \ref{sectionMethodology}), the generation of unitary matrices that fill $U(n)$ according Haar measure ensures the Gram matrices we are generating comprehend the entire set of possible Gram matrices homogeneously.
+Furthermore, we observe how the group generated results lay under the results for general ensembles \gls{sdp}s, i.e.
+these results are bounded from below by the group generated results.
 
@@
 \hspace{20pt}In this section, we present the main results of the project.
-Specifically, we provide analytical results for generic ensembles and examine how the success probabilities for quantum state exclusion are distributed in relation to the lower bound defined by group-generated ensembles.
+Specifically, we provide analytical results for generic ensembles and examine how the success probabilities for quantum state exclusion are distributed in relation to the lower bound defined by group generated ensembles.
 
@@
 These ensembles were generated uniformly by sampling unitary matrices $ U $ from $U(n)$, which determine the Gram matrices via the decomposition $\mathcal{G} = U D U^\dagger$.
-Ensembles with Gram matrices structurally similar to those of group-generated ensembles, particularly those diagonalized in the Fourier basis\footnote{Recall that we are working with ensembles of a prime number of states, for which the only known analytical result corresponds to the Gram matrix generated by $\mathbb{Z}/n\mathbb{Z}$, which is diagonalized in the Fourier basis.
-A more complete study would consider other group-generated cases.}, yield lower success probabilities.
+Ensembles with Gram matrices structurally similar to those of group generated ensembles, particularly those diagonalized in the Fourier basis\footnote{Recall that we are working with ensembles of a prime number of states, for which the only known analytical result corresponds to the Gram matrix generated by $\mathbb{Z}/n\mathbb{Z}$, which is diagonalized in the Fourier basis.
+A more complete study would consider other group generated cases.}, yield lower success probabilities.
 
 Interestingly, there exists a threshold of deviation from the Fourier basis beyond which all ensembles yield a success probability of 1.
-In other words, beyond a certain \emph{distance} from the group-generated case, i.e.
+In other words, beyond a certain \emph{distance} from the group generated case, i.e.
 the Fourier basis, the ensembles become sufficiently distinguishable to allow perfect exclusion, regardless of the specific basis in which their Gram matrices are diagonalised.
@@
 
-As before, no ensembles yields lower success exclusion probabilities than the lower bound, proving this as a lower bound of the generic case scenario.
+As before, no ensemble yields a success exclusion probability below the theoretical lower bound.
 
@@
 	\centering
-	\includegraphics[width=0.49\textwidth, trim={1.0cm 0.3cm 2.4cm 1.5cm}, clip]{../Plots/ExclusionMinimumErrorRandomDistributionZ7Prob0.924.pdf}
-	\includegraphics[width=0.49\textwidth, trim={1.0cm 0.3cm 2.4cm 1.5cm}, clip]{../Plots/ExclusionMinimumErrorRandomDistributionZ11Prob0.926.pdf}
+	\includegraphics[width=0.49\textwidth, trim={1.5cm 0.3cm 2.4cm 1.5cm}, clip]{../Plots/ExclusionMinimumErrorRandomDistributionZ7Prob0.924.pdf}
+	\includegraphics[width=0.49\textwidth, trim={1.5cm 0.3cm 2.4cm 1.5cm}, clip]{../Plots/ExclusionMinimumErrorRandomDistributionZ11Prob0.926.pdf}
 	\caption{Hisotgram depicting the distribution of generated Gram Matrices via the success probability for \gls{me} protocol with a lower bound of 0.926 for 7 states (left) and 11 states (right) ensembles of random priors probabilities.}
@@
 \end{figure}
-In Figure~\ref{FigureDistZ7Z11}, we present the corresponding results for the \gls{me} protocol applied to ensembles composed of 7 (left) and 11 (right) quantum states, with a lower bound on the success exclusion probability of 0.926.
-As the number of states increases, the distribution approaches a Landau shape \cite{landau}.
-For ensembles of 7 elements, we still observe the phenomenon of accumulation near the perfect exclusion region.
-However, in the case of 11 states, only a small fraction of ensembles reach the perfect exclusion regime since the peak of the distribution is more narrow and the ensembles tend to agglomerate exclusion probabilities arround this peak.
+
+In Figure~\ref{FigureDistZ7Z11}, we present the results for the ME protocol applied to ensembles of 7 (left) and 11 (right) quantum states, with a fixed analytical lower bound on the success exclusion probability of 0.926.
+As the number of states increases, the resulting distributions tend to exhibit a Landau-like shape \cite{landau}.
+For the 7-state ensembles, we continue to observe a significant accumulation near the perfect exclusion region.
+However, in the case of 11 states, only a small fraction of ensembles achieve perfect exclusion.
+Furthermore, the main peak of the Landau-like distribution is narrower, and ensembles tend to cluster around this peak rather than at the upper limit.
+
+This behavior can be understood in terms of the relative freedom of success exclusion probabilities.
+As discussed in Appendix~\ref{sectionLimitCaseScenarios}, any exclusion probability for a generic ensemble of $n$ states must exceed $\frac{n-1}{n}$, the result expected from a random exclusion strategy.
+Therefore, the exclusion probabilities for 7 and 11 quantum states must lie within the following intervals,
+\begin{align*}
+\left[\frac{6}{7},1\right]\sim\left[0.858,1\right]\quad \left[\frac{10}{11},1\right]\sim\left[0.909,1\right],
+\end{align*}
+
+Although both cases are analyzed with the same lower bound of 0.926, they are not relatively equivalent.
+For the 7 state case, this lower bound lies approximately at the midpoint of the possible interval, thereby pushing the generation of random ensembles closer to the perfect exclusion.
+This results in the observable peak of ensembles of success exclusion probability of 1.
+\footnote{Notice that when we refer to \emph{perfect exclusion} there is no direct connection to the \emph{perfect exclussion regime} provided in Eq.
+(\ref{equationPerfectExclusionCondition}).
+In this regime of eigenvalues all the Gram Matrices give rise to ensembles where perfect exclusion can be performed.
+Now we are outside this regime, i.e.
+the lower analytical bound is different from 1, but still we can find ensembles where perfect exclusion can be acomplished.} In contrast, for the 11 state case, the analytical lower bound is very close to the minimum of the allowed region, meaning ensembles are relatively farther from perfect exclusion, hence, the peak located at 1 does not appear.
+
+We can interpret this phenomenon as the lower bound compressing the region in which exclusion probabilities can appear.
+For 7 states, the interval is more compressed, forcing a greater amount of ensembles to exhibit high exclusion probabilities, and thus more frequently reach the perfect exclusion, forming a peak.
+
+This compression effect also helps to explain the location of the peak in the Landau-shaped distribution.
+In the 11 state case, the lower bound is closer to the exclusion probability expected from a random strategy.
+As a result, the eigenvalues\footnote{Note that all ensembles in Figure~\ref{FigureDistZ7Z11} share the same eigenvalues to ensure consistency with the analytical lower bound.} of the corresponding Gram matrices resemble those of an ensemble composed entirely of identical states.\footnote{This corresponds to the limit case scenario described in Appendix~\ref{sectionLimitCaseScenarios}, where the Gram matrix has one non-zero eigenvalue and all others equal to zero.} Therefore, most Gram matrices correspond to ensembles with very similar states yielding to exclusion probabilities close to the analytical lower bound since this is almost the same as the exact result of ensembles conformed by the same state.
+In contrast, the eigenvalues for the 7 state case are significantly different from this limit case, leading to more diverse exclusion probabilities and a higher chance of achieving perfect exclusion.
+
+In Figure (\ref{FigureDistZ7Z11ZE}), we present the corresponding results for ensembles composed of 7 (left) and 11 (right) quantum states under the \gls{ze} protocol.
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.49\textwidth, trim={1.5cm 0.3cm 2.4cm 1.5cm}, clip]{../Plots/ExclusionZeroErrorRandomDistributionZ7Prob0.553.pdf}
+	\includegraphics[width=0.49\textwidth, trim={1.5cm 0.3cm 2.4cm 1.5cm}, clip]{../Plots/ExclusionZeroErrorRandomDistributionZ11Prob0.5.pdf}
+	\caption{Hisotgram depicting the distribution of generated Gram Matrices via the success probability for \gls{ze} protocol with a lower bound of 0.553 for 7 states (left) and 11 states (right) ensembles of random priors probabilities.}
+	\label{FigureDistZ7Z11ZE}
+\end{figure}
+
+As depicted in Figure (\ref{FigureDistZ7Z11ZE}), the compression effect, previously observed in the \gls{me} protocol, is even more pronounced in the \gls{ze} setting.
+Here, the majority of ensembles yield a success exclusion probability of 1, leading to a broad peak at the upper end of the distribution.
+Notably, this effect appears equally strong in both the 7 and 11 state cases.
+
+As shown in Appendix~\ref{sectionLimitCaseScenarios}, the lower bound on the success exclusion probability for the \gls{ze} protocol, when using a random exclusion strategy, is always 0, regardless of the number of states in the ensemble.
+That is, in the limit case of an ensemble composed entirely of identical states, perfect exclusion becomes impossible, and the probability drops to zero.
+Consequently, success probabilities under the \gls{ze} protocol must lie within the full interval $[0,1]$ for any ensemble size, i.e.
+the usual interval.
+
+Therefore, unlike in the \gls{me} protocol, the compression effect induced by the analytical lower bound in the \gls{ze} scenario applies equally across all ensemble sizes since this are equally compressed.
+This explains why the distributions in both the 7 and 11 state cases are similarly skewed toward ensembles where perfect exclusion can be accomplished.
+
+One might perceive an apparent inconsistency with the previous discussion, where we claimed that success probabilities under the \gls{ze} protocol to be higher than those obtained with the \gls{me} protocol.
+This discrepancy arises because the eigenvalues of the Gram matrices used in the \gls{ze} analysis differ from those in Figure (\ref{FigureDistZ7Z11}), which pertain to the \gls{me} protocol.
+In the \gls{ze} setting, the eigenvalues have been shifted in such a way that the ensembles are more likely to achieve perfect exclusion.
+As a result, most ensembles cluster around a success exclusion probability of 1 and no inconsistency raises up.
 
@@
 
-\hspace{20pt}The intuition behind the exclusion task for group-generated ensembles being the worst case scenario for this task, thus yielding a lower bound for the probability of excluding a hypothesis state in the general case is as follows.
+\hspace{20pt}The intuition behind the exclusion task for group generated ensembles being the worst case scenario for this task, thus yielding a lower bound for the probability of excluding a hypothesis state in the general case is as follows.
 Consider an ensemble $\{\ket{\psi_i}\}_{i=1}^n$ with a certain degree of symmetry, and a state $\ket{\psi_j}$ known to be a member of this ensemble.
-Our goal is to perform the exclusion task, i.e., to identify a state $\ket{\psi_k} \in \{\ket{\psi_i}\}_{i=1}^n$ such that we \emph{suspect} $\ket{\psi_k} \neq \ket{\psi_j}$\footnote{We emphasize the word \emph{suspect} because in many scenarios we are not certain about $\ket{\psi_k} \neq \ket{\psi_j}$, which corresponds to the \emph{non-perfect exclusion} case.}.
+Our goal is to perform the exclusion task, i.e., to identify a state $\ket{\psi_k} \in \{\ket{\psi_i}\}_{i=1}^n$ such that we \emph{belive} $\ket{\psi_k} \neq \ket{\psi_j}$\footnote{We emphasize the word \emph{belive} because in many scenarios we are not certain about $\ket{\psi_k} \neq \ket{\psi_j}$, which corresponds to the \emph{non-perfect exclusion} case.}.
 
@@
 
-In such a group-generated ensemble, distinguishing any pair of states is equally difficult due to symmetry.
+In such a group generated ensemble, distinguishing any pair of states is equally difficult due to symmetry.
 Therefore, exclusion becomes more challenging, representing a worst-case scenario compared to the asymmetric case.
@@
 
-\hspace{20pt}We have presented a robust protocol for generating ensembles of quantum states, along with their corresponding prior probabilities, in a manner that uniformly samples the full space of possible ensembles.
+\hspace{20pt}We have presented a robust protocol for generating ensembles of quantum states, along with their corresponding prior probabilities, in a manner that uniformly samples the full space of possible ensembles\footnote{The protocol is presented in the \emph{Methodology} section (Section \ref{sectionMethodology}).
+}.
 This approach ensures a comprehensive and unbiased exploration for the study of Quantum State Exclusion (\gls{qse}).
-Using this ensemble generation method, we have computed the corresponding Semidefinite Programming (\gls{sdp}) optimization problems, allowing us to numerically verify and support the analytical results obtained for the success and error probabilities associated with group-generated ensembles.
-
-The analytical results, presented in Section~\ref{sectionPreviousResults} \emph{Previous Results}, for the success probability in Quantum State Exclusion (\gls{qse}) for the Minimum Error (\gls{me}) and Zero Error (\gls{ze}) protocols for equal prior probabilities for group-generated ensambles have provide lower bounds for the success probability in Quantum State Exclusion (\gls{qse}) the same protocols.
-Our numerical simulations confirm that these group-generated ensembles consistently achieve the lowest exclusion success probabilities, thus validating their role as theoretical lower bounds when compared to the broader set of randomly generated ensembles.
+Using this ensemble generation method, we have computed the corresponding Semidefinite Programming (\gls{sdp}) optimization problems, allowing us to numerically verify and support the analytical results obtained for the success and error probabilities associated with group generated ensembles.
+
+The analytical results, presented in Section~\ref{sectionPreviousResults} \emph{Previous Results}, for the success probability in Quantum State Exclusion (\gls{qse}) for the Minimum Error (\gls{me}) and Zero Error (\gls{ze}) protocols for equal prior probabilities for group generated ensambles have provide lower bounds for the success probability in Quantum State Exclusion (\gls{qse}) for the same protocols.
+Our numerical simulations confirm that these group generated ensembles consistently achieve the lowest exclusion success probabilities, thus validating their role as theoretical lower bounds when compared to the broader set of randomly generated ensembles.
 We have also offered conceptual insights into the intuition of why these bounds persist in the general case, including a geometric interpretation based on Gram matrix structure and ensemble distinguishability.
 
-In addition, we have explored in detail the specific case of the cyclic group $\mathbb{Z}/3\mathbb{Z}$, the only group-generated ensemble that can be faithfully represented in two dimensions.
+In addition, we have explored in detail the specific case of the cyclic group $\mathbb{Z}/3\mathbb{Z}$, the only group generated ensemble that can be faithfully represented in two dimensions.
 This visualization not only has provided intuition but also demonstrates the practical advantage of \gls{qse} over its counterpart, Quantum State Discrimination (\gls{qsd}).
@@
 Extending this analysis to more generic ensembles, that may reveal new structural properties and exclusion capabilities.
-Furthermore, from the results and discussions in this project it results obvious that research in hybrid protocols that interpolate between Minimum Error \gls{me} and Zero Error \gls{ze} protocols as well as \gls{qse} and \gls{qsd} could potentially yield more optimal performance in practical applications.
-
-In summary, this work contributes both rigorous numerical evidence and conceptual motivation for viewing group-generated ensembles as the worst case scenario in the study of quantum state exclusion, i.e.
+Furthermore, from the results and discussions in this project it results obvious that research in hybrid protocols that interpolate between Minimum Error (\gls{me}) and Zero Error (\gls{ze}) protocols as well as \gls{qse} and \gls{qsd} could potentially yield more optimal performance in practical applications.
+
+In summary, this work contributes both rigorous numerical evidence and conceptual motivation for viewing group generated ensembles as the worst case scenario in the study of quantum state exclusion, i.e.
 leading up to a lower bound in the exclusion probability.
@@
 \newpage
-\bibliographystyle{plain}
+%\bibliographystyle{unsrtnat}
 \bibliography{references}
+
 %%%%%%%%
@@
 \printnoidxglossary[type=main, title={\vspace{-1cm}}, nonumberlist, nogroupskip, style=super]
-
+\newpage
 \section*{Acknowledgements}
@@
 
-\section{Computation of Gram Matrices for a group-generated ensembles}\label{appendixComputationGroupGeneratedGramMatrices}
-
-\hspace{20pt}We can compute the Gram matrix for any group-generated ensemble by using the Cayley table~\cite{CayleyTable}, also known as the \emph{multiplication table}, of the group.
+\section{Computation of Gram Matrices for a group generated ensembles}\label{appendixComputationGroupGeneratedGramMatrices}
+
+\hspace{20pt}We can compute the Gram matrix for any group generated ensemble by using the Cayley table~\cite{CayleyTable}, also known as the \emph{multiplication table}, of the group.
 For example, consider the smallest non-commutative group, $S_3$, consisting of the symmetries and rotations of an equilateral triangle.
@@
 We now identify $S_3$ as a group of unitary matrices\footnote{We treat each group element as a unitary matrix, and the group operation as matrix multiplication.}.
-It follows that the Gram matrix of the $S_3$ group-generated ensemble is the matrix of expected values of the Cayley table entries with respect to the seed state $\ket{\psi}$.
+It follows that the Gram matrix of the $S_3$ group generated ensemble is the matrix of expected values of the Cayley table entries with respect to the seed state $\ket{\psi}$.
 That is,
@@
 which implies the unitary matrices corresponding to the triangle symmetries $p$, $q$, and $r$ are Hermitian.
-As a matter of fact we know the eigenvalues of this matrices can only be $\pm 1$ and at least one of them must be $-1$.\footnote{Otherwise, they would be the identity and we know them to be different by construction.} This procedure generalizes to any finite group $G$, showing that computing the Cayley table is equivalent to computing the Gram matrix of the corresponding group-generated ensemble.
+As a matter of fact we know the eigenvalues of this matrices can only be $\pm 1$ and at least one of them must be $-1$.\footnote{Otherwise, they would be the identity and we know them to be different by construction.} This procedure generalizes to any finite group $G$, showing that computing the Cayley table is equivalent to computing the Gram matrix of the corresponding group generated ensemble.
 
@@
 \hspace{20pt}Here we present the results for the Quantum State Discrimination (\gls{qsd}) task to motivate the problem and highlight contrasts with the Quantum State Exclusion (\gls{qse}) task, which is the focus of this study.
+
+In Figure (\ref{FigureQSDMEZ3ZHeatmap}) we present the \gls{me} (left) and \gls{ze} (right) protocols results for the \gls{qsd} task.
+Recalling the probabilities are shown as functions of the modulus $|c|$ ($x$-axis) and phase $\theta$ ($y$-axis) of the overlap $c=|c|^{i\theta}$, which fully determines the Gram matrix.
+Notice we take equal prior probabilities, as discussed in the analytical results in Section (\ref{sectionPreviousResults}).
+This result is the analogous of Figure (\ref{FigureQSEMEZ3ZHeatmap}) for \gls{qsd}.
 
@@
 	\end{overpic}
-	\caption{Heatmap of the success probability for minimum error (\gls{me}) quantum state discrimination for a $\mathbb{Z}/3\mathbb{Z}$ group-generated ensemble.}
+	\caption{Heatmap of the success probability for minimum error (\gls{me}) quantum state discrimination for a $\mathbb{Z}/3\mathbb{Z}$ group generated ensemble.}
 	\label{FigureQSDMEZ3ZHeatmap}
@@
 
-As expected, no ensemble yields a success probability below $1/3$, consistent with the discussion in Section (\ref{sectionLimitCaseScenarios}).
+As expected, no ensemble yields a success probability below $1/3$, consistent with the discussion in Appendix (\ref{sectionLimitCaseScenarios}).
 Moreover, as the modulus of the overlap approaches zero, the success probability approaches one, corresponding to orthogonal states, again matching expectations.
@@
 	\end{overpic}
-	\caption{Heatmap of the success probability for zero-error (\gls{ze}) quantum state discrimination for a $\mathbb{Z}/3\mathbb{Z}$ group-generated ensemble.}
+	\caption{Heatmap of the success probability for zero-error (\gls{ze}) quantum state discrimination for a $\mathbb{Z}/3\mathbb{Z}$ group generated ensemble.}
 	\label{FigureQSDZEZ3ZHeatmap}
@@
 
-Again, the ZE protocol yields lower probabilities due to its constraints and the limit case scenarios match with the previos discussion in Section (\ref{sectionLimitCaseScenarios}) and Section (\ref{sectionResultsAndDiscussion}).
+Again, the ZE protocol yields lower probabilities due to its constraints and the limit case scenarios match with the previous discussion in Appendix (\ref{sectionLimitCaseScenarios}) and Section (\ref{sectionResultsAndDiscussion}).
 
@@
 the same state is repeated $n$ times in the ensemble with the same probability.\footnote{This case may appear paradoxical, since there is no way to distinguish between identical states.
-Nevertheless, we present it as a limiting scenario.} The Gram matrix reads:
+Nevertheless, we present it as a limiting scenario.} The Gram matrix reads,
 \begin{align*}
@@
 (\ref{equationPerfectExclusionCondition}), i.e., we are in the non-perfect exclusion regime.
-In fact, we can interpret this ensemble as a group-generated ensemble from the \emph{trivial group},\footnote{The trivial group is the group consisting solely of the neutral/identity element.} which generates no variation.
+In fact, we can interpret this ensemble as a group generated ensemble from the \emph{trivial group},\footnote{The trivial group is the group consisting solely of the neutral/identity element.} which generates no variation.
 
